### 2015-03-08 document/ms.tex
initial paper skeleton

% This paper is part of the single transits project.
% Copyright 2015 Dan Foreman-Mackey (NYU) and the co-authors listed below.
%
%  RULES OF THE GAME
%
%  * 80 characters
%  * line breaks at the ends of sentences
%  * eqnarrys ONLY
%  * ``light curve'' not ``light-curve'' or ``lightcurve''
%  * Do not put in any comments that might get tweeted by @OverheardOnAph
%    (or maybe do put in a few....)
%  * ``percent'' (not \%) is a unit, as is ppm, so 5~percent.
%  * that is all.
%

\documentclass[12pt,preprint]{aastex}

\pdfoutput=1

\usepackage{color,hyperref}
\definecolor{linkcolor}{rgb}{0,0,0.5}
\hypersetup{colorlinks=true,linkcolor=linkcolor,citecolor=linkcolor,
            filecolor=linkcolor,urlcolor=linkcolor}
\usepackage{url}
\usepackage{amssymb,amsmath}
\usepackage{subfigure}
\usepackage{booktabs}

\usepackage{natbib}
\bibliographystyle{apj}

\newcommand{\project}[1]{\textsl{#1}} % hogg say
\newcommand{\kepler}{\project{Kepler}}
\newcommand{\KT}{\project{K2}}
\newcommand{\tess}{\project{TESS}}
\newcommand{\jwst}{\project{JWST}}
\newcommand{\terra}{\project{TERRA}}
\newcommand{\pdc}{\project{PDC}}
\newcommand{\license}{MIT License}
\newcommand{\projectname}{\project{ketu}}

\newcommand{\paper}{\textsl{Article}}

\newcommand{\foreign}[1]{\emph{#1}}
\newcommand{\etal}{\foreign{et\,al.}}
\newcommand{\etc}{\foreign{etc.}}
\newcommand{\True}{\foreign{True}}
\newcommand{\Truth}{\foreign{Truth}}

\newcommand{\figref}[1]{\ref{fig:#1}}
\newcommand{\Fig}[1]{\figurename~\figref{#1}}
\newcommand{\fig}[1]{\Fig{#1}}
\newcommand{\figlabel}[1]{\label{fig:#1}}
\newcommand{\Tab}[1]{Table~\ref{tab:#1}}
\newcommand{\tab}[1]{\Tab{#1}}
\newcommand{\tablabel}[1]{\label{tab:#1}}
\newcommand{\Eq}[1]{Equation~(\ref{eq:#1})}
\newcommand{\eq}[1]{\Eq{#1}}
\newcommand{\eqalt}[1]{Equation~\ref{eq:#1}}
\newcommand{\eqlabel}[1]{\label{eq:#1}}
\newcommand{\sectionname}{Section}
\newcommand{\Sect}[1]{\sectionname~\ref{sect:#1}}
\newcommand{\sect}[1]{\Sect{#1}}
\newcommand{\sectalt}[1]{\ref{sect:#1}}
\newcommand{\App}[1]{Appendix~\ref{sect:#1}}
\newcommand{\app}[1]{\App{#1}}
\newcommand{\sectlabel}[1]{\label{sect:#1}}

\newcommand{\BIC}{{\ensuremath{\mathrm{BIC}}}}
\newcommand{\TIC}{{\ensuremath{\mathrm{TIC}}}}
\newcommand{\T}{\ensuremath{\mathrm{T}}}
\newcommand{\dd}{\ensuremath{\,\mathrm{d}}}
\newcommand{\bvec}[1]{{\ensuremath{\boldsymbol{#1}}}}
\newcommand{\appropto}{\mathrel{\vcenter{
  \offinterlineskip\halign{\hfil$##$\cr
    \propto\cr\noalign{\kern2pt}\sim\cr\noalign{\kern-2pt}}}}}
\newcommand{\densityunit}{{\ensuremath{\mathrm{nat}^{-2}}}}

% TO DOS
\newcommand{\todo}[3]{{\color{#2}\emph{#1}: #3}}
\newcommand{\dfmtodo}[1]{\todo{DFM}{red}{#1}}
\newcommand{\hoggtodo}[1]{\todo{HOGG}{blue}{#1}}

% Notation for this paper.
\newcommand{\flux}{{\ensuremath{f}}}
\newcommand{\ferr}{{\ensuremath{\sigma_\flux}}}
\newcommand{\attime}{{\ensuremath{t}}}
\newcommand{\basis}{{\bvec{A}}}
\newcommand{\weights}{{\bvec{w}}}

\newcommand{\period}{{\ensuremath{P}}}
\newcommand{\phase}{{\ensuremath{T^0}}}
\newcommand{\duration}{{\ensuremath{D}}}
\newcommand{\depth}{{\ensuremath{Z}}}
\newcommand{\transittime}{{\ensuremath{T}}}
\newcommand{\impact}{{\ensuremath{b}}}
\newcommand{\ecc}{{\ensuremath{e}}}
\newcommand{\pomega}{{\ensuremath{\omega}}}

\newcommand{\datareleaseurl}{{\url{http://bbq.dfm.io/ketu}}}

\begin{document}

\title{%
    The search for single transit events in the \kepler\ data
}

\newcommand{\nyu}{2}
\newcommand{\mpia}{3}
\newcommand{\cds}{4}
\newcommand{\mpis}{5}
\author{%
    Daniel~Foreman-Mackey\altaffilmark{1,\nyu},
    David~W.~Hogg\altaffilmark{\nyu,\mpia,\cds},
    Bernhard~Sch\"olkopf\altaffilmark{\mpis},
    \etal
}
\altaffiltext{1}         {To whom correspondence should be addressed:
                          \url{danfm@nyu.edu}}
\altaffiltext{\nyu}      {Center for Cosmology and Particle Physics,
                          Department of Physics, New York University,
                          4 Washington Place, New York, NY, 10003, USA}
\altaffiltext{\mpia}     {Max-Planck-Institut f\"ur Astronomie,
                          K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{\cds}      {Center for Data Science,
                          New York University,
                          726 Broadway, 7th Floor, New York, NY, 10003, USA}
\altaffiltext{\mpis}     {Max Planck Institute for Intelligent Systems
                          Spemannstrasse 38, 72076 T\"ubingen, Germany}

\begin{abstract}

\end{abstract}

\keywords{%
methods: data analysis
---
methods: statistical
---
catalogs
---
planetary systems
---
stars: statistics
}

\section{Introduction}

Hi \citep{kois}.

\acknowledgments
It is a pleasure to thank
\ldots
for helpful contributions to the ideas and code presented here.
DFM and DWH were partially supported by the National Science Foundation
(grant IIS-1124794),
the National Aeronautics and Space Administration
(grant NNX12AI50G), and the Moore--Sloan Data Science Environment at NYU.

This research made use of the NASA \project{Astrophysics Data System} and the
NASA Exoplanet Archive.
The Archive is operated by the California Institute of Technology, under
contract with NASA under the Exoplanet Exploration Program.
This \paper\ includes data collected by the \kepler\ mission. Funding for the
\kepler\ mission is provided by the NASA Science Mission directorate.
We are grateful to the entire \kepler\ team, past and present.
Their tireless efforts were all essential to the tremendous success of the mission
and the successes of \KT, present and future.
These data were obtained from the Mikulski Archive for Space Telescopes
(MAST).
STScI is operated by the Association of Universities for Research in
Astronomy, Inc., under NASA contract NAS5-26555.
Support for MAST is provided by the NASA Office of Space Science via grant
NNX13AC07G and by other grants and contracts.

{\it Facilities:} \facility{Kepler}

\appendix

\section{Some appendix}

\clearpage
\bibliography{single}
\clearpage

% \begin{figure}[p]
% \begin{center}
% \includegraphics{figures/pca.pdf}
% \end{center}
% \caption{%
% The top 10 eigen light curves (ELCs) generated by running principal component
% analysis on all the aperture photometry from Campaign~1.
% \figlabel{pca}}
% \end{figure}

\end{document}

### 2015-03-08 document/ms.tex
first draft of abstract

@@
 \title{%
-    The search for single transit events in the \kepler\ data
+    The search for long-period transiting planets in the \kepler\ light curves
 }
@@
                           K\"onigstuhl 17, D-69117 Heidelberg, Germany}
-\altaffiltext{\cds}      {Center for Data Science,
-                          New York University,
+\altaffiltext{\cds}      {Center for Data Science, New York University,
                           726 Broadway, 7th Floor, New York, NY, 10003, USA}
@@
 \begin{abstract}
+
+Many of the most dynamically interesting planets will be on orbits longer
+than the baseline of existing transit surveys (\kepler, \KT).
+Future surveys (\TESS, PLATO?) will have such a short continuous coverage that
+even habitable zone planets around M-dwarfs will only present a single transit
+signal.
+Searches for these transiting planets are plagued by false
+signals---especially when pushed to low signal-to-noise---and statistical
+studies of their population are complicated by weak constraints on the
+physical parameters of the system and high rates of false positives.
+We develop and present a computationally expensive but tractable method of
+searching for single transits using supervised classification methods from
+the machine learning literature.
+For each month of photometry, we train a random forest classifier on a large
+number of simulated signals injected into the photometry of the same star at
+different times.
+Then, the model's prediction as a function of transit time is evaluated and
+times above a threshold probability---chosen for each star to yield a sample
+with $\sim99$~percent purity---are given as candidate transits.
+Each candidate must then pass a final round of vetting including BLAH BLAH
+BLAH.
+Applied to every light curve in the \kepler\ archive this method yields a
+list of XXXX long-period transiting planet candidates.
+Using an informative prior on their eccentricities, we derive weak constraints
+on the orbital periods of the candidates and demonstrate that this puts an
+upper limit of ZZZZ on the occurrence rate of these planets.
 

### 2015-03-08 document/ms.tex
more words and hackin

@@
 than the baseline of existing transit surveys (\kepler, \KT).
-Future surveys (\TESS, PLATO?) will have such a short continuous coverage that
+Future surveys (\tess, PLATO?) will have such a short continuous coverage that
 even habitable zone planets around M-dwarfs will only present a single transit
@@
 
-Hi \citep{kois}.
+\begin{itemize}
+
+\item Description of the physical significance of these planets
+
+\item Discussion of previous attempts (papers by Gaudi, Yee, Payne, Bakos,
+\etc).
+
+\item Comparison of method to filtering methods and an argument for why
+supervised classification should be more robust to false alarms given a large
+enough training set
+
+\end{itemize}
+
+\citep{kois}
+
+\section{Dataset \& pre-processing}
+
+\section{Training the classifier}
+
+The positive examples of planet transits in the training set is generated by
+randomly selecting 121 cadence-long chunks of photometry and multiplying in a
+transit model generated by sampling the physical parameters from SOME
+DISTRIBUTIONS listed in SOME TABLE.
+The negative examples are randomly chosen chunks of the same length.
+When the model is to be used to search for transits in a specific month of
+data, the examples from that month are removed from the training set and the
+remaining examples are used.
+
+Practically, the features used as input to the classifier are just the flux
+values themselves normalized to unit median flux.
+
+\section{Search}
+
+\section{Transit candidates \& their orbits}
+
+\section{Detection efficiency \& false alarms}
+
+\section{Astrophysical false positives}
+
+\section{The population of long-period transiting planets}
+
+\section{Discussion}
 

### 2015-03-08 mlsing.py

@@ -58,6 +58,12 @@ def simulation_system(q1, q2, period, t0, ror, b):
     return s
 
 
+def normalize_inputs(X):
+    X /= np.median(X, axis=1)[:, None]
+    X[:, :] = np.log(X)
+    return X
+
+
 def generate_injections(lcs, npos=10000, nneg=None,
                         min_period=2e3, max_period=1e4,
                         min_ror=0.03, max_ror=0.3):
@@ -74,7 +80,7 @@ def generate_injections(lcs, npos=10000, nneg=None,
     for j in range(len(pos_sims)):
         # Generate the simulation parameters.
         nlc = np.random.randint(len(lcs))
-        ntt = np.random.randint(HALF_WIDTH, len(t)-HALF_WIDTH)
+        ntt = np.random.randint(HALF_WIDTH, len(lcs[nlc][0])-HALF_WIDTH)
         pos_pars.append([
             nlc, ntt, lcs[nlc][0][ntt],
             np.random.rand(), np.random.rand(),
@@ -94,12 +100,12 @@ def generate_injections(lcs, npos=10000, nneg=None,
     neg_pars = []
     for j in range(len(neg_sims)):
         nlc = np.random.randint(len(lcs))
-        ntt = np.random.randint(HALF_WIDTH, len(t)-HALF_WIDTH)
+        ntt = np.random.randint(HALF_WIDTH, len(lcs[nlc][0])-HALF_WIDTH)
         neg_pars.append([nlc, ntt, lcs[nlc][0][ntt]] + 6*[np.nan])
         neg_sims[j] = lcs[nlc][1][ntt+inds]
 
     # Format the arrays for sklearn.
-    X = np.concatenate((pos_sims, neg_sims), axis=0)
+    X = normalize_inputs(np.concatenate((pos_sims, neg_sims), axis=0))
     y = np.ones(len(X))
     y[len(pos_sims):] = 0
 

### 2015-03-30 document/ms.tex
some words and refs

--- 2015-03-08 document/ms.tex
@@
 
-\newcommand{\project}[1]{\textsl{#1}} % hogg say
+\newcommand{\project}[1]{\textsl{#1}}
 \newcommand{\kepler}{\project{Kepler}}
@@
 \title{%
-    The search for long-period transiting planets in the \kepler\ light curves
+    Searching for long-period transiting planets in the \kepler\ light curves
+    using supervised classification
 }
@@
 \newcommand{\nyu}{2}
-\newcommand{\mpia}{3}
-\newcommand{\cds}{4}
+\newcommand{\cds}{3}
+\newcommand{\mpia}{4}
 \newcommand{\mpis}{5}
 \author{%
-    Daniel~Foreman-Mackey\altaffilmark{1,\nyu},
+    Daniel~Foreman-Mackey\altaffilmark{1,\nyu,\cds},
     David~W.~Hogg\altaffilmark{\nyu,\mpia,\cds},
@@
                           4 Washington Place, New York, NY, 10003, USA}
+\altaffiltext{\cds}      {Center for Data Science, New York University,
+                          726 Broadway, 7th Floor, New York, NY, 10003, USA}
 \altaffiltext{\mpia}     {Max-Planck-Institut f\"ur Astronomie,
                           K\"onigstuhl 17, D-69117 Heidelberg, Germany}
-\altaffiltext{\cds}      {Center for Data Science, New York University,
-                          726 Broadway, 7th Floor, New York, NY, 10003, USA}
 \altaffiltext{\mpis}     {Max Planck Institute for Intelligent Systems
@@
 
-Hi \citep{kois}.
+\begin{itemize}
+
+\item Description of the physical significance of these planets
+
+\item Discussion of previous attempts (papers by Gaudi, Yee, Payne, Bakos,
+\etc).
+
+\item Comparison of method to filtering methods and an argument for why
+supervised classification should be more robust to false alarms given a large
+enough training set
+
+\end{itemize}
+
+\citep{kois}
+
+\section{Data preparation}
+
+The \kepler\ Mission measured photometry for about 150,000 stars at half-hour
+cadence for a baseline of over four years.
+We aim to search these time series for single transits of long-period planets
+and single eclipses of binary stars.
+These data are made available on
+MAST\footnote{\url{https://archive.stsci.edu/kepler/}} and, for each target,
+we downloaded the full set of light curve files provided by Data Release 24
+\citep{Thompson:2015}.
+From these files, we extracted the PDC time series and split them into
+``sections'' with no more than two contiguous missing or flagged data points.
+The PDC light curves have been corrected for the instrumental effects caused
+by the spacecraft using a data-driven model of the focal plane
+\citep{Stumpe:2012, Smith:2012}.
+Crucially, an attempt is also made by the PDC procedure to remove sharp
+instrumental artifacts like ``sudden pixel sensitivity dropouts (SPSDs)''.
+Any remaining missing data points are filled in using linear interpolation
+resulting in sections of contiguous time series measurements with nearly
+uniform time sampling.
+This procedure yields about 150 \emph{light curve sections} for the typical
+\kepler\ target.
+
+The goal of this project is to discover the transits of long-period planets
+that have not yet been discovered.
+Therefore, when studying the light curve of an eclipsing binary star or a star
+with known transiting planet candidates---on shorter periods---we also remove
+all the in-transit data for the candidate using the parameters provided by the
+\project{NASA Exoplanet
+Archive}\footnote{\url{http://exoplanetarchive.ipac.caltech.edu/}; We
+downloaded the \texttt{cumulative} table of \kepler\ Objects of Interest on
+2015-03-25.}.
+
+As we discuss further below, a key assumption of our analysis is that the
+process generating any non-transit variability or noise in the light curve
+is stationary.
+
+Every three months, the \kepler\ spacecraft rolled 90~degrees to maintain its
+orientation with respect to the Sun.
+This means that each star landed on a different set of pixels each quarter
+and, therefore, the systematic signals caused by any specific spacecraft
+orientation won't be shared between neighboring quarters.
+A year later, however, the pointing would return to nearly the same setup and
+each star ends up back on many of the same pixels.
+This manifests itself in the light curves by causing the observations
+separated by a year to be qualitatively similar.
+
+For reasons that will become clear in \sect{search}, we split the light curve
+sections into 3 disjoint sets.
+We use these sets to run a train/validate/test procedure so the goal is to
+have representative samples in each set.
+Therefore, we attempt to split the sections intelligently; evenly
+distributing sections from the same quarter and season across the splits.
+When this is not possible, we randomly assign the section to a split.
+
+\section{Random forest classification}
+
+A common task in the machine learning literature is called \emph{supervised
+classification} where the goal is to separate objects into classes
+represented by sets of labeled examples.
+One example from the astronomy literature is the problem of star--galaxy
+separation (\dfmtodo{cite}).
+In this problem, there are a set of images or photometric measurements that
+have been classified---by some other method---as either a star or galaxy
+observation and the goal is to transfer these labels to a set of observations
+that have not yet been classified.
+For a more in-depth discussion of the application of these techniques in
+astronomy, the interested reader is directed to \citet{Ivezic:2013}.
+
+The Random Forest (RF) classification model \citep{Breiman:2001} has become
+very popular in the machine learning community.
+It has also been applied with great success in astronomy \citep[for
+example]{Richards:2011, Richards:2012} \dfmtodo{others}.
+The RF model works by building
+
+\section{Search procedure}\sectlabel{search}
+
+\paragraph{Generate the training \& validation sets}
+
+\paragraph{Train}
+
+\paragraph{Validate}
+
+\paragraph{Test}
+
+\section{Tuning parameters}
+
+\paragraph{The parameters}
+
+\paragraph{Objective function}
+
+\section{Demonstration}
+
+\paragraph{Successes}
+
+\paragraph{Failures}
+
+\section{Parameter estimation}
+
+\section{Population inference}
+
+\section{Results}
+
+\section{Discussion}
 
@@
 \clearpage
-\bibliography{single}
+\bibliography{peerless}
 \clearpage

### 2015-03-30 document/ms.tex
words about injections, recall, and precision

@@
 
-\citep{kois}
-
 \section{Data preparation}
@@
 example]{Richards:2011, Richards:2012} \dfmtodo{others}.
-The RF model works by building
+The RF model works by fitting an ensemble of decision trees to randomly
+selected subsamples of the training dataset.
+Each tree in the forest is ``grown'' by greedily choosing decision boundaries
+that optimize the separation of the training data in randomly selected
+subsets of the features until the separation is complete, each leaf contains
+only one class or, at most, a fixed number of samples.
+At each branch, the decision boundary is set by maximizing either the entropy
+or the ``gini'' coefficient.
+
+For the problem of single transit search, our problem can be phrased as a
+classification problem where we want to assign every $K$ data point long chunk
+of light curve into either the \texttt{transit} or \texttt{no transit} class.
+This problem doesn't fall under the standard format of a supervised
+classification problem because very few long-period transits have actually
+been observed or classified.
+We do think, however, that we have a good physical generative model for the
+signal of interest and most of the observations of each star have no transits.
+Therefore, we can train the model on simulated signals.
 
@@
 
+To search for single transits in the light curve of a specific star, we fit
+three random forest models.
+
 \paragraph{Generate the training \& validation sets}
+
+We need to train the classification model on simulated signals.
+To simulate these training and validation examples, we randomly select
+sections of 121 contiguous flux measurements and simulate the transit signal
+induced by the physical orbit of a large planet.
+The specific distribution of simulated parameters is listed in \dfmtodo{some
+table}.
+In the simulations, we take limb darkening and integration time into account
+\dfmtodo{cite}.
+Since we expect most of the systematic variability to be time-reversible, we
+augment the training set with simulations injected into the reversed time
+series \dfmtodo{cite some examples of rotational invariance}.
+The training set also includes an equal number of negative examples---time
+series chunks of the same length without a simulated transit injection.
+By virtue of the fact that we are specifically searching for single transits
+it is safe to assume that none of the negative samples from the other light
+curve sections will have no transits.
+
+We also generate a validation set of simulated signals.
+This set is identical to the training set except it is simulated in sections
+of light curve that are not used for training.
+As discussed below, this set is used to determine the transit significance
+threshold required to achieve a pure sample.
+
+In practice, we only need to train three models on the three disjoint
+training sets and then for each model, we validate and test on both of the
+remaining splits.
+
+\paragraph{Features}
+
+In many supervised classification problems, a sophisticated feature
+extraction method is used to improve the performance of the procedure.
+For this specific problem, we find excellent performance using the 121
+normalized flux values as the features.
+The depth of the transit and the noise in the light curve is not irrelevant
+to detection so we don't normalize the features to unit variance in the
+standard way.
+Instead, we normalize each sample (feature vector) by it's empirical median
+value and take the logarithm.
+Another option for a feature set could be the Fourier transform or wavelet
+transform of the light curve section.
+Alternatively, the spectrogram of the fluxes in a larger window.
+We have experimented briefly with this options finding similar performance.
 
@@
 
-\section{Tuning parameters}
+\section{Tuning parameters}\sectlabel{tuning}
+
+Many choices need to be made in building this classification model.
+These choices can be specified by a set of parameters that can be tuned the
+optimize the performance of the method.
+At this point, it's probably worth discussing how one might specifically
+measure the ``performance'' of a search for transits.
+The goal is, of course, to \emph{find transiting planets}.
+Therefore, we would like to develop a method that finds the most planets
+possible.
+This will, in general, trade off with the purity of the sample.
+For example, a method that returns every possible point the light curve as a
+planet candidate will be guaranteed to find every signal in the dataset---it
+will have excellent completeness or \emph{recall}---but almost every
+candidate will be false---the \emph{precision} is low.
+This is obviously not what we want.
+Instead, the more relevant metric is probably the recall at fixed (high)
+precision.
+
+Let's be clear about what we mean by the terms \emph{precision} and
+\emph{recall} in this context because they have specific definitions in the
+machine learning that will be useful in our discussion here.
+Recall is the probability, integrated across the full parameter space of
+interest that a true transit signal will be detected by the method.
+In astronomy, this quantity is generally called the completeness or the
+detection efficiency and it is routinely measured for transit surveys
+\dfmtodo{cite}.
+On the other hand, precision is the probability that a positive classification
+will be true.
+In other words, for a given candidate that our pipeline spits out, the
+probability that it is a false alarm is given by one minus the precision.
+In astronomy, precision is generally hard or impossible to measure because we
+have no ground truth; we don't know that \emph{there is definitely no transit}
+at a given time in the light curve.
+However, with a few weak assumptions, we can, in practice, estimate the
+precision of our single transit search robustly.
+
+\paragraph{Estimating the survey precision}
+
+There are two key assumptions that enter into our precision calculation.
+The first is that all transiting planets with more than one transit and a
+large signal-to-noise ratio have been previously discovered by one of the many
+transit searches applied the \kepler\ dataset \dfmtodo{cite}.
+This is a safe assumption because, for large planets, these surveys are all
+largely complete out to periods yielding only 2 or 3 transits in the \kepler\
+baseline \dfmtodo{cite}.
+The second necessary assumption is less robust but it is required for a
+completely reliable measurement of the survey precision.
+This assumption is that the noise processes in the data are stationary.
+In other words, the transit-like noise signals in the training and validation
+sets must be ``similar'' to the signals in the target section.
+The PDC processing of the data successfully removes most of the
+instrument-induced signals with some exceptions that are discussed in
+\sect{demo}.
+Perhaps we make the further assumption that the stellar variability is
+also stationary.
+
+Under these assumptions, the precision of the search procedure is
+estimated using a set of injections.
 
@@
 
-\section{Demonstration}
+\section{Demonstration}\sectlabel{demo}
 

### 2015-04-07 document/ms.tex
adding prediction plot and some words about expected number of single transits

@@
 % Notation for this paper.
-\newcommand{\flux}{{\ensuremath{f}}}
-\newcommand{\ferr}{{\ensuremath{\sigma_\flux}}}
-\newcommand{\attime}{{\ensuremath{t}}}
-\newcommand{\basis}{{\bvec{A}}}
-\newcommand{\weights}{{\bvec{w}}}
-
 \newcommand{\period}{{\ensuremath{P}}}
-\newcommand{\phase}{{\ensuremath{T^0}}}
-\newcommand{\duration}{{\ensuremath{D}}}
-\newcommand{\depth}{{\ensuremath{Z}}}
-\newcommand{\transittime}{{\ensuremath{T}}}
-\newcommand{\impact}{{\ensuremath{b}}}
-\newcommand{\ecc}{{\ensuremath{e}}}
-\newcommand{\pomega}{{\ensuremath{\omega}}}
+\newcommand{\rp}{{\ensuremath{R_\mathrm{P}}}}
+\newcommand{\rate}{{\ensuremath{\Gamma}}}
 
@@
 
+\section{Estimated yield}
+
+Before the launch of the \kepler\ Mission, \citet{Yee:2008} predicted the
+yield of single transit events based on the planet occurrence rates estimated
+based on small catalog of radial velocity discoveries \citep{Butler:2006}.
+Using these early results and the pre-launch specifications of the \kepler\
+Mission, \citet{Yee:2008} predicted that \kepler\ would discover $\sim 6$
+single transit events in the full dataset.
+Now that the Mission is complete and we have better estimates of the
+occurrence rate and distribution of planets \citep[for example][]{Dong:2013,
+Petigura:2013, Foreman-Mackey:2014, Dressing:2015}, we can update the
+predicted yield for single transit events in the \kepler\ light curves.
+To make this estimate, we extrapolate the distribution of large planets on
+relatively short orbits out to longer periods, taking detection efficiency
+and the survey and targeting properties into account.
+
+We will base our estimate on an assumed model $Q_k(\rp,\,\period)$ for the
+absolute probability of detecting a planet with radius \rp\ and period
+\period\ orbiting the star $k$, and the occurrence rate distribution
+\begin{eqnarray}
+\rate (\rp,\,\period) &=& \frac{\dd N}{\dd\ln\rp\dd\ln\period} \quad,
+\end{eqnarray}
+the expected number of planets per star, per logarithmic radius, per
+logarithmic period.
+Given these two quantities, the expected number of single transits in the
+\kepler\ data is given by
+\begin{eqnarray}
+N &=& \sum_{k=1}^K N_k
+\end{eqnarray}
+where the sum is over the $K$ stars in the sample and $N_k$ is the expected
+number of observable transits around star $k$
+\begin{eqnarray}\eqlabel{nk}
+N_k &=& \int Q_k(\rp,\,\period) \, \rate (\rp,\,\period)
+    \dd\ln\rp \dd\ln\period \quad.
+\end{eqnarray}
+The integral in \eq{nk} is over the full range of target parameters.
+
+For the purposes of this discussion, we assume an approximate simple detection
+efficiency model with three contributions: the geometric transit probability,
+the temporal transit probability, and signal-to-noise ratio threshold of the
+search technique.
+Assuming circular orbits, the geometric transit probability is given by
+\citep{Winn:2010}
+\begin{eqnarray}
+Q_k^\mathrm{(geom)}(\rp,\,\period) &=& \frac{R_k}{a} \\
+&=& \left( \frac{4\,\pi^2}{G\,M_k} \right)^{1/3} \, R_k \, \period^{-2/3}
+\end{eqnarray}
+where $R_k$ and $M_k$ are the radius and mass of the star $k$ respectively.
+The eccentricity distribution of these long-period planets will affect this
+transit probability \citep{Kipping:2014} but this simple prescription should
+be sufficient for a rough estimate.
+For long-period orbits, the temporal transit probability will be given by
+\begin{eqnarray}
+Q_k^\mathrm{(time)}(\rp,\,\period) &=& \frac{T_k}{\period}
+\end{eqnarray}
+where $T_k$ is the total time that \kepler\ spent observing the star $k$.
+Finally, the detection threshold depends on the detailed sensitivity of the
+search procedure but we will approximate it as a simple step function in
+signal-to-noise ratio of the transit.
+This contribution will be given approximately by
+\begin{eqnarray}
+Q_k^\mathrm{(detect)}(\rp,\,\period) &=& \left\{\begin{array}{ll}
+1 & \mathrm{if}\,\left(\rp/R_k\right)^2 > f\,\sigma_k \\
+0 & \mathrm{otherwise}
+\end{array}\right.
+\end{eqnarray}
+where $\sigma_k$ is an estimate of the noise in light curve of star $k$ and
+$f$ is the detection threshold for the method.
+
+Combining the detection efficiency components, the integral from \eq{nk}
+becomes
+\begin{eqnarray}
+N_k &=& \left( \frac{4\,\pi^2}{G\,M_k} \right)^{1/3} \, R_k \, T_k
+    \int_{\rp_\mathrm{min}} ^{\rp_\mathrm{max}} \frac{\dd\rp}{\rp}
+    \int_{\period_\mathrm{min}} ^{\period_\mathrm{max}}
+        \period^{-8/3}\,\rate(\rp,\,\period) \dd\period
+\end{eqnarray}
+where all the integration limits are set by the target parameter space.
+Because of the detection probability threshold, $\rp_\mathrm{min}$ can be no
+smaller than $R_k\,\sqrt{f\,\sigma_k}$.
+\citet{Dong:2013} used the catalog of short period transiting planets found
+by \kepler\ to constrain a model for the occurrence rate of large planets of
+the form
+\begin{eqnarray}
+\rate(\rp,\,\period) &=& C\,\left(\frac{\period}{10\,\mathrm{d}}\right)^\beta
+\end{eqnarray}
+in a set of radius bins.
+
+Assuming the stellar parameters provided by the NASA Exoplanet
+Archive\footnote{\dfmtodo{URL for kepler stellar table; downloaded on SOME
+DATE.}} \dfmtodo{cite Huber} and approximating the stellar noise using the
+15-hour CDPP \dfmtodo{cite CDPP}, \dfmtodo{some figure} shows the extrapolated
+number of transiting planets with $\period > 1500\,\mathrm{d}$ based on the
+\citet{Dong:2013} power-law model.
+For a detection threshold $f\sim10$, the expected number of single transit
+events in the \kepler\ light curves is $\sim 120$.
+
+\begin{figure}[p]
+\begin{center}
+\includegraphics{figures/predict.pdf}
+\end{center}
+\caption{%
+The expected number of single transit events---extrapolated from the
+\citet{Dong:2013} power-law model fit to the shorter period \kepler\
+candidates---as a function of the effective signal-to-noise threshold of the
+search procedure.
+The shaded region indicates the uncertainties propagated from the model
+parameters.
+\figlabel{predict}}
+\end{figure}
+
 \section{Data preparation}
@@
 instrumental artifacts like ``sudden pixel sensitivity dropouts (SPSDs)''.
-Any remaining missing data points are filled in using linear interpolation
-resulting in sections of contiguous time series measurements with nearly
-uniform time sampling.
-This procedure yields about 150 \emph{light curve sections} for the typical
-\kepler\ target.
 
@@
 2015-03-25.}.
+
+\paragraph{Terminology}
+
+Any remaining missing data points are filled in using linear interpolation
+resulting in sections of contiguous time series measurements with nearly
+uniform time sampling.
+This procedure yields about 150 \emph{light curve sections} for the typical
+\kepler\ target.
 
@@
 Therefore, we can train the model on simulated signals.
+
+We use the \project{scikit-learn}\citep{Pedregosa:2011} implementation of the
+RF classification algorithm\footnote{Specifically we use the
+\texttt{RandomForestClassifier} object;
+\url{http://scikit-learn.org/stable/modules/generated/sklearn.ensemble.RandomForestClassifier.html}.}.
 

### 2015-04-07 document/figures/predict.py

@@ -1,0 +1,87 @@
+# -*- coding: utf-8 -*-
+
+from __future__ import division, print_function
+
+from plot_setup import COLORS, SQUARE_FIGSIZE
+
+import peerless
+import numpy as np
+import matplotlib.pyplot as pl
+from matplotlib.ticker import ScalarFormatter
+
+# Newton's constant in R_Sun^3 M_Sun^{-1} {days}^{-2}.
+G = 2945.4625385377644
+
+# Get the stellar data.
+kic = peerless.catalogs.KICatalog().df
+
+# This is the factor out front of the integral.
+T_k = kic.dataspan*kic.dutycycle
+factor = np.array(T_k * kic.radius * (4*np.pi**2/(G*kic.mass))**(1./3))
+
+# Pre-compute the stellar noise and base radius scale.
+sig_k = 1e-6 * kic.rrmscdpp15p0
+r_k = np.array(np.sqrt(sig_k) * kic.radius)
+
+# We'll integrate for all periods above 1500 days.
+P_min = 1500.
+
+# These are the fits in radial bins from Dong & Zhu (2013)
+rad_rngs = [
+    # R_min, R_max, C, C_err, beta, beta_err
+    (0.01, 0.02, 0.66, 0.08, -0.10, 0.12),
+    (0.02, 0.04, 0.49, 0.03, 0.11, 0.05),
+    (0.04, 0.08, 0.040, 0.008, 0.70, 0.10),
+    (0.08, 0.16, 0.023, 0.007, 0.50, 0.17),
+]
+
+
+# Compute the expected number of single transits for a given detection
+# threshold.
+def compute_expected_number(threshold):
+    N = np.zeros((3, len(factor)))
+    for rmn, rmx, C, C_err, beta, beta_err in rad_rngs:
+        for j, (bb, cc) in enumerate(zip(beta + beta_err*np.array([-1, 0, 1]),
+                                         C + C_err*np.array([-1, 0, 1]))):
+            # Compute the bounds of the radius integral.
+            rmin = np.array(np.sqrt(threshold) * r_k)
+            rmin[rmin < rmn] = rmn
+            rmin[rmin > rmx] = rmx
+
+            # Compute the integral over period.
+            p = bb - 5./3
+            p_fac = -P_min**p / p
+
[…]

### 2015-04-07 peerless/data.py
larger min_break

@@ -47,7 +47,7 @@ def load_light_curves_for_kic(kicid, clobber=False, remove_kois=True, **kwargs):
     return load_light_curves(fns, **kwargs)
 
 
-def load_light_curves(fns, pdc=True, min_break=1, delete=False,
+def load_light_curves(fns, pdc=True, min_break=10, delete=False,
                       remove_kois=None, downsample=1):
     # Find any KOIs.
     if remove_kois is not None:

### 2015-04-07 cluster_scripts/mercer/run.py
adding collect script and a few tweaks

@@ -7,6 +7,7 @@ import os
 import argparse
 import peerless
 import numpy as np
+import pandas as pd
 
 # Parse the command line arguments.
 parser = argparse.ArgumentParser()
@@ -25,11 +26,16 @@ if args.profile_dir is not None:
     poolargs["profile_dir"] = args.profile_dir
 
 # Only select G-stars.
+kois = peerless.catalogs.KOICatalog().df
+kois = kois[kois.koi_pdisposition == "CANDIDATE"]
 stlr = peerless.catalogs.KICatalog().df
+stlr = pd.merge(kois, stlr, on="kepid", how="left")
+
 select = (stlr.teff > 4100) & (stlr.teff < 6100)
 select &= (stlr.logg > 4.0) & (stlr.logg < 4.9)
 select &= (stlr.kepmag > 10.0) & (stlr.kepmag < 15)
 kicids = np.array(stlr[select].kepid)
+print(len(kicids))
 
 # Set up the lock files.
 fns = map(os.path.join(args.out_dir, "{0}.lock").format, kicids)

### 2015-04-07 document/ms.tex

@@
 \newcommand{\tablabel}[1]{\label{tab:#1}}
-\newcommand{\Eq}[1]{Equation~(\ref{eq:#1})}
+\renewcommand{\eqref}[1]{\ref{eq:#1}}
+\newcommand{\Eq}[1]{Equation~(\eqref{#1})}
 \newcommand{\eq}[1]{\Eq{#1}}
-\newcommand{\eqalt}[1]{Equation~\ref{eq:#1}}
+\newcommand{\eqalt}[1]{Equation~\eqref{#1}}
 \newcommand{\eqlabel}[1]{\label{eq:#1}}
@@
 yield of single transit events based on the planet occurrence rates estimated
-based on small catalog of radial velocity discoveries \citep{Butler:2006}.
+based on small catalog of radial velocity discoveries \citep{Butler:2006} and
+a fit to their occurrence rate \citep{Cumming:2008}.
 Using these early results and the pre-launch specifications of the \kepler\
@@
 \citep{Winn:2010}
-\begin{eqnarray}
+\begin{eqnarray}\eqlabel{q-geom}
 Q_k^\mathrm{(geom)}(\rp,\,\period) &=& \frac{R_k}{a} \\
@@
 For long-period orbits, the temporal transit probability will be given by
-\begin{eqnarray}
+\begin{eqnarray}\eqlabel{q-time}
 Q_k^\mathrm{(time)}(\rp,\,\period) &=& \frac{T_k}{\period}
@@
 becomes
-\begin{eqnarray}
+\begin{eqnarray}\eqlabel{nk-2}
 N_k &=& \left( \frac{4\,\pi^2}{G\,M_k} \right)^{1/3} \, R_k \, T_k
@@
 in a set of radius bins.
+Using this model, the integral in \eq{nk-2} becomes
+\begin{eqnarray}
+N_k &=& \left( \frac{4\,\pi^2}{G\,M_k} \right)^{1/3} \, R_k \, T_k \,
+    \sum_{j=1}^J \frac{C_j}{(10\,\mathrm{d})^{\beta_j}}\,
+    \ln \left( \frac{\rp_{\mathrm{max},j}}{\rp_{\mathrm{min},j}} \right) \,
+    \left[ \frac{{\period_\mathrm{min}}^{\beta_j - 5/3}}{5/3-\beta_j} \right]
+\end{eqnarray}
+where the sum is over the $J$ radial bins studied by \citet{Dong:2013}.
+It's important to note that the model used by \citet{Dong:2013} is given in
+base-10 logarithms so the units must be converted to natural logarithms as
+appropriate.
 
@@
 For a detection threshold $f\sim10$, the expected number of single transit
-events in the \kepler\ light curves is $\sim 120$.
+events in the \kepler\ light curves is $\sim 150$.
+
+This results is much more optimistic than the pre-launch estimate from
+\citet{Yee:2008} for a few reasons.
+One effect is that, the \kepler\ Mission ran for more than four
+years---longer than the fiducial Mission goal---and $\sim190,000$ stars were
+targeted for nearly the full baseline instead of the original 100,000.
+\dfmtodo{Explain other reasons.}
 
@@
 
-The \kepler\ Mission measured photometry for about 150,000 stars at half-hour
+The \kepler\ Mission measured photometry for about 190,000 stars at half-hour
 cadence for a baseline of over four years.
@@
 
-\section{Demonstration}\sectlabel{demo}
+\section{Preliminary results}\sectlabel{demo}
+
+\paragraph{A discovery}
 
@@
 
+Even though only one transit is observed, it is still possible to estimate the
+orbital period of these planet candidates using independent constraints on the
+stellar properties.
+This technique is similar in spirit to the ``photoeccentric effect''
+\citep{Dawson:2012} and ``asterodensity profiling'' \citep{Kipping:2012}.
+The fundamental principle is that, the transit duration is a measurement of
+the instantaneous velocity of the planetary motion and this yields a
+constraint on the orbital period when combining this with a measurement of the
+stellar density and a prior on the eccentricity of the orbit.
+
+In practice, we directly model the light curve as being generated by a planet
+on an eccentric Keplerian orbit transiting a limb darkened star and
+marginalize over all the orbital elements and physical parameters.
+We take limb darkening and the finite exposure time into account
+\citep{Mandel:2002, Kipping:2010, Kipping:2013} and use an empirical
+Beta function prior on the eccentricity \citep{Kipping:2013a}.
+
 \section{Population inference}
+
+Based on our single transit discoveries, we now want to place a limit on
+the occurrence rate of long-period planets.
+Since we only have one discovery thus far, we'll make the simplifying
+assumption that the rate is flat in log-period and log-radius in the range
+$1000\,\mathrm{d} < \period < 5000\,\mathrm{d}$ and $5\,R_\odot <
+20\,R_\odot$.
+For this distribution, \citet{Foreman-Mackey:2014} derived the analytic
+maximum likelihood result
+\begin{eqnarray}
+\rate &=& \frac{N_\mathrm{obs}}{\int Q(w)\dd w}
+\end{eqnarray}
+where $\rate$ is the occurrence rate per natural logarithm in period and
+radius, $N_\mathrm{obs}$ is the number of detections, and the integral is over
+the completeness measurements for every star that has been searched.
+If we make the simplifying assumption that the detectability of a transit
+depends on period only through Equations~(\eqref{q-geom})
+and~(\eqref{q-time}), then this integral becomes
+\begin{eqnarray}
+\int Q(w)\dd w &=& \sum_{k=1}^K
+    \left( \frac{4\,\pi^2}{G\,M_k} \right)^{1/3} \, R_k \, T_k \, Q_k \,
+    \int \period^{-8/3}\,\rp^{-1} \dd\rp\dd\period \\
+ &=& \sum_{k=1}^K
+    \left( \frac{4\,\pi^2}{G\,M_k} \right)^{1/3} \, R_k \, T_k \, Q_k \,
+    \ln \left(\frac{\rp_\mathrm{max}}{\rp_\mathrm{min}}\right)
+    \frac{3}{5} \,
+    \left[{\period_\mathrm{min}}^{-5/3} - {\period_\mathrm{max}}^{-5/3}\right]
+\end{eqnarray}
+where the sum is over all the targeted stars.
 

### 2015-04-08 document/ms.tex
words for intro

@@
 
-\begin{itemize}
+The transit method of exoplanet detection and characterization has been
+demonstrated as a powerful method for building systematic catalogs of
+exoplanets.
+Despite the great success of the \kepler\ Mission with thousands of planet
+discoveries \dfmtodo{cite}, current methods for exoplanet discoveries are
+currently limited in the range of orbital periods that can be studied.
+Specifically, the standard transit search procedures only discover signals
+with at least three observed transits \dfmtodo{cite Jenkins, Petigura, \etc}.
+For \kepler, with a baseline of about four years, this sets an upper limit on
+the detectable periods of just over a year.
+In the Solar System, Jupiter---with a period of 12 years---dominates the
+planetary dynamics and, since it would only exhibit at most one transit in the
+\kepler\ data, it would be missed by most existing transit search procedures.
+It is possible to discover long-period planets like this using targeted radial
+velocity (RV) surveys \dfmtodo{cite} but the cost of implementing a systematic
+RV search is substantially higher than searching the existing and forthcoming
+photometric data for single transits.
 
-\item Description of the physical significance of these planets
+There are two main technical barriers to a search for single transit events.
+The first is that the transit probability for long-period planets is very low;
+scaling as $\propto\period^{-5/3}$ for orbital periods longer than the
+baseline of contiguous observations.
+Therefore, even if long-period planets are intrinsically common, they will
+still be underrepresented in a transiting sample.
+The second challenge is that there are substantial signals in the observed
+light curves caused by stochastic processes---both instrumental
+(pointing jitter, temperature variations, \etc) and astrophysical (stellar
+variability, \etc)---that can masquerade as transit signals.
+In practice, even using the most sophisticated systematics removal methods,
+these false signal far outnumber the true single transits.
 
-\item Discussion of previous attempts (papers by Gaudi, Yee, Payne, Bakos,
-\etc).
+Nearly every transit search algorithm is built on the same principles and many
+of the same decisions are made.
+In particular, at the heart of most methods is a matched filtering step where
+the likelihood of an approximate transit model is computed on a grid in the
+physical parameters \dfmtodo{cite}.
+Using these methods, and substantial hand-curation, some long-period
+transiting candidates have been published \citep[for example][]{Batalha:2013,
+Huang:2013, Kipping:2014a}.
+For more recent data releases, the community has settled on more conservative
+selection criteria where candidates are required to have multiple transits
+\citep[for example][]{Petigura:2013, Burke:2014}.
+This means that there has never been a systematic search for single transits
+in the full \kepler\ dataset.
 
-\item Comparison of method to filtering methods and an argument for why
-supervised classification should be more robust to false alarms given a large
-enough training set
+A qualitatively different approach to planet search is employed by the
+\project{Planet Hunters} (PH)
+project\footnote{\url{http://www.planethunters.org/}} \citep{Fischer:2012}.
+PH is a ``citizen science'' project where visitors to the website look at
+sections of light curve and mark the locations of transits that can be
+identified visually.
+Visual inspection can be a useful search technique for large single transits
+because humans are able to robustly distinguish transit signals from the noise
+and this project has yielded some promising long-period candidates and
+confirmed planets \citep[for example][]{Wang:2013}.
+One shortcoming of the PH method is that it can be difficult to fully quantify
+the performance (completeness and reliability) of the search and PH does not
+evaluate their users using synthetic transit signals as is now common practice
+in the transit search literature.
+This means that the PH sample of candidates cannot be used for robust
+population inference.
 
-\end{itemize}
+We propose a transit search method that shares some similarities with the PH
+model but, instead of human classifiers, we use a supervised classification
+model trained on large numbers of simulated transit signals injected into
+real \kepler\ light curves.
+This procedure is motivated because, by definition, most randomly selected
+sections of light curve contain no transits and there is an excellent physical
+model for the signals of interest.
+If we can train a classification model to robustly separate light curve
+sections with transits from sections without then we should be able to use
+this in-place of the humans to find single transit events.
 
@@
 15-hour CDPP \dfmtodo{cite CDPP}, \dfmtodo{some figure} shows the extrapolated
-number of transiting planets with $\period > 1500\,\mathrm{d}$ based on the
-\citet{Dong:2013} power-law model.
+number of transiting planets with $1500\,\mathrm{d} < \period <
+5000\,\mathrm{d}$ based on the \citet{Dong:2013} power-law model.
 For a detection threshold $f\sim10$, the expected number of single transit
-events in the \kepler\ light curves is $\sim 150$.
+events in the \kepler\ light curves is $\sim 60$.
 

### 2015-04-08 document/ms.tex
one or two more words
WORDS WORDS WORDS

@@
 \newcommand{\figlabel}[1]{\label{fig:#1}}
+
 \newcommand{\Tab}[1]{Table~\ref{tab:#1}}
@@
 \newcommand{\tablabel}[1]{\label{tab:#1}}
+
 \renewcommand{\eqref}[1]{\ref{eq:#1}}
@@
 \newcommand{\eqlabel}[1]{\label{eq:#1}}
+
 \newcommand{\sectionname}{Section}
-\newcommand{\Sect}[1]{\sectionname~\ref{sect:#1}}
+\newcommand{\sectref}[1]{\ref{sect:#1}}
+\newcommand{\Sect}[1]{\sectionname~\sectref{#1}}
 \newcommand{\sect}[1]{\Sect{#1}}
-\newcommand{\sectalt}[1]{\ref{sect:#1}}
-\newcommand{\App}[1]{Appendix~\ref{sect:#1}}
+\newcommand{\sectalt}[1]{\sectref{#1}}
+\newcommand{\App}[1]{Appendix~\sectref{#1}}
 \newcommand{\app}[1]{\App{#1}}
@@
 this in-place of the humans to find single transit events.
+This method is novel as a means to transit search and it differs substantially
+from the standard methods.
 
-\section{Estimated yield}
+Automated classification processes have been hugely successful in the machine
+learning literature when applied to the right datasets \dfmtodo{cite some
+things}.
+Many astronomical problems can't be naturally solved by the standard machine
+learning models because of their heterogeneous character and heteroscedastic
+uncertainties.
+The search for single transits, however, is an excellent use case when applied
+with care.
+The noise in the light curve of a given star is relatively consistent for the
+full baseline of observation and we have a very good physical generative model
+for the transit signal so we can simulate arbitrarily large sets of training
+examples.
+
+In the training step, a Random Forest (RF) classifier is trained to
+distinguish---based only on the light curve itself---between sections of light
+curve that contain transits from sections of the same size that do not.
+This model is then used to find candidates in left-out sections of the light
+curve.
+In principle, this model can capture arbitrarily complicated non-linear
+structure in the decision space and if the training set is large and complete
+it will ``learn'' the shape of a physical transit.
+In practice, classification algorithms like this also require a complete set
+of ``negative'' training examples so further vetting using physical models
+is necessary.
+
+In \sect{est}, we extrapolate a recent model of the distribution of exoplanets
+to the long periods considered in this \paper.
+Using an approximate but realistic model for the detection efficiency of a
+search for single transits, we estimate that $\sim 60$ single transit events
+should be detectable in the archival \kepler\ dataset.
+In \sect{data}, we describe the data and outline the structure exploited by
+our transit search procedure.
+In \sect{rfc}, we briefly describe the Random Forest classification framework
+and in \sect{search} we outline the steps used to apply this model for transit
+search.
+This method requires the setting of many tuning parameters and the
+optimization of these choices is both computationally and intellectually
+challenging so in \sect{tuning} we discuss some steps in this direction.
+In \sect{demo}, we demonstrate the feasibility of this method, present a
+single transit discovery, and indicate some interesting weaknesses of the
+method.
+In \sectionname s~\sectref{params} and~\sectref{exopop}, we describe the
+parameter estimation that is possible given a single transit and outline the
+prospects for exoplanet population inference given a catalog of single transit
+discoveries.
+
+\section{Estimated yield}\sectlabel{est}
 
@@
 
-\section{Data preparation}
+\section{Data preparation}\sectlabel{data}
 
@@
 MAST\footnote{\url{https://archive.stsci.edu/kepler/}} and, for each target,
-we downloaded the full set of light curve files provided by Data Release 24
-\citep{Thompson:2015}.
+we downloaded the full set of long cadence light curve files provided by Data
+Release 24 \citep{Thompson:2015}.
 From these files, we extracted the PDC time series and split them into
-``sections'' with no more than two contiguous missing or flagged data points.
+``sections'' with no more than ten contiguous missing or flagged data points.
 The PDC light curves have been corrected for the instrumental effects caused
@@
 instrumental artifacts like ``sudden pixel sensitivity dropouts (SPSDs)''.
+The success rate of this correction procedure is much higher than in earlier
+data releases but, as discussed in \sect{demo}, there remain some cases that
+are not properly accounted for.
 
@@
 uniform time sampling.
-This procedure yields about 150 \emph{light curve sections} for the typical
+This procedure yields about 100 \emph{light curve sections} for the typical
 \kepler\ target.
@@
 
-\section{Random forest classification}
+\section{Random forest classification}\sectlabel{rfc}
 
@@
 represented by sets of labeled examples.
-One example from the astronomy literature is the problem of star--galaxy
-separation (\dfmtodo{cite}).
-In this problem, there are a set of images or photometric measurements that
-have been classified---by some other method---as either a star or galaxy
-observation and the goal is to transfer these labels to a set of observations
-that have not yet been classified.
+In the astronomy literature, supervised classification has been used for
+variable star classification \citep{Richards:2011} star--galaxy separation
+\citep{Fadely:2012}, galaxy morphology prediction \citep{Dieleman:2015}, and
+other applications.
+In each of these problems, there are a set of measurements that have been
+assigned classes---by some other method; often manually---and the goal is to
+transfer these labels to a set of observations that have not yet been
+labeled.
 For a more in-depth discussion of the application of these techniques in
@@
 
-The Random Forest (RF) classification model \citep{Breiman:2001} has become
-very popular in the machine learning community.
+In our problem of transit search, we want to ``label'' sections of light curve
+with either the \texttt{transit} or \texttt{no transit} class.
+This problem doesn't fall under the standard format of a supervised
+classification problem because very few long-period transits have actually
+been observed or classified.
+We do think, however, that we have a good physical generative model for the
+signal of interest and most of the observations of each star have no transits.
+Therefore, we train the model on simulated signals.
+
+The Random Forest (RF) classification model \citep{Breiman:2001} is a popular
+model in the machine learning community where it is a common go-to model for
+basic classification tasks.
 It has also been applied with great success in astronomy \citep[for
@@
 
-For the problem of single transit search, our problem can be phrased as a
-classification problem where we want to assign every $K$ data point long chunk
-of light curve into either the \texttt{transit} or \texttt{no transit} class.
-This problem doesn't fall under the standard format of a supervised
-classification problem because very few long-period transits have actually
-been observed or classified.
-We do think, however, that we have a good physical generative model for the
-signal of interest and most of the observations of each star have no transits.
-Therefore, we can train the model on simulated signals.
+We use the \project{scikit-learn} \citep{Pedregosa:2011} version of the RF
+classification algorithm\footnote{Specifically we use the
+\texttt{RandomForestClassifier} object;
+\url{http://scikit-learn.org/stable/modules/generated/sklearn.ensemble.RandomForestClassifier.html}.}
+implemented in \project{Python}.
+This implementation has state-of-the-art speed and
+performance\footnote{\url{http://blog.explainmydata.com/2014/03/big-speedup-for-random-forest-learning.html}}
+while maintaining a flexible and user-friendly interface.
 
-We use the \project{scikit-learn}\citep{Pedregosa:2011} implementation of the
-RF classification algorithm\footnote{Specifically we use the
-\texttt{RandomForestClassifier} object;
-\url{http://scikit-learn.org/stable/modules/generated/sklearn.ensemble.RandomForestClassifier.html}.}.
+\section{Search methodology}\sectlabel{search}
 
-\section{Search procedure}\sectlabel{search}
+Now, we will apply the RF classification model to search for single transits
+in \kepler\ light curves.
+The basic structure of the problem, applied to the light curve of a single
+star, is:
+\begin{enumerate}
 
-To search for single transits in the light curve of a specific star, we fit
-three random forest models.
+{\item {\bf train} a classifier on simulated signals injected into a subset of
+the light curves sections,}
+
+{\item {\bf validate} the model on signals injected into a different subset of
+the data to estimate the precision of the results,}
+
+{\item {\bf test} the classifier by applying it to a final subset of the
+data---disjoint from the previous two sets---to predict the class
+(\texttt{transit} or \texttt{no transit}) of each light curve section, and}
+
+{\item iterate until the entire light curve has been classified.}
+
+\end{enumerate}
+This means that searching a single light curve involves training, validating,
+and testing at least 3 RF models.
+In practice, we find that it is sufficient to split the data (intelligently)
+into 3 disjoint subsets so that we need only train 3 classifiers for each
+star.
+
+A key assumption of this model is that the classes are sufficiently
+represented in feature space.
+In other words, the training set must span both of the classes.
+Given a large enough training set, this is not difficult for the
+\texttt{transit} class; we can simulate a transit for any combination of
+physical parameters.
+This is much more difficult for the \texttt{no transit} class.
+Since we don't have a generative model for the stellar and instrumental
+variability or other artifacts, we cannot simulate negative examples that
+cover the full space of possibilities.
+Instead we are using sections of real light curves as the \texttt{no transit}
+examples.
+This means that there are a finite number of samples available for training
+and validation, and if there is a qualitatively different signal in the test
+set that is not generated by a transit, the model is at risk of unpredictably
+misclassifying that section.
+This problem can be largely mitigated by careful splitting of the dataset---as
+described below---but there are inevitably some false signals that are not
+properly accounted for.
 
@@
 augment the training set with simulations injected into the reversed time
-series \dfmtodo{cite some examples of rotational invariance}.
+series \citep[for example][]{Dieleman:2015}.
 The training set also includes an equal number of negative examples---time
@@
 
-\paragraph{Features}
+\paragraph{Feature selection}
 
@@
 We have experimented briefly with this options finding similar performance.
-
-\paragraph{Train}
-
-\paragraph{Validate}
-
-\paragraph{Test}
 
@@
 
-\section{Parameter estimation}
+\section{Parameter estimation}\sectlabel{params}
 
@@
 
-\section{Population inference}
+\section{Prospects for population inference}\sectlabel{exopop}
 
@@
 
-\section{Results}
-
-\section{Discussion}
+\section{Discussion}\sectlabel{discussion}
 

### 2015-04-08 document/ms.tex
WORDS

@@
 
-\newcommand{\paper}{\textsl{Article}}
+\newcommand{\paper}{article}
 
@@
 
-\paragraph{Generate the training \& validation sets}
+The following \sectionname s detail the application of this search procedure
+from the training set simulations through to the candidate selection.
+These candidates are then vetted by hand although more robust methods should
+be possible as discussed in \sect{vetting}.
+Finally, \sect{features} explores alternative representations of the data or
+features.
 
-We need to train the classification model on simulated signals.
-To simulate these training and validation examples, we randomly select
-sections of 121 contiguous flux measurements and simulate the transit signal
+\subsection{Splitting the dataset}
+
+It is crucial that the model used to test for transits in a raw \kepler\
+light curve not be trained on the same data.
+We must split the light curve of each star into 3 disjoint sets.
+For the model to work well, we require that the signals induced by
+variability, noise, and other systematics be consistent between splits.
+It is, therefore, necessary that we assign the splits carefully.
+As discussed in \sect{data}, a light curve can be separated naturally into
+``sections'' of contiguous measurements; these are the base unit for splitting
+the dataset.
+For the typical \kepler\ target, this division is finer than month long
+chunks and there are about 100 sections for each light curve.
+Each light curve section is cut out of a specific ``quarter'' and each quarter
+was observed during a specific ``season''.
+
+These divisions are relevant to this discussion because the spacecraft
+pointing across a quarter was extremely precise and the photometric aperture
+is fixed to the same pixels for the full quarter.
+Therefore, the instrumentally-induced systematics tend to be qualitatively
+consistent on quarter-long time scales.
+Every three months, the \kepler\ spacecraft rolled by 90~degrees causing the
+stars to end up on a different detector every quarter.
+This means that while the astrophysical variability should be shared between
+quarters at some level, the instrumental effects can be very different.
+A year later, however, the spacecraft returned to the original pointing.
+As a result, the data quality is also similar for observations made in the
+same season.
+
+In order to take advantage of the natural structure of the observations, we
+try to evenly distribute observations from each quarter and season across the
+three sets.
+When this is not possible (with Quarter 0, for example), we randomly assign
+the section to a split.
+
+\subsection{Transit simulations}
+
+As mentioned previously, we train the RF classification models on a set
+simulated transit signals injected into real light curves and a set of light
+curve sections assumed to contain no transits.
+For each data split, we construct a set of 20,000 \texttt{transit} samples and
+an equal number of \texttt{no transit} examples.
+Each of these samples is generated by randomly selecting a section of 201
+contiguous flux measurements from the split.
+Since we expect most of the systematic variability to be symmetric in time, we
+augment the training set by reversing the time series for half of the samples.
+This is analogous to image processing methods that exploit rotation and
+translational symmetries \citep[for an example from astronomy
+see][]{Dieleman:2015}.
+
+To generate the \texttt{transit} examples, we simulate the transit signal
 induced by the physical orbit of a large planet.
-The specific distribution of simulated parameters is listed in \dfmtodo{some
+The specific distribution of simulation parameters is listed in \dfmtodo{some
 table}.
-In the simulations, we take limb darkening and integration time into account
-\dfmtodo{cite}.
-Since we expect most of the systematic variability to be time-reversible, we
-augment the training set with simulations injected into the reversed time
-series \citep[for example][]{Dieleman:2015}.
-The training set also includes an equal number of negative examples---time
-series chunks of the same length without a simulated transit injection.
-By virtue of the fact that we are specifically searching for single transits
-it is safe to assume that none of the negative samples from the other light
-curve sections will have no transits.
+In these simulations, we take limb darkening and integration time into
+account\footnote{\url{https://github.com/dfm/transit}}
+\citep{Mandel:2002, Kipping:2010}.
+For the purposes of this \paper, we only simulate circular orbits under the
+assumption that a single transit of a planet on an elliptical orbit would be
+nearly identical to a circular orbit at a different period.
 
-We also generate a validation set of simulated signals.
-This set is identical to the training set except it is simulated in sections
-of light curve that are not used for training.
-As discussed below, this set is used to determine the transit significance
-threshold required to achieve a pure sample.
+\subsection{Initial candidate detection}
 
-In practice, we only need to train three models on the three disjoint
-training sets and then for each model, we validate and test on both of the
-remaining splits.
+\subsection{Candidate vetting}\sectlabel{vetting}
 
-\paragraph{Feature selection}
+\subsection{Feature selection}\sectlabel{features}
 

### 2015-04-08 document/ms.tex
words about training

@@
 
-\newcommand{\BIC}{{\ensuremath{\mathrm{BIC}}}}
-\newcommand{\TIC}{{\ensuremath{\mathrm{TIC}}}}
 \newcommand{\T}{\ensuremath{\mathrm{T}}}
@@
 \newcommand{\rate}{{\ensuremath{\Gamma}}}
+\newcommand{\score}{{\ensuremath{S}}}
 
@@
 \citep[for example][]{Petigura:2013, Burke:2014}.
+Even the \project{QATS} algorithm \dfmtodo{cite} for finding quasiperiodic
+transits builds on much the same infrastructure.
 This means that there has never been a systematic search for single transits
@@
 
-The \kepler\ Mission measured photometry for about 190,000 stars at half-hour
-cadence for a baseline of over four years.
-We aim to search these time series for single transits of long-period planets
+The \kepler\ Mission measured photometric time series for about 190,000 stars
+at half-hour cadence for a baseline of over four years.
+We aim to search these light curves for single transits of long-period planets
 and single eclipses of binary stars.
@@
 2015-03-25.}.
-
-\paragraph{Terminology}
-
-Any remaining missing data points are filled in using linear interpolation
-resulting in sections of contiguous time series measurements with nearly
-uniform time sampling.
-This procedure yields about 100 \emph{light curve sections} for the typical
-\kepler\ target.
-
-As we discuss further below, a key assumption of our analysis is that the
-process generating any non-transit variability or noise in the light curve
-is stationary.
-
-Every three months, the \kepler\ spacecraft rolled 90~degrees to maintain its
-orientation with respect to the Sun.
-This means that each star landed on a different set of pixels each quarter
-and, therefore, the systematic signals caused by any specific spacecraft
-orientation won't be shared between neighboring quarters.
-A year later, however, the pointing would return to nearly the same setup and
-each star ends up back on many of the same pixels.
-This manifests itself in the light curves by causing the observations
-separated by a year to be qualitatively similar.
-
-For reasons that will become clear in \sect{search}, we split the light curve
-sections into 3 disjoint sets.
-We use these sets to run a train/validate/test procedure so the goal is to
-have representative samples in each set.
-Therefore, we attempt to split the sections intelligently; evenly
-distributing sections from the same quarter and season across the splits.
-When this is not possible, we randomly assign the section to a split.
 
@@
 
-\subsection{Splitting the dataset}
+\subsection{Splitting the dataset}\sectlabel{split}
 
@@
 As discussed in \sect{data}, a light curve can be separated naturally into
-``sections'' of contiguous measurements; these are the base unit for splitting
-the dataset.
+``sections'' of nearly contiguous measurements; these are the base unit for
+splitting the dataset.
 For the typical \kepler\ target, this division is finer than month long
@@
 
-\subsection{Initial candidate detection}
+The dataset will still have some missing or flagged fluxes.
+In order to account for these missing points, we linearly interpolate these
+values based on their neighbors.
+For consistency, we perform the interpolation on the training set \emph{after
+injecting the synthetic transit signals}.
+Before passing the light curve sections to the model at any stage, we
+normalize the section by its empirical median and take the logarithm of the
+fluxes.
+This normalization appears to yield better performance in some test cases but
+better performance might be achieved using optimized methods.
+This choice is discussed further in \sect{params}.
+
+\subsection{Training, validation, and testing}
+
+For each subset of the data, we train a RF classifier on the 40,000 training
+examples generated from the light curves in that split.
+The \texttt{RandomForestClassifier} implementation from \project{scikit-learn}
+has several tuning parameters that could be optimized using cross-validation
+but we find acceptable performance in most cases using fixed values.
+Specifically, we use a forest with 1000 trees by setting
+\texttt{num\_estimators = 1000}.
+We discuss this choice and the settings for other parameters in more detail in
+\sect{params}.
+
+Using this classifier, fit to one of the light curve subsets, we validate its
+performance on each set of simulations from the two other splits.
+This results in two precision--recall curves for the classifier.
+The \emph{precision} is an empirical measurement of the sample purity (or
+false positive rate) and \emph{recall} is a measurement of the completeness
+(the probability of detecting a true signal).
+Since the RF classifier scores each class and with a continuous value \score\
+between 0 and 1, both precision and recall can be tuned by changing the
+threshold value of \score\ above which the signal is considered a candidate.
+For each model--validation set pair, we ambitiously choose the threshold in
+order to obtain a precision of 100~percent.
+The result of this procedure applied to the three splits is three classifiers
+with two score thresholds each.
+
+Each of these six models has been fit using two splits so we then apply it to
+the raw light curves (without injected signals) from the remaining, untouched
+splits.
+This yields a \texttt{transit} class score as a function of transit time and
+any points above the detection threshold are passed along to the candidate
+selection procedure.
+
+At this point, there are two class predictions from two different models for
+every light curve section.
+Any section that is classified as \texttt{transit} by \emph{both models} is
+accepted as a single transit candidate.
+
+\dfmtodo{make a figure}
 

### 2015-04-08 document/ms.tex
words in ur FACE

@@
 \newcommand{\datareleaseurl}{{\url{http://bbq.dfm.io/ketu}}}
+
+% no more bad lines!
+\sloppy\sloppypar
 
@@
 
-\subsection{Training, validation, and testing}
+\subsection{Training, validation, and testing}\sectlabel{train}
 
@@
 
+While the search procedure described in the previous sections is quite robust
+to false alarms, single transit events are extremely rare (as discussed in
+\sect{est}) and because of substantial violations of the model assumptions,
+false signals continue to outnumber the true signals in this catalog of
+candidate transits.
+To mitigate this problem, we manually inspect the light curves of candidate
+signals.
+As future work, we expect to automate this procedure by fitting a physical
+transit model and comparing it to simple models of stellar variability and
+instrumental artifacts.
+For this \paper, however, the catalog of candidates is sufficiently small that
+manual inspection is tractable.
+As demonstrated in \sect{demo}, the most common misclassifications are caused
+by astrophysical variability but some remaining systematic effects are also
+incorrectly labeled as candidates.
+
 \subsection{Feature selection}\sectlabel{features}
@@
 extraction method is used to improve the performance of the procedure.
-For this specific problem, we find excellent performance using the 121
+For this specific problem, we find excellent performance using the 201
 normalized flux values as the features.
@@
 
-Many choices need to be made in building this classification model.
-These choices can be specified by a set of parameters that can be tuned the
-optimize the performance of the method.
-At this point, it's probably worth discussing how one might specifically
-measure the ``performance'' of a search for transits.
-The goal is, of course, to \emph{find transiting planets}.
-Therefore, we would like to develop a method that finds the most planets
-possible.
-This will, in general, trade off with the purity of the sample.
-For example, a method that returns every possible point the light curve as a
-planet candidate will be guaranteed to find every signal in the dataset---it
-will have excellent completeness or \emph{recall}---but almost every
-candidate will be false---the \emph{precision} is low.
-This is obviously not what we want.
-Instead, the more relevant metric is probably the recall at fixed (high)
-precision.
+Many choices need to be made in building this search procedure.
+Each of these choices can be specified by a set of parameters that can be
+tuned to optimize the method.
+In order to tune these parameters, we must decide on a quantitative
+measurement of the ``performance''.
+The goal is, of course, to \emph{robustly discover transiting planets}.
+In other words, the aim is a procedure that maximizes both \emph{recall} and
+\emph{precision}.
 
-Let's be clear about what we mean by the terms \emph{precision} and
-\emph{recall} in this context because they have specific definitions in the
-machine learning that will be useful in our discussion here.
-Recall is the probability, integrated across the full parameter space of
-interest that a true transit signal will be detected by the method.
-In astronomy, this quantity is generally called the completeness or the
-detection efficiency and it is routinely measured for transit surveys
-\dfmtodo{cite}.
+As discussed previously, recall is the probability, integrated across the full
+parameter space of interest that a true transit signal will be detected by the
+method.
+In astronomy, this quantity is generally called the completeness or detection
+efficiency and it is routinely measured for transit surveys \dfmtodo{cite}.
 On the other hand, precision is the probability that a positive classification
 will be true.
-In other words, for a given candidate that our pipeline spits out, the
-probability that it is a false alarm is given by one minus the precision.
-In astronomy, precision is generally hard or impossible to measure because we
-have no ground truth; we don't know that \emph{there is definitely no transit}
-at a given time in the light curve.
-However, with a few weak assumptions, we can, in practice, estimate the
-precision of our single transit search robustly.
+In astronomy, precision is generally hard to measure because we rarely have
+access to the ground truth.
+For this problem, correctly computing the recall is impossible because we
+never know that \emph{there is definitely no transit} at a given time in the
+light curve.
 
-\paragraph{Estimating the survey precision}
+What's more, it is not in general possible to maximize both recall and
+precision because transit signals are not completely separable from false
+positives.
+This means that, as the recall of the method improves, the false positive rate
+will also increase, reducing the precision.
+We must, therefore, choose a trade-off between recall and precision that
+represents our objective.
+The informal tradition in the transit search literature is to build a
+procedure that maximizes the recall at an extremely high ($\sim 100$~percent)
+fixed precision.
 
-There are two key assumptions that enter into our precision calculation.
+The main tuning parameters of the method are as follows:
+\begin{itemize}
+
+{\item \emph{the number of training and validation examples for each data
+split} --- The performance of most classification models improves drastically
+as the size of the training set increases but in this case we are limited by
+the number of \texttt{no transit} samples that are available since we have no
+generative model for the variability and systematics.
+For this \paper, we choose 20,000 positive \texttt{transit} samples per split
+and an equal number of negative examples.}
+
+{\item \emph{the range of physical parameters used to simulate the transit
+signals} --- The search will be most sensitive to transits with parameters
+spanned by the training set but training on too many low signal-to-noise
+examples in noisy light curves leads to decreased precision.
+The parameter ranges used for the demonstrations here are given in
+\dfmtodo{some table}.}
+
+{\item \emph{tuning parameters of the RF implementation} --- The
+\texttt{RandomForestClassifier} implementation has a few tuning parameters.
+The most important of these seems to be \texttt{num\_estimators}, the number
+of decision trees used in the forest.
+Increasing \texttt{num\_estimators} leads to substantial computational cost
+with diminishing returns on the search performance.
+Otherwise, there are a few parameters (for example, \texttt{max\_features},
+\texttt{min\_samples\_split}, and \texttt{min\_samples\_leaf}) that can be
+used to regularize the model but we have found that the performance is
+insensitive to these choices.
+As a trade-off between performance and computational cost, we set
+\texttt{num\_estimators = 1000} in all the examples shown in this \paper.}
+
+\end{itemize}
+In detail, the optimal set of decisions and parameter settings will be
+different for every target---and probably even for every permutation of the
+data splits.
+In practice, we find that the performance of the search is fairly insensitive
+to most of these choices so we choose parameters that seem to work well in
+most cases and leave optimization for future work.
+
+\paragraph{Estimating the precision}
+
+We estimate the precision of each RF classification model on the validation
+set as described in \sect{train}.
+As discussed in that \sectionname, we choose a target precision to
+100~percent and set the score threshold accordingly.
+This estimate is only applicable to the test set under two major assumptions.
 The first is that all transiting planets with more than one transit and a
@@
 baseline \dfmtodo{cite}.
-The second necessary assumption is less robust but it is required for a
-completely reliable measurement of the survey precision.
+The second assumption is not always valid so it makes this estimate of the
+precision only approximate and not completely reliable.
 This assumption is that the noise processes in the data are stationary.
 In other words, the transit-like noise signals in the training and validation
-sets must be ``similar'' to the signals in the target section.
-The PDC processing of the data successfully removes most of the
-instrument-induced signals with some exceptions that are discussed in
-\sect{demo}.
-Perhaps we make the further assumption that the stellar variability is
-also stationary.
-
-Under these assumptions, the precision of the search procedure is
-estimated using a set of injections.
-
-\paragraph{The parameters}
-
-\paragraph{Objective function}
+sets must be ``similar'' to the signals in the test section.
+This constraint is nearly satisfied when the PDC light curves are used
+(\sect{data}) and the data are split carefully (\sect{split}).
+As demonstrated by the mis-classifications shown in \sect{demo}, however, it
+is clear that violations to this rule do exist in the data and final vetting
+of the candidates must be applied using a physical understanding of the
+signals.
 
@@
 \paragraph{A discovery}
-
-\paragraph{Successes}
 

### 2015-04-08 document/ms.tex
candidates figure

@@
 
+As a demonstration of the feasibility of this method to search for single
+transit events, we selected 3500 bright, Sun-like stars based on the revised
+stellar parameters collected and measured for a recent \kepler\ data release
+\citep{Huber:2014}.
+The targets were selected in the parameter range
+\begin{itemize}
+
+\item effective temperature:
+        $4100\,\mathrm{K} < T_\mathrm{eff} < 6100\,\mathrm{K}$,
+
+\item surface gravity:  $4.0 < \log g < 4.9$, and
+
+\item \kepler\ magnitude: $15 > K_\mathrm{p} > 10$.
+
+\end{itemize}
+
+This search results in 596 candidate transits in the light curves of these
+3500 stars.
+The vast majority of these candidates are misclassified false positives and
+many of them are caused by astrophysical sources.
+To weed out known astrophysical sources, we cross-match this list against
+known eclipsing binary stars \citep{Matijevic:2012} and stars with substantial
+variability \citep{McQuillan:2014}.
+Removing these signals results in 273 candidates.
+
 \paragraph{A discovery}

### 2015-04-09 document/figures/params.py
parameter inference figure

@@ -1,0 +1,150 @@
+# -*- coding: utf-8 -*-
+
+from __future__ import division, print_function
+
+from plot_setup import COLORS
+from matplotlib import rcParams
+rcParams["font.size"] = 16
+
+import emcee
+import transit
+import peerless
+import numpy as np
+import pandas as pd
+from scipy.stats import beta
+import matplotlib.pyplot as pl
+
+kicid = 10602068
+
+# Load the data.
+kic = peerless.catalogs.KICatalog().df
+cands = pd.read_csv("3k_candidates.csv")
+cands = pd.merge(cands, kic, left_on="kicid", right_on="kepid", how="left",
+                 suffixes=["", "_kic"])
+
+# Pull out the target candidate.
+cand = cands[cands.kicid == kicid]
+period = float(cand.nn_period)
+rp = float(cand.nn_rp)
+b = float(cand.nn_b)
+t0 = float(cand.time)
+
+rstar = float(cand.radius)
+rstar_err1 = float(cand.radius_err1)
+rstar_err2 = float(cand.radius_err2)
+ln_rstar = np.log(rstar)
+ln_rstar_err = 0.5 * (np.log(rstar + rstar_err1) - np.log(rstar) +
+                      np.log(rstar) - np.log(rstar + rstar_err2))
+
+mstar = float(cand.mass)
+mstar_err1 = float(cand.mass_err1)
+mstar_err2 = float(cand.mass_err2)
+ln_mstar = np.log(mstar)
+ln_mstar_err = 0.5 * (np.log(mstar + mstar_err1) - np.log(mstar) +
+                      np.log(mstar) - np.log(mstar + mstar_err2))
+
+# Set up the model.
+system = transit.System(transit.Central(mass=mstar, radius=rstar))
+system.add_body(transit.Body(
+    period=period, r=1.3*rp, b=b, t0=t0,
+))
+
+# Load the light curves.
+lcs = peerless.data.load_light_curves_for_kic(kicid, min_break=10)
+texp = lcs[0].texp
+t = np.concatenate([lc.time for lc in lcs])
+f = np.concatenate([lc.flux for lc in lcs])
+fe = np.concatenate([lc.yerr + np.zeros_like(lc.time) for lc in lcs])
+
+# Find the minimum allowed period.
+m = np.isfinite(t)
[…]

### 2015-04-09 document/ms.tex
parameter inference figure
more samples and words

@@
 Removing these signals results in 273 candidates.
-
-\paragraph{A discovery}
+Of these candidates only one (KIC 10602068) is a convincing transit and the
+others all appear to be caused by systematic effects, instrumental or
+astrophysical.
+\Fig{candidates} shows some representative candidate signals from this final
+list.
 
@@
 
-\section{Parameter estimation}\sectlabel{params}
+\begin{figure}[p]
+\begin{center}
+\includegraphics[width=0.5\textwidth]{figures/candidates.pdf}
+\end{center}
+\caption{%
+\figlabel{candidates}}
+\end{figure}
 
-Even though only one transit is observed, it is still possible to estimate the
-orbital period of these planet candidates using independent constraints on the
-stellar properties.
+\section{KIC 10602068: A discovery}\sectlabel{params}
+
+In the 3500 light curves we searched for this \paper, we discovered one
+convincing single transit signal at $830.80921\pm0.00015$~KBJD in the light
+curve of the 14.9~Kep-mag G-dwarf KIC 10602068.
+Despite the fact that this is a very large signal, its discovery has never
+been reported.
+Given the estimate of $\sim 60$ detectable single transits in the full
+\kepler\ archival dataset, we expect about one discovery in 3500 light curves.
+
+Even though only one transit is observed, it is still possible to place
+constraints on the physical properties---even the orbital period---of this
+transiting body.
 This technique is similar in spirit to the ``photoeccentric effect''
 \citep{Dawson:2012} and ``asterodensity profiling'' \citep{Kipping:2012}.
-The fundamental principle is that, the transit duration is a measurement of
+The fundamental principle is that the transit duration is a measurement of
 the instantaneous velocity of the planetary motion and this yields a
@@
 stellar density and a prior on the eccentricity of the orbit.
+
+The \citet{Huber:2014} parameters for this star place it as a G-dwarf with a
+radius of $\sim 0.9\,R_\odot$ $2.02 \pm 0.25\,R_\mathrm{J}$.
 

### 2015-04-09 document/figures/params.py

@@ -6,6 +6,7 @@ from plot_setup import COLORS
 from matplotlib import rcParams
 rcParams["font.size"] = 16
 
+import h5py
 import emcee
 import transit
 import peerless
@@ -33,15 +34,15 @@ rstar = float(cand.radius)
 rstar_err1 = float(cand.radius_err1)
 rstar_err2 = float(cand.radius_err2)
 ln_rstar = np.log(rstar)
-ln_rstar_err = 0.5 * (np.log(rstar + rstar_err1) - np.log(rstar) +
-                      np.log(rstar) - np.log(rstar + rstar_err2))
+ln_rstar_err = max(np.log(rstar + rstar_err1) - np.log(rstar),
+                   np.log(rstar) - np.log(rstar + rstar_err2))
 
 mstar = float(cand.mass)
 mstar_err1 = float(cand.mass_err1)
 mstar_err2 = float(cand.mass_err2)
 ln_mstar = np.log(mstar)
-ln_mstar_err = 0.5 * (np.log(mstar + mstar_err1) - np.log(mstar) +
-                      np.log(mstar) - np.log(mstar + mstar_err2))
+ln_mstar_err = max(np.log(mstar + mstar_err1) - np.log(mstar),
+                   np.log(mstar) - np.log(mstar + mstar_err2))
 
 # Set up the model.
 system = transit.System(transit.Central(mass=mstar, radius=rstar))
@@ -138,6 +139,14 @@ ensemble = emcee.Ensemble(TransitWalker(), coords)
 print("Burn-in 2")
 sampler.reset()
 ensemble = sampler.run(ensemble, 5000)
+
+print("Production")
+sampler.reset()
+ensemble = sampler.run(ensemble, 50000)
+
+with h5py.File("params.h5", "w") as fh:
+    fh.create_dataset("coords", data=sampler.get_coords())
+    fh.create_dataset("lnprob", data=sampler.get_lnprob())
 
 # Find best sample and plot.
 samples = sampler.get_coords(flat=True)

### 2015-04-09 document/ms.tex
physiscal params plots

@@
 \newcommand{\tess}{\project{TESS}}
+\newcommand{\plato}{\project{PLATO}}
 \newcommand{\jwst}{\project{JWST}}
@@
 
-Many of the most dynamically interesting planets will be on orbits longer
-than the baseline of existing transit surveys (\kepler, \KT).
-Future surveys (\tess, PLATO?) will have such a short continuous coverage that
+Many of the most dynamically important planets have orbits longer than
+the baseline of existing transit surveys (\kepler, \KT).
+Future surveys (\tess, \plato) will have such a short continuous coverage that
 even habitable zone planets around M-dwarfs will only present a single transit
@@
 method.
-In \sectionname s~\sectref{params} and~\sectref{exopop}, we describe the
-parameter estimation that is possible given a single transit and outline the
-prospects for exoplanet population inference given a catalog of single transit
-discoveries.
+In \sectionname s~\sectref{params} we describe the parameter estimation that
+is possible given a single transit.
+
+% and outline the prospects for exoplanet
+% population inference given a catalog of single transit discoveries.
 
@@
 
-\section{Prospects for population inference}\sectlabel{exopop}
+% \section{Prospects for population inference}\sectlabel{exopop}
 
-Based on our single transit discoveries, we now want to place a limit on
-the occurrence rate of long-period planets.
-Since we only have one discovery thus far, we'll make the simplifying
-assumption that the rate is flat in log-period and log-radius in the range
-$1000\,\mathrm{d} < \period < 5000\,\mathrm{d}$ and $5\,R_\odot <
-20\,R_\odot$.
-For this distribution, \citet{Foreman-Mackey:2014} derived the analytic
-maximum likelihood result
-\begin{eqnarray}
-\rate &=& \frac{N_\mathrm{obs}}{\int Q(w)\dd w}
-\end{eqnarray}
-where $\rate$ is the occurrence rate per natural logarithm in period and
-radius, $N_\mathrm{obs}$ is the number of detections, and the integral is over
-the completeness measurements for every star that has been searched.
-If we make the simplifying assumption that the detectability of a transit
-depends on period only through Equations~(\eqref{q-geom})
-and~(\eqref{q-time}), then this integral becomes
-\begin{eqnarray}
-\int Q(w)\dd w &=& \sum_{k=1}^K
-    \left( \frac{4\,\pi^2}{G\,M_k} \right)^{1/3} \, R_k \, T_k \, Q_k \,
-    \int \period^{-8/3}\,\rp^{-1} \dd\rp\dd\period \\
- &=& \sum_{k=1}^K
-    \left( \frac{4\,\pi^2}{G\,M_k} \right)^{1/3} \, R_k \, T_k \, Q_k \,
-    \ln \left(\frac{\rp_\mathrm{max}}{\rp_\mathrm{min}}\right)
-    \frac{3}{5} \,
-    \left[{\period_\mathrm{min}}^{-5/3} - {\period_\mathrm{max}}^{-5/3}\right]
-\end{eqnarray}
-where the sum is over all the targeted stars.
+% Based on our single transit discoveries, we now want to place a limit on
+% the occurrence rate of long-period planets.
+% Since we only have one discovery thus far, we'll make the simplifying
+% assumption that the rate is flat in log-period and log-radius in the range
+% $1000\,\mathrm{d} < \period < 5000\,\mathrm{d}$ and $5\,R_\odot <
+% 20\,R_\odot$.
+% For this distribution, \citet{Foreman-Mackey:2014} derived the analytic
+% maximum likelihood result
+% \begin{eqnarray}
+% \rate &=& \frac{N_\mathrm{obs}}{\int Q(w)\dd w}
+% \end{eqnarray}
+% where $\rate$ is the occurrence rate per natural logarithm in period and
+% radius, $N_\mathrm{obs}$ is the number of detections, and the integral is over
+% the completeness measurements for every star that has been searched.
+% If we make the simplifying assumption that the detectability of a transit
+% depends on period only through Equations~(\eqref{q-geom})
+% and~(\eqref{q-time}), then this integral becomes
+% \begin{eqnarray}
+% \int Q(w)\dd w &=& \sum_{k=1}^K
+%     \left( \frac{4\,\pi^2}{G\,M_k} \right)^{1/3} \, R_k \, T_k \, Q_k \,
+%     \int \period^{-8/3}\,\rp^{-1} \dd\rp\dd\period \\
+%  &=& \sum_{k=1}^K
+%     \left( \frac{4\,\pi^2}{G\,M_k} \right)^{1/3} \, R_k \, T_k \, Q_k \,
+%     \ln \left(\frac{\rp_\mathrm{max}}{\rp_\mathrm{min}}\right)
+%     \frac{3}{5} \,
+%     \left[{\period_\mathrm{min}}^{-5/3} - {\period_\mathrm{max}}^{-5/3}\right]
+% \end{eqnarray}
+% where the sum is over all the targeted stars.
 

### 2015-04-09 document/figures/plot_params.py

@@ -1,0 +1,144 @@
+# -*- coding: utf-8 -*-
+
+from __future__ import division, print_function
+
+from plot_setup import COLORS
+from matplotlib import rcParams
+rcParams["font.size"] = 16
+
+import h5py
+import transit
+import triangle
+import peerless
+import numpy as np
+import pandas as pd
+from scipy.stats import beta
+import matplotlib.pyplot as pl
+
+
+with h5py.File("params.h5", "r") as fh:
+    samples = fh["coords"][...]
+    lnprob = fh["lnprob"][...]
+
+pl.clf()
+pl.plot(samples[:, :, 1], alpha=0.5)
+pl.savefig("time.png")
+
+
+flat = samples[::10].reshape((-1, samples.shape[-1]))
+
+e = np.sum(flat[:, -2:]**2, axis=1)
+pl.clf()
+pl.hist(e, 40, normed=True)
+x = np.linspace(1e-5, 0.8, 500)
+pl.plot(x, beta.pdf(x, 1.12, 3.09))
+pl.savefig("blah.png")
+
+
+r_star = np.exp(flat[:, 1])
+r_p = np.exp(flat[:, 5]) / 0.0995
+
+fig = triangle.corner(np.vstack([r_p, np.log10(np.exp(flat[:, 6])),
+                                 flat[:, 8], e]).T,
+                      levels=[0.68, 0.95],
+                      smooth=1.0, smooth1d=1.0,
+                      fill_contours=True, plot_datapoints=False,
+                      labels=["$R_p / R_\mathrm{J}$",
+                              r"$\log_{10}\,P/\mathrm{day}$", "$b$", "$e$"])
+fig.savefig("corner.pdf")
+
+assert 0
+
+# Compute the radius.
+r_p = flat[:, 1]  # np.exp(flat[:, 5]) / 0.0995
+pl.hist(r_p)
+pl.savefig("blah.png")
+q = triangle.quantile(r_p, [0.16, 0.5, 0.84])
+print(q[0], np.diff(q))
+
+kicid = 10602068
+
+# Load the data.
+kic = peerless.catalogs.KICatalog().df
+cands = pd.read_csv("3k_candidates.csv")
+cands = pd.merge(cands, kic, left_on="kicid", right_on="kepid", how="left",
+                 suffixes=["", "_kic"])
+
+# Pull out the target candidate.
+cand = cands[cands.kicid == kicid]
[…]

### 2015-04-09 document/figures/params.py
moar steps

@@ -6,6 +6,7 @@ from plot_setup import COLORS
 from matplotlib import rcParams
 rcParams["font.size"] = 16
 
+import sys
 import h5py
 import emcee
 import transit
@@ -34,15 +35,15 @@ rstar = float(cand.radius)
 rstar_err1 = float(cand.radius_err1)
 rstar_err2 = float(cand.radius_err2)
 ln_rstar = np.log(rstar)
-ln_rstar_err = max(np.log(rstar + rstar_err1) - np.log(rstar),
-                   np.log(rstar) - np.log(rstar + rstar_err2))
+ln_rstar_err = np.mean([np.log(rstar + rstar_err1) - np.log(rstar),
+                        np.log(rstar) - np.log(rstar + rstar_err2)])
 
 mstar = float(cand.mass)
 mstar_err1 = float(cand.mass_err1)
 mstar_err2 = float(cand.mass_err2)
 ln_mstar = np.log(mstar)
-ln_mstar_err = max(np.log(mstar + mstar_err1) - np.log(mstar),
-                   np.log(mstar) - np.log(mstar + mstar_err2))
+ln_mstar_err = np.mean([np.log(mstar + mstar_err1) - np.log(mstar),
+                        np.log(mstar) - np.log(mstar + mstar_err2)])
 
 # Set up the model.
 system = transit.System(transit.Central(mass=mstar, radius=rstar))
@@ -87,7 +88,7 @@ class TransitWalker(emcee.BaseWalker):
             return -np.inf
 
         lp += beta.logpdf(e, 1.12, 3.09)
-        return lp
+        return lp  # + lnp
 
     def lnlikefn(self, p):
         lnfs, lnrs, lnms, q1, q2 = p[:5]
@@ -119,30 +120,38 @@ class TransitWalker(emcee.BaseWalker):
 p0 = np.array([0.0, ln_rstar, ln_mstar, 0.5, 0.5, np.log(rp), np.log(period),
                t0, b, 0.0, 0.0])
 nwalkers, ndim = 32, len(p0)
-coords = p0 + 1e-8 * np.random.randn(nwalkers, ndim)
-ensemble = emcee.Ensemble(TransitWalker(), coords)
-assert np.all(np.isfinite(ensemble.lnprob))
 sampler = emcee.Sampler()
 
-print("Burn-in 1")
-ensemble = sampler.run(ensemble, 2000)
+if "restart" in sys.argv:
[…]

### 2015-04-09 peerless/model.py

@@ -398,7 +398,6 @@ class Model(object):
         return self
 
     def normalize_inputs(self, X):
-        # X /= np.median(X, axis=1)[:, None]
         if self.wavelet is None:
             t = np.arange(X.shape[1])
             for i, x in enumerate(X):
@@ -406,6 +405,8 @@ class Model(object):
                 x[~m] = np.interp(t[~m], t[m], x[m])
                 X[i, :] = np.log(x) - np.log(np.median(x))
         else:
+            assert False, "WAVELETS ARE BROKEN"
+            X /= np.median(X, axis=1)[:, None]
             for i, x in enumerate(X):
                 X[i, :] = np.concatenate(pywt.dwt(x - 1.0, self.wavelet))[:-1]
         return X

### 2015-04-09 document/ms.tex
physical parameters plot and abstract edits

@@
 
-Many of the most dynamically important planets have orbits longer than
-the baseline of existing transit surveys (\kepler, \KT).
-Future surveys (\tess, \plato) will have such a short continuous coverage that
-even habitable zone planets around M-dwarfs will only present a single transit
-signal.
-Searches for these transiting planets are plagued by false
+Many of the most dynamically important planets have orbits longer than the
+baseline of existing transit surveys (\kepler, \KT).
+Future surveys (\tess, \plato) are planned to have shorter continuous coverage
+that even habitable zone planets around M-dwarfs will only present a single
+transit event.
+Searches for these long-period transiting planets are plagued by false
 signals---especially when pushed to low signal-to-noise---and statistical
@@
 the machine learning literature.
-For each month of photometry, we train a random forest classifier on a large
-number of simulated signals injected into the photometry of the same star at
-different times.
-Then, the model's prediction as a function of transit time is evaluated and
-times above a threshold probability---chosen for each star to yield a sample
-with $\sim99$~percent purity---are given as candidate transits.
-Each candidate must then pass a final round of vetting including BLAH BLAH
-BLAH.
-Applied to every light curve in the \kepler\ archive this method yields a
-list of XXXX long-period transiting planet candidates.
-Using an informative prior on their eccentricities, we derive weak constraints
-on the orbital periods of the candidates and demonstrate that this puts an
-upper limit of ZZZZ on the occurrence rate of these planets.
+For each star, we train several random forest classifiers on simulated signals
+injected into different subsets of the data.
+These models are evaluated on the raw photometry to assign a transit
+probability at each time.
+As a proof of concept, we apply this method to 3500 light curves from the
+\kepler\ archival dataset and discover a previously unknown single transit
+candidate.
+Assuming a bound Keplerian orbit and using an informative prior on the
+eccentricity, we measure a radius of $2\,R_\mathrm{J}$ and derive a weak
+constraint on the orbital period.
 
@@
 In the 3500 light curves we searched for this \paper, we discovered one
-convincing single transit signal at $830.80921\pm0.00015$~KBJD in the light
+convincing single transit signal at $830.8093\pm0.0002$~KBJD in the light
 curve of the 14.9~Kep-mag G-dwarf KIC 10602068.
@@
 The \citet{Huber:2014} parameters for this star place it as a G-dwarf with a
-radius of $\sim 0.9\,R_\odot$ $2.02 \pm 0.25\,R_\mathrm{J}$.
+radius of $\sim 0.9\,R_\odot$
+$2.1 \pm 0.4\,R_\mathrm{J}$.
 
@@
 Beta function prior on the eccentricity \citep{Kipping:2013a}.
+
+\begin{figure}[p]
+\begin{center}
+\includegraphics[width=\textwidth]{figures/corner.pdf}
+\end{center}
+\caption{%
+Posterior constraints on the physical parameters of the body transiting KIC
+10602068 assuming a bound Keplerian orbit.
+\figlabel{corner}}
+\end{figure}
 

### 2015-04-09 document/figures/plot_params.py

@@ -12,7 +12,6 @@ import triangle
 import peerless
 import numpy as np
 import pandas as pd
-from scipy.stats import beta
 import matplotlib.pyplot as pl
 
 
@@ -28,23 +27,26 @@ pl.savefig("time.png")
 flat = samples[::10].reshape((-1, samples.shape[-1]))
 
 e = np.sum(flat[:, -2:]**2, axis=1)
-pl.clf()
-pl.hist(e, 40, normed=True)
-x = np.linspace(1e-5, 0.8, 500)
-pl.plot(x, beta.pdf(x, 1.12, 3.09))
-pl.savefig("blah.png")
-
-
 r_star = np.exp(flat[:, 1])
 r_p = np.exp(flat[:, 5]) / 0.0995
+log10p = np.log10(np.exp(flat[:, 6]))
+b = flat[:, 8]
+t0 = flat[:, 7]
+t00 = np.round(np.median(t0) * 10) * 0.1
+phys = np.vstack([r_p, log10p, (t0-t00)*24, b, e]).T
+for p in np.concatenate((phys.T, [t0]), axis=0):
+    q = triangle.quantile(p, [0.16, 0.5, 0.84])
+    print(q[1], np.diff(q))
 
-fig = triangle.corner(np.vstack([r_p, np.log10(np.exp(flat[:, 6])),
-                                 flat[:, 8], e]).T,
+fig = triangle.corner(phys,
                       levels=[0.68, 0.95],
                       smooth=1.0, smooth1d=1.0,
                       fill_contours=True, plot_datapoints=False,
-                      labels=["$R_p / R_\mathrm{J}$",
-                              r"$\log_{10}\,P/\mathrm{day}$", "$b$", "$e$"])
+                      labels=["$R_p\,[R_\mathrm{J}]$",
+                              r"$\log_{10}\,P/\mathrm{day}$",
+                              (r"$t_0 - {0:.1f}\,\mathrm{{KBJD}}\,"
+                               "[\mathrm{{hr}}]$").format(t00),
+                              "$b$", "$e$"])
 fig.savefig("corner.pdf")
 
 assert 0

### 2015-04-09 document/ms.tex
WORDS IN UR FACE TEHSIS

@@
 \newcommand{\license}{MIT License}
-\newcommand{\projectname}{\project{ketu}}
 
@@
 Despite the great success of the \kepler\ Mission with thousands of planet
-discoveries \dfmtodo{cite}, current methods for exoplanet discoveries are
+discoveries \citep{Burke:2014}, current methods for exoplanet discoveries are
 currently limited in the range of orbital periods that can be studied.
 Specifically, the standard transit search procedures only discover signals
-with at least three observed transits \dfmtodo{cite Jenkins, Petigura, \etc}.
+with at least three observed transits \citep[for example][]{Petigura:2013,
+Burke:2014}.
 For \kepler, with a baseline of about four years, this sets an upper limit on
@@
 It is possible to discover long-period planets like this using targeted radial
-velocity (RV) surveys \dfmtodo{cite} but the cost of implementing a systematic
-RV search is substantially higher than searching the existing and forthcoming
-photometric data for single transits.
+velocity (RV) surveys \citep[for example][]{Butler:2006, Knutson:2014} but the
+cost of implementing a systematic RV search is substantially higher than
+searching the existing and forthcoming photometric data for single transits.
 
@@
 the likelihood of an approximate transit model is computed on a grid in the
-physical parameters \dfmtodo{cite}.
+physical parameters \citep[\kepler\ Data Processing
+Handbook\footnote{\url{https://archive.stsci.edu/kepler/manuals/KSCI-19081-001_Data_Processing_Handbook.pdf}};][]{%
+Petigura:2013, Huang:2013, Dressing:2015, Foreman-Mackey:2015}.
 Using these methods, and substantial hand-curation, some long-period
@@
 \citep[for example][]{Petigura:2013, Burke:2014}.
-Even the \project{QATS} algorithm \dfmtodo{cite} for finding quasiperiodic
-transits builds on much the same infrastructure.
+Even the \project{QATS} algorithm \citep{Carter:2013} for finding
+quasiperiodic transits builds on much the same infrastructure.
 This means that there has never been a systematic search for single transits
@@
 Automated classification processes have been hugely successful in the machine
-learning literature when applied to the right datasets \dfmtodo{cite some
-things}.
+learning literature.
+% when applied to the right datasets \dfmtodo{cite some things}.
 Many astronomical problems can't be naturally solved by the standard machine
@@
 Assuming the stellar parameters provided by the NASA Exoplanet
-Archive\footnote{\dfmtodo{URL for kepler stellar table; downloaded on SOME
-DATE.}} \dfmtodo{cite Huber} and approximating the stellar noise using the
-15-hour CDPP \dfmtodo{cite CDPP}, \dfmtodo{some figure} shows the extrapolated
-number of transiting planets with $1500\,\mathrm{d} < \period <
-5000\,\mathrm{d}$ based on the \citet{Dong:2013} power-law model.
+Archive\footnote{We downloaded the \texttt{q1\_q16\_stellar} table from
+\url{http://exoplanetarchive.ipac.caltech.edu/} on 2015-04-03.}
+\citep{Huber:2014} and approximating the stellar noise using the 15-hour CDPP
+\citep{Christiansen:2012}, \fig{predict} shows the extrapolated number of
+transiting planets with $1500\,\mathrm{d} < \period < 5000\,\mathrm{d}$ based
+on the \citet{Dong:2013} power-law model.
 For a detection threshold $f\sim10$, the expected number of single transit
@@
 targeted for nearly the full baseline instead of the original 100,000.
-\dfmtodo{Explain other reasons.}
+\dfmtodo{Explain the other reasons.}
 
@@
 It has also been applied with great success in astronomy \citep[for
-example]{Richards:2011, Richards:2012} \dfmtodo{others}.
+example][]{Richards:2011, Richards:2012, Jenkins:2014}.
 The RF model works by fitting an ensemble of decision trees to randomly
@@
 induced by the physical orbit of a large planet.
-The specific distribution of simulation parameters is listed in \dfmtodo{some
-table}.
+The specific distribution of simulation parameters is listed in \tab{params}.
 In these simulations, we take limb darkening and integration time into
@@
 This choice is discussed further in \sect{params}.
+
+\begin{table}[htbp]
+\begin{center}
+\begin{tabular}{lcc}
+\toprule
+Parameter & Units & Distribution \\
+\midrule
+
+limb darkening parameters $q_1$ and $q_2$ & --- & $q \sim U(0,\,1)$ \\
+orbital period \period & days & $\ln \period \sim U(\ln 1500,\,\ln 5000)$ \\
+reference transit time $\delta t$ & days & $\delta t \sim U(-0.15,\,0.15)$ \\
+planet radius \rp & $R_\oplus$ & $\ln \rp \sim U(\ln 5,\,\ln 20)$ \\
+impact parameter $b$ & --- & $b \sim U(0,\,1)$ \\
+
+\bottomrule
+\end{tabular}
+\end{center}
+\caption{%
+The distribution of physical parameters for the injected signals.
+The limb darkening parameterization is given by \citet{Kipping:2013}.
+\tablabel{params}}
+\end{table}
 
@@
 
-\dfmtodo{make a figure}
+% \dfmtodo{make a figure}
 
@@
 Alternatively, the spectrogram of the fluxes in a larger window.
-We have experimented briefly with this options finding similar performance.
+We have experimented briefly with these options but find similar performance
+on the cases that we tested.
 
@@
 In astronomy, this quantity is generally called the completeness or detection
-efficiency and it is routinely measured for transit surveys \dfmtodo{cite}.
+efficiency and it is routinely measured for transit surveys
+\citep{Petigura:2013, Dressing:2015, Foreman-Mackey:2015}.
 On the other hand, precision is the probability that a positive classification
@@
 The parameter ranges used for the demonstrations here are given in
-\dfmtodo{some table}.}
+\tab{params}.}
 
@@
 large signal-to-noise ratio have been previously discovered by one of the many
-transit searches applied the \kepler\ dataset \dfmtodo{cite}.
+transit searches applied the \kepler\ dataset \citep{Burke:2014}.
 This is a safe assumption because, for large planets, these surveys are all
 largely complete out to periods yielding only 2 or 3 transits in the \kepler\
-baseline \dfmtodo{cite}.
+baseline \citep[for example][]{Petigura:2013}.
 The second assumption is not always valid so it makes this estimate of the
@@
 
+\dfmtodo{Add some discussion of the failures and make suggestions for better
+vetting techniques.}
+
 \begin{figure}[p]
@@
 \caption{%
+Some representative light curve sections that were labeled as candidates by
+the single transit search.
+The light curve in the top-left panel is a convincing transit signal but the
+other panels all appear to be caused by stellar variability or instrumental
+effects.
 \figlabel{candidates}}
@@
 Given the estimate of $\sim 60$ detectable single transits in the full
-\kepler\ archival dataset, we expect about one discovery in 3500 light curves.
-
-Even though only one transit is observed, it is still possible to place
-constraints on the physical properties---even the orbital period---of this
-transiting body.
+\kepler\ archival dataset, we do expect about one discovery in 3500 light
+curves.
+
+Even though only one transit is observed, if we assume that the transit is
+caused by a body on a Keplerian orbit around the host star, we can place
+constraints on the physical properties---even the orbital period---of the
+transiting candidate.
 This technique is similar in spirit to the ``photoeccentric effect''
@@
 
-The \citet{Huber:2014} parameters for this star place it as a G-dwarf with a
-radius of $\sim 0.9\,R_\odot$
-$2.1 \pm 0.4\,R_\mathrm{J}$.
-
-In practice, we directly model the light curve as being generated by a planet
-on an eccentric Keplerian orbit transiting a limb darkened star and
-marginalize over all the orbital elements and physical parameters.
-We take limb darkening and the finite exposure time into account
-\citep{Mandel:2002, Kipping:2010, Kipping:2013} and use an empirical
-Beta function prior on the eccentricity \citep{Kipping:2013a}.
+The photometrically derived physical properties for this star place it as a
+G-dwarf with a mass and radius of about 90~percent Solar \citep{Huber:2014}.
+Using these constraints and a beta function prior on the eccentricity of the
+orbit \citep{Kipping:2013a}, we run Markov Chain Monte Carlo
+\citep{Foreman-Mackey:2013} to sample the posterior probability for the
+physical parameters of the system.
+In this analysis, we take limb darkening and the finite exposure time into
+account \citep{Mandel:2002, Kipping:2010, Kipping:2013}.
+The results of this chain marginalized into the relevant physical dimensions
+are shown in \fig{corner}.
+The radius of the transiting body is measured to be $2.1 \pm
+0.4\,R_\mathrm{J}$.
+The period is very weakly constrained above a lower limit of
+$760\,\mathrm{days}$---set by the fact that a second transit is not
+detected---with 68~percent of the posterior mass in the range $760\,\mathrm{d}
+< \period < 1347\,\mathrm{d}$.
+
+Given the large radius of this candidate, it is probably stellar in nature
+instead of planetary but this could be easily confirmed using radial velocity
+follow-up.
 
@@
 
+The discovery and characterization of transiting planets based on a single
+transit event is crucial for the future of transiting exoplanet surveys.
+Many of the most dynamically influential planets---like Jupiter in our Solar
+system---exhibit only a single transit in the full observational baseline of
+the \kepler.
+This will become even more of a problem as upcoming surveys move to shorter
+contiguous observations.
+For example, the \tess\ Mission is planned to get full-sky coverage at
+half-hour cadence but most of the sky will only be targeted for a month.
+This means that even habitable zone planets orbiting cool stars will transit
+their host \emph{at most once in the entire lifetime of the Mission}!
+
+To date, no methods exist for systematically and robustly discovering single
+transit events based on large photometric surveys.
+In this \paper, we present a novel and conceptually unique solution to this
+problem drawing on machine learning methods for supervised classification.
+This method has immense potential because it can be designed to be very robust
+to false positives and it can exploit the detailed shape of physical transits.
+
+Despite the fact that single transits are unlikely even if these long-period
+planets are intrinsically common, we estimate that $\sim 60$ events should be
+detectable in the \kepler\ archival dataset by extrapolating recent models of
+planet occurrence rates and taking selection effects into account.
+When applied to 3500 light curves from the \kepler\ dataset, this method
+recovers one previously unknown single transit event at
+$830.8093\pm0.0002$~KBJD in the light curve of KIC 10602068.
+This rate is consistent with the predicted yield of 60 events in the full
+dataset of 190,000 light curves.
+
+Assuming a bound Keplerian orbit, we place constraints on the physical
+properties of this transit candidate KIC 10602068.01.
+Using photometrically derived stellar properties, we find that this candidate
+has a radius of $2.1 \pm 0.4\,R_\mathrm{J}$ placing it as a very large planet
+or brown dwarf or a small star.
+
+This method for transit search is built using supervised classification and
+its performance relies on several strong assumptions about the datasets and
+these assumptions are sometimes violated leading to some transit-like signals
+that appear to be caused by noise to be misclassified as transits.
+The most severe assumption is that the noise properties of the data are
+stationary.
+In other words, we assume that variability in one subset of a light curve is
+completely spanned by the variability in the other sections.
+This assumption is, in general, false because the stochastic processes that
+cause stellar variability are complicated and non-stationary and the detector
+is plagued by non-negligible catastrophic changes in sensitivity and response.
+We attempt to mitigate this problem by using light curves that have been
+preprocessed to remove most of the instrumental effects and carefully dividing
+the data into subsets but some false positives are still incorrectly
+identified as candidates.
+
+One possible method for reducing the false positive rate would be to augment
+the training dataset using heuristic simulations of common false positives or
+the light curves of ``similar'' stars.
+Another option is to recognize that this search drastically reduces the
+parameter space requiring evaluation and comparing the predictive power of
+a transit model to other heuristic models including stellar variability or
+instrumental effects.
+
 \acknowledgments

### 2015-04-09 document/figures/plot_params.py

@@ -38,6 +38,8 @@ for p in np.concatenate((phys.T, [t0]), axis=0):
     q = triangle.quantile(p, [0.16, 0.5, 0.84])
     print(q[1], np.diff(q))
 
+print(10 ** (triangle.quantile(log10p, [0.68])))
+
 fig = triangle.corner(phys,
                       levels=[0.68, 0.95],
                       smooth=1.0, smooth1d=1.0,

### 2015-05-05 document/ms.tex
refs

@@
 Despite the great success of the \kepler\ Mission with thousands of planet
-discoveries \citep{Burke:2014}, current methods for exoplanet discoveries are
-currently limited in the range of orbital periods that can be studied.
+discoveries \citep{Burke:2014, Rowe:2015}, current methods for exoplanet
+discoveries are currently limited in the range of orbital periods that can be
+studied.
 Specifically, the standard transit search procedures only discover signals
 with at least three observed transits \citep[for example][]{Petigura:2013,
-Burke:2014}.
+Burke:2014, Rowe:2015}.
 For \kepler, with a baseline of about four years, this sets an upper limit on
@@
 selection criteria where candidates are required to have multiple transits
-\citep[for example][]{Petigura:2013, Burke:2014}.
+\citep[for example][]{Petigura:2013, Burke:2014, Rowe:2015}.
 Even the \project{QATS} algorithm \citep{Carter:2013} for finding
@@
 large signal-to-noise ratio have been previously discovered by one of the many
-transit searches applied the \kepler\ dataset \citep{Burke:2014}.
+transit searches applied the \kepler\ dataset \citep{Burke:2014, Rowe:2015}.
 This is a safe assumption because, for large planets, these surveys are all

### 2015-05-05 peerless/vetting.py
adding model comparison code

@@ -1,0 +1,205 @@
+# -*- coding: utf-8 -*-
+
+from __future__ import division, print_function
+
+__all__ = ["fit_gp", "fit_box", "fit_step", "fit_transit"]
+
+from itertools import product
+
+import numpy as np
+from scipy.ndimage.filters import gaussian_filter
+from scipy.optimize import minimize, OptimizeResult
+
+import transit
+import george
+from george.kernels import Matern32Kernel
+
+
+def fit_gp(x, y, yerr):
+    # Remove missing data.
+    m = np.isfinite(y) & np.isfinite(y)
+    ym = y[m] - 1.0
+
+    # Initialize the GP.
+    gp = init_gp(x[m], ym, yerr)
+
+    # Define the model.
+    def nll(p):
+        gp.kernel[:] = p
+        return -gp.lnlikelihood(ym, quiet=True)
+
+    def grad_nll(p):
+        gp.kernel[:] = p
+        return -gp.grad_lnlikelihood(ym, quiet=True)
+
+    # Optimize.
+    p0 = gp.kernel.vector
+    init = nll(p0)
+    result = minimize(nll, p0, jac=grad_nll, method="L-BFGS-B",
+                      bounds=[(None, None), (0.0, None)])
+    gp.kernel[:] = result.x
+
+    # Save the results.
+    result.initial_lnlike = -init
+    result.gp = gp
+    result.lnlike = -result.fun
+
+    # Compute prediction.
+    bkg = result.gp.predict(ym, x[m], mean_only=True)
+    result.prediction = 1.0 + bkg
+
+    return result
+
+
+def fit_box(x, y, yerr, t0s, taus, gp=None):
+    if gp is None:
+        gp = init_gp(x, y, yerr)
+
+    # Remove missing data.
+    m = np.isfinite(y) & np.isfinite(y)
+    xm, ym = x[m], y[m]
+
+    # Define the model.
+    def model((t0, tau), x):
+        m = np.abs(x-t0) < 0.5*tau
+        if not m.sum():
+            return None
+        mod = np.zeros_like(x)
+        mod[m] = -1.0
+        return mod
+
+    return fit_linear(xm, ym, gp, model, product(t0s, taus))
+
+
+def fit_step(x, y, yerr, t0s, gp=None):
+    if gp is None:
+        gp = init_gp(x, y, yerr)
+
+    # Remove missing data.
+    m = np.isfinite(y) & np.isfinite(y)
+    xm, ym = x[m], y[m]
+
[…]

### 2015-05-05 peerless/__init__.py
vetting

@@ -1,3 +1,3 @@
 # -*- coding: utf-8 -*-
-__all__ = ["data", "model", "search", "catalogs", "settings"]
-from . import data, model, search, catalogs, settings
+__all__ = ["data", "model", "search", "catalogs", "settings", "vetting"]
+from . import data, model, search, catalogs, settings, vetting

### 2015-12-21 new_search.py
the FPs are mostly EBs

@@ -17,7 +17,7 @@ from george import kernels, ModelingMixin
 import transit
 
 from peerless._search import search
-from peerless.catalogs import KICatalog, EBCatalog
+from peerless.catalogs import KICatalog, EBCatalog, KOICatalog
 from peerless.data import (load_light_curves_for_kic, running_median_trend,
                            load_light_curves)
 
@@ -460,9 +460,17 @@ if __name__ == "__main__":
 
     # Remove EBs from the target list.
     if not args.include_ebs:
+        # Start with EB catalog:
         ebs = set(np.array(EBCatalog().df["#KIC"]))
         l0 = len(kicids)
         kicids = np.array([i for i in kicids if i not in ebs])
+
+        # Then the KOI false positives:
+        kois = KOICatalog().df
+        kois = kois[kois.koi_disposition == "FALSE POSITIVE"]
+        kois = set(np.array(kois.kepid))
+        kicids = np.array([i for i in kicids if i not in kois])
+
         print("Removed {0} known EBs from target list".format(l0-len(kicids)))
 
     # Check and create the output directory.

### 2015-12-21 peerless/data.py

@@ -7,7 +7,6 @@ __all__ = ["load_light_curves_for_kic", "load_light_curves", "LightCurve",
 
 import os
 import fitsio
-import logging
 import requests
 import numpy as np
 from scipy.ndimage.measurements import label
@@ -56,7 +55,7 @@ def load_light_curves(fns, pdc=True, delete=False, remove_kois=False,
         df = KOICatalog().df
         kois = df[df.kepid == remove_kois]
         if len(kois):
-            logging.info("Removing {0} known KOIs".format(len(kois)))
+            print("Removing {0} known KOIs".format(len(kois)))
 
     # Load the light curves.
     lcs = []

### 2015-12-21 new_search.py
better logging

@@ -192,6 +192,8 @@ def get_peaks(kicid=None,
             n = gp.get_parameter_names()
             if name == "transit":
                 bounds[n.index("mean:t0")] = (t0 - 0.5*tau, t0 + 0.5*tau)
+                bounds[n.index("mean:q1")] = (-10, 10)
+                bounds[n.index("mean:q2")] = (-10, 10)
             if "kernel:k2:ln_M_0_0" in n:
                 bounds[n.index("kernel:k2:ln_M_0_0")] = (
                     np.log(0.1), None
@@ -201,22 +203,33 @@ def get_peaks(kicid=None,
                 (2*np.log(np.median(yerr)), None)
 
             # Optimize.
-            print(gp.nll(gp.get_vector(), y))
             r = minimize(gp.nll, gp.get_vector(), jac=gp.grad_nll, args=(y,),
                          method="L-BFGS-B", bounds=bounds)
-            if verbose:
-                print(r)
+            gp.set_vector(r.x)
+
             if not r.success:
                 peak["lnlike_{0}".format(name)] = -r.fun
                 peak["bic_{0}".format(name)] = -np.inf
                 continue
+            else:
+                preds.append(gp.predict(y, x, return_cov=False))
+                # Compute the -0.5*BIC.
+                peak["lnlike_{0}".format(name)] = -r.fun
+                peak["bic_{0}".format(name)] = (-r.fun -
+                                                0.5*len(r.x)*np.log(len(x)))
 
-            gp.set_vector(r.x)
-            preds.append(gp.predict(y, x, return_cov=False))
-
-            # Compute the -0.5*BIC.
-            peak["lnlike_{0}".format(name)] = -r.fun
-            peak["bic_{0}".format(name)] = -r.fun - 0.5*len(r.x)*np.log(len(x))
+            if verbose:
+                print("Peak {0}:".format(i))
+                print("For model: '{0}'".format(name))
+                print("Converged? {0}".format(r.success))
+                print("Log-likelihood: {0}"
+                      .format(peak["lnlike_{0}".format(name)]))
+                print("-0.5 * BIC: {0}"
+                      .format(peak["bic_{0}".format(name)]))
+                print("Parameters:")
+                for k, v in zip(gp.get_parameter_names(), gp.get_vector()):
+                    print("  {0}: {1:.4f}".format(k, v))
+                print()
 
         # Save the transit parameters.
[…]

### 2015-12-21 new_search.py
step init, outliers, etc.

@@ -31,6 +31,7 @@ def get_peaks(kicid=None,
               noise_hw=15.0,
               detect_thresh=20.0,
               max_peaks=3,
+              min_datapoints=10,
               output_dir="output",
               plot_all=False,
               delete=True,
@@ -56,6 +57,9 @@ def get_peaks(kicid=None,
 
     :param max_peaks:
         The maximum number of peaks to analyze in detail. (default: 3)
+
+    :param min_datapoints:
+        The minimum number of in-transit data points. (default: 10)
 
     :param output_dir:
         The parent directory for the plots. (default: output)
@@ -103,7 +107,7 @@ def get_peaks(kicid=None,
     noise = np.nan + np.zeros_like(s2n)
     noise[m] = running_median_trend(time[m], np.abs(s2n[m]), noise_hw)
 
-    # Find peaks about the fiducial threshold.
+    # Find peaks above the fiducial threshold.
     m = s2n > detect_thresh * noise
     peaks = []
     while np.any(m):
@@ -136,6 +140,7 @@ def get_peaks(kicid=None,
 
     # For each peak, plot the diagnostic plots and vet.
     basedir = os.path.join(output_dir, "{0}".format(kicid))
+    final_peaks = []
     for i, peak in enumerate(peaks):
         # Vetting.
         t0 = peak["t0"]
@@ -145,13 +150,15 @@ def get_peaks(kicid=None,
         x = lc0.raw_time
         y = lc0.raw_flux
         yerr = lc0.raw_ferr
+        if np.sum(np.abs(x - t0) < 0.5*tau) < min_datapoints:
+            continue
 
         peak["chunk_min_time"] = x.min()
         peak["chunk_max_time"] = x.max()
 
         # Mean models:
         # 1. constant
-        constant = np.mean(y)
+        constant = np.median(y)
 
         # 2. transit
         system = transit.SimpleSystem(
@@ -165,22 +172,26 @@ def get_peaks(kicid=None,
         system.freeze_parameter("impact")
 
         # 3. step
+        ind = np.argmax(np.abs(np.diff(y)))
         step = StepModel(
-            height=d,
+            height=y[ind] - y[ind+1],
             frac_var=0.0,
             value=1.0,
-            width=1.0,
-            t0=t0 - 0.5*tau,
+            width=0.0,
+            t0=0.5*(x[ind] + x[ind+1]),
         )
-
-        # from george.modeling import check_gradient
-        # print(check_gradient(step, x))
[…]

### 2015-12-21 peerless/data.py

@@ -7,6 +7,7 @@ __all__ = ["load_light_curves_for_kic", "load_light_curves", "LightCurve",
 
 import os
 import fitsio
+import logging
 import requests
 import numpy as np
 from scipy.ndimage.measurements import label
@@ -71,6 +72,9 @@ def load_light_curves(fns, pdc=True, delete=False, remove_kois=False,
         else:
             y = data["SAP_FLUX"]
             yerr = data["SAP_FLUX_ERR"]
+        if np.any(y[np.isfinite(y)] < 0.0):
+            logging.warning("invalid data: flux < 0")
+            continue
 
         # Load the meta data.
         hdr = fitsio.read_header(fn, 0)

### 2015-12-21 new_search.py
adding box model

@@ -188,11 +188,27 @@ def get_peaks(kicid=None,
                 best = (d, w)
         step.width = best[1]
 
+        # 4. box:
+        inds = np.argsort(np.diff(y))
+        inds = np.sort([inds[0], inds[-1]])
+        m = (i < np.arange(len(x))) & (np.arange(len(x)) <= inds[1])
+        tmn, tmx = 0.5 * (x[inds] + x[inds + 1])
+        fin = np.mean(y[m])
+        fout = np.mean(y[~m])
+        box = BoxModel(tmn, tmx, in_value=fin, out_value=fout)
+
+        # from george.modeling import check_gradient
+        # print(check_gradient(box, x))
+
         # Loop over models and compare them.
+        models = [
+            ("gp", constant),
+            ("box", box),
+            ("step", step),
+            ("transit", system),
+        ]
         preds = []
-        for name, mean_model in [("gp", constant),
-                                 ("step", step),
-                                 ("transit", system), ]:
+        for name, mean_model in models:
             kernel = np.var(y) * kernels.Matern32Kernel(2**2)
             gp = george.GP(kernel, mean=mean_model, fit_mean=True,
                            white_noise=2*np.log(np.mean(yerr)),
@@ -288,6 +304,7 @@ def get_peaks(kicid=None,
         accept_bic = (
             (peak["bic_transit"] > peak["bic_gp"]) &
             (peak["bic_transit"] > peak["bic_outlier"]) &
+            (peak["bic_transit"] > peak["bic_box"]) &
             (peak["bic_transit"] > peak["bic_step"]) &
             True
         )
@@ -322,6 +339,7 @@ def get_peaks(kicid=None,
         [ax.plot(x, (p-1)*1e3) for p in preds]
         ax.plot(x, (system.get_value(x)-1)*1e3)
         ax.plot(x, (step.get_value(x)-1)*1e3)
+        ax.plot(x, (box.get_value(x)-1)*1e3)
 
         # De-trended flux.
         row = axes[1]
@@ -408,6 +426,26 @@ class StepModel(ModelingMixin):
             t0=-ew*factor,
             height=f * mp * ep - (1 - f) * mm * em,
             frac_var=-f*f*self.height*(mp*ep + mm*em),
+        )
+
+
+class BoxModel(ModelingMixin):
+
+    def __init__(self, mn, mx, **kwargs):
+        self.mn = mn
+        self.mx = mx
[…]

### 2015-12-21 new_search.py
plotting styles

@@ -207,7 +207,7 @@ def get_peaks(kicid=None,
             ("step", step),
             ("transit", system),
         ]
-        preds = []
+        preds = dict()
         for name, mean_model in models:
             kernel = np.var(y) * kernels.Matern32Kernel(2**2)
             gp = george.GP(kernel, mean=mean_model, fit_mean=True,
@@ -233,9 +233,7 @@ def get_peaks(kicid=None,
             r = minimize(gp.nll, gp.get_vector(), jac=gp.grad_nll, args=(y,),
                          method="L-BFGS-B", bounds=bounds)
             gp.set_vector(r.x)
-
-            if r.success:
-                preds.append(gp.predict(y, x, return_cov=False))
+            preds[name] = gp.predict(y, x, return_cov=False)
 
             # Compute the -0.5*BIC.
             peak["lnlike_{0}".format(name)] = -r.fun
@@ -283,6 +281,7 @@ def get_peaks(kicid=None,
             gp.set_vector(r.x)
             peak["lnlike_outlier"] = -r.fun
             peak["bic_outlier"] = -r.fun-0.5*N*np.log(len(x))
+            preds["outlier"] = gp.predict(y0, x, return_cov=False)
 
             if verbose:
                 print("Peak {0}:".format(i))
@@ -336,15 +335,17 @@ def get_peaks(kicid=None,
 
         row[0].set_ylabel("raw [ppt]")
         ax = row[1]
-        [ax.plot(x, (p-1)*1e3) for p in preds]
-        ax.plot(x, (system.get_value(x)-1)*1e3)
-        ax.plot(x, (step.get_value(x)-1)*1e3)
-        ax.plot(x, (box.get_value(x)-1)*1e3)
+
+        ax.plot(x, (preds["gp"]-1)*1e3, "g", lw=1.5)
+        ax.plot(x, (preds["outlier"]-1)*1e3, "--g", lw=1.5)
+        ax.plot(x, (system.get_value(x)-1)*1e3, "r", lw=1.5)
+        ax.plot(x, (step.get_value(x)-1)*1e3, "b", lw=1.5)
+        ax.plot(x, (box.get_value(x)-1)*1e3, "m", lw=1.5)
 
         # De-trended flux.
         row = axes[1]
         for ax in row:
-            [ax.plot(lc.time, (lc.flux-1)*1e3, "-k") for lc in lcs]
[…]

### 2015-12-21 new_search.py
second box model

@@ -191,21 +191,24 @@ def get_peaks(kicid=None,
         # 4. box:
         inds = np.argsort(np.diff(y))
         inds = np.sort([inds[0], inds[-1]])
-        m = (i < np.arange(len(x))) & (np.arange(len(x)) <= inds[1])
-        tmn, tmx = 0.5 * (x[inds] + x[inds + 1])
-        fin = np.mean(y[m])
-        fout = np.mean(y[~m])
-        box = BoxModel(tmn, tmx, in_value=fin, out_value=fout)
+        boxes = []
+        for tmn, tmx in (0.5 * (x[inds] + x[inds + 1]),
+                         (t0-0.5*tau, t0+0.5*tau)):
+            m = (tmn < x) & (x < tmx)
+            fin = np.mean(y[m])
+            fout = np.mean(y[~m])
+            boxes.append(BoxModel(tmn, tmx, in_value=fin, out_value=fout))
 
         # from george.modeling import check_gradient
         # print(check_gradient(box, x))
 
         # Loop over models and compare them.
         models = [
-            ("gp", constant),
-            ("box", box),
-            ("step", step),
             ("transit", system),
+            ("gp", constant),
+            ("box1", boxes[0]),
+            ("step", step),
+            ("box2", boxes[1]),
         ]
         preds = dict()
         for name, mean_model in models:
@@ -235,6 +238,10 @@ def get_peaks(kicid=None,
             gp.set_vector(r.x)
             preds[name] = gp.predict(y, x, return_cov=False)
 
+            if name == "transit":
+                models[-1][1].mn = system.t0 - 0.5*system.duration
+                models[-1][1].mx = system.t0 + 0.5*system.duration
+
             # Compute the -0.5*BIC.
             peak["lnlike_{0}".format(name)] = -r.fun
             peak["bic_{0}".format(name)] = -r.fun-0.5*len(r.x)*np.log(len(x))
@@ -251,6 +258,9 @@ def get_peaks(kicid=None,
                 for k, v in zip(gp.get_parameter_names(), gp.get_vector()):
                     print("  {0}: {1:.4f}".format(k, v))
                 print()
+
+            if peak["bic_{0}".format(name)] > peak["bic_transit"]:
+                break
 
             # Deal with outliers.
             if name != "gp":
@@ -300,13 +310,9 @@ def get_peaks(kicid=None,
[…]

### 2015-12-21 new_search.py
better transit initialization

@@ -150,7 +150,10 @@ def get_peaks(kicid=None,
         x = lc0.raw_time
         y = lc0.raw_flux
         yerr = lc0.raw_ferr
-        if np.sum(np.abs(x - t0) < 0.5*tau) < min_datapoints:
+        ndata = np.sum(np.abs(x - t0) < 0.5*tau)
+        if ndata < min_datapoints:
+            logging.warning("there are only {0} data points in transit"
+                            .format(ndata))
             continue
 
         peak["chunk_min_time"] = x.min()
@@ -161,15 +164,24 @@ def get_peaks(kicid=None,
         constant = np.median(y)
 
         # 2. transit
+        m = np.abs(x - t0) < tau
+        ind = np.arange(len(x))[m][np.argmin(y[m])]
         system = transit.SimpleSystem(
             period=3000.0,
-            t0=t0,
-            ror=np.sqrt(d),
+            t0=x[ind],
+            ror=np.sqrt(max(d, 1.0 - y[ind])),
             duration=tau,
             impact=0.5,
         )
         system.freeze_parameter("ln_period")
         system.freeze_parameter("impact")
+        best = (np.inf, 0.0)
+        for dur in np.linspace(0.1*tau, 2*tau, 50):
+            system.duration = dur
+            d = np.sum((y - system.get_value(x))**2)
+            if d < best[0]:
+                best = (d, dur)
+        system.duration = best[1]
 
         # 3. step
         ind = np.argmax(np.abs(np.diff(y)))
@@ -224,8 +236,8 @@ def get_peaks(kicid=None,
 
             if name == "transit":
                 bounds[n.index("mean:t0")] = (t0 - 0.5*tau, t0 + 0.5*tau)
-                bounds[n.index("mean:q1_param")] = (-10, 10)
-                bounds[n.index("mean:q2_param")] = (-10, 10)
+                bounds[n.index("mean:q1_param")] = (-20, 20)
+                bounds[n.index("mean:q2_param")] = (-20, 20)
 
             bounds[n.index("kernel:k2:ln_M_0_0")] = (np.log(0.1), None)
             bounds[n.index("white:value")] = (2*np.log(np.median(yerr)), None)
@@ -311,7 +323,8 @@ def get_peaks(kicid=None,
 
         # Accept the peak?
         accept_bic = all(
-            peak["bic_transit"] > peak["bic_{0}".format(k)] for k, _ in models
[…]

### 2015-12-21 new_search.py
more metadata etc.

@@ -156,6 +156,10 @@ def get_peaks(kicid=None,
                             .format(ndata))
             continue
 
+        for k in ["channel", "skygroup", "module", "output", "quarter",
+                  "season"]:
+            peak[k] = lc0.meta[k]
+
         peak["chunk_min_time"] = x.min()
         peak["chunk_max_time"] = x.max()
 
@@ -217,10 +221,10 @@ def get_peaks(kicid=None,
         # Loop over models and compare them.
         models = [
             ("transit", system),
+            ("box1", boxes[1]),
             ("gp", constant),
-            ("box1", boxes[0]),
+            ("box2", boxes[0]),
             ("step", step),
-            ("box2", boxes[1]),
         ]
         preds = dict()
         for name, mean_model in models:
@@ -250,9 +254,10 @@ def get_peaks(kicid=None,
             gp.set_vector(r.x)
             preds[name] = gp.predict(y, x, return_cov=False)
 
+            # Initialize one of the boxes using the transit shape.
             if name == "transit":
-                models[-1][1].mn = system.t0 - 0.5*system.duration
-                models[-1][1].mx = system.t0 + 0.5*system.duration
+                models[1][1].mn = system.t0 - 0.5*system.duration
+                models[1][1].mx = system.t0 + 0.5*system.duration
 
             # Compute the -0.5*BIC.
             peak["lnlike_{0}".format(name)] = -r.fun
@@ -327,9 +332,9 @@ def get_peaks(kicid=None,
             for k, _ in models
         ) and (peak["bic_transit"] > peak["bic_outlier"])
         accept_time = (
-            (peak["transit_time"] - peak["transit_duration"]
+            (peak["transit_time"] - 0.5*peak["transit_duration"]
              > peak["chunk_min_time"]) and
-            (peak["transit_time"] + peak["transit_duration"]
+            (peak["transit_time"] + 0.5*peak["transit_duration"]
              < peak["chunk_max_time"])
         )
         accept = accept_bic and accept_time
@@ -590,6 +595,7 @@ if __name__ == "__main__":
     columns = [
         "kicid", "num_peaks", "peak_id",
         "accept_bic", "accept_time",
+        "channel", "skygroup", "module", "output", "quarter", "season",
         "chunk", "t0", "s2n", "bkg", "depth", "depth_ivar",
         "transit_ror", "transit_duration", "transit_time",
         "chunk_min_time", "chunk_max_time",

### 2015-12-21 peerless/data.py

@@ -93,7 +93,7 @@ def load_light_curves(fns, pdc=True, delete=False, remove_kois=False,
                 period = float(koi.koi_period)
                 t0 = float(koi.koi_time0bk) % period
                 tau = float(koi.koi_duration) / 24.
-                m = np.abs((x-t0+0.5*period) % period-0.5*period) < tau
+                m = np.abs((x-t0+0.5*period) % period-0.5*period) < 0.8 * tau
                 y[m] = np.nan
 
         # Remove bad quality points.

### 2015-12-21 new_search.py
what if GP model doesn't run?

@@ -360,7 +360,8 @@ def get_peaks(kicid=None,
         row[0].set_ylabel("raw [ppt]")
         ax = row[1]
 
-        ax.plot(x, (preds["gp"]-1)*1e3, "g", lw=1.5)
+        if "gp" in preds:
+            ax.plot(x, (preds["gp"]-1)*1e3, "g", lw=1.5)
         if "outlier" in preds:
             ax.plot(x, (preds["outlier"]-1)*1e3, "--g", lw=1.5)
         ax.plot(x, (system.get_value(x)-1)*1e3, "r", lw=1.5)

### 2015-12-21 peerless/data.py

@@ -55,8 +55,8 @@ def load_light_curves(fns, pdc=True, delete=False, remove_kois=False,
     if remove_kois:
         df = KOICatalog().df
         kois = df[df.kepid == remove_kois]
-        if len(kois):
-            print("Removing {0} known KOIs".format(len(kois)))
+        # if len(kois):
+        #     print("Removing {0} known KOIs".format(len(kois)))
 
     # Load the light curves.
     lcs = []

### 2015-12-21 document/ms.tex
q bounds

@@
 \title{%
-    Searching for long-period transiting planets in the \kepler\ light curves
-    using supervised classification
+Automated detection \& characterization of long-period transits in the
+\kepler\ archive
 }
 
-\newcommand{\nyu}{2}
-\newcommand{\cds}{3}
-\newcommand{\mpia}{4}
-\newcommand{\mpis}{5}
+\newcommand{\uw}{3}
+\newcommand{\nyu}{4}
+\newcommand{\cds}{5}
+\newcommand{\mpia}{6}
+\newcommand{\mpis}{7}
 \author{%
-    Daniel~Foreman-Mackey\altaffilmark{1,\nyu,\cds},
+    Daniel~Foreman-Mackey\altaffilmark{1,2,\uw},
     David~W.~Hogg\altaffilmark{\nyu,\mpia,\cds},
@@
 \altaffiltext{1}         {To whom correspondence should be addressed:
-                          \url{danfm@nyu.edu}}
+                          \url{danfm@uw.edu}}
+\altaffiltext{2}         {Sagan Fellow}
+\altaffiltext{\uw}       {Astronomy Department, University of Washington,
+                          Seattle, WA, 98195, USA}
 \altaffiltext{\nyu}      {Center for Cosmology and Particle Physics,

### 2015-12-21 new_search.py

@@ -240,8 +240,8 @@ def get_peaks(kicid=None,
 
             if name == "transit":
                 bounds[n.index("mean:t0")] = (t0 - 0.5*tau, t0 + 0.5*tau)
-                bounds[n.index("mean:q1_param")] = (-20, 20)
-                bounds[n.index("mean:q2_param")] = (-20, 20)
+                bounds[n.index("mean:q1_param")] = (-10, 10)
+                bounds[n.index("mean:q2_param")] = (-10, 10)
 
             bounds[n.index("kernel:k2:ln_M_0_0")] = (np.log(0.1), None)
             bounds[n.index("white:value")] = (2*np.log(np.median(yerr)), None)

### 2015-12-21 document/ms.tex
more step models

@@
 
-Many of the most dynamically important planets have orbits longer than the
-baseline of existing transit surveys (\kepler, \KT).
-Future surveys (\tess, \plato) are planned to have shorter continuous coverage
-that even habitable zone planets around M-dwarfs will only present a single
-transit event.
-Searches for these long-period transiting planets are plagued by false
-signals---especially when pushed to low signal-to-noise---and statistical
-studies of their population are complicated by weak constraints on the
-physical parameters of the system and high rates of false positives.
-We develop and present a computationally expensive but tractable method of
-searching for single transits using supervised classification methods from
-the machine learning literature.
-For each star, we train several random forest classifiers on simulated signals
-injected into different subsets of the data.
-These models are evaluated on the raw photometry to assign a transit
-probability at each time.
-As a proof of concept, we apply this method to 3500 light curves from the
-\kepler\ archival dataset and discover a previously unknown single transit
-candidate.
-Assuming a bound Keplerian orbit and using an informative prior on the
-eccentricity, we measure a radius of $2\,R_\mathrm{J}$ and derive a weak
-constraint on the orbital period.
+Hi.
 
@@
 
-We propose a transit search method that shares some similarities with the PH
-model but, instead of human classifiers, we use a supervised classification
-model trained on large numbers of simulated transit signals injected into
-real \kepler\ light curves.
-This procedure is motivated because, by definition, most randomly selected
-sections of light curve contain no transits and there is an excellent physical
-model for the signals of interest.
-If we can train a classification model to robustly separate light curve
-sections with transits from sections without then we should be able to use
-this in-place of the humans to find single transit events.
-This method is novel as a means to transit search and it differs substantially
-from the standard methods.
-
-Automated classification processes have been hugely successful in the machine
-learning literature.
-% when applied to the right datasets \dfmtodo{cite some things}.
-Many astronomical problems can't be naturally solved by the standard machine
-learning models because of their heterogeneous character and heteroscedastic
-uncertainties.
-The search for single transits, however, is an excellent use case when applied
-with care.
-The noise in the light curve of a given star is relatively consistent for the
-full baseline of observation and we have a very good physical generative model
-for the transit signal so we can simulate arbitrarily large sets of training
+\section{Data preparation}\sectlabel{data}
+
+The \kepler\ Mission measured photometric time series for about 190,000 stars
+at half-hour cadence for a baseline of over four years.
+We aim to search these light curves for single transits of long-period planets
+and single eclipses of binary stars.
+These data are made available on
+MAST\footnote{\url{https://archive.stsci.edu/kepler/}} and, for each target,
+we downloaded the full set of long cadence light curve files provided by Data
+Release 24 \citep{Thompson:2015}.
+From these files, we extracted the PDC time series and split them into
+``sections'' with no more than ten contiguous missing or flagged data points.
+The PDC light curves have been corrected for the instrumental effects caused
+by the spacecraft using a data-driven model of the focal plane
+\citep{Stumpe:2012, Smith:2012}.
+Crucially, an attempt is also made by the PDC procedure to remove sharp
+instrumental artifacts like ``sudden pixel sensitivity dropouts (SPSDs)''.
+The success rate of this correction procedure is much higher than in earlier
+data releases but, as discussed in \sect{demo}, there remain some cases that
+are not properly accounted for.
+
+The goal of this project is to discover the transits of long-period planets
+that have not yet been discovered.
+Therefore, when studying the light curve of an eclipsing binary star or a star
+with known transiting planet candidates---on shorter periods---we also remove
+all the in-transit data for the candidate using the parameters provided by the
+\project{NASA Exoplanet
+Archive}\footnote{\url{http://exoplanetarchive.ipac.caltech.edu/}; We
+downloaded the \texttt{cumulative} table of \kepler\ Objects of Interest on
+2015-03-25.}.
+
+\section{Random forest classification}\sectlabel{rfc}
+
+A common task in the machine learning literature is called \emph{supervised
+classification} where the goal is to separate objects into classes
+represented by sets of labeled examples.
+In the astronomy literature, supervised classification has been used for
+variable star classification \citep{Richards:2011} star--galaxy separation
+\citep{Fadely:2012}, galaxy morphology prediction \citep{Dieleman:2015}, and
+other applications.
+In each of these problems, there are a set of measurements that have been
+assigned classes---by some other method; often manually---and the goal is to
+transfer these labels to a set of observations that have not yet been
+labeled.
+For a more in-depth discussion of the application of these techniques in
+astronomy, the interested reader is directed to \citet{Ivezic:2013}.
+
+In our problem of transit search, we want to ``label'' sections of light curve
+with either the \texttt{transit} or \texttt{no transit} class.
+This problem doesn't fall under the standard format of a supervised
+classification problem because very few long-period transits have actually
+been observed or classified.
+We do think, however, that we have a good physical generative model for the
+signal of interest and most of the observations of each star have no transits.
+Therefore, we train the model on simulated signals.
+
+The Random Forest (RF) classification model \citep{Breiman:2001} is a popular
+model in the machine learning community where it is a common go-to model for
+basic classification tasks.
+It has also been applied with great success in astronomy \citep[for
+example][]{Richards:2011, Richards:2012, Jenkins:2014}.
+The RF model works by fitting an ensemble of decision trees to randomly
+selected subsamples of the training dataset.
+Each tree in the forest is ``grown'' by greedily choosing decision boundaries
+that optimize the separation of the training data in randomly selected
+subsets of the features until the separation is complete, each leaf contains
+only one class or, at most, a fixed number of samples.
+At each branch, the decision boundary is set by maximizing either the entropy
+or the ``gini'' coefficient.
+
+We use the \project{scikit-learn} \citep{Pedregosa:2011} version of the RF
+classification algorithm\footnote{Specifically we use the
+\texttt{RandomForestClassifier} object;
+\url{http://scikit-learn.org/stable/modules/generated/sklearn.ensemble.RandomForestClassifier.html}.}
+implemented in \project{Python}.
+This implementation has state-of-the-art speed and
+performance\footnote{\url{http://blog.explainmydata.com/2014/03/big-speedup-for-random-forest-learning.html}}
+while maintaining a flexible and user-friendly interface.
+
+\section{Search methodology}\sectlabel{search}
+
+Now, we will apply the RF classification model to search for single transits
+in \kepler\ light curves.
+The basic structure of the problem, applied to the light curve of a single
+star, is:
+\begin{enumerate}
+
+{\item {\bf train} a classifier on simulated signals injected into a subset of
+the light curves sections,}
+
+{\item {\bf validate} the model on signals injected into a different subset of
+the data to estimate the precision of the results,}
+
+{\item {\bf test} the classifier by applying it to a final subset of the
+data---disjoint from the previous two sets---to predict the class
+(\texttt{transit} or \texttt{no transit}) of each light curve section, and}
+
+{\item iterate until the entire light curve has been classified.}
+
+\end{enumerate}
+This means that searching a single light curve involves training, validating,
+and testing at least 3 RF models.
+In practice, we find that it is sufficient to split the data (intelligently)
+into 3 disjoint subsets so that we need only train 3 classifiers for each
+star.
+
+A key assumption of this model is that the classes are sufficiently
+represented in feature space.
+In other words, the training set must span both of the classes.
+Given a large enough training set, this is not difficult for the
+\texttt{transit} class; we can simulate a transit for any combination of
+physical parameters.
+This is much more difficult for the \texttt{no transit} class.
+Since we don't have a generative model for the stellar and instrumental
+variability or other artifacts, we cannot simulate negative examples that
+cover the full space of possibilities.
+Instead we are using sections of real light curves as the \texttt{no transit}
 examples.
-
-In the training step, a Random Forest (RF) classifier is trained to
-distinguish---based only on the light curve itself---between sections of light
-curve that contain transits from sections of the same size that do not.
-This model is then used to find candidates in left-out sections of the light
-curve.
-In principle, this model can capture arbitrarily complicated non-linear
-structure in the decision space and if the training set is large and complete
-it will ``learn'' the shape of a physical transit.
-In practice, classification algorithms like this also require a complete set
-of ``negative'' training examples so further vetting using physical models
-is necessary.
-
-In \sect{est}, we extrapolate a recent model of the distribution of exoplanets
-to the long periods considered in this \paper.
-Using an approximate but realistic model for the detection efficiency of a
-search for single transits, we estimate that $\sim 60$ single transit events
-should be detectable in the archival \kepler\ dataset.
-In \sect{data}, we describe the data and outline the structure exploited by
-our transit search procedure.
-In \sect{rfc}, we briefly describe the Random Forest classification framework
-and in \sect{search} we outline the steps used to apply this model for transit
-search.
-This method requires the setting of many tuning parameters and the
-optimization of these choices is both computationally and intellectually
-challenging so in \sect{tuning} we discuss some steps in this direction.
-In \sect{demo}, we demonstrate the feasibility of this method, present a
-single transit discovery, and indicate some interesting weaknesses of the
+This means that there are a finite number of samples available for training
+and validation, and if there is a qualitatively different signal in the test
+set that is not generated by a transit, the model is at risk of unpredictably
+misclassifying that section.
+This problem can be largely mitigated by careful splitting of the dataset---as
+described below---but there are inevitably some false signals that are not
+properly accounted for.
+
+The following \sectionname s detail the application of this search procedure
+from the training set simulations through to the candidate selection.
+These candidates are then vetted by hand although more robust methods should
+be possible as discussed in \sect{vetting}.
+Finally, \sect{features} explores alternative representations of the data or
+features.
+
+\subsection{Splitting the dataset}\sectlabel{split}
+
+It is crucial that the model used to test for transits in a raw \kepler\
+light curve not be trained on the same data.
+We must split the light curve of each star into 3 disjoint sets.
+For the model to work well, we require that the signals induced by
+variability, noise, and other systematics be consistent between splits.
+It is, therefore, necessary that we assign the splits carefully.
+As discussed in \sect{data}, a light curve can be separated naturally into
+``sections'' of nearly contiguous measurements; these are the base unit for
+splitting the dataset.
+For the typical \kepler\ target, this division is finer than month long
+chunks and there are about 100 sections for each light curve.
+Each light curve section is cut out of a specific ``quarter'' and each quarter
+was observed during a specific ``season''.
+
+These divisions are relevant to this discussion because the spacecraft
+pointing across a quarter was extremely precise and the photometric aperture
+is fixed to the same pixels for the full quarter.
+Therefore, the instrumentally-induced systematics tend to be qualitatively
+consistent on quarter-long time scales.
+Every three months, the \kepler\ spacecraft rolled by 90~degrees causing the
+stars to end up on a different detector every quarter.
+This means that while the astrophysical variability should be shared between
+quarters at some level, the instrumental effects can be very different.
+A year later, however, the spacecraft returned to the original pointing.
+As a result, the data quality is also similar for observations made in the
+same season.
+
+In order to take advantage of the natural structure of the observations, we
+try to evenly distribute observations from each quarter and season across the
+three sets.
+When this is not possible (with Quarter 0, for example), we randomly assign
+the section to a split.
+
+\subsection{Transit simulations}
+
+As mentioned previously, we train the RF classification models on a set
+simulated transit signals injected into real light curves and a set of light
+curve sections assumed to contain no transits.
+For each data split, we construct a set of 20,000 \texttt{transit} samples and
+an equal number of \texttt{no transit} examples.
+Each of these samples is generated by randomly selecting a section of 201
+contiguous flux measurements from the split.
+Since we expect most of the systematic variability to be symmetric in time, we
+augment the training set by reversing the time series for half of the samples.
+This is analogous to image processing methods that exploit rotation and
+translational symmetries \citep[for an example from astronomy
+see][]{Dieleman:2015}.
+
+To generate the \texttt{transit} examples, we simulate the transit signal
+induced by the physical orbit of a large planet.
+The specific distribution of simulation parameters is listed in \tab{params}.
+In these simulations, we take limb darkening and integration time into
+account\footnote{\url{https://github.com/dfm/transit}}
+\citep{Mandel:2002, Kipping:2010}.
+For the purposes of this \paper, we only simulate circular orbits under the
+assumption that a single transit of a planet on an elliptical orbit would be
+nearly identical to a circular orbit at a different period.
+
+The dataset will still have some missing or flagged fluxes.
+In order to account for these missing points, we linearly interpolate these
+values based on their neighbors.
+For consistency, we perform the interpolation on the training set \emph{after
+injecting the synthetic transit signals}.
+Before passing the light curve sections to the model at any stage, we
+normalize the section by its empirical median and take the logarithm of the
+fluxes.
+This normalization appears to yield better performance in some test cases but
+better performance might be achieved using optimized methods.
+This choice is discussed further in \sect{params}.
+
+\begin{table}[htbp]
+\begin{center}
+\begin{tabular}{lcc}
+\toprule
+Parameter & Units & Distribution \\
+\midrule
+
+limb darkening parameters $q_1$ and $q_2$ & --- & $q \sim U(0,\,1)$ \\
+orbital period \period & days & $\ln \period \sim U(\ln 1500,\,\ln 5000)$ \\
+reference transit time $\delta t$ & days & $\delta t \sim U(-0.15,\,0.15)$ \\
+planet radius \rp & $R_\oplus$ & $\ln \rp \sim U(\ln 5,\,\ln 20)$ \\
+impact parameter $b$ & --- & $b \sim U(0,\,1)$ \\
+
+\bottomrule
+\end{tabular}
+\end{center}
+\caption{%
+The distribution of physical parameters for the injected signals.
+The limb darkening parameterization is given by \citet{Kipping:2013}.
+\tablabel{params}}
+\end{table}
+
+\subsection{Training, validation, and testing}\sectlabel{train}
+
+For each subset of the data, we train a RF classifier on the 40,000 training
+examples generated from the light curves in that split.
+The \texttt{RandomForestClassifier} implementation from \project{scikit-learn}
+has several tuning parameters that could be optimized using cross-validation
+but we find acceptable performance in most cases using fixed values.
+Specifically, we use a forest with 1000 trees by setting
+\texttt{num\_estimators = 1000}.
+We discuss this choice and the settings for other parameters in more detail in
+\sect{params}.
+
+Using this classifier, fit to one of the light curve subsets, we validate its
+performance on each set of simulations from the two other splits.
+This results in two precision--recall curves for the classifier.
+The \emph{precision} is an empirical measurement of the sample purity (or
+false positive rate) and \emph{recall} is a measurement of the completeness
+(the probability of detecting a true signal).
+Since the RF classifier scores each class and with a continuous value \score\
+between 0 and 1, both precision and recall can be tuned by changing the
+threshold value of \score\ above which the signal is considered a candidate.
+For each model--validation set pair, we ambitiously choose the threshold in
+order to obtain a precision of 100~percent.
+The result of this procedure applied to the three splits is three classifiers
+with two score thresholds each.
+
+Each of these six models has been fit using two splits so we then apply it to
+the raw light curves (without injected signals) from the remaining, untouched
+splits.
+This yields a \texttt{transit} class score as a function of transit time and
+any points above the detection threshold are passed along to the candidate
+selection procedure.
+
+At this point, there are two class predictions from two different models for
+every light curve section.
+Any section that is classified as \texttt{transit} by \emph{both models} is
+accepted as a single transit candidate.
+
+% \dfmtodo{make a figure}
+
+\subsection{Candidate vetting}\sectlabel{vetting}
+
+While the search procedure described in the previous sections is quite robust
+to false alarms, single transit events are extremely rare (as discussed in
+\sect{est}) and because of substantial violations of the model assumptions,
+false signals continue to outnumber the true signals in this catalog of
+candidate transits.
+To mitigate this problem, we manually inspect the light curves of candidate
+signals.
+As future work, we expect to automate this procedure by fitting a physical
+transit model and comparing it to simple models of stellar variability and
+instrumental artifacts.
+For this \paper, however, the catalog of candidates is sufficiently small that
+manual inspection is tractable.
+As demonstrated in \sect{demo}, the most common misclassifications are caused
+by astrophysical variability but some remaining systematic effects are also
+incorrectly labeled as candidates.
+
+\subsection{Feature selection}\sectlabel{features}
+
+In many supervised classification problems, a sophisticated feature
+extraction method is used to improve the performance of the procedure.
+For this specific problem, we find excellent performance using the 201
+normalized flux values as the features.
+The depth of the transit and the noise in the light curve is not irrelevant
+to detection so we don't normalize the features to unit variance in the
+standard way.
+Instead, we normalize each sample (feature vector) by it's empirical median
+value and take the logarithm.
+Another option for a feature set could be the Fourier transform or wavelet
+transform of the light curve section.
+Alternatively, the spectrogram of the fluxes in a larger window.
+We have experimented briefly with these options but find similar performance
+on the cases that we tested.
+
+\section{Tuning parameters}\sectlabel{tuning}
+
+Many choices need to be made in building this search procedure.
+Each of these choices can be specified by a set of parameters that can be
+tuned to optimize the method.
+In order to tune these parameters, we must decide on a quantitative
+measurement of the ``performance''.
+The goal is, of course, to \emph{robustly discover transiting planets}.
+In other words, the aim is a procedure that maximizes both \emph{recall} and
+\emph{precision}.
+
+As discussed previously, recall is the probability, integrated across the full
+parameter space of interest that a true transit signal will be detected by the
 method.
-In \sectionname s~\sectref{params} we describe the parameter estimation that
-is possible given a single transit.
-
-% and outline the prospects for exoplanet
-% population inference given a catalog of single transit discoveries.
+In astronomy, this quantity is generally called the completeness or detection
+efficiency and it is routinely measured for transit surveys
+\citep{Petigura:2013, Dressing:2015, Foreman-Mackey:2015}.
+On the other hand, precision is the probability that a positive classification
+will be true.
+In astronomy, precision is generally hard to measure because we rarely have
+access to the ground truth.
+For this problem, correctly computing the recall is impossible because we
+never know that \emph{there is definitely no transit} at a given time in the
+light curve.
+
+What's more, it is not in general possible to maximize both recall and
+precision because transit signals are not completely separable from false
+positives.
+This means that, as the recall of the method improves, the false positive rate
+will also increase, reducing the precision.
+We must, therefore, choose a trade-off between recall and precision that
+represents our objective.
+The informal tradition in the transit search literature is to build a
+procedure that maximizes the recall at an extremely high ($\sim 100$~percent)
+fixed precision.
+
+The main tuning parameters of the method are as follows:
+\begin{itemize}
+
+{\item \emph{the number of training and validation examples for each data
+split} --- The performance of most classification models improves drastically
+as the size of the training set increases but in this case we are limited by
+the number of \texttt{no transit} samples that are available since we have no
+generative model for the variability and systematics.
+For this \paper, we choose 20,000 positive \texttt{transit} samples per split
+and an equal number of negative examples.}
+
+{\item \emph{the range of physical parameters used to simulate the transit
+signals} --- The search will be most sensitive to transits with parameters
+spanned by the training set but training on too many low signal-to-noise
+examples in noisy light curves leads to decreased precision.
+The parameter ranges used for the demonstrations here are given in
+\tab{params}.}
+
+{\item \emph{tuning parameters of the RF implementation} --- The
+\texttt{RandomForestClassifier} implementation has a few tuning parameters.
+The most important of these seems to be \texttt{num\_estimators}, the number
+of decision trees used in the forest.
+Increasing \texttt{num\_estimators} leads to substantial computational cost
+with diminishing returns on the search performance.
+Otherwise, there are a few parameters (for example, \texttt{max\_features},
+\texttt{min\_samples\_split}, and \texttt{min\_samples\_leaf}) that can be
+used to regularize the model but we have found that the performance is
+insensitive to these choices.
+As a trade-off between performance and computational cost, we set
+\texttt{num\_estimators = 1000} in all the examples shown in this \paper.}
+
+\end{itemize}
+In detail, the optimal set of decisions and parameter settings will be
+different for every target---and probably even for every permutation of the
+data splits.
+In practice, we find that the performance of the search is fairly insensitive
+to most of these choices so we choose parameters that seem to work well in
+most cases and leave optimization for future work.
+
+\paragraph{Estimating the precision}
+
+We estimate the precision of each RF classification model on the validation
+set as described in \sect{train}.
+As discussed in that \sectionname, we choose a target precision to
+100~percent and set the score threshold accordingly.
+This estimate is only applicable to the test set under two major assumptions.
+The first is that all transiting planets with more than one transit and a
+large signal-to-noise ratio have been previously discovered by one of the many
+transit searches applied the \kepler\ dataset \citep{Burke:2014, Rowe:2015}.
+This is a safe assumption because, for large planets, these surveys are all
+largely complete out to periods yielding only 2 or 3 transits in the \kepler\
+baseline \citep[for example][]{Petigura:2013}.
+The second assumption is not always valid so it makes this estimate of the
+precision only approximate and not completely reliable.
+This assumption is that the noise processes in the data are stationary.
+In other words, the transit-like noise signals in the training and validation
+sets must be ``similar'' to the signals in the test section.
+This constraint is nearly satisfied when the PDC light curves are used
+(\sect{data}) and the data are split carefully (\sect{split}).
+As demonstrated by the mis-classifications shown in \sect{demo}, however, it
+is clear that violations to this rule do exist in the data and final vetting
+of the candidates must be applied using a physical understanding of the
+signals.
+
+\section{Preliminary results}\sectlabel{demo}
+
+As a demonstration of the feasibility of this method to search for single
+transit events, we selected 3500 bright, Sun-like stars based on the revised
+stellar parameters collected and measured for a recent \kepler\ data release
+\citep{Huber:2014}.
+The targets were selected in the parameter range
+\begin{itemize}
+
+\item effective temperature:
+        $4100\,\mathrm{K} < T_\mathrm{eff} < 6100\,\mathrm{K}$,
+
+\item surface gravity:  $4.0 < \log g < 4.9$, and
+
+\item \kepler\ magnitude: $15 > K_\mathrm{p} > 10$.
+
+\end{itemize}
+
+This search results in 596 candidate transits in the light curves of these
+3500 stars.
+The vast majority of these candidates are misclassified false positives and
+many of them are caused by astrophysical sources.
+To weed out known astrophysical sources, we cross-match this list against
+known eclipsing binary stars \citep{Matijevic:2012} and stars with substantial
+variability \citep{McQuillan:2014}.
+Removing these signals results in 273 candidates.
+Of these candidates only one (KIC 10602068) is a convincing transit and the
+others all appear to be caused by systematic effects, instrumental or
+astrophysical.
+\Fig{candidates} shows some representative candidate signals from this final
+list.
+
+\paragraph{Failures}
+
+\dfmtodo{Add some discussion of the failures and make suggestions for better
+vetting techniques.}
+
+\begin{figure}[p]
+\begin{center}
+\includegraphics[width=0.5\textwidth]{figures/candidates.pdf}
+\end{center}
+\caption{%
+Some representative light curve sections that were labeled as candidates by
+the single transit search.
+The light curve in the top-left panel is a convincing transit signal but the
+other panels all appear to be caused by stellar variability or instrumental
+effects.
+\figlabel{candidates}}
+\end{figure}
+
+\section{KIC 10602068: A discovery}\sectlabel{params}
+
+In the 3500 light curves we searched for this \paper, we discovered one
+convincing single transit signal at $830.8093\pm0.0002$~KBJD in the light
+curve of the 14.9~Kep-mag G-dwarf KIC 10602068.
+Despite the fact that this is a very large signal, its discovery has never
+been reported.
+Given the estimate of $\sim 60$ detectable single transits in the full
+\kepler\ archival dataset, we do expect about one discovery in 3500 light
+curves.
+
+Even though only one transit is observed, if we assume that the transit is
+caused by a body on a Keplerian orbit around the host star, we can place
+constraints on the physical properties---even the orbital period---of the
+transiting candidate.
+This technique is similar in spirit to the ``photoeccentric effect''
+\citep{Dawson:2012} and ``asterodensity profiling'' \citep{Kipping:2012}.
+The fundamental principle is that the transit duration is a measurement of
+the instantaneous velocity of the planetary motion and this yields a
+constraint on the orbital period when combining this with a measurement of the
+stellar density and a prior on the eccentricity of the orbit.
+
+The photometrically derived physical properties for this star place it as a
+G-dwarf with a mass and radius of about 90~percent Solar \citep{Huber:2014}.
+Using these constraints and a beta function prior on the eccentricity of the
+orbit \citep{Kipping:2013a}, we run Markov Chain Monte Carlo
+\citep{Foreman-Mackey:2013} to sample the posterior probability for the
+physical parameters of the system.
+In this analysis, we take limb darkening and the finite exposure time into
+account \citep{Mandel:2002, Kipping:2010, Kipping:2013}.
+The results of this chain marginalized into the relevant physical dimensions
+are shown in \fig{corner}.
+The radius of the transiting body is measured to be $2.1 \pm
+0.4\,R_\mathrm{J}$.
+The period is very weakly constrained above a lower limit of
+$760\,\mathrm{days}$---set by the fact that a second transit is not
+detected---with 68~percent of the posterior mass in the range $760\,\mathrm{d}
+< \period < 1347\,\mathrm{d}$.
+
+Given the large radius of this candidate, it is probably stellar in nature
+instead of planetary but this could be easily confirmed using radial velocity
+follow-up.
+
+\begin{figure}[p]
+\begin{center}
+\includegraphics[width=\textwidth]{figures/corner.pdf}
+\end{center}
+\caption{%
+Posterior constraints on the physical parameters of the body transiting KIC
+10602068 assuming a bound Keplerian orbit.
+\figlabel{corner}}
+\end{figure}
+
+% \section{Prospects for population inference}\sectlabel{exopop}
+
+% Based on our single transit discoveries, we now want to place a limit on
+% the occurrence rate of long-period planets.
+% Since we only have one discovery thus far, we'll make the simplifying
+% assumption that the rate is flat in log-period and log-radius in the range
+% $1000\,\mathrm{d} < \period < 5000\,\mathrm{d}$ and $5\,R_\odot <
+% 20\,R_\odot$.
+% For this distribution, \citet{Foreman-Mackey:2014} derived the analytic
+% maximum likelihood result
+% \begin{eqnarray}
+% \rate &=& \frac{N_\mathrm{obs}}{\int Q(w)\dd w}
+% \end{eqnarray}
+% where $\rate$ is the occurrence rate per natural logarithm in period and
+% radius, $N_\mathrm{obs}$ is the number of detections, and the integral is over
+% the completeness measurements for every star that has been searched.
+% If we make the simplifying assumption that the detectability of a transit
+% depends on period only through Equations~(\eqref{q-geom})
+% and~(\eqref{q-time}), then this integral becomes
+% \begin{eqnarray}
+% \int Q(w)\dd w &=& \sum_{k=1}^K
+%     \left( \frac{4\,\pi^2}{G\,M_k} \right)^{1/3} \, R_k \, T_k \, Q_k \,
+%     \int \period^{-8/3}\,\rp^{-1} \dd\rp\dd\period \\
+%  &=& \sum_{k=1}^K
+%     \left( \frac{4\,\pi^2}{G\,M_k} \right)^{1/3} \, R_k \, T_k \, Q_k \,
+%     \ln \left(\frac{\rp_\mathrm{max}}{\rp_\mathrm{min}}\right)
+%     \frac{3}{5} \,
+%     \left[{\period_\mathrm{min}}^{-5/3} - {\period_\mathrm{max}}^{-5/3}\right]
+% \end{eqnarray}
+% where the sum is over all the targeted stars.
+
+\section{Discussion}\sectlabel{discussion}
+
+The discovery and characterization of transiting planets based on a single
+transit event is crucial for the future of transiting exoplanet surveys.
+Many of the most dynamically influential planets---like Jupiter in our Solar
+system---exhibit only a single transit in the full observational baseline of
+the \kepler.
+This will become even more of a problem as upcoming surveys move to shorter
+contiguous observations.
+For example, the \tess\ Mission is planned to get full-sky coverage at
+half-hour cadence but most of the sky will only be targeted for a month.
+This means that even habitable zone planets orbiting cool stars will transit
+their host \emph{at most once in the entire lifetime of the Mission}!
+
+To date, no methods exist for systematically and robustly discovering single
+transit events based on large photometric surveys.
+In this \paper, we present a novel and conceptually unique solution to this
+problem drawing on machine learning methods for supervised classification.
+This method has immense potential because it can be designed to be very robust
+to false positives and it can exploit the detailed shape of physical transits.
+
+Despite the fact that single transits are unlikely even if these long-period
+planets are intrinsically common, we estimate that $\sim 60$ events should be
+detectable in the \kepler\ archival dataset by extrapolating recent models of
+planet occurrence rates and taking selection effects into account.
+When applied to 3500 light curves from the \kepler\ dataset, this method
+recovers one previously unknown single transit event at
+$830.8093\pm0.0002$~KBJD in the light curve of KIC 10602068.
+This rate is consistent with the predicted yield of 60 events in the full
+dataset of 190,000 light curves.
+
+Assuming a bound Keplerian orbit, we place constraints on the physical
+properties of this transit candidate KIC 10602068.01.
+Using photometrically derived stellar properties, we find that this candidate
+has a radius of $2.1 \pm 0.4\,R_\mathrm{J}$ placing it as a very large planet
+or brown dwarf or a small star.
+
+This method for transit search is built using supervised classification and
+its performance relies on several strong assumptions about the datasets and
+these assumptions are sometimes violated leading to some transit-like signals
+that appear to be caused by noise to be misclassified as transits.
+The most severe assumption is that the noise properties of the data are
+stationary.
+In other words, we assume that variability in one subset of a light curve is
+completely spanned by the variability in the other sections.
+This assumption is, in general, false because the stochastic processes that
+cause stellar variability are complicated and non-stationary and the detector
+is plagued by non-negligible catastrophic changes in sensitivity and response.
+We attempt to mitigate this problem by using light curves that have been
+preprocessed to remove most of the instrumental effects and carefully dividing
+the data into subsets but some false positives are still incorrectly
+identified as candidates.
+
+One possible method for reducing the false positive rate would be to augment
+the training dataset using heuristic simulations of common false positives or
+the light curves of ``similar'' stars.
+Another option is to recognize that this search drastically reduces the
+parameter space requiring evaluation and comparing the predictive power of
+a transit model to other heuristic models including stellar variability or
+instrumental effects.
+
+\acknowledgments
+It is a pleasure to thank
+\ldots
+for helpful contributions to the ideas and code presented here.
+DFM and DWH were partially supported by the National Science Foundation
+(grant IIS-1124794),
+the National Aeronautics and Space Administration
+(grant NNX12AI50G), and the Moore--Sloan Data Science Environment at NYU.
+
+This research made use of the NASA \project{Astrophysics Data System} and the
+NASA Exoplanet Archive.
+The Archive is operated by the California Institute of Technology, under
+contract with NASA under the Exoplanet Exploration Program.
+This \paper\ includes data collected by the \kepler\ mission. Funding for the
+\kepler\ mission is provided by the NASA Science Mission directorate.
+We are grateful to the entire \kepler\ team, past and present.
+Their tireless efforts were all essential to the tremendous success of the mission
+and the successes of \KT, present and future.
+These data were obtained from the Mikulski Archive for Space Telescopes
+(MAST).
+STScI is operated by the Association of Universities for Research in
+Astronomy, Inc., under NASA contract NAS5-26555.
+Support for MAST is provided by the NASA Office of Space Science via grant
+NNX13AC07G and by other grants and contracts.
+
+{\it Facilities:} \facility{Kepler}
+
+\appendix
 
@@
 
-\section{Data preparation}\sectlabel{data}
-
-The \kepler\ Mission measured photometric time series for about 190,000 stars
-at half-hour cadence for a baseline of over four years.
-We aim to search these light curves for single transits of long-period planets
-and single eclipses of binary stars.
-These data are made available on
-MAST\footnote{\url{https://archive.stsci.edu/kepler/}} and, for each target,
-we downloaded the full set of long cadence light curve files provided by Data
-Release 24 \citep{Thompson:2015}.
-From these files, we extracted the PDC time series and split them into
-``sections'' with no more than ten contiguous missing or flagged data points.
-The PDC light curves have been corrected for the instrumental effects caused
-by the spacecraft using a data-driven model of the focal plane
-\citep{Stumpe:2012, Smith:2012}.
-Crucially, an attempt is also made by the PDC procedure to remove sharp
-instrumental artifacts like ``sudden pixel sensitivity dropouts (SPSDs)''.
-The success rate of this correction procedure is much higher than in earlier
-data releases but, as discussed in \sect{demo}, there remain some cases that
-are not properly accounted for.
-
-The goal of this project is to discover the transits of long-period planets
-that have not yet been discovered.
-Therefore, when studying the light curve of an eclipsing binary star or a star
-with known transiting planet candidates---on shorter periods---we also remove
-all the in-transit data for the candidate using the parameters provided by the
-\project{NASA Exoplanet
-Archive}\footnote{\url{http://exoplanetarchive.ipac.caltech.edu/}; We
-downloaded the \texttt{cumulative} table of \kepler\ Objects of Interest on
-2015-03-25.}.
-
-\section{Random forest classification}\sectlabel{rfc}
-
-A common task in the machine learning literature is called \emph{supervised
-classification} where the goal is to separate objects into classes
-represented by sets of labeled examples.
-In the astronomy literature, supervised classification has been used for
-variable star classification \citep{Richards:2011} star--galaxy separation
-\citep{Fadely:2012}, galaxy morphology prediction \citep{Dieleman:2015}, and
-other applications.
-In each of these problems, there are a set of measurements that have been
-assigned classes---by some other method; often manually---and the goal is to
-transfer these labels to a set of observations that have not yet been
-labeled.
-For a more in-depth discussion of the application of these techniques in
-astronomy, the interested reader is directed to \citet{Ivezic:2013}.
-
-In our problem of transit search, we want to ``label'' sections of light curve
-with either the \texttt{transit} or \texttt{no transit} class.
-This problem doesn't fall under the standard format of a supervised
-classification problem because very few long-period transits have actually
-been observed or classified.
-We do think, however, that we have a good physical generative model for the
-signal of interest and most of the observations of each star have no transits.
-Therefore, we train the model on simulated signals.
-
-The Random Forest (RF) classification model \citep{Breiman:2001} is a popular
-model in the machine learning community where it is a common go-to model for
-basic classification tasks.
-It has also been applied with great success in astronomy \citep[for
-example][]{Richards:2011, Richards:2012, Jenkins:2014}.
-The RF model works by fitting an ensemble of decision trees to randomly
-selected subsamples of the training dataset.
-Each tree in the forest is ``grown'' by greedily choosing decision boundaries
-that optimize the separation of the training data in randomly selected
-subsets of the features until the separation is complete, each leaf contains
-only one class or, at most, a fixed number of samples.
-At each branch, the decision boundary is set by maximizing either the entropy
-or the ``gini'' coefficient.
-
-We use the \project{scikit-learn} \citep{Pedregosa:2011} version of the RF
-classification algorithm\footnote{Specifically we use the
-\texttt{RandomForestClassifier} object;
-\url{http://scikit-learn.org/stable/modules/generated/sklearn.ensemble.RandomForestClassifier.html}.}
-implemented in \project{Python}.
-This implementation has state-of-the-art speed and
-performance\footnote{\url{http://blog.explainmydata.com/2014/03/big-speedup-for-random-forest-learning.html}}
-while maintaining a flexible and user-friendly interface.
-
-\section{Search methodology}\sectlabel{search}
-
-Now, we will apply the RF classification model to search for single transits
-in \kepler\ light curves.
-The basic structure of the problem, applied to the light curve of a single
-star, is:
-\begin{enumerate}
-
-{\item {\bf train} a classifier on simulated signals injected into a subset of
-the light curves sections,}
-
-{\item {\bf validate} the model on signals injected into a different subset of
-the data to estimate the precision of the results,}
-
-{\item {\bf test} the classifier by applying it to a final subset of the
-data---disjoint from the previous two sets---to predict the class
-(\texttt{transit} or \texttt{no transit}) of each light curve section, and}
-
-{\item iterate until the entire light curve has been classified.}
-
-\end{enumerate}
-This means that searching a single light curve involves training, validating,
-and testing at least 3 RF models.
-In practice, we find that it is sufficient to split the data (intelligently)
-into 3 disjoint subsets so that we need only train 3 classifiers for each
-star.
-
-A key assumption of this model is that the classes are sufficiently
-represented in feature space.
-In other words, the training set must span both of the classes.
-Given a large enough training set, this is not difficult for the
-\texttt{transit} class; we can simulate a transit for any combination of
-physical parameters.
-This is much more difficult for the \texttt{no transit} class.
-Since we don't have a generative model for the stellar and instrumental
-variability or other artifacts, we cannot simulate negative examples that
-cover the full space of possibilities.
-Instead we are using sections of real light curves as the \texttt{no transit}
+\section{Supervised classification}
+
+We propose a transit search method that shares some similarities with the PH
+model but, instead of human classifiers, we use a supervised classification
+model trained on large numbers of simulated transit signals injected into
+real \kepler\ light curves.
+This procedure is motivated because, by definition, most randomly selected
+sections of light curve contain no transits and there is an excellent physical
+model for the signals of interest.
+If we can train a classification model to robustly separate light curve
+sections with transits from sections without then we should be able to use
+this in-place of the humans to find single transit events.
+This method is novel as a means to transit search and it differs substantially
+from the standard methods.
+
+Automated classification processes have been hugely successful in the machine
+learning literature.
+% when applied to the right datasets \dfmtodo{cite some things}.
+Many astronomical problems can't be naturally solved by the standard machine
+learning models because of their heterogeneous character and heteroscedastic
+uncertainties.
+The search for single transits, however, is an excellent use case when applied
+with care.
+The noise in the light curve of a given star is relatively consistent for the
+full baseline of observation and we have a very good physical generative model
+for the transit signal so we can simulate arbitrarily large sets of training
 examples.
-This means that there are a finite number of samples available for training
-and validation, and if there is a qualitatively different signal in the test
-set that is not generated by a transit, the model is at risk of unpredictably
-misclassifying that section.
-This problem can be largely mitigated by careful splitting of the dataset---as
-described below---but there are inevitably some false signals that are not
-properly accounted for.
-
-The following \sectionname s detail the application of this search procedure
-from the training set simulations through to the candidate selection.
-These candidates are then vetted by hand although more robust methods should
-be possible as discussed in \sect{vetting}.
-Finally, \sect{features} explores alternative representations of the data or
-features.
-
-\subsection{Splitting the dataset}\sectlabel{split}
-
-It is crucial that the model used to test for transits in a raw \kepler\
-light curve not be trained on the same data.
-We must split the light curve of each star into 3 disjoint sets.
-For the model to work well, we require that the signals induced by
-variability, noise, and other systematics be consistent between splits.
-It is, therefore, necessary that we assign the splits carefully.
-As discussed in \sect{data}, a light curve can be separated naturally into
-``sections'' of nearly contiguous measurements; these are the base unit for
-splitting the dataset.
-For the typical \kepler\ target, this division is finer than month long
-chunks and there are about 100 sections for each light curve.
-Each light curve section is cut out of a specific ``quarter'' and each quarter
-was observed during a specific ``season''.
-
-These divisions are relevant to this discussion because the spacecraft
-pointing across a quarter was extremely precise and the photometric aperture
-is fixed to the same pixels for the full quarter.
-Therefore, the instrumentally-induced systematics tend to be qualitatively
-consistent on quarter-long time scales.
-Every three months, the \kepler\ spacecraft rolled by 90~degrees causing the
-stars to end up on a different detector every quarter.
-This means that while the astrophysical variability should be shared between
-quarters at some level, the instrumental effects can be very different.
-A year later, however, the spacecraft returned to the original pointing.
-As a result, the data quality is also similar for observations made in the
-same season.
-
-In order to take advantage of the natural structure of the observations, we
-try to evenly distribute observations from each quarter and season across the
-three sets.
-When this is not possible (with Quarter 0, for example), we randomly assign
-the section to a split.
-
-\subsection{Transit simulations}
-
-As mentioned previously, we train the RF classification models on a set
-simulated transit signals injected into real light curves and a set of light
-curve sections assumed to contain no transits.
-For each data split, we construct a set of 20,000 \texttt{transit} samples and
-an equal number of \texttt{no transit} examples.
-Each of these samples is generated by randomly selecting a section of 201
-contiguous flux measurements from the split.
-Since we expect most of the systematic variability to be symmetric in time, we
-augment the training set by reversing the time series for half of the samples.
-This is analogous to image processing methods that exploit rotation and
-translational symmetries \citep[for an example from astronomy
-see][]{Dieleman:2015}.
-
-To generate the \texttt{transit} examples, we simulate the transit signal
-induced by the physical orbit of a large planet.
-The specific distribution of simulation parameters is listed in \tab{params}.
-In these simulations, we take limb darkening and integration time into
-account\footnote{\url{https://github.com/dfm/transit}}
-\citep{Mandel:2002, Kipping:2010}.
-For the purposes of this \paper, we only simulate circular orbits under the
-assumption that a single transit of a planet on an elliptical orbit would be
-nearly identical to a circular orbit at a different period.
-
-The dataset will still have some missing or flagged fluxes.
-In order to account for these missing points, we linearly interpolate these
-values based on their neighbors.
-For consistency, we perform the interpolation on the training set \emph{after
-injecting the synthetic transit signals}.
-Before passing the light curve sections to the model at any stage, we
-normalize the section by its empirical median and take the logarithm of the
-fluxes.
-This normalization appears to yield better performance in some test cases but
-better performance might be achieved using optimized methods.
-This choice is discussed further in \sect{params}.
-
-\begin{table}[htbp]
-\begin{center}
-\begin{tabular}{lcc}
-\toprule
-Parameter & Units & Distribution \\
-\midrule
-
-limb darkening parameters $q_1$ and $q_2$ & --- & $q \sim U(0,\,1)$ \\
-orbital period \period & days & $\ln \period \sim U(\ln 1500,\,\ln 5000)$ \\
-reference transit time $\delta t$ & days & $\delta t \sim U(-0.15,\,0.15)$ \\
-planet radius \rp & $R_\oplus$ & $\ln \rp \sim U(\ln 5,\,\ln 20)$ \\
-impact parameter $b$ & --- & $b \sim U(0,\,1)$ \\
-
-\bottomrule
-\end{tabular}
-\end{center}
-\caption{%
-The distribution of physical parameters for the injected signals.
-The limb darkening parameterization is given by \citet{Kipping:2013}.
-\tablabel{params}}
-\end{table}
-
-\subsection{Training, validation, and testing}\sectlabel{train}
-
-For each subset of the data, we train a RF classifier on the 40,000 training
-examples generated from the light curves in that split.
-The \texttt{RandomForestClassifier} implementation from \project{scikit-learn}
-has several tuning parameters that could be optimized using cross-validation
-but we find acceptable performance in most cases using fixed values.
-Specifically, we use a forest with 1000 trees by setting
-\texttt{num\_estimators = 1000}.
-We discuss this choice and the settings for other parameters in more detail in
-\sect{params}.
-
-Using this classifier, fit to one of the light curve subsets, we validate its
-performance on each set of simulations from the two other splits.
-This results in two precision--recall curves for the classifier.
-The \emph{precision} is an empirical measurement of the sample purity (or
-false positive rate) and \emph{recall} is a measurement of the completeness
-(the probability of detecting a true signal).
-Since the RF classifier scores each class and with a continuous value \score\
-between 0 and 1, both precision and recall can be tuned by changing the
-threshold value of \score\ above which the signal is considered a candidate.
-For each model--validation set pair, we ambitiously choose the threshold in
-order to obtain a precision of 100~percent.
-The result of this procedure applied to the three splits is three classifiers
-with two score thresholds each.
-
-Each of these six models has been fit using two splits so we then apply it to
-the raw light curves (without injected signals) from the remaining, untouched
-splits.
-This yields a \texttt{transit} class score as a function of transit time and
-any points above the detection threshold are passed along to the candidate
-selection procedure.
-
-At this point, there are two class predictions from two different models for
-every light curve section.
-Any section that is classified as \texttt{transit} by \emph{both models} is
-accepted as a single transit candidate.
-
-% \dfmtodo{make a figure}
-
-\subsection{Candidate vetting}\sectlabel{vetting}
-
-While the search procedure described in the previous sections is quite robust
-to false alarms, single transit events are extremely rare (as discussed in
-\sect{est}) and because of substantial violations of the model assumptions,
-false signals continue to outnumber the true signals in this catalog of
-candidate transits.
-To mitigate this problem, we manually inspect the light curves of candidate
-signals.
-As future work, we expect to automate this procedure by fitting a physical
-transit model and comparing it to simple models of stellar variability and
-instrumental artifacts.
-For this \paper, however, the catalog of candidates is sufficiently small that
-manual inspection is tractable.
-As demonstrated in \sect{demo}, the most common misclassifications are caused
-by astrophysical variability but some remaining systematic effects are also
-incorrectly labeled as candidates.
-
-\subsection{Feature selection}\sectlabel{features}
-
-In many supervised classification problems, a sophisticated feature
-extraction method is used to improve the performance of the procedure.
-For this specific problem, we find excellent performance using the 201
-normalized flux values as the features.
-The depth of the transit and the noise in the light curve is not irrelevant
-to detection so we don't normalize the features to unit variance in the
-standard way.
-Instead, we normalize each sample (feature vector) by it's empirical median
-value and take the logarithm.
-Another option for a feature set could be the Fourier transform or wavelet
-transform of the light curve section.
-Alternatively, the spectrogram of the fluxes in a larger window.
-We have experimented briefly with these options but find similar performance
-on the cases that we tested.
-
-\section{Tuning parameters}\sectlabel{tuning}
-
-Many choices need to be made in building this search procedure.
-Each of these choices can be specified by a set of parameters that can be
-tuned to optimize the method.
-In order to tune these parameters, we must decide on a quantitative
-measurement of the ``performance''.
-The goal is, of course, to \emph{robustly discover transiting planets}.
-In other words, the aim is a procedure that maximizes both \emph{recall} and
-\emph{precision}.
-
-As discussed previously, recall is the probability, integrated across the full
-parameter space of interest that a true transit signal will be detected by the
-method.
-In astronomy, this quantity is generally called the completeness or detection
-efficiency and it is routinely measured for transit surveys
-\citep{Petigura:2013, Dressing:2015, Foreman-Mackey:2015}.
-On the other hand, precision is the probability that a positive classification
-will be true.
-In astronomy, precision is generally hard to measure because we rarely have
-access to the ground truth.
-For this problem, correctly computing the recall is impossible because we
-never know that \emph{there is definitely no transit} at a given time in the
-light curve.
-
-What's more, it is not in general possible to maximize both recall and
-precision because transit signals are not completely separable from false
-positives.
-This means that, as the recall of the method improves, the false positive rate
-will also increase, reducing the precision.
-We must, therefore, choose a trade-off between recall and precision that
-represents our objective.
-The informal tradition in the transit search literature is to build a
-procedure that maximizes the recall at an extremely high ($\sim 100$~percent)
-fixed precision.
-
-The main tuning parameters of the method are as follows:
-\begin{itemize}
-
-{\item \emph{the number of training and validation examples for each data
-split} --- The performance of most classification models improves drastically
-as the size of the training set increases but in this case we are limited by
-the number of \texttt{no transit} samples that are available since we have no
-generative model for the variability and systematics.
-For this \paper, we choose 20,000 positive \texttt{transit} samples per split
-and an equal number of negative examples.}
-
-{\item \emph{the range of physical parameters used to simulate the transit
-signals} --- The search will be most sensitive to transits with parameters
-spanned by the training set but training on too many low signal-to-noise
-examples in noisy light curves leads to decreased precision.
-The parameter ranges used for the demonstrations here are given in
-\tab{params}.}
-
-{\item \emph{tuning parameters of the RF implementation} --- The
-\texttt{RandomForestClassifier} implementation has a few tuning parameters.
-The most important of these seems to be \texttt{num\_estimators}, the number
-of decision trees used in the forest.
-Increasing \texttt{num\_estimators} leads to substantial computational cost
-with diminishing returns on the search performance.
-Otherwise, there are a few parameters (for example, \texttt{max\_features},
-\texttt{min\_samples\_split}, and \texttt{min\_samples\_leaf}) that can be
-used to regularize the model but we have found that the performance is
-insensitive to these choices.
-As a trade-off between performance and computational cost, we set
-\texttt{num\_estimators = 1000} in all the examples shown in this \paper.}
-
-\end{itemize}
-In detail, the optimal set of decisions and parameter settings will be
-different for every target---and probably even for every permutation of the
-data splits.
-In practice, we find that the performance of the search is fairly insensitive
-to most of these choices so we choose parameters that seem to work well in
-most cases and leave optimization for future work.
-
-\paragraph{Estimating the precision}
-
-We estimate the precision of each RF classification model on the validation
-set as described in \sect{train}.
-As discussed in that \sectionname, we choose a target precision to
-100~percent and set the score threshold accordingly.
-This estimate is only applicable to the test set under two major assumptions.
-The first is that all transiting planets with more than one transit and a
-large signal-to-noise ratio have been previously discovered by one of the many
-transit searches applied the \kepler\ dataset \citep{Burke:2014, Rowe:2015}.
-This is a safe assumption because, for large planets, these surveys are all
-largely complete out to periods yielding only 2 or 3 transits in the \kepler\
-baseline \citep[for example][]{Petigura:2013}.
-The second assumption is not always valid so it makes this estimate of the
-precision only approximate and not completely reliable.
-This assumption is that the noise processes in the data are stationary.
-In other words, the transit-like noise signals in the training and validation
-sets must be ``similar'' to the signals in the test section.
-This constraint is nearly satisfied when the PDC light curves are used
-(\sect{data}) and the data are split carefully (\sect{split}).
-As demonstrated by the mis-classifications shown in \sect{demo}, however, it
-is clear that violations to this rule do exist in the data and final vetting
-of the candidates must be applied using a physical understanding of the
-signals.
-
-\section{Preliminary results}\sectlabel{demo}
-
-As a demonstration of the feasibility of this method to search for single
-transit events, we selected 3500 bright, Sun-like stars based on the revised
-stellar parameters collected and measured for a recent \kepler\ data release
-\citep{Huber:2014}.
-The targets were selected in the parameter range
-\begin{itemize}
-
-\item effective temperature:
-        $4100\,\mathrm{K} < T_\mathrm{eff} < 6100\,\mathrm{K}$,
-
-\item surface gravity:  $4.0 < \log g < 4.9$, and
-
-\item \kepler\ magnitude: $15 > K_\mathrm{p} > 10$.
-
-\end{itemize}
-
-This search results in 596 candidate transits in the light curves of these
-3500 stars.
-The vast majority of these candidates are misclassified false positives and
-many of them are caused by astrophysical sources.
-To weed out known astrophysical sources, we cross-match this list against
-known eclipsing binary stars \citep{Matijevic:2012} and stars with substantial
-variability \citep{McQuillan:2014}.
-Removing these signals results in 273 candidates.
-Of these candidates only one (KIC 10602068) is a convincing transit and the
-others all appear to be caused by systematic effects, instrumental or
-astrophysical.
-\Fig{candidates} shows some representative candidate signals from this final
-list.
-
-\paragraph{Failures}
-
-\dfmtodo{Add some discussion of the failures and make suggestions for better
-vetting techniques.}
-
-\begin{figure}[p]
-\begin{center}
-\includegraphics[width=0.5\textwidth]{figures/candidates.pdf}
-\end{center}
-\caption{%
-Some representative light curve sections that were labeled as candidates by
-the single transit search.
-The light curve in the top-left panel is a convincing transit signal but the
-other panels all appear to be caused by stellar variability or instrumental
-effects.
-\figlabel{candidates}}
-\end{figure}
-
-\section{KIC 10602068: A discovery}\sectlabel{params}
-
-In the 3500 light curves we searched for this \paper, we discovered one
-convincing single transit signal at $830.8093\pm0.0002$~KBJD in the light
-curve of the 14.9~Kep-mag G-dwarf KIC 10602068.
-Despite the fact that this is a very large signal, its discovery has never
-been reported.
-Given the estimate of $\sim 60$ detectable single transits in the full
-\kepler\ archival dataset, we do expect about one discovery in 3500 light
-curves.
-
-Even though only one transit is observed, if we assume that the transit is
-caused by a body on a Keplerian orbit around the host star, we can place
-constraints on the physical properties---even the orbital period---of the
-transiting candidate.
-This technique is similar in spirit to the ``photoeccentric effect''
-\citep{Dawson:2012} and ``asterodensity profiling'' \citep{Kipping:2012}.
-The fundamental principle is that the transit duration is a measurement of
-the instantaneous velocity of the planetary motion and this yields a
-constraint on the orbital period when combining this with a measurement of the
-stellar density and a prior on the eccentricity of the orbit.
-
-The photometrically derived physical properties for this star place it as a
-G-dwarf with a mass and radius of about 90~percent Solar \citep{Huber:2014}.
-Using these constraints and a beta function prior on the eccentricity of the
-orbit \citep{Kipping:2013a}, we run Markov Chain Monte Carlo
-\citep{Foreman-Mackey:2013} to sample the posterior probability for the
-physical parameters of the system.
-In this analysis, we take limb darkening and the finite exposure time into
-account \citep{Mandel:2002, Kipping:2010, Kipping:2013}.
-The results of this chain marginalized into the relevant physical dimensions
-are shown in \fig{corner}.
-The radius of the transiting body is measured to be $2.1 \pm
-0.4\,R_\mathrm{J}$.
-The period is very weakly constrained above a lower limit of
-$760\,\mathrm{days}$---set by the fact that a second transit is not
-detected---with 68~percent of the posterior mass in the range $760\,\mathrm{d}
-< \period < 1347\,\mathrm{d}$.
-
-Given the large radius of this candidate, it is probably stellar in nature
-instead of planetary but this could be easily confirmed using radial velocity
-follow-up.
-
-\begin{figure}[p]
-\begin{center}
-\includegraphics[width=\textwidth]{figures/corner.pdf}
-\end{center}
-\caption{%
-Posterior constraints on the physical parameters of the body transiting KIC
-10602068 assuming a bound Keplerian orbit.
-\figlabel{corner}}
-\end{figure}
-
-% \section{Prospects for population inference}\sectlabel{exopop}
-
-% Based on our single transit discoveries, we now want to place a limit on
-% the occurrence rate of long-period planets.
-% Since we only have one discovery thus far, we'll make the simplifying
-% assumption that the rate is flat in log-period and log-radius in the range
-% $1000\,\mathrm{d} < \period < 5000\,\mathrm{d}$ and $5\,R_\odot <
-% 20\,R_\odot$.
-% For this distribution, \citet{Foreman-Mackey:2014} derived the analytic
-% maximum likelihood result
-% \begin{eqnarray}
-% \rate &=& \frac{N_\mathrm{obs}}{\int Q(w)\dd w}
-% \end{eqnarray}
-% where $\rate$ is the occurrence rate per natural logarithm in period and
-% radius, $N_\mathrm{obs}$ is the number of detections, and the integral is over
-% the completeness measurements for every star that has been searched.
-% If we make the simplifying assumption that the detectability of a transit
-% depends on period only through Equations~(\eqref{q-geom})
-% and~(\eqref{q-time}), then this integral becomes
-% \begin{eqnarray}
-% \int Q(w)\dd w &=& \sum_{k=1}^K
-%     \left( \frac{4\,\pi^2}{G\,M_k} \right)^{1/3} \, R_k \, T_k \, Q_k \,
-%     \int \period^{-8/3}\,\rp^{-1} \dd\rp\dd\period \\
-%  &=& \sum_{k=1}^K
-%     \left( \frac{4\,\pi^2}{G\,M_k} \right)^{1/3} \, R_k \, T_k \, Q_k \,
-%     \ln \left(\frac{\rp_\mathrm{max}}{\rp_\mathrm{min}}\right)
-%     \frac{3}{5} \,
-%     \left[{\period_\mathrm{min}}^{-5/3} - {\period_\mathrm{max}}^{-5/3}\right]
-% \end{eqnarray}
-% where the sum is over all the targeted stars.
-
-\section{Discussion}\sectlabel{discussion}
-
-The discovery and characterization of transiting planets based on a single
-transit event is crucial for the future of transiting exoplanet surveys.
-Many of the most dynamically influential planets---like Jupiter in our Solar
-system---exhibit only a single transit in the full observational baseline of
-the \kepler.
-This will become even more of a problem as upcoming surveys move to shorter
-contiguous observations.
-For example, the \tess\ Mission is planned to get full-sky coverage at
-half-hour cadence but most of the sky will only be targeted for a month.
-This means that even habitable zone planets orbiting cool stars will transit
-their host \emph{at most once in the entire lifetime of the Mission}!
-
-To date, no methods exist for systematically and robustly discovering single
-transit events based on large photometric surveys.
-In this \paper, we present a novel and conceptually unique solution to this
-problem drawing on machine learning methods for supervised classification.
-This method has immense potential because it can be designed to be very robust
-to false positives and it can exploit the detailed shape of physical transits.
-
-Despite the fact that single transits are unlikely even if these long-period
-planets are intrinsically common, we estimate that $\sim 60$ events should be
-detectable in the \kepler\ archival dataset by extrapolating recent models of
-planet occurrence rates and taking selection effects into account.
-When applied to 3500 light curves from the \kepler\ dataset, this method
-recovers one previously unknown single transit event at
-$830.8093\pm0.0002$~KBJD in the light curve of KIC 10602068.
-This rate is consistent with the predicted yield of 60 events in the full
-dataset of 190,000 light curves.
-
-Assuming a bound Keplerian orbit, we place constraints on the physical
-properties of this transit candidate KIC 10602068.01.
-Using photometrically derived stellar properties, we find that this candidate
-has a radius of $2.1 \pm 0.4\,R_\mathrm{J}$ placing it as a very large planet
-or brown dwarf or a small star.
-
-This method for transit search is built using supervised classification and
-its performance relies on several strong assumptions about the datasets and
-these assumptions are sometimes violated leading to some transit-like signals
-that appear to be caused by noise to be misclassified as transits.
-The most severe assumption is that the noise properties of the data are
-stationary.
-In other words, we assume that variability in one subset of a light curve is
-completely spanned by the variability in the other sections.
-This assumption is, in general, false because the stochastic processes that
-cause stellar variability are complicated and non-stationary and the detector
-is plagued by non-negligible catastrophic changes in sensitivity and response.
-We attempt to mitigate this problem by using light curves that have been
-preprocessed to remove most of the instrumental effects and carefully dividing
-the data into subsets but some false positives are still incorrectly
-identified as candidates.
-
-One possible method for reducing the false positive rate would be to augment
-the training dataset using heuristic simulations of common false positives or
-the light curves of ``similar'' stars.
-Another option is to recognize that this search drastically reduces the
-parameter space requiring evaluation and comparing the predictive power of
-a transit model to other heuristic models including stellar variability or
-instrumental effects.
-
-\acknowledgments
-It is a pleasure to thank
-\ldots
-for helpful contributions to the ideas and code presented here.
-DFM and DWH were partially supported by the National Science Foundation
-(grant IIS-1124794),
-the National Aeronautics and Space Administration
-(grant NNX12AI50G), and the Moore--Sloan Data Science Environment at NYU.
-
-This research made use of the NASA \project{Astrophysics Data System} and the
-NASA Exoplanet Archive.
-The Archive is operated by the California Institute of Technology, under
-contract with NASA under the Exoplanet Exploration Program.
-This \paper\ includes data collected by the \kepler\ mission. Funding for the
-\kepler\ mission is provided by the NASA Science Mission directorate.
-We are grateful to the entire \kepler\ team, past and present.
-Their tireless efforts were all essential to the tremendous success of the mission
-and the successes of \KT, present and future.
-These data were obtained from the Mikulski Archive for Space Telescopes
-(MAST).
-STScI is operated by the Association of Universities for Research in
-Astronomy, Inc., under NASA contract NAS5-26555.
-Support for MAST is provided by the NASA Office of Space Science via grant
-NNX13AC07G and by other grants and contracts.
-
-{\it Facilities:} \facility{Kepler}
-
-\appendix
-
-\section{Some appendix}
+
+In the training step, a Random Forest (RF) classifier is trained to
+distinguish---based only on the light curve itself---between sections of light
+curve that contain transits from sections of the same size that do not.
+This model is then used to find candidates in left-out sections of the light
+curve.
+In principle, this model can capture arbitrarily complicated non-linear
+structure in the decision space and if the training set is large and complete
+it will ``learn'' the shape of a physical transit.
+In practice, classification algorithms like this also require a complete set
+of ``negative'' training examples so further vetting using physical models
+is necessary.
+
+% In \sect{est}, we extrapolate a recent model of the distribution of exoplanets
+% to the long periods considered in this \paper.
+% Using an approximate but realistic model for the detection efficiency of a
+% search for single transits, we estimate that $\sim 60$ single transit events
+% should be detectable in the archival \kepler\ dataset.
+% In \sect{data}, we describe the data and outline the structure exploited by
+% our transit search procedure.
+% In \sect{rfc}, we briefly describe the Random Forest classification framework
+% and in \sect{search} we outline the steps used to apply this model for transit
+% search.
+% This method requires the setting of many tuning parameters and the
+% optimization of these choices is both computationally and intellectually
+% challenging so in \sect{tuning} we discuss some steps in this direction.
+% In \sect{demo}, we demonstrate the feasibility of this method, present a
+% single transit discovery, and indicate some interesting weaknesses of the
+% method.
+% In \sectionname s~\sectref{params} we describe the parameter estimation that
+% is possible given a single transit.
+
+% and outline the prospects for exoplanet
+% population inference given a catalog of single transit discoveries.
 

### 2015-12-21 new_search.py

@@ -188,21 +188,25 @@ def get_peaks(kicid=None,
         system.duration = best[1]
 
         # 3. step
-        ind = np.argmax(np.abs(np.diff(y)))
-        step = StepModel(
-            height=y[ind] - y[ind+1],
-            frac_var=0.0,
-            value=1.0,
-            width=0.0,
-            t0=0.5*(x[ind] + x[ind+1]),
-        )
-        best = (np.inf, 0.0)
-        for w in np.linspace(-2, 2, 50):
-            step.width = w
-            d = np.sum((y - step.get_value(x))**2)
-            if d < best[0]:
-                best = (d, w)
-        step.width = best[1]
+        steps = []
+        for ind in [np.argmax(np.abs(np.diff(y))),
+                    np.argmin(np.abs(x - (t0 - 0.5*tau))),
+                    np.argmin(np.abs(x - (t0 + 0.5*tau)))]:
+            step = StepModel(
+                height=y[ind] - y[ind+1],
+                frac_var=0.0,
+                value=1.0,
+                width=0.0,
+                t0=0.5*(x[ind] + x[ind+1]),
+            )
+            best = (np.inf, 0.0)
+            for w in np.linspace(-2, 2, 50):
+                step.width = w
+                d = np.sum((y - step.get_value(x))**2)
+                if d < best[0]:
+                    best = (d, w)
+            step.width = best[1]
+            steps.append(step)
 
         # 4. box:
         inds = np.argsort(np.diff(y))
@@ -224,7 +228,9 @@ def get_peaks(kicid=None,
             ("box1", boxes[1]),
             ("gp", constant),
             ("box2", boxes[0]),
-            ("step", step),
+            ("step1", steps[0]),
+            ("step2", steps[1]),
+            ("step3", steps[2]),
         ]
         preds = dict()
         for name, mean_model in models:
@@ -365,7 +371,7 @@ def get_peaks(kicid=None,
         if "outlier" in preds:
             ax.plot(x, (preds["outlier"]-1)*1e3, "--g", lw=1.5)
         ax.plot(x, (system.get_value(x)-1)*1e3, "r", lw=1.5)
-        ax.plot(x, (step.get_value(x)-1)*1e3, "b", lw=1.5)
+        [ax.plot(x, (st.get_value(x)-1)*1e3, "b", lw=1.5) for st in steps]
[…]

### 2015-12-21 document/ms.tex
removing classification discussion from the paper

@@
 
-\section{Random forest classification}\sectlabel{rfc}
-
-A common task in the machine learning literature is called \emph{supervised
-classification} where the goal is to separate objects into classes
-represented by sets of labeled examples.
-In the astronomy literature, supervised classification has been used for
-variable star classification \citep{Richards:2011} star--galaxy separation
-\citep{Fadely:2012}, galaxy morphology prediction \citep{Dieleman:2015}, and
-other applications.
-In each of these problems, there are a set of measurements that have been
-assigned classes---by some other method; often manually---and the goal is to
-transfer these labels to a set of observations that have not yet been
-labeled.
-For a more in-depth discussion of the application of these techniques in
-astronomy, the interested reader is directed to \citet{Ivezic:2013}.
-
-In our problem of transit search, we want to ``label'' sections of light curve
-with either the \texttt{transit} or \texttt{no transit} class.
-This problem doesn't fall under the standard format of a supervised
-classification problem because very few long-period transits have actually
-been observed or classified.
-We do think, however, that we have a good physical generative model for the
-signal of interest and most of the observations of each star have no transits.
-Therefore, we train the model on simulated signals.
-
-The Random Forest (RF) classification model \citep{Breiman:2001} is a popular
-model in the machine learning community where it is a common go-to model for
-basic classification tasks.
-It has also been applied with great success in astronomy \citep[for
-example][]{Richards:2011, Richards:2012, Jenkins:2014}.
-The RF model works by fitting an ensemble of decision trees to randomly
-selected subsamples of the training dataset.
-Each tree in the forest is ``grown'' by greedily choosing decision boundaries
-that optimize the separation of the training data in randomly selected
-subsets of the features until the separation is complete, each leaf contains
-only one class or, at most, a fixed number of samples.
-At each branch, the decision boundary is set by maximizing either the entropy
-or the ``gini'' coefficient.
-
-We use the \project{scikit-learn} \citep{Pedregosa:2011} version of the RF
-classification algorithm\footnote{Specifically we use the
-\texttt{RandomForestClassifier} object;
-\url{http://scikit-learn.org/stable/modules/generated/sklearn.ensemble.RandomForestClassifier.html}.}
-implemented in \project{Python}.
-This implementation has state-of-the-art speed and
-performance\footnote{\url{http://blog.explainmydata.com/2014/03/big-speedup-for-random-forest-learning.html}}
-while maintaining a flexible and user-friendly interface.
-
-\section{Search methodology}\sectlabel{search}
-
-Now, we will apply the RF classification model to search for single transits
-in \kepler\ light curves.
-The basic structure of the problem, applied to the light curve of a single
-star, is:
-\begin{enumerate}
-
-{\item {\bf train} a classifier on simulated signals injected into a subset of
-the light curves sections,}
-
-{\item {\bf validate} the model on signals injected into a different subset of
-the data to estimate the precision of the results,}
-
-{\item {\bf test} the classifier by applying it to a final subset of the
-data---disjoint from the previous two sets---to predict the class
-(\texttt{transit} or \texttt{no transit}) of each light curve section, and}
-
-{\item iterate until the entire light curve has been classified.}
-
-\end{enumerate}
-This means that searching a single light curve involves training, validating,
-and testing at least 3 RF models.
-In practice, we find that it is sufficient to split the data (intelligently)
-into 3 disjoint subsets so that we need only train 3 classifiers for each
-star.
-
-A key assumption of this model is that the classes are sufficiently
-represented in feature space.
-In other words, the training set must span both of the classes.
-Given a large enough training set, this is not difficult for the
-\texttt{transit} class; we can simulate a transit for any combination of
-physical parameters.
-This is much more difficult for the \texttt{no transit} class.
-Since we don't have a generative model for the stellar and instrumental
-variability or other artifacts, we cannot simulate negative examples that
-cover the full space of possibilities.
-Instead we are using sections of real light curves as the \texttt{no transit}
-examples.
-This means that there are a finite number of samples available for training
-and validation, and if there is a qualitatively different signal in the test
-set that is not generated by a transit, the model is at risk of unpredictably
-misclassifying that section.
-This problem can be largely mitigated by careful splitting of the dataset---as
-described below---but there are inevitably some false signals that are not
-properly accounted for.
-
-The following \sectionname s detail the application of this search procedure
-from the training set simulations through to the candidate selection.
-These candidates are then vetted by hand although more robust methods should
-be possible as discussed in \sect{vetting}.
-Finally, \sect{features} explores alternative representations of the data or
-features.
-
-\subsection{Splitting the dataset}\sectlabel{split}
-
-It is crucial that the model used to test for transits in a raw \kepler\
-light curve not be trained on the same data.
-We must split the light curve of each star into 3 disjoint sets.
-For the model to work well, we require that the signals induced by
-variability, noise, and other systematics be consistent between splits.
-It is, therefore, necessary that we assign the splits carefully.
-As discussed in \sect{data}, a light curve can be separated naturally into
-``sections'' of nearly contiguous measurements; these are the base unit for
-splitting the dataset.
-For the typical \kepler\ target, this division is finer than month long
-chunks and there are about 100 sections for each light curve.
-Each light curve section is cut out of a specific ``quarter'' and each quarter
-was observed during a specific ``season''.
-
-These divisions are relevant to this discussion because the spacecraft
-pointing across a quarter was extremely precise and the photometric aperture
-is fixed to the same pixels for the full quarter.
-Therefore, the instrumentally-induced systematics tend to be qualitatively
-consistent on quarter-long time scales.
-Every three months, the \kepler\ spacecraft rolled by 90~degrees causing the
-stars to end up on a different detector every quarter.
-This means that while the astrophysical variability should be shared between
-quarters at some level, the instrumental effects can be very different.
-A year later, however, the spacecraft returned to the original pointing.
-As a result, the data quality is also similar for observations made in the
-same season.
-
-In order to take advantage of the natural structure of the observations, we
-try to evenly distribute observations from each quarter and season across the
-three sets.
-When this is not possible (with Quarter 0, for example), we randomly assign
-the section to a split.
-
-\subsection{Transit simulations}
-
-As mentioned previously, we train the RF classification models on a set
-simulated transit signals injected into real light curves and a set of light
-curve sections assumed to contain no transits.
-For each data split, we construct a set of 20,000 \texttt{transit} samples and
-an equal number of \texttt{no transit} examples.
-Each of these samples is generated by randomly selecting a section of 201
-contiguous flux measurements from the split.
-Since we expect most of the systematic variability to be symmetric in time, we
-augment the training set by reversing the time series for half of the samples.
-This is analogous to image processing methods that exploit rotation and
-translational symmetries \citep[for an example from astronomy
-see][]{Dieleman:2015}.
-
-To generate the \texttt{transit} examples, we simulate the transit signal
-induced by the physical orbit of a large planet.
-The specific distribution of simulation parameters is listed in \tab{params}.
-In these simulations, we take limb darkening and integration time into
-account\footnote{\url{https://github.com/dfm/transit}}
-\citep{Mandel:2002, Kipping:2010}.
-For the purposes of this \paper, we only simulate circular orbits under the
-assumption that a single transit of a planet on an elliptical orbit would be
-nearly identical to a circular orbit at a different period.
-
-The dataset will still have some missing or flagged fluxes.
-In order to account for these missing points, we linearly interpolate these
-values based on their neighbors.
-For consistency, we perform the interpolation on the training set \emph{after
-injecting the synthetic transit signals}.
-Before passing the light curve sections to the model at any stage, we
-normalize the section by its empirical median and take the logarithm of the
-fluxes.
-This normalization appears to yield better performance in some test cases but
-better performance might be achieved using optimized methods.
-This choice is discussed further in \sect{params}.
-
-\begin{table}[htbp]
-\begin{center}
-\begin{tabular}{lcc}
-\toprule
-Parameter & Units & Distribution \\
-\midrule
-
-limb darkening parameters $q_1$ and $q_2$ & --- & $q \sim U(0,\,1)$ \\
-orbital period \period & days & $\ln \period \sim U(\ln 1500,\,\ln 5000)$ \\
-reference transit time $\delta t$ & days & $\delta t \sim U(-0.15,\,0.15)$ \\
-planet radius \rp & $R_\oplus$ & $\ln \rp \sim U(\ln 5,\,\ln 20)$ \\
-impact parameter $b$ & --- & $b \sim U(0,\,1)$ \\
-
-\bottomrule
-\end{tabular}
-\end{center}
-\caption{%
-The distribution of physical parameters for the injected signals.
-The limb darkening parameterization is given by \citet{Kipping:2013}.
-\tablabel{params}}
-\end{table}
-
-\subsection{Training, validation, and testing}\sectlabel{train}
-
-For each subset of the data, we train a RF classifier on the 40,000 training
-examples generated from the light curves in that split.
-The \texttt{RandomForestClassifier} implementation from \project{scikit-learn}
-has several tuning parameters that could be optimized using cross-validation
-but we find acceptable performance in most cases using fixed values.
-Specifically, we use a forest with 1000 trees by setting
-\texttt{num\_estimators = 1000}.
-We discuss this choice and the settings for other parameters in more detail in
-\sect{params}.
-
-Using this classifier, fit to one of the light curve subsets, we validate its
-performance on each set of simulations from the two other splits.
-This results in two precision--recall curves for the classifier.
-The \emph{precision} is an empirical measurement of the sample purity (or
-false positive rate) and \emph{recall} is a measurement of the completeness
-(the probability of detecting a true signal).
-Since the RF classifier scores each class and with a continuous value \score\
-between 0 and 1, both precision and recall can be tuned by changing the
-threshold value of \score\ above which the signal is considered a candidate.
-For each model--validation set pair, we ambitiously choose the threshold in
-order to obtain a precision of 100~percent.
-The result of this procedure applied to the three splits is three classifiers
-with two score thresholds each.
-
-Each of these six models has been fit using two splits so we then apply it to
-the raw light curves (without injected signals) from the remaining, untouched
-splits.
-This yields a \texttt{transit} class score as a function of transit time and
-any points above the detection threshold are passed along to the candidate
-selection procedure.
-
-At this point, there are two class predictions from two different models for
-every light curve section.
-Any section that is classified as \texttt{transit} by \emph{both models} is
-accepted as a single transit candidate.
-
-% \dfmtodo{make a figure}
-
-\subsection{Candidate vetting}\sectlabel{vetting}
-
-While the search procedure described in the previous sections is quite robust
-to false alarms, single transit events are extremely rare (as discussed in
-\sect{est}) and because of substantial violations of the model assumptions,
-false signals continue to outnumber the true signals in this catalog of
-candidate transits.
-To mitigate this problem, we manually inspect the light curves of candidate
-signals.
-As future work, we expect to automate this procedure by fitting a physical
-transit model and comparing it to simple models of stellar variability and
-instrumental artifacts.
-For this \paper, however, the catalog of candidates is sufficiently small that
-manual inspection is tractable.
-As demonstrated in \sect{demo}, the most common misclassifications are caused
-by astrophysical variability but some remaining systematic effects are also
-incorrectly labeled as candidates.
-
-\subsection{Feature selection}\sectlabel{features}
-
-In many supervised classification problems, a sophisticated feature
-extraction method is used to improve the performance of the procedure.
-For this specific problem, we find excellent performance using the 201
-normalized flux values as the features.
-The depth of the transit and the noise in the light curve is not irrelevant
-to detection so we don't normalize the features to unit variance in the
-standard way.
-Instead, we normalize each sample (feature vector) by it's empirical median
-value and take the logarithm.
-Another option for a feature set could be the Fourier transform or wavelet
-transform of the light curve section.
-Alternatively, the spectrogram of the fluxes in a larger window.
-We have experimented briefly with these options but find similar performance
-on the cases that we tested.
-
-\section{Tuning parameters}\sectlabel{tuning}
-
-Many choices need to be made in building this search procedure.
-Each of these choices can be specified by a set of parameters that can be
-tuned to optimize the method.
-In order to tune these parameters, we must decide on a quantitative
-measurement of the ``performance''.
-The goal is, of course, to \emph{robustly discover transiting planets}.
-In other words, the aim is a procedure that maximizes both \emph{recall} and
-\emph{precision}.
-
-As discussed previously, recall is the probability, integrated across the full
-parameter space of interest that a true transit signal will be detected by the
-method.
-In astronomy, this quantity is generally called the completeness or detection
-efficiency and it is routinely measured for transit surveys
-\citep{Petigura:2013, Dressing:2015, Foreman-Mackey:2015}.
-On the other hand, precision is the probability that a positive classification
-will be true.
-In astronomy, precision is generally hard to measure because we rarely have
-access to the ground truth.
-For this problem, correctly computing the recall is impossible because we
-never know that \emph{there is definitely no transit} at a given time in the
-light curve.
-
-What's more, it is not in general possible to maximize both recall and
-precision because transit signals are not completely separable from false
-positives.
-This means that, as the recall of the method improves, the false positive rate
-will also increase, reducing the precision.
-We must, therefore, choose a trade-off between recall and precision that
-represents our objective.
-The informal tradition in the transit search literature is to build a
-procedure that maximizes the recall at an extremely high ($\sim 100$~percent)
-fixed precision.
-
-The main tuning parameters of the method are as follows:
-\begin{itemize}
-
-{\item \emph{the number of training and validation examples for each data
-split} --- The performance of most classification models improves drastically
-as the size of the training set increases but in this case we are limited by
-the number of \texttt{no transit} samples that are available since we have no
-generative model for the variability and systematics.
-For this \paper, we choose 20,000 positive \texttt{transit} samples per split
-and an equal number of negative examples.}
-
-{\item \emph{the range of physical parameters used to simulate the transit
-signals} --- The search will be most sensitive to transits with parameters
-spanned by the training set but training on too many low signal-to-noise
-examples in noisy light curves leads to decreased precision.
-The parameter ranges used for the demonstrations here are given in
-\tab{params}.}
-
-{\item \emph{tuning parameters of the RF implementation} --- The
-\texttt{RandomForestClassifier} implementation has a few tuning parameters.
-The most important of these seems to be \texttt{num\_estimators}, the number
-of decision trees used in the forest.
-Increasing \texttt{num\_estimators} leads to substantial computational cost
-with diminishing returns on the search performance.
-Otherwise, there are a few parameters (for example, \texttt{max\_features},
-\texttt{min\_samples\_split}, and \texttt{min\_samples\_leaf}) that can be
-used to regularize the model but we have found that the performance is
-insensitive to these choices.
-As a trade-off between performance and computational cost, we set
-\texttt{num\_estimators = 1000} in all the examples shown in this \paper.}
-
-\end{itemize}
-In detail, the optimal set of decisions and parameter settings will be
-different for every target---and probably even for every permutation of the
-data splits.
-In practice, we find that the performance of the search is fairly insensitive
-to most of these choices so we choose parameters that seem to work well in
-most cases and leave optimization for future work.
-
-\paragraph{Estimating the precision}
-
-We estimate the precision of each RF classification model on the validation
-set as described in \sect{train}.
-As discussed in that \sectionname, we choose a target precision to
-100~percent and set the score threshold accordingly.
-This estimate is only applicable to the test set under two major assumptions.
-The first is that all transiting planets with more than one transit and a
-large signal-to-noise ratio have been previously discovered by one of the many
-transit searches applied the \kepler\ dataset \citep{Burke:2014, Rowe:2015}.
-This is a safe assumption because, for large planets, these surveys are all
-largely complete out to periods yielding only 2 or 3 transits in the \kepler\
-baseline \citep[for example][]{Petigura:2013}.
-The second assumption is not always valid so it makes this estimate of the
-precision only approximate and not completely reliable.
-This assumption is that the noise processes in the data are stationary.
-In other words, the transit-like noise signals in the training and validation
-sets must be ``similar'' to the signals in the test section.
-This constraint is nearly satisfied when the PDC light curves are used
-(\sect{data}) and the data are split carefully (\sect{split}).
-As demonstrated by the mis-classifications shown in \sect{demo}, however, it
-is clear that violations to this rule do exist in the data and final vetting
-of the candidates must be applied using a physical understanding of the
-signals.
-
-\section{Preliminary results}\sectlabel{demo}
-
-As a demonstration of the feasibility of this method to search for single
-transit events, we selected 3500 bright, Sun-like stars based on the revised
-stellar parameters collected and measured for a recent \kepler\ data release
-\citep{Huber:2014}.
-The targets were selected in the parameter range
-\begin{itemize}
-
-\item effective temperature:
-        $4100\,\mathrm{K} < T_\mathrm{eff} < 6100\,\mathrm{K}$,
-
-\item surface gravity:  $4.0 < \log g < 4.9$, and
-
-\item \kepler\ magnitude: $15 > K_\mathrm{p} > 10$.
-
-\end{itemize}
-
-This search results in 596 candidate transits in the light curves of these
-3500 stars.
-The vast majority of these candidates are misclassified false positives and
-many of them are caused by astrophysical sources.
-To weed out known astrophysical sources, we cross-match this list against
-known eclipsing binary stars \citep{Matijevic:2012} and stars with substantial
-variability \citep{McQuillan:2014}.
-Removing these signals results in 273 candidates.
-Of these candidates only one (KIC 10602068) is a convincing transit and the
-others all appear to be caused by systematic effects, instrumental or
-astrophysical.
-\Fig{candidates} shows some representative candidate signals from this final
-list.
-
-\paragraph{Failures}
-
-\dfmtodo{Add some discussion of the failures and make suggestions for better
-vetting techniques.}
-
-\begin{figure}[p]
-\begin{center}
-\includegraphics[width=0.5\textwidth]{figures/candidates.pdf}
-\end{center}
-\caption{%
-Some representative light curve sections that were labeled as candidates by
-the single transit search.
-The light curve in the top-left panel is a convincing transit signal but the
-other panels all appear to be caused by stellar variability or instrumental
-effects.
-\figlabel{candidates}}
-\end{figure}
-
-\section{KIC 10602068: A discovery}\sectlabel{params}
-
-In the 3500 light curves we searched for this \paper, we discovered one
-convincing single transit signal at $830.8093\pm0.0002$~KBJD in the light
-curve of the 14.9~Kep-mag G-dwarf KIC 10602068.
-Despite the fact that this is a very large signal, its discovery has never
-been reported.
-Given the estimate of $\sim 60$ detectable single transits in the full
-\kepler\ archival dataset, we do expect about one discovery in 3500 light
-curves.
-
-Even though only one transit is observed, if we assume that the transit is
-caused by a body on a Keplerian orbit around the host star, we can place
-constraints on the physical properties---even the orbital period---of the
-transiting candidate.
-This technique is similar in spirit to the ``photoeccentric effect''
-\citep{Dawson:2012} and ``asterodensity profiling'' \citep{Kipping:2012}.
-The fundamental principle is that the transit duration is a measurement of
-the instantaneous velocity of the planetary motion and this yields a
-constraint on the orbital period when combining this with a measurement of the
-stellar density and a prior on the eccentricity of the orbit.
-
-The photometrically derived physical properties for this star place it as a
-G-dwarf with a mass and radius of about 90~percent Solar \citep{Huber:2014}.
-Using these constraints and a beta function prior on the eccentricity of the
-orbit \citep{Kipping:2013a}, we run Markov Chain Monte Carlo
-\citep{Foreman-Mackey:2013} to sample the posterior probability for the
-physical parameters of the system.
-In this analysis, we take limb darkening and the finite exposure time into
-account \citep{Mandel:2002, Kipping:2010, Kipping:2013}.
-The results of this chain marginalized into the relevant physical dimensions
-are shown in \fig{corner}.
-The radius of the transiting body is measured to be $2.1 \pm
-0.4\,R_\mathrm{J}$.
-The period is very weakly constrained above a lower limit of
-$760\,\mathrm{days}$---set by the fact that a second transit is not
-detected---with 68~percent of the posterior mass in the range $760\,\mathrm{d}
-< \period < 1347\,\mathrm{d}$.
-
-Given the large radius of this candidate, it is probably stellar in nature
-instead of planetary but this could be easily confirmed using radial velocity
-follow-up.
-
-\begin{figure}[p]
-\begin{center}
-\includegraphics[width=\textwidth]{figures/corner.pdf}
-\end{center}
-\caption{%
-Posterior constraints on the physical parameters of the body transiting KIC
-10602068 assuming a bound Keplerian orbit.
-\figlabel{corner}}
-\end{figure}
-
-% \section{Prospects for population inference}\sectlabel{exopop}
-
-% Based on our single transit discoveries, we now want to place a limit on
-% the occurrence rate of long-period planets.
-% Since we only have one discovery thus far, we'll make the simplifying
-% assumption that the rate is flat in log-period and log-radius in the range
-% $1000\,\mathrm{d} < \period < 5000\,\mathrm{d}$ and $5\,R_\odot <
-% 20\,R_\odot$.
-% For this distribution, \citet{Foreman-Mackey:2014} derived the analytic
-% maximum likelihood result
-% \begin{eqnarray}
-% \rate &=& \frac{N_\mathrm{obs}}{\int Q(w)\dd w}
-% \end{eqnarray}
-% where $\rate$ is the occurrence rate per natural logarithm in period and
-% radius, $N_\mathrm{obs}$ is the number of detections, and the integral is over
-% the completeness measurements for every star that has been searched.
-% If we make the simplifying assumption that the detectability of a transit
-% depends on period only through Equations~(\eqref{q-geom})
-% and~(\eqref{q-time}), then this integral becomes
-% \begin{eqnarray}
-% \int Q(w)\dd w &=& \sum_{k=1}^K
-%     \left( \frac{4\,\pi^2}{G\,M_k} \right)^{1/3} \, R_k \, T_k \, Q_k \,
-%     \int \period^{-8/3}\,\rp^{-1} \dd\rp\dd\period \\
-%  &=& \sum_{k=1}^K
-%     \left( \frac{4\,\pi^2}{G\,M_k} \right)^{1/3} \, R_k \, T_k \, Q_k \,
-%     \ln \left(\frac{\rp_\mathrm{max}}{\rp_\mathrm{min}}\right)
-%     \frac{3}{5} \,
-%     \left[{\period_\mathrm{min}}^{-5/3} - {\period_\mathrm{max}}^{-5/3}\right]
-% \end{eqnarray}
-% where the sum is over all the targeted stars.
-
 \section{Discussion}\sectlabel{discussion}
@@
 
-\section{Supervised classification}
-
-We propose a transit search method that shares some similarities with the PH
-model but, instead of human classifiers, we use a supervised classification
-model trained on large numbers of simulated transit signals injected into
-real \kepler\ light curves.
-This procedure is motivated because, by definition, most randomly selected
-sections of light curve contain no transits and there is an excellent physical
-model for the signals of interest.
-If we can train a classification model to robustly separate light curve
-sections with transits from sections without then we should be able to use
-this in-place of the humans to find single transit events.
-This method is novel as a means to transit search and it differs substantially
-from the standard methods.
-
-Automated classification processes have been hugely successful in the machine
-learning literature.
-% when applied to the right datasets \dfmtodo{cite some things}.
-Many astronomical problems can't be naturally solved by the standard machine
-learning models because of their heterogeneous character and heteroscedastic
-uncertainties.
-The search for single transits, however, is an excellent use case when applied
-with care.
-The noise in the light curve of a given star is relatively consistent for the
-full baseline of observation and we have a very good physical generative model
-for the transit signal so we can simulate arbitrarily large sets of training
-examples.
-
-In the training step, a Random Forest (RF) classifier is trained to
-distinguish---based only on the light curve itself---between sections of light
-curve that contain transits from sections of the same size that do not.
-This model is then used to find candidates in left-out sections of the light
-curve.
-In principle, this model can capture arbitrarily complicated non-linear
-structure in the decision space and if the training set is large and complete
-it will ``learn'' the shape of a physical transit.
-In practice, classification algorithms like this also require a complete set
-of ``negative'' training examples so further vetting using physical models
-is necessary.
-
-% In \sect{est}, we extrapolate a recent model of the distribution of exoplanets
-% to the long periods considered in this \paper.
-% Using an approximate but realistic model for the detection efficiency of a
-% search for single transits, we estimate that $\sim 60$ single transit events
-% should be detectable in the archival \kepler\ dataset.
-% In \sect{data}, we describe the data and outline the structure exploited by
-% our transit search procedure.
-% In \sect{rfc}, we briefly describe the Random Forest classification framework
-% and in \sect{search} we outline the steps used to apply this model for transit
-% search.
-% This method requires the setting of many tuning parameters and the
-% optimization of these choices is both computationally and intellectually
-% challenging so in \sect{tuning} we discuss some steps in this direction.
-% In \sect{demo}, we demonstrate the feasibility of this method, present a
-% single transit discovery, and indicate some interesting weaknesses of the
-% method.
-% In \sectionname s~\sectref{params} we describe the parameter estimation that
-% is possible given a single transit.
-
-% and outline the prospects for exoplanet
-% population inference given a catalog of single transit discoveries.
-
 \clearpage

### 2015-12-23 new_search.py
better step initialization

@@ -10,6 +10,7 @@ from functools import partial
 import matplotlib.pyplot as pl
 from multiprocessing import Pool
 from scipy.optimize import minimize
+from collections import OrderedDict
 
 import george
 from george import kernels, ModelingMixin
@@ -188,10 +189,11 @@ def get_peaks(kicid=None,
         system.duration = best[1]
 
         # 3. step
-        steps = []
-        for ind in [np.argmax(np.abs(np.diff(y))),
-                    np.argmin(np.abs(x - (t0 - 0.5*tau))),
-                    np.argmin(np.abs(x - (t0 + 0.5*tau)))]:
+        best = (np.inf, 0, 0.0)
+        # for ind in [np.argmax(np.abs(np.diff(y))),
+        #             np.argmin(np.abs(x - (t0 - 0.5*tau))),
+        #             np.argmin(np.abs(x - (t0 + 0.5*tau)))]:
+        for ind in range(len(y) - 1):
             step = StepModel(
                 height=y[ind] - y[ind+1],
                 frac_var=0.0,
@@ -199,14 +201,19 @@ def get_peaks(kicid=None,
                 width=0.0,
                 t0=0.5*(x[ind] + x[ind+1]),
             )
-            best = (np.inf, 0.0)
-            for w in np.linspace(-2, 2, 50):
+            for w in np.linspace(-2, 2, 10):
                 step.width = w
                 d = np.sum((y - step.get_value(x))**2)
                 if d < best[0]:
-                    best = (d, w)
-            step.width = best[1]
-            steps.append(step)
+                    best = (d, ind, w)
+        _, ind, w = best
+        step = StepModel(
+            height=y[ind] - y[ind+1],
+            frac_var=0.0,
+            value=1.0,
+            width=w,
+            t0=0.5*(x[ind] + x[ind+1]),
+        )
 
         # 4. box:
         inds = np.argsort(np.diff(y))
@@ -223,17 +230,17 @@ def get_peaks(kicid=None,
         # print(check_gradient(box, x))
 
         # Loop over models and compare them.
-        models = [
+        models = OrderedDict([
             ("transit", system),
             ("box1", boxes[1]),
+            ("step", step),
             ("gp", constant),
             ("box2", boxes[0]),
-            ("step1", steps[0]),
-            ("step2", steps[1]),
-            ("step3", steps[2]),
-        ]
[…]

### 2015-12-23 new_search.py
quiet args

@@ -240,8 +240,8 @@ def get_peaks(kicid=None,
 
             if name == "transit":
                 bounds[n.index("mean:t0")] = (t0 - 0.5*tau, t0 + 0.5*tau)
-                bounds[n.index("mean:q1_param")] = (-20, 20)
-                bounds[n.index("mean:q2_param")] = (-20, 20)
+                bounds[n.index("mean:q1_param")] = (-10, 10)
+                bounds[n.index("mean:q2_param")] = (-10, 10)
 
             bounds[n.index("kernel:k2:ln_M_0_0")] = (np.log(0.1), None)
             bounds[n.index("white:value")] = (2*np.log(np.median(yerr)), None)
@@ -538,6 +538,7 @@ if __name__ == "__main__":
         plot_all=args.plot_all,
         max_peaks=args.max_peaks,
         verbose=args.verbose,
+        quiet=args.quiet,
         delete=args.clean,
     )
 

### 2015-12-23 document/ms.tex
document structure

@@
     Bernhard~Sch\"olkopf\altaffilmark{\mpis},
-    \etal
+    and others
 }
@@
 
+\section{Single transit search}
+
+Previous automated searches for transits in the \kepler\ light
+curves have restricted their results to candidates with at least three
+observable transits in the dataset.
+This restriction minimizes contamination by false alarms at low
+signal-to-noise.
+Noise in the light curves introduced by stellar or instrumental variability
+can easily masquerade as a small planet with a long orbital period and lead to
+
 \section{Data preparation}\sectlabel{data}
+
+We start with the PDC-MAP light curves downloaded from
+MAST\footnote{\url{https://archive.stsci.edu/kepler/}}.
 
@@
 2015-03-25.}.
+
+\section{Candidate vetting}
+
+\paragraph{Light curve}
+
+Blah.
+
+\paragraph{Pixel-level}
+
+Blah.
+
+\paragraph{Auxiliary data}
+
+Blah.
+
+\section{Results}
+
+\section{Completeness \& reliability}
 

### 2016-01-04 document/ms.tex
adding a figure

@@
 
-Blah.
+\begin{figure}[p]
+\begin{center}
+\includegraphics[width=\textwidth]{figures/model_comp.pdf}
+\end{center}
+\caption{%
+Model comparison.
+\figlabel{model-comp}}
+\end{figure}
 
@@
 
-\begin{figure}[p]
-\begin{center}
-\includegraphics{figures/predict.pdf}
-\end{center}
-\caption{%
-The expected number of single transit events---extrapolated from the
-\citet{Dong:2013} power-law model fit to the shorter period \kepler\
-candidates---as a function of the effective signal-to-noise threshold of the
-search procedure.
-The shaded region indicates the uncertainties propagated from the model
-parameters.
-\figlabel{predict}}
-\end{figure}
-
 \clearpage

### 2016-01-04 document/figures/model_comp.py

@@ -7,22 +7,21 @@ from plot_setup import COLORS
 import os
 import pickle
 import numpy as np
-import pandas as pd
 import matplotlib.pyplot as pl
 
 from peerless.search import search
 
 models = [
-    ("transit", "transit", 8426957, 0),
+    ("variability", "gp", 7220674, 0),
     ("step", "step", 8631697, 0),
     ("box", "box2", 5521451, 0),
-    ("variability", "gp", 7220674, 0),
+    ("transit", "transit", 8426957, 0),
 ]
 
-fig, axes = pl.subplots(1, len(models), figsize=(4*len(models), 4.3))
+fig, axes = pl.subplots(2, 2, figsize=(8, 8))
 
 os.makedirs("cache", exist_ok=True)
-for i, (disp, name, kicid, peak_id) in enumerate(models):
+for a, ax, (disp, name, kicid, peak_id) in zip("abcd", axes.flatten(), models):
     fn = os.path.join("cache", "{0}.pkl".format(kicid))
     if os.path.exists(fn):
         print("using cached file: {0}".format(fn))
@@ -34,7 +33,6 @@ for i, (disp, name, kicid, peak_id) in enumerate(models):
         with open(fn, "wb") as f:
             pickle.dump(results, f, -1)
 
-    ax = axes[i]
     peak = results.peaks[peak_id]
     t0 = peak["transit_time"]
     rng = t0 + np.array([-2, 2])
@@ -45,15 +43,14 @@ for i, (disp, name, kicid, peak_id) in enumerate(models):
     x0 = np.linspace(rng[0], rng[1], 500)
     ax.plot(24*(x[m] - t0), y[m], ".", color=COLORS["DATA"])
 
-    # mu = gp.mean.get_value(x0)
-    # ax.plot(24*(x0 - t0), mu, color=COLORS["MODEL_1"], lw=2)
-
     mu = gp.predict(y0, x0, return_cov=False)
     ax.plot(24*(x0 - t0), mu, color=COLORS["MODEL_2"], lw=2.5, alpha=0.8)
+    ax.annotate("({0})".format(a), xy=(0, 0), xycoords="axes fraction",
+                xytext=(5, 12), textcoords="offset points")
 
     ax.set_xlim(24*(rng - t0))
     ax.set_yticklabels([])
     ax.set_xlabel("hours since event")
-    ax.set_title("KIC {0}: {1}".format(kicid, disp))
[…]

### 2016-01-05 peerless/data.py
save transit depth and stuff

@@ -77,14 +77,9 @@ def load_light_curves(fns, pdc=True, delete=False, remove_kois=False,
 
         # Load the meta data.
         hdr = fitsio.read_header(fn, 0)
-        meta = dict(
-            channel=hdr["CHANNEL"],
-            skygroup=hdr["SKYGROUP"],
-            module=hdr["MODULE"],
-            output=hdr["OUTPUT"],
-            quarter=hdr["QUARTER"],
-            season=hdr["SEASON"],
-        )
+        meta = dict((k.lower(), hdr[k]) for k in hdr)
+        hdr = fitsio.read_header(fn, 2)
+        header = dict((k, hdr[k]) for k in hdr)
 
         # Remove any KOI points.
         if remove_kois:
@@ -115,7 +110,7 @@ def load_light_curves(fns, pdc=True, delete=False, remove_kois=False,
             m0 = m & (labels == i)
             if not np.any(m0):
                 continue
-            lcs.append(LightCurve(x[m0], y[m0], yerr[m0], meta,
+            lcs.append(LightCurve(x[m0], y[m0], yerr[m0], meta, header,
                                   data["MOM_CENTR1"][m0],
                                   data["MOM_CENTR2"][m0],
                                   data["POS_CORR1"][m0],
@@ -138,7 +133,7 @@ def running_median_trend(x, y, hw=2.0):
 
 class LightCurve(object):
 
-    def __init__(self, time, flux, ferr, meta,
+    def __init__(self, time, flux, ferr, meta, header,
                  mom_cen_1, mom_cen_2, pos_corr_1, pos_corr_2,
                  texp=TEXP, hw=2.0):
         self.trend = running_median_trend(time, flux, hw=hw)
@@ -158,6 +153,7 @@ class LightCurve(object):
         self.pos_corr_2 = np.ascontiguousarray(pos_corr_2, dtype=float)
 
         self.meta = meta
+        self.header = header
         self.footprint = self.time.max() - self.time.min()
         self.texp = texp
 

### 2016-01-05 document/ms.tex
figs

@@
 
-\section{Single transit search}
+\section{Data selection \& preparation}\sectlabel{data}
 
-Previous automated searches for transits in the \kepler\ light
-curves have restricted their results to candidates with at least three
-observable transits in the dataset.
-This restriction minimizes contamination by false alarms at low
-signal-to-noise.
-Noise in the light curves introduced by stellar or instrumental variability
-can easily masquerade as a small planet with a long orbital period and lead to
+For the purposes of this \paper, we select the 40,000 brightest G and K dwarfs
+from the \kepler\ catalog using the following parameters:
 
-\section{Data preparation}\sectlabel{data}
+        % m = (4200 <= stlr.teff) & (stlr.teff <= 6100)
+        % m &= stlr.radius <= 1.15
+        % m &= stlr.dataspan > 365.25*2.
+        % m &= stlr.dutycycle > 0.6
+        % m &= stlr.rrmscdpp07p5 <= 1000.
+        % m &= stlr.kepmag < 15.
+
+\begin{itemize}
+{\item $4200\unit{K} \le T_\mathfm{eff} \le 6100\unit{K}$}
+
+\end{itemize}
 
@@
 \caption{%
-Model comparison.
+Representative examples of candidate events flagged by the initial search.
+Each example falls into a different model category and the figure shows the
+data as black points and the best fit mean model prediction.
+The examples represent the following model categories:
+\emph{(a)} variability, \emph{(b)} step, \emph{(c)} box, and \emph{(d)}
+transit.
 \figlabel{model-comp}}

### 2016-01-05 peerless/fit.py
mpi

@@ -1,0 +1,234 @@
+# -*- coding: utf-8 -*-
+
+__all__ = ["TransitModel", "setup_fit"]
+
+import numpy as np
+from scipy.stats import beta
+import matplotlib.pyplot as pl
+from scipy.optimize import minimize
+
+import george
+from george import kernels
+
+import transit
+
+from .data import load_light_curves_for_kic
+
+
+class TransitModel(object):
+
+    eb = beta(1.12, 3.09)
+
+    def __init__(self, gps, system, smass, smass_err, srad, srad_err,
+                 fit_lcs, other_lcs):
+        self.t0rng = system.bodies[0].t0 + np.array([-1., 1.])
+        self.gps = gps
+        self.system = system
+        self.smass = smass
+        self.smass_err = smass_err
+        self.srad = srad
+        self.srad_err = srad_err
+        self.fit_lcs = fit_lcs
+        self.other_lcs = other_lcs
+
+    # Probabilistic model:
+    def lnprior(self):
+        if not (self.t0rng[0] < self.system.bodies[0].t0 < self.t0rng[1]):
+            return -np.inf
+
+        lp = 0.0
+
+        # planet
+        body = self.system.bodies[0]
+        if body.b < 0.0:
+            lp -= 1e6  # horror
+        lp -= np.log(body.a)
+        lp += self.eb.logpdf(body.e)
+
+        # stellar parameters
+        star = self.system.central
+        lp -= 0.5 * (
+            ((star.mass - self.smass) / self.smass_err) ** 2 +
+            ((star.radius - self.srad) / self.srad_err) ** 2
+        )
+
+        # limb darkening
+        q = star.q1
+        lp -= np.logaddexp(-np.log(q), -np.log(1.0 - q))
+        q = star.q2
+        lp -= np.logaddexp(-np.log(q), -np.log(1.0 - q))
+
+        return lp
+
+    def lnlike(self):
+        system = self.system
+        ll = 0.0
+        preds = []
+        for gp, lc in zip(self.gps, self.fit_lcs):
+            mu = system.light_curve(lc.time, texp=lc.texp, maxdepth=2)
+            r = lc.flux - mu
+            ll += gp.lnlikelihood(r, quiet=True)
+            if not (np.any(mu < system.central.flux) and np.isfinite(ll)):
+                return -np.inf, (0, None)
+            preds.append((gp.predict(r, lc.time, return_cov=False), mu))
+
+        # Compute number of cadences with transits in the other light curves.
[…]

### 2016-01-08 document/ms.tex
dmv writing

@@
 \newcommand{\period}{{\ensuremath{P}}}
-\newcommand{\rp}{{\ensuremath{R_\mathrm{P}}}}
-\newcommand{\rate}{{\ensuremath{\Gamma}}}
-\newcommand{\score}{{\ensuremath{S}}}
+\newcommand{\unit}[1]{{\ensuremath{\,\mathrm{#1}}}}
 
@@
 
-For the purposes of this \paper, we select the 40,000 brightest G and K dwarfs
-from the \kepler\ catalog using the following parameters:
-
-        % m = (4200 <= stlr.teff) & (stlr.teff <= 6100)
-        % m &= stlr.radius <= 1.15
-        % m &= stlr.dataspan > 365.25*2.
-        % m &= stlr.dutycycle > 0.6
-        % m &= stlr.rrmscdpp07p5 <= 1000.
-        % m &= stlr.kepmag < 15.
-
+For the purposes of this \paper, we select the $\sim40,000$ brightest and
+quietest G and K dwarfs from the \kepler\ catalog using the following
+parameters:
 \begin{itemize}
-{\item $4200\unit{K} \le T_\mathfm{eff} \le 6100\unit{K}$}
-
+{\item $4200\unit{K} \le T_\mathrm{eff} \le 6100\unit{K}$,}
+{\item $R_\star \le 1.15\,R_\odot$,}
+{\item $K_p \le 15\unit{mag}$, and}
+{\item $\mathrm{CDPP}_{7.5\unit{hrs}} \le 1000\unit{ppm}$.}
 \end{itemize}
+We also restrict the sample to only include targets with a data span of more
+than two years and a duty cycle of better than $0.6$.
+Since the \kepler\ data have been searched for shorter period planets
+\dfmtodo{CITE Coughlin} and eclipsing binaries \dfmtodo{CITE EB catalog} than
+targeted by this project, we censor these previously known targets.
+For the known EBs, we simply remove these targets from the candidate list.
+For the confirmed and candidate KOIs from \dfmtodo{Coughlin}, we remove data
+within 2 transit durations of the known candidates.
 
@@
 
-\section{Estimated yield}\sectlabel{est}
-
-Before the launch of the \kepler\ Mission, \citet{Yee:2008} predicted the
-yield of single transit events based on the planet occurrence rates estimated
-based on small catalog of radial velocity discoveries \citep{Butler:2006} and
-a fit to their occurrence rate \citep{Cumming:2008}.
-Using these early results and the pre-launch specifications of the \kepler\
-Mission, \citet{Yee:2008} predicted that \kepler\ would discover $\sim 6$
-single transit events in the full dataset.
-Now that the Mission is complete and we have better estimates of the
-occurrence rate and distribution of planets \citep[for example][]{Dong:2013,
-Petigura:2013, Foreman-Mackey:2014, Dressing:2015}, we can update the
-predicted yield for single transit events in the \kepler\ light curves.
-To make this estimate, we extrapolate the distribution of large planets on
-relatively short orbits out to longer periods, taking detection efficiency
-and the survey and targeting properties into account.
-
-We will base our estimate on an assumed model $Q_k(\rp,\,\period)$ for the
-absolute probability of detecting a planet with radius \rp\ and period
-\period\ orbiting the star $k$, and the occurrence rate distribution
-\begin{eqnarray}
-\rate (\rp,\,\period) &=& \frac{\dd N}{\dd\ln\rp\dd\ln\period} \quad,
-\end{eqnarray}
-the expected number of planets per star, per logarithmic radius, per
-logarithmic period.
-Given these two quantities, the expected number of single transits in the
-\kepler\ data is given by
-\begin{eqnarray}
-N &=& \sum_{k=1}^K N_k
-\end{eqnarray}
-where the sum is over the $K$ stars in the sample and $N_k$ is the expected
-number of observable transits around star $k$
-\begin{eqnarray}\eqlabel{nk}
-N_k &=& \int Q_k(\rp,\,\period) \, \rate (\rp,\,\period)
-    \dd\ln\rp \dd\ln\period \quad.
-\end{eqnarray}
-The integral in \eq{nk} is over the full range of target parameters.
-
-For the purposes of this discussion, we assume an approximate simple detection
-efficiency model with three contributions: the geometric transit probability,
-the temporal transit probability, and signal-to-noise ratio threshold of the
-search technique.
-Assuming circular orbits, the geometric transit probability is given by
-\citep{Winn:2010}
-\begin{eqnarray}\eqlabel{q-geom}
-Q_k^\mathrm{(geom)}(\rp,\,\period) &=& \frac{R_k}{a} \\
-&=& \left( \frac{4\,\pi^2}{G\,M_k} \right)^{1/3} \, R_k \, \period^{-2/3}
-\end{eqnarray}
-where $R_k$ and $M_k$ are the radius and mass of the star $k$ respectively.
-The eccentricity distribution of these long-period planets will affect this
-transit probability \citep{Kipping:2014} but this simple prescription should
-be sufficient for a rough estimate.
-For long-period orbits, the temporal transit probability will be given by
-\begin{eqnarray}\eqlabel{q-time}
-Q_k^\mathrm{(time)}(\rp,\,\period) &=& \frac{T_k}{\period}
-\end{eqnarray}
-where $T_k$ is the total time that \kepler\ spent observing the star $k$.
-Finally, the detection threshold depends on the detailed sensitivity of the
-search procedure but we will approximate it as a simple step function in
-signal-to-noise ratio of the transit.
-This contribution will be given approximately by
-\begin{eqnarray}
-Q_k^\mathrm{(detect)}(\rp,\,\period) &=& \left\{\begin{array}{ll}
-1 & \mathrm{if}\,\left(\rp/R_k\right)^2 > f\,\sigma_k \\
-0 & \mathrm{otherwise}
-\end{array}\right.
-\end{eqnarray}
-where $\sigma_k$ is an estimate of the noise in light curve of star $k$ and
-$f$ is the detection threshold for the method.
-
-Combining the detection efficiency components, the integral from \eq{nk}
-becomes
-\begin{eqnarray}\eqlabel{nk-2}
-N_k &=& \left( \frac{4\,\pi^2}{G\,M_k} \right)^{1/3} \, R_k \, T_k
-    \int_{\rp_\mathrm{min}} ^{\rp_\mathrm{max}} \frac{\dd\rp}{\rp}
-    \int_{\period_\mathrm{min}} ^{\period_\mathrm{max}}
-        \period^{-8/3}\,\rate(\rp,\,\period) \dd\period
-\end{eqnarray}
-where all the integration limits are set by the target parameter space.
-Because of the detection probability threshold, $\rp_\mathrm{min}$ can be no
-smaller than $R_k\,\sqrt{f\,\sigma_k}$.
-\citet{Dong:2013} used the catalog of short period transiting planets found
-by \kepler\ to constrain a model for the occurrence rate of large planets of
-the form
-\begin{eqnarray}
-\rate(\rp,\,\period) &=& C\,\left(\frac{\period}{10\,\mathrm{d}}\right)^\beta
-\end{eqnarray}
-in a set of radius bins.
-Using this model, the integral in \eq{nk-2} becomes
-\begin{eqnarray}
-N_k &=& \left( \frac{4\,\pi^2}{G\,M_k} \right)^{1/3} \, R_k \, T_k \,
-    \sum_{j=1}^J \frac{C_j}{(10\,\mathrm{d})^{\beta_j}}\,
-    \ln \left( \frac{\rp_{\mathrm{max},j}}{\rp_{\mathrm{min},j}} \right) \,
-    \left[ \frac{{\period_\mathrm{min}}^{\beta_j - 5/3}}{5/3-\beta_j} \right]
-\end{eqnarray}
-where the sum is over the $J$ radial bins studied by \citet{Dong:2013}.
-It's important to note that the model used by \citet{Dong:2013} is given in
-base-10 logarithms so the units must be converted to natural logarithms as
-appropriate.
-
-Assuming the stellar parameters provided by the NASA Exoplanet
-Archive\footnote{We downloaded the \texttt{q1\_q16\_stellar} table from
-\url{http://exoplanetarchive.ipac.caltech.edu/} on 2015-04-03.}
-\citep{Huber:2014} and approximating the stellar noise using the 15-hour CDPP
-\citep{Christiansen:2012}, \fig{predict} shows the extrapolated number of
-transiting planets with $1500\,\mathrm{d} < \period < 5000\,\mathrm{d}$ based
-on the \citet{Dong:2013} power-law model.
-For a detection threshold $f\sim10$, the expected number of single transit
-events in the \kepler\ light curves is $\sim 60$.
-
-This results is much more optimistic than the pre-launch estimate from
-\citet{Yee:2008} for a few reasons.
-One effect is that, the \kepler\ Mission ran for more than four
-years---longer than the fiducial Mission goal---and $\sim190,000$ stars were
-targeted for nearly the full baseline instead of the original 100,000.
-\dfmtodo{Explain the other reasons.}
+\section{Supervised classification}
 

### 2016-01-20 document/figures/full_sample.py
full sample plot

@@ -1,0 +1,54 @@
+# -*- coding: utf-8 -*-
+
+from plot_setup import COLORS
+
+import matplotlib
+import numpy as np
+import matplotlib.pyplot as pl
+
+from peerless.catalogs import KOICatalog
+
+fig, ax = pl.subplots(1, 1, figsize=(6, 4))
+
+kois = KOICatalog().df
+m = kois.koi_disposition == "CONFIRMED"
+x, y = kois[m].koi_period, kois[m].koi_prad
+
+x0 = np.exp(np.linspace(np.log(0.1), np.log(9e4), 500))
+for f in np.exp(np.linspace(np.log(0.001), np.log(100), 8)):
+    y0 = np.sqrt(f * np.sqrt(x0))
+    ax.plot(x0, y0, "k", lw=0.5, alpha=0.5)
+
+ax.loglog(x, y, ".k", ms=4)
+ax.set_xlim(1.1, 450.)
+ax.set_ylim(0.3, 30)
+ax.set_xlabel("orbital period [days]")
+ax.set_ylabel("planet radius [$R_\oplus$]")
+
+fmt = matplotlib.ticker.FormatStrFormatter("%.0f")
+ax.xaxis.set_major_formatter(fmt)
+ax.yaxis.set_major_formatter(fmt)
+
+# Plot KOIs.
+m = kois.koi_disposition == "CANDIDATE"
+x, y = kois[m].koi_period, kois[m].koi_prad
+ax.plot(x, y, ".", color="#6baed6", ms=3, alpha=0.3, zorder=-1)
+
+# Plot the solar system.
+rad = np.array("2439.7 6051.8 6371.00 3389.5 69911 58232 25362 24622"
+               .split(), dtype=float)
+period = np.array("0.2408467 0.61519726 1.0000174 1.8808476 11.862615 "
+                  "29.447498 84.016846 164.79132".split(), dtype=float)
+ax.plot(period * 365, rad / rad[2], "o", color="#fd8d3c")
+ax.set_xlim(0.5, max(x0))
+ax.axvline(4.2*365 / 2., color="k", alpha=0.6)
+ax.axvline(4.2*365, color="k", ls="dashed", alpha=0.6)
+
+# xerr = np.array(fits[["period_err_1", "period_err_2"]]).T
+# yerr = np.array(fits[["radius_err_1", "radius_err_2"]]).T / 0.01
+# x = np.array(fits.period)
[…]

### 2016-01-21 document/figures/full_sample.py
adding fits

@@ -4,6 +4,7 @@ from plot_setup import COLORS
 
 import matplotlib
 import numpy as np
+import pandas as pd
 import matplotlib.pyplot as pl
 
 from peerless.catalogs import KOICatalog
@@ -19,7 +20,7 @@ for f in np.exp(np.linspace(np.log(0.001), np.log(100), 8)):
     y0 = np.sqrt(f * np.sqrt(x0))
     ax.plot(x0, y0, "k", lw=0.5, alpha=0.5)
 
-ax.loglog(x, y, ".k", ms=4)
+ax.loglog(x, y, ".", color=COLORS["DATA"], ms=4)
 ax.set_xlim(1.1, 450.)
 ax.set_ylim(0.3, 30)
 ax.set_xlabel("orbital period [days]")
@@ -32,23 +33,27 @@ ax.yaxis.set_major_formatter(fmt)
 # Plot KOIs.
 m = kois.koi_disposition == "CANDIDATE"
 x, y = kois[m].koi_period, kois[m].koi_prad
-ax.plot(x, y, ".", color="#6baed6", ms=3, alpha=0.3, zorder=-1)
+ax.plot(x, y, ".",  # color=COLORS["MODEL_1"],
+        ms=3, alpha=0.3, zorder=-1)
 
 # Plot the solar system.
 rad = np.array("2439.7 6051.8 6371.00 3389.5 69911 58232 25362 24622"
                .split(), dtype=float)
 period = np.array("0.2408467 0.61519726 1.0000174 1.8808476 11.862615 "
                   "29.447498 84.016846 164.79132".split(), dtype=float)
-ax.plot(period * 365, rad / rad[2], "o", color="#fd8d3c")
+ax.plot(period * 365, rad / rad[2], "o",  # color=COLORS["MODEL_2"],
+        ms=4, mec="none")
 ax.set_xlim(0.5, max(x0))
 ax.axvline(4.2*365 / 2., color="k", alpha=0.6)
 ax.axvline(4.2*365, color="k", ls="dashed", alpha=0.6)
 
-# xerr = np.array(fits[["period_err_1", "period_err_2"]]).T
-# yerr = np.array(fits[["radius_err_1", "radius_err_2"]]).T / 0.01
-# x = np.array(fits.period)
-# y = np.array(fits.radius) / 0.01
-# ax.errorbar(x, y, xerr=xerr, yerr=yerr, fmt=".g", capsize=0)
[…]

### 2016-01-31 document/ms.tex
adding fits
A few words for the abstract

@@
 
-Hi.
+The \kepler\ Mission has discovered thousands of exoplanets and revolutionized
+our understanding of their population.
+This large, homogeneous catalog of discoveries has enabled rigorous studies of
+the occurrence rate of exoplanets and extra-Solar planetary systems as a
+function of their physical properties.
+Transit survey like \kepler\ are most sensitive to planets with shorter
+orbital periods than the gas giant planets that dominate the dynamics of our
+Solar System.
+We performed a fully-automated search for the transits of long-period
+exoplanets in the archival \kepler\ light curves and announce XXX planet
+candidates.
+Since our method involves no human intervention, we empirically characterize
+the completeness and reliability of our search.
+Based on these results, we measure the average occurrence rate of exoplanets
+smaller than Jupiter and with orbital periods longer than 700 days to be $\dd
+N = YYY \pm ZZZ\dd \ln P \dd \ln R$.
 
@@
 Burke:2014, Rowe:2015}.
-For \kepler, with a baseline of about four years, this sets an upper limit on
-the detectable periods of just over a year.
+For \kepler, with a baseline of about four years, this sets an absolute upper
+limit on the detectable periods of about two years.
 In the Solar System, Jupiter---with a period of 12 years---dominates the
@@
 It is possible to discover long-period planets like this using targeted radial
-velocity (RV) surveys \citep[for example][]{Butler:2006, Knutson:2014} but the
-cost of implementing a systematic RV search is substantially higher than
-searching the existing and forthcoming photometric data for single transits.
+velocity (RV) surveys \citep[for example][]{Butler:2006, Knutson:2014}
+\dfmtodo{CITE Bryan \etal} but the cost of implementing a systematic RV search
+is substantially higher than searching the existing and forthcoming
+photometric data for single transits.
 
@@
 and this project has yielded some promising long-period candidates and
-confirmed planets \citep[for example][]{Wang:2013}.
+confirmed planets \citep[for example][]{Wang:2013} \dfmtodo{CITE Wang 2015}.
 One shortcoming of the PH method is that it can be difficult to fully quantify
@@
 evaluate their users using synthetic transit signals as is now common practice
-in the transit search literature.
+in the transit search literature \dfmtodo{is this still true?}.
 This means that the PH sample of candidates cannot be used for robust
 population inference.
+
+To study the occurrence rate of long-period exoplanets, we developed a
+fully-automated method for searching the archival \kepler\ light curves for
+these systems with only one or two transits.
 
@@
 \section{Results}
+
+\begin{figure}[p]
+\begin{center}
+\includegraphics{figures/full_sample.pdf}
+\end{center}
+\caption{%
+Blah.
+\figlabel{full-sample}}
+\end{figure}
 

### 2016-01-31 document/ms.tex
method intro words

@@
 
-To study the occurrence rate of long-period exoplanets, we developed a
+To study the occurrence rate of long-period exoplanets, we have developed a
 fully-automated method for searching the archival \kepler\ light curves for
 these systems with only one or two transits.
+Using this method, we detect XXX long-period transiting planet candidates and
+YYY long-period eclipsing binary candidates.
+We estimate that the population level false positive rate in this exoplanet
+candidate sample is about ZZZ\%.
+By injecting synthetic transit signals into the \kepler\ light curves, we
+measure the completeness of our search method.
+Based on this catalog of exoplanet candidates and the search completeness, we
+constrain the occurrence rate of long-period exoplanets.
+For large planets, these results are consistent with previous measurements of
+long-period, giant planet occurrence rates based on radial velocity surveys
+and we demonstrate that small---and possibly rocky---planets are more common
+than their larger counterparts even at long orbital periods.
+
+\section{The search for long-period exoplanets}
+
+Data from the \kepler\ Mission has been used to discover a diverse zoo of
+thousands of exoplanets of all sizes orbiting stars of all types.
+It has be demonstrated that these discoveries can be used to place constraints
+on the occurrence rate of exoplanets \dfmtodo{CITE}.
+These results are sensitive to the detection efficiency and reliability of the
+transit discovery methods \dfmtodo{CITE Burke}.
+
+The search for long-period planets presents several unique challenges.
+Of these, the most important is the inevitable sensitively to signals falsely
+identified as being caused by a transit exoplanet when it is actually a
+systematic false alarm (noise) or an astrophysical false positive.
+In the following paragraphs, we detail our method for addressing these
+challenges and quantifying their effects.
+In summary, we identify false alarms by developing a conservative automated
+candidate vetting algorithm using the full light curve of each target star and
+measure the incompleteness introduced by this procedure.
+To account for astrophysical false positives, we discard candidates that fail
+the standard transit centroid tests and then statistically incorporate
+uncertainties introduced by false positives missed by this procedure at a
+population level.
+
+\section{Candidate vetting}
+
+\paragraph{Light curve}
+
+\begin{figure}[p]
+\begin{center}
+\includegraphics[width=\textwidth]{figures/model_comp.pdf}
+\end{center}
+\caption{%
+Representative examples of candidate events flagged by the initial search.
+Each example falls into a different model category and the figure shows the
+data as black points and the best fit mean model prediction.
+The examples represent the following model categories:
+\emph{(a)} variability, \emph{(b)} step, \emph{(c)} box, and \emph{(d)}
+transit.
+\figlabel{model-comp}}
+\end{figure}
+
+\paragraph{Pixel-level}
+
+Blah.
+
+\paragraph{Auxiliary data}
+
+Blah.
 
@@
 2015-03-25.}.
-
-\section{Candidate vetting}
-
-\paragraph{Light curve}
-
-\begin{figure}[p]
-\begin{center}
-\includegraphics[width=\textwidth]{figures/model_comp.pdf}
-\end{center}
-\caption{%
-Representative examples of candidate events flagged by the initial search.
-Each example falls into a different model category and the figure shows the
-data as black points and the best fit mean model prediction.
-The examples represent the following model categories:
-\emph{(a)} variability, \emph{(b)} step, \emph{(c)} box, and \emph{(d)}
-transit.
-\figlabel{model-comp}}
-\end{figure}
-
-\paragraph{Pixel-level}
-
-Blah.
-
-\paragraph{Auxiliary data}
-
-Blah.
 

### 2016-02-01 document/ms.tex
checking my monte carlo skills

@@
 \newcommand{\unit}[1]{{\ensuremath{\,\mathrm{#1}}}}
+
+\newcommand{\params}{{\ensuremath{\bvec{w}}}}
+\newcommand{\poppars}{{\ensuremath{\theta}}}
 
@@
 
+\section{The occurrence rate of long-period exoplanets}
+
+Geometric:
+
+\begin{eqnarray}
+Q_{\mathrm{geom},k} (\params) &=& \frac{R_{\star,k}}{a_k(\params)} \\
+&=& \left[\frac{4\,\pi^2}{G\,M_{\star,k}}\right]^{1/3}\,R_{\star,k}\,P^{-2/3}
+\end{eqnarray}
+
+Temporal:
+
+\begin{eqnarray}
+Q_{\mathrm{temp},k} (\params) &=& \frac{T_k}{P}
+\end{eqnarray}
+where $T_k$ is the total observing baseline for target $k$.
+Combined with the detection efficiency $Q_{\mathrm{det}}(\params)$ (assumed to
+be constant for each target), the total completeness as a function of the
+parameters is
+\begin{eqnarray}
+Q_k(\params) &=& Q_{\mathrm{det},k}(\params) \,
+                 Q_{\mathrm{temp},k} (\params) \,
+                 Q_{\mathrm{geom},k} (\params) \\
+&=& Q_{\mathrm{det},k}(\params) \,
+    \left[\frac{4\,\pi^2}{G\,M_{\star,k}}\right]^{1/3}\,
+    R_{\star,k}\,T_k\,P^{-5/3} \quad.
+\end{eqnarray}
+
+The likelihood function for the catalog of planet candidates is
+\begin{eqnarray}
+p(\{\params_n\}\,|\,\poppars) &\propto&
+    \exp \left(
+        \int f_\poppars (\params)\,\sum_{k=1}^K Q_k(\params) \dd\params
+    \right) \, \prod_{n=1}^N f_\poppars (\params_n) \quad.
+\end{eqnarray}
+
+Therefore
+\begin{eqnarray}
+\int f_\poppars (\params)\,\sum_{k=1}^K Q_k(\params) \dd\ln P\dd\ln R &=&
+    \bar{Q}\,\int Q_{\mathrm{det}}(\params)\,f_\poppars(\params)\,P^{-5/3}
+        \dd\ln P\dd\ln R
+\end{eqnarray}
+where
+\begin{eqnarray}
+\bar{Q} &=& \sum_{k=1}^K
+    \left[\frac{4\,\pi^2}{G\,M_{\star,k}}\right]^{1/3}\,R_{\star,k}\,T_k
+\quad.
+\end{eqnarray}
+
+The easiest way to evaluate this integral in practice is to use Monte Carlo
+integration to find
+\begin{eqnarray}
+\int Q_{\mathrm{det}}(\params)\,f_\poppars(\params)\,P^{-5/3}\dd\ln P\dd\ln R
+&=& \frac{F}{J}\sum_{j=1}^J Q_{\mathrm{det}}(P^{(j)},\,R^{(j)})\,
+        f_\poppars(P^{(j)},\,R^{(j)})
+\end{eqnarray}
+where
+\begin{eqnarray}
+F &=& \frac{3}{5}\,[P_\mathrm{min}^{-5/3}-P_\mathrm{max}^{-5/3}]\,
+      [\ln R_\mathrm{max} - \ln R_\mathrm{min}]
+\end{eqnarray}
+and
+\begin{eqnarray}
+P^{(j)} \sim P^{-8/3} &\mathrm{and}&
+\ln R^{(j)} \sim \mathcal{U}(\ln R_\mathrm{min},\,\ln R_\mathrm{max})
+\end{eqnarray}
+
+\begin{eqnarray}
+f_\poppars (\params) &=& \frac{1}{f_0}\,C\,P^\alpha\,R^\beta
+\end{eqnarray}
+where
+\begin{eqnarray}
+f_0 &=&
+    \int_{P_\mathrm{min}}^{P_\mathrm{max}}
+    \int_{R_\mathrm{min}}^{R_\mathrm{max}}
+    P^\alpha\,R^\beta\dd\ln P\dd\ln R
+\end{eqnarray}
+
 \section{Discussion}\sectlabel{discussion}

### 2016-02-01 document/figures/integration_demo.py

@@ -1,0 +1,42 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+r"""
+A test for how to do the integral
+
+I = \int_{\ln x_1}^{\ln x_2} f(\ln x) x^{-5/3} d\ln x
+  = \int_{x_1}^{x_2} f(\ln x) x^{-5/3} x^{-1} dx
+
+if f(\ln x) = f0:
+
+I = f0 \, (x_2^{-5/3} - x_1^{-5/3}) / (-5/3)
+
+if f(\ln x) = x^b:
+
+I = (x_2^{-5/3+b} - x_1^{-5/3+b}) / (-5/3+b)
+
+"""
+
+import numpy as np
+
+
+def sample_power_law(n, mn, mx, size=None):
+    u = np.random.uniform(size=size)
+    np1 = n + 1.0
+    a = mx**np1
+    b = mn**np1
+    return (
+        (u*a + (1-u)*b) ** (1. / np1),
+        (a - b) / np1
+    )
+
+
+power = -5/3
+
+f0 = 0.1
+mn, mx = 0.5, 10.0
+samples, norm = sample_power_law(power-1.0, mn, mx, 2000000)
+print(np.mean(f0 * np.ones_like(samples)) * norm, f0 * norm)
+
+beta = -0.5
+beta_plus = beta + power
+print(np.mean(samples**beta)*norm, (mx**beta_plus-mn**beta_plus)/beta_plus)

### 2016-02-03 document/ms.tex
co-authors

@@
 %  * ``light curve'' not ``light-curve'' or ``lightcurve''
-%  * Do not put in any comments that might get tweeted by @OverheardOnAph
-%    (or maybe do put in a few....)
-%  * ``percent'' (not \%) is a unit, as is ppm, so 5~percent.
 %  * that is all.
@@
     Bernhard~Sch\"olkopf\altaffilmark{\mpis},
+    Eric~Agol\altaffilmark{\uw},
     and others

### 2016-02-03 peerless/fit.py
better initialization

@@ -20,9 +20,10 @@ class TransitModel(object):
 
     eb = beta(1.12, 3.09)
 
-    def __init__(self, gps, system, smass, smass_err, srad, srad_err,
+    def __init__(self, spec, gps, system, smass, smass_err, srad, srad_err,
                  fit_lcs, other_lcs):
-        self.t0rng = system.bodies[0].t0 + np.array([-1., 1.])
+        self.spec = spec
+        self.t0rng = system.bodies[0].t0 + np.array([-0.5, 0.5])
         self.gps = gps
         self.system = system
         self.smass = smass
@@ -31,6 +32,29 @@ class TransitModel(object):
         self.srad_err = srad_err
         self.fit_lcs = fit_lcs
         self.other_lcs = other_lcs
+
+        body = self.system.bodies[0]
+        mx = (
+            self.lnlike(compute_blob=False)[0],
+            (body.b, body.radius, body.period)
+        )
+        print(mx)
+        prng = np.exp(np.append(np.linspace(np.log(0.1), np.log(10.0), 21), 0))
+        rrng = np.append(np.linspace(0.5, 2, 11), 0)
+        rstar = self.system.central.radius
+        for per in body.period*prng:
+            body.period = per
+            for rad in body.radius*rrng:
+                body.radius = rad
+                for b in np.linspace(0, (1.0+0.99*rad/rstar)**4, 10)**(1/4.):
+                    body.b = b
+                    ll = self.lnlike(compute_blob=False)[0]
+                    if ll > mx[0]:
+                        mx = (ll, (b, rad, per))
+        print(mx)
+        body.b = mx[1][0]
+        body.radius = mx[1][1]
+        body.period = mx[1][2]
 
     # Probabilistic model:
     def lnprior(self):
@@ -67,7 +91,7 @@ class TransitModel(object):
         preds = []
         for gp, lc in zip(self.gps, self.fit_lcs):
             mu = system.light_curve(lc.time, texp=lc.texp, maxdepth=2)
-            r = lc.flux - mu
+            r = (lc.flux - mu) * 1e3
             ll += gp.lnlikelihood(r, quiet=True)
             if not (np.any(mu < system.central.flux) and np.isfinite(ll)):
                 return -np.inf, (0, None)
@@ -125,14 +149,20 @@ class TransitModel(object):
         self.system.thaw_parameter("central:*")
[…]

### 2016-02-03 peerless/fit.py
init w blacklist

@@ -157,7 +157,6 @@ class TransitModel(object):
             r = (lc.flux - mu) * 1e3
             p0 = gp.get_vector()
             r = minimize(gp.nll, p0, jac=gp.grad_nll, args=(r, ))
-            print(r)
             if r.success:
                 gp.set_vector(r.x)
             else:

### 2016-02-03 peerless/fit.py
correctly trim light curves

@@ -38,7 +38,6 @@ class TransitModel(object):
             self.lnlike(compute_blob=False)[0],
             (body.b, body.radius, body.period)
         )
-        print(mx)
         prng = np.exp(np.append(np.linspace(np.log(0.1), np.log(10.0), 21), 0))
         rrng = np.append(np.linspace(0.5, 2, 11), 0)
         rstar = self.system.central.radius
@@ -262,7 +261,8 @@ def setup_fit(args, fit_kois=False, max_points=300):
         if np.any(f < 1.0):
             i = np.argmin(f)
             inds = np.arange(len(f))
-            m = np.sort(np.argsort(np.abs(inds - i))[:max_points])
+            m = np.zeros(len(lc.time), dtype=bool)
+            m[np.sort(np.argsort(np.abs(inds - i))[:max_points])] = True
             if np.any(f[~m] < system.central.flux):
                 m = np.ones(len(lc.time), dtype=bool)
             lc.time = np.ascontiguousarray(lc.time[m])

### 2016-02-07 document/figures/targets.py
adding target list

@@ -1,0 +1,53 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+from plot_setup import COLORS
+
+import numpy as np
+import matplotlib.pyplot as pl
+from peerless.catalogs import (
+    KICatalog, KOICatalog, EBCatalog, BlacklistCatalog
+)
+
+
+stlr = KICatalog().df
+m = (4200 <= stlr.teff) & (stlr.teff <= 6100)
+m &= stlr.radius <= 1.15
+m &= stlr.dataspan > 365.25*2.
+m &= stlr.dutycycle > 0.6
+m &= stlr.rrmscdpp07p5 <= 1000.
+m &= stlr.kepmag < 15.
+kicids = np.array(list(np.array(stlr[m].kepid)), dtype=int)
+
+# Remove known EBs.
+ebs = set(np.array(EBCatalog().df["#KIC"]))
+
+# Then the KOI false positives:
+kois = KOICatalog().df
+kois = kois[kois.koi_disposition == "FALSE POSITIVE"]
+fps = set(np.array(kois.kepid))
+
+# And then finally the blacklist.
+bl = set(np.array(BlacklistCatalog().df.kicid))
+
+# The full list of ignores.
+ignore = ebs | fps | bl
+m &= ~stlr.kepid.isin(ignore)
+
+fig, ax = pl.subplots(1, 1, figsize=(4, 4))
+ax.plot(stlr[~m].teff, stlr[~m].logg, ".", color=COLORS["DATA"], ms=2,
+        alpha=1.0, rasterized=True)
+ax.plot(stlr[m].teff, stlr[m].logg, ".", color=COLORS["MODEL_2"], ms=2,
+        alpha=1.0, rasterized=True)
+ax.set_xlim(8250, 3500)
+ax.set_ylim(5.1, 3.5)
+ax.set_ylabel("$\log g$")
+ax.set_xlabel("$T_\mathrm{eff}$")
+ax.xaxis.set_major_locator(pl.MaxNLocator(4))
+ax.yaxis.set_major_locator(pl.MaxNLocator(5))
+fig.set_tight_layout(True)
+fig.savefig("targets.pdf", dpi=400)
+
+print("Found {0} targets".format(m.sum()))
+
+np.savetxt("targets.txt", kicids, fmt="%d")

### 2016-02-07 document/ms.tex

@@
 
-\documentclass[12pt,preprint]{aastex}
+\documentclass[onecolumn]{aastex6}
 
@@
 \usepackage{natbib}
-\bibliographystyle{apj}
+\bibliographystyle{aasjournal}
 
@@
 
-\newcommand{\figref}[1]{\ref{fig:#1}}
-\newcommand{\Fig}[1]{\figurename~\figref{#1}}
-\newcommand{\fig}[1]{\Fig{#1}}
+% \newcommand{\figref}[1]{\ref{fig:#1}}
+% \newcommand{\Fig}[1]{\figurename~\figref{#1}}
+% \newcommand{\fig}[1]{\Fig{#1}}
 \newcommand{\figlabel}[1]{\label{fig:#1}}
 
-\newcommand{\Tab}[1]{Table~\ref{tab:#1}}
-\newcommand{\tab}[1]{\Tab{#1}}
+% \newcommand{\Tab}[1]{Table~\ref{tab:#1}}
+% \newcommand{\tab}[1]{\Tab{#1}}
 \newcommand{\tablabel}[1]{\label{tab:#1}}
 
-\renewcommand{\eqref}[1]{\ref{eq:#1}}
-\newcommand{\Eq}[1]{Equation~(\eqref{#1})}
-\newcommand{\eq}[1]{\Eq{#1}}
-\newcommand{\eqalt}[1]{Equation~\eqref{#1}}
+% \renewcommand{\eqref}[1]{\ref{eq:#1}}
+% \newcommand{\Eq}[1]{Equation~(\eqref{#1})}
+% \newcommand{\eq}[1]{\Eq{#1}}
+% \newcommand{\eqalt}[1]{Equation~\eqref{#1}}
 \newcommand{\eqlabel}[1]{\label{eq:#1}}
@@
 
+% \slugcomment{Not to appear in Nonlearned J., 45.}
+
 \begin{document}
@@
 \title{%
-Automated detection \& characterization of long-period transits in the
-\kepler\ archive
+The occurrence rate of long-period exoplanets
 }
 
-\newcommand{\uw}{3}
-\newcommand{\nyu}{4}
-\newcommand{\cds}{5}
-\newcommand{\mpia}{6}
-\newcommand{\mpis}{7}
-\author{%
-    Daniel~Foreman-Mackey\altaffilmark{1,2,\uw},
-    David~W.~Hogg\altaffilmark{\nyu,\mpia,\cds},
-    Bernhard~Sch\"olkopf\altaffilmark{\mpis},
-    Eric~Agol\altaffilmark{\uw},
-    and others
-}
-\altaffiltext{1}         {To whom correspondence should be addressed:
-                          \url{danfm@uw.edu}}
-\altaffiltext{2}         {Sagan Fellow}
-\altaffiltext{\uw}       {Astronomy Department, University of Washington,
+\newcommand{\uw}  {Astronomy Department, University of Washington,
                    Seattle, WA, 98195, USA}
-\altaffiltext{\nyu}      {Center for Cosmology and Particle Physics,
-                          Department of Physics, New York University,
+\newcommand{\nyu} {Center for Cosmology and Particle Physics,
+                   New York University,
                    4 Washington Place, New York, NY, 10003, USA}
-\altaffiltext{\cds}      {Center for Data Science, New York University,
+\newcommand{\cds} {Center for Data Science, New York University,
                    726 Broadway, 7th Floor, New York, NY, 10003, USA}
-\altaffiltext{\mpia}     {Max-Planck-Institut f\"ur Astronomie,
+\newcommand{\mpia}{Max-Planck-Institut f\"ur Astronomie,
                    K\"onigstuhl 17, D-69117 Heidelberg, Germany}
-\altaffiltext{\mpis}     {Max Planck Institute for Intelligent Systems
+\newcommand{\mpis}{Max Planck Institute for Intelligent Systems
                    Spemannstrasse 38, 72076 T\"ubingen, Germany}
+
+\author{Daniel~Foreman-Mackey\altaffilmark{1,2}}
+\affil{\uw}
+
+\author{David~W.~Hogg}
+\affil{\nyu \\ \mpia \\ \cds}
+
+\author{Bernhard~Sch\"olkopf}
+\affil{\mpis}
+
+\author{Eric~Agol}
+\affil{\uw}
+
+\and
+
+\author{and others}
+
+\altaffiltext{1}{\url{danfm@uw.edu}}
+\altaffiltext{2}{Sagan Fellow}
 
@@
 NNX13AC07G and by other grants and contracts.
+Computing resources were provided by High Performance Computing (HPC) at New
+York University (NYU).
 
-{\it Facilities:} \facility{Kepler}
+\facility{Kepler}
 

### 2016-02-07 document/figures/targets.py
saving the correct target list

@@ -17,7 +17,6 @@ m &= stlr.dataspan > 365.25*2.
 m &= stlr.dutycycle > 0.6
 m &= stlr.rrmscdpp07p5 <= 1000.
 m &= stlr.kepmag < 15.
-kicids = np.array(list(np.array(stlr[m].kepid)), dtype=int)
 
 # Remove known EBs.
 ebs = set(np.array(EBCatalog().df["#KIC"]))
@@ -50,4 +49,4 @@ fig.savefig("targets.pdf", dpi=400)
 
 print("Found {0} targets".format(m.sum()))
 
-np.savetxt("targets.txt", kicids, fmt="%d")
+np.savetxt("targets.txt", np.array(stlr[m].kepid), fmt="%d")

### 2016-02-08 document/ms.tex
fancy author latex junk

@@
 
-\documentclass[onecolumn]{aastex6}
+\documentclass[preprint]{aastex}
 
@@
 
-\newcommand{\uw}  {Astronomy Department, University of Washington,
+\newcounter{affilcounter}
+\setcounter{affilcounter}{2}
+\altaffiltext{1}{\url{danfm@uw.edu}; Sagan Fellow}
+
+\edef \uw {\arabic{affilcounter}}\stepcounter{affilcounter}
+\altaffiltext{\uw}       {Astronomy Department, University of Washington,
                           Seattle, WA, 98195, USA}
-\newcommand{\nyu} {Center for Cosmology and Particle Physics,
+
+\edef \scda {\arabic{affilcounter}}\stepcounter{affilcounter}
+\altaffiltext{\scda}     {Simons Center for Data Analysis, 160 Fifth Avenue,
+                          7th floor, New York, NY 10010, USA}
+
+\edef \nyu       {\arabic{affilcounter}}\stepcounter{affilcounter}
+\altaffiltext{\nyu}      {Center for Cosmology and Particle Physics,
                           New York University,
                           4 Washington Place, New York, NY, 10003, USA}
-\newcommand{\cds} {Center for Data Science, New York University,
+
+\edef \cds       {\arabic{affilcounter}}\stepcounter{affilcounter}
+\altaffiltext{\cds}      {Center for Data Science, New York University,
                           726 Broadway, 7th Floor, New York, NY, 10003, USA}
-\newcommand{\mpia}{Max-Planck-Institut f\"ur Astronomie,
+
+\edef \mpia      {\arabic{affilcounter}}\stepcounter{affilcounter}
+\altaffiltext{\mpia}     {Max-Planck-Institut f\"ur Astronomie,
                           K\"onigstuhl 17, D-69117 Heidelberg, Germany}
-\newcommand{\mpis}{Max Planck Institute for Intelligent Systems
+
+\edef \princeton {\arabic{affilcounter}}\stepcounter{affilcounter}
+\altaffiltext{\princeton}{Department of Astrophysics, Princeton University,
+                          Princeton, NJ, 08544, USA}
+
+\edef \mpis      {\arabic{affilcounter}}\stepcounter{affilcounter}
+\altaffiltext{\mpis}     {Max Planck Institute for Intelligent Systems
                           Spemannstrasse 38, 72076 T\"ubingen, Germany}
 
-\author{Daniel~Foreman-Mackey\altaffilmark{1,2}}
-\affil{\uw}
-
-\author{David~W.~Hogg}
-\affil{\nyu \\ \mpia \\ \cds}
-
-\author{Bernhard~Sch\"olkopf}
-\affil{\mpis}
-
-\author{Eric~Agol}
-\affil{\uw}
-
-\and
-
-\author{and others}
-
-\altaffiltext{1}{\url{danfm@uw.edu}}
-\altaffiltext{2}{Sagan Fellow}
+\author{%
+    Daniel~Foreman-Mackey\altaffilmark{1,\uw},
+    David~W.~Hogg\altaffilmark{\scda,\nyu,\mpia,\cds},
+    Timothy~D.~Morton\altaffilmark{\princeton},
+    Bernhard~Sch\"olkopf\altaffilmark{\mpis},
+    Eric~Agol\altaffilmark{\uw},
+    and others
+}
 

### 2016-02-11 prediction/sims.py
BinaryPopulation object defined

@@ -1,0 +1,194 @@
+from __future__ import print_function, division
+
+import numpy as np
+
+from isochrones.dartmouth import Dartmouth_Isochrone
+from vespa.stars.utils import draw_eccs # this is a function that returns
+                                        # empirically reasonably eccentricities
+                                        # for given binary periods.
+from scipy.stats import norm 
+from vespa.transit_basic import _quadratic_ld
+
+from vespa.stars.utils import G, MSUN, RSUN, AU, DAY
+
+def draw_powerlaw(alpha, rng, N=1):
+    """
+    Returns random variate according to x^alpha, between rng[0] and rng[1]
+    """
+    if alpha == -1:
+        alpha = -1.0000001
+    # Normalization factor
+    x0, x1 = rng
+    C = (alpha + 1) / (x1**(alpha + 1) - x0**(alpha + 1))
+    
+    if N==1:
+        u = np.random.random()
+    else:
+        u = np.random.random(N)
+    x = ((u * (alpha + 1)) / C + x0**(alpha + 1))**(1./(alpha + 1))
+
+    return x
+
+def semimajor(P,mstar=1):
+    """Returns semimajor axis in AU given P in days, mstar in solar masses.
+    """
+    return ((P*DAY/2/np.pi)**2*G*mstar*MSUN)**(1./3)/AU
+
+
+class BinaryPopulation(object):
+    """
+    Initialized with population of primary stars
+
+    """
+    #parameters for binary population (for period in years)
+    param_names = ['fB', 'gamma', 'qmin', 'mu_logp', 'sig_logp']
+    default_params = [0.4, 0.3, 0.1, np.log10(250), 2.3]
+
+    # Physical and orbital parameters that can be accessed.
+    physical_props = ['mass_A', 'radius_A',
+                      'mass_B', 'radius_B', 'flux_ratio']
+
+    orbital_props = ['period', 'ecc', 'w', 'inc', 'a',
+                      'b_pri', 'b_sec', 'k', 'tra', 'occ',
+                      'd_pri', 'd_sec', 'T14_pri', 'T14_sec']
+                     
+    # property dictionary mapping to DataFrame column
+    # Default here is for KICatalog names
+    prop_columns = {'mass_A': 'mass', 'radius_A': 'radius'}
+
+    def __init__(self, stars, params=None, band='Kepler', 
+                 ic=Dartmouth_Isochrone):
+
+        self.stars = stars
[…]

### 2016-02-12 peerless/fit.py
more flexible init

@@ -36,25 +36,33 @@ class TransitModel(object):
         body = self.system.bodies[0]
         mx = (
             self.lnlike(compute_blob=False)[0],
-            (body.b, body.radius, body.period)
+            (body.b, body.radius, body.period, body.e, body.omega)
         )
-        prng = np.exp(np.append(np.linspace(np.log(0.1), np.log(10.0), 21), 0))
-        rrng = np.append(np.linspace(0.5, 2, 11), 0)
+        prng = np.exp(np.append(np.linspace(np.log(0.5), np.log(2.0), 6), 0))
+        rrng = body.radius * np.append(np.linspace(0.8, 1.2, 6), 1.0)
         rstar = self.system.central.radius
-        for per in body.period*prng:
-            body.period = per
-            for rad in body.radius*rrng:
-                body.radius = rad
-                for b in np.linspace(0, (1.0+0.99*rad/rstar)**4, 10)**(1/4.):
-                    body.b = b
-                    ll, blob = self.lnlike(compute_blob=False)
-
-                    if blob[1] == 0 and ll > mx[0]:
-                        mx = (ll, (b, rad, per))
+        for ecc in np.linspace(0, 0.8, 4):
+            body.e = ecc
+            for w in np.linspace(-np.pi, np.pi, 4):
+                body.omega = w
+                # self.system.central.dilution = dil
+                for per in body.period*prng:
+                    body.period = per
+                    for rad in rrng:
+                        body.radius = rad
+                        for b in np.linspace(0, 1.0+0.9*rad/rstar, 6):
+                            body.b = b
+                            ll, blob = self.lnlike(compute_blob=False)
+                            if ll > mx[0]:
+                                ll, blob = self.lnlike(compute_blob=True)
+                                if blob[0] == 0:
+                                    mx = (ll, (b, rad, per, ecc, w))
         print(mx)
+        body.e = mx[1][3]
+        body.omega = mx[1][4]
+        body.period = mx[1][2]
         body.b = mx[1][0]
         body.radius = mx[1][1]
-        body.period = mx[1][2]
 
     # Probabilistic model:
     def lnprior(self):

### 2016-02-17 document/ms.tex
figure fixes
a new figure

@@
 
-\documentclass[preprint]{aastex}
+\documentclass[twocolumn]{aastex6}
+% \documentclass[onecolumn]{aastex6}
+% \documentclass[preprint]{aastex}
 
@@
 
-\section{The search for long-period exoplanets}
-
 Data from the \kepler\ Mission has been used to discover a diverse zoo of
 thousands of exoplanets of all sizes orbiting stars of all types.
-It has be demonstrated that these discoveries can be used to place constraints
-on the occurrence rate of exoplanets \dfmtodo{CITE}.
+It has be demonstrated that these catalogs of exoplanet discoveries can be
+used to place constraints on the occurrence rate of exoplanets \dfmtodo{CITE}.
 These results are sensitive to the detection efficiency and reliability of the
-transit discovery methods \dfmtodo{CITE Burke}.
+discovery methodology \dfmtodo{CITE Burke}.
 
-The search for long-period planets presents several unique challenges.
-Of these, the most important is the inevitable sensitively to signals falsely
-identified as being caused by a transit exoplanet when it is actually a
-systematic false alarm (noise) or an astrophysical false positive.
-In the following paragraphs, we detail our method for addressing these
-challenges and quantifying their effects.
-In summary, we identify false alarms by developing a conservative automated
-candidate vetting algorithm using the full light curve of each target star and
-measure the incompleteness introduced by this procedure.
-To account for astrophysical false positives, we discard candidates that fail
-the standard transit centroid tests and then statistically incorporate
-uncertainties introduced by false positives missed by this procedure at a
-population level.
+\section{The fully-automated search for long-period exoplanets}
 
-\section{Candidate vetting}
+To find long-period exoplanets in the \kepler\ light curves, we search for
+individual, high signal-to-noise transit signals using a fully-automated
+procedure that can be broken into three main steps:
+\begin{enumerate}
+{\item an initial candidate search using a box-shaped matched filter,}
+{\item light curve-level vetting (using automated model comparison) to remove
+signals that don't match a transit shape, and}
+{\item pixel-level vetting to remove some astrophysical false positives.}
+\end{enumerate}
+The following sections describe each of these steps in more detail.
 
-\paragraph{Light curve}
+% The search for long-period planets presents several unique challenges.
+% Of these, the most important is the inevitable sensitively to signals falsely
+% identified as being caused by a transit exoplanet when it is actually a
+% systematic false alarm (noise) or an astrophysical false positive.
+% In the following paragraphs, we detail our method for addressing these
+% challenges and quantifying their effects.
+% In summary, we identify false alarms by developing a conservative automated
+% candidate vetting algorithm using the full light curve of each target star and
+% measure the incompleteness introduced by this procedure.
+% To account for astrophysical false positives, we discard candidates that fail
+% the standard transit centroid tests and then statistically incorporate
+% uncertainties introduced by false positives missed by this procedure at a
+% population level.
 
-\begin{figure}[p]
+\subsection{Finding box-shaped candidate events}
+
+It is not feasible to compute a full model comparison at every time in the
+light curve so we must first find potentially interesting events.
+To generate this list, we apply a standard ``box least squares'' (BLS;
+\dfmtodo{CITE}) method with a single (non-periodic) box.
+First, we filter the PDC (\dfmtodo{CITE}) light curves using a running
+windowed median with a half-width of \dfmtodo{how many} to remove stellar
+variability.
+We then compute the signal-to-noise of the depth of a 0.6~day long transit on
+a grid of times spanning the full \kepler\ baseline.
+To avoid edge effects, we apodize this detection scalar near any large gaps in
+the time series using a logistic function with width equal to one transit
+duration.
+Finally, we estimate the noise in the time series using a robust running
+windowed variance estimate of the detection scalar and accepting peaks more
+than 25-times this noise as candidates.
+
+\subsection{Light curve-level vetting}
+
+\subsection{Pixel-level vetting}
+
+\begin{figure*}
 \begin{center}
@@
 \figlabel{model-comp}}
-\end{figure}
+\end{figure*}
 
@@
 within 2 transit durations of the known candidates.
+
+\begin{figure*}
+\begin{center}
+\includegraphics{figures/targets.pdf}
+\end{center}
+\caption{%
+Blah.
+\figlabel{targets}}
+\end{figure*}
 
@@
 
-\begin{figure}[p]
+\begin{figure*}
 \begin{center}
@@
 \figlabel{full-sample}}
-\end{figure}
+\end{figure*}
 

### 2016-02-17 document/figures/initial_candidates.py

@@ -1,0 +1,36 @@
+# -*- coding: utf-8 -*-
+
+from __future__ import division, print_function
+
+from plot_setup import COLORS
+
+import os
+import pickle
+import numpy as np
+import matplotlib.pyplot as pl
+
+from peerless.search import search
+
+kicid = 8505215
+# kicid = 10842718
+# kicid = 10287723
+# kicid = 6551440
+fn = os.path.join("cache", "init-{0}.pkl".format(kicid))
+if os.path.exists(fn):
+    print("using cached file: {0}".format(fn))
+    with open(fn, "rb") as f:
+        results = pickle.load(f)
+else:
+    results = search((kicid, None), verbose=True, delete=False)
+    with open(fn, "wb") as f:
+        pickle.dump(results, f, -1)
+
+fig, ax = pl.subplots(1, 1, figsize=(8, 4))
+ax.plot(results.search_time, results.search_scalar, color=COLORS["DATA"])
+ax.plot(results.search_time, results.search_background,
+        color=COLORS["MODEL_2"])
+ax.plot(results.search_time, results.detect_thresh*results.search_background,
+        color=COLORS["MODEL_2"], ls="dashed")
+ax.set_xlim(results.search_time.min(), results.search_time.max())
+
+fig.savefig("initial_candidates.pdf", bbox_inches="tight")

### 2016-02-17 peerless/search.py
fixing linalg failure

@@ -402,6 +402,7 @@ def search(kicid_and_injection=None,
                     C[np.diag_indices_from(C)] += err**2
                     alpha = np.linalg.solve(C, A)
                     ATA = np.dot(AT, alpha)
+                    ATA[np.diag_indices_from(ATA)] *= 1 + 1e-8
                     mu = np.mean(c)
                     a = np.linalg.solve(C, c - mu)
                     w = np.linalg.solve(ATA, np.dot(AT, a))

### 2016-02-18 document/ms.tex
section headings

@@
 \title{%
-The occurrence rate of long-period exoplanets
+Single \& double transits discovered in the \kepler\ archive: \\
+the frequency of long-period exoplanets
 }
@@
 
-\section{The fully-automated search for long-period exoplanets}
+\section{The fully-automated search for long-period transiting exoplanets}
 
@@
 
-\paragraph{Pixel-level}
+\section{A catalog of exoplanet \& binary candidates}
 
-Blah.
-
-\paragraph{Auxiliary data}
-
-Blah.
-
-\section{Data selection \& preparation}\sectlabel{data}
+\subsection{Target selection}\sectlabel{data}
 
@@
 
-\section{Results}
+\subsection{Parameter estimation}
 
@@
 
-\section{Completeness \& reliability}
+\subsection{Discussion of some interesting systems}
+
+\section{Empirical search completeness}
 
@@
 \end{eqnarray}
+
+\section{Astrophysical false positives}
+
+Tim to write some words here.
 

### 2016-02-18 prediction/sims.py
about to play around with qR

@@ -1,13 +1,18 @@
 from __future__ import print_function, division
 
 import numpy as np
+import matplotlib.pyplot as plt
+from sklearn.ensemble import RandomForestRegressor
+from sklearn.preprocessing import StandardScaler
+from sklearn.pipeline import Pipeline
 
 from isochrones.dartmouth import Dartmouth_Isochrone
+DAR = Dartmouth_Isochrone()
+DAR.radius(1,9.5,0) #prime the isochrone object
 from vespa.stars.utils import draw_eccs # this is a function that returns
                                         # empirically reasonably eccentricities
                                         # for given binary periods.
-from scipy.stats import norm, binom
-from vespa.transit_basic import _quadratic_ld
+from vespa.transit_basic import _quadratic_ld, eclipse_tt, NoEclipseError
 
 from vespa.stars.utils import G, MSUN, RSUN, AU, DAY
 
@@ -48,16 +53,18 @@ class BinaryPopulation(object):
     physical_props = ['mass_A', 'radius_A',
                       'mass_B', 'radius_B', 'flux_ratio']
 
-    orbital_props = ['period', 'ecc', 'w', 'inc', 'a',
+    orbital_props = ['period', 'ecc', 'w', 'inc', 'a', 'aR',
                       'b_pri', 'b_sec', 'k', 'tra', 'occ',
-                      'd_pri', 'd_sec', 'T14_pri', 'T14_sec']
+                      'd_pri', 'd_sec', 'T14_pri', 'T14_sec',
+                      'T23_pri', 'T23_sec']
                      
     # property dictionary mapping to DataFrame column
     # Default here is for KICatalog names
-    prop_columns = {'mass_A': 'mass', 'radius_A': 'radius'}
+    #  Don't use KIC radius here; recalc for consistency.
+    prop_columns = {'mass_A': 'mass'}
 
     def __init__(self, stars, params=None, band='Kepler', 
-                 ic=Dartmouth_Isochrone):
+                 ic=DAR, **kwargs):
 
         self.stars = stars
         self.band = band
@@ -67,12 +74,27 @@ class BinaryPopulation(object):
         for k,v in self.prop_columns.items():
             self.stars.loc[:, k] = self.stars.loc[:, v]
 
+        self.set_params(**kwargs)
+
+        self._dmag_pipeline = None
+
     @property
     def params(self):
[…]

### 2016-02-18 prediction/sims.py
reparametrized popultion for qR; now using learned regressions rather than isochrones calls to regenerate pops

@@ -3,7 +3,8 @@ from __future__ import print_function, division
 import numpy as np
 import matplotlib.pyplot as plt
 from sklearn.ensemble import RandomForestRegressor
-from sklearn.preprocessing import StandardScaler
+from sklearn.linear_model import LinearRegression
+from sklearn.preprocessing import StandardScaler, PolynomialFeatures
 from sklearn.pipeline import Pipeline
 
 from isochrones.dartmouth import Dartmouth_Isochrone
@@ -24,13 +25,14 @@ def draw_powerlaw(alpha, rng, N=1):
         alpha = -1.0000001
     # Normalization factor
     x0, x1 = rng
-    C = (alpha + 1) / (x1**(alpha + 1) - x0**(alpha + 1))
+    x0_alpha_p_1 = x0**(alpha + 1)
+    C = (alpha + 1) / (x1**(alpha + 1) - x0_alpha_p_1)
     
     if N==1:
         u = np.random.random()
     else:
         u = np.random.random(N)
-    x = ((u * (alpha + 1)) / C + x0**(alpha + 1))**(1./(alpha + 1))
+    x = ((u * (alpha + 1)) / C + x0_alpha_p_1)**(1./(alpha + 1))
 
     return x
 
@@ -46,7 +48,7 @@ class BinaryPopulation(object):
 
     """
     #parameters for binary population (for period in years)
-    param_names = ['fB', 'gamma', 'qmin', 'mu_logp', 'sig_logp']
+    param_names = ['fB', 'gamma', 'qRmin', 'mu_logp', 'sig_logp']
     default_params = [0.4, 0.3, 0.1, np.log10(250), 2.3]
 
     # Physical and orbital parameters that can be accessed.
@@ -63,6 +65,9 @@ class BinaryPopulation(object):
     #  Don't use KIC radius here; recalc for consistency.
     prop_columns = {'mass_A': 'mass'}
 
+    # Minimum radius allowed, in Rsun.
+    min_radius = 0.11
+
     def __init__(self, stars, params=None, band='Kepler', 
                  ic=DAR, **kwargs):
 
@@ -76,7 +81,8 @@ class BinaryPopulation(object):
 
         self.set_params(**kwargs)
 
-        self._dmag_pipeline = None
+        self._fluxrat_pipeline = None
+        self._q_pipeline = None
 
     @property
     def params(self):
@@ -117,25 +123,12 @@ class BinaryPopulation(object):
                 self._generate_orbits()
[…]

### 2016-02-18 prediction/sims.py
added get_N_observed function

@@ -1,6 +1,7 @@
 from __future__ import print_function, division
 
 import numpy as np
+import pandas as pd
 import matplotlib.pyplot as plt
 from sklearn.ensemble import RandomForestRegressor
 from sklearn.linear_model import LinearRegression
@@ -305,7 +306,8 @@ class BinaryPopulation(object):
         return np.maximum(pri, sec).sum()
         
 
-    def observe(self, query=None, fit_trap=False, new=False):
+    def observe(self, query=None, fit_trap=False, new=False,
+                texp=1626./86400):
         """
         Returns catalog of the following observable quantities:
           
@@ -320,6 +322,8 @@ class BinaryPopulation(object):
        
         assumes stars dataframe has 'dataspan' and 'dutycycle' columns
         """
+        if fit_trap:
+            new = True
         if new:
             self._generate_binaries()
             self._generate_orbits()
@@ -365,23 +369,50 @@ class BinaryPopulation(object):
         df.loc[:, 'n_sec'] = n_sec
 
         m = (df.n_pri > 0) | (df.n_sec > 0)
-        catalog = df[m]
+        catalog = df[m].copy()
         
+        N = len(catalog)
+        catalog.loc[:, 'trap_dur_pri'] = np.zeros(N)
+        catalog.loc[:, 'trap_depth_pri'] = np.zeros(N)
+        catalog.loc[:, 'trap_slope_pri'] = np.zeros(N)
+        catalog.loc[:, 'trap_dur_sec'] = np.zeros(N)
+        catalog.loc[:, 'trap_depth_sec'] = np.zeros(N)
+        catalog.loc[:, 'trap_slope_sec'] = np.zeros(N)
+
+        period = catalog.period.values
+        k = catalog.k.values
+        b_pri = catalog.b_pri.values
+        b_sec = catalog.b_sec.values
+        aR = catalog.aR.values
+        flux_ratio = catalog.flux_ratio.values
+        ecc = catalog.ecc.values
+        w = catalog.w.values
+        tra = catalog.tra.values
+        occ = catalog.occ.values
+
+        trapfit_kwargs = dict(npts=50, width=2, cadence=texp)
         if fit_trap:
-            for i,s in catalog.iterrows():
+            for i in xrange(N):
                 # Primary
-                if s.tra:
-                    dur_pri, depth_pri, slope_pri = eclipse_tt(P=s.period, p0=s.k, b=s.b_pri,
[…]

### 2016-02-27 document/ms.tex
finally writing some words

@@
 
-\documentclass[twocolumn]{aastex6}
-% \documentclass[onecolumn]{aastex6}
+% \documentclass[twocolumn]{aastex6}
+\documentclass[onecolumn]{aastex6}
 % \documentclass[preprint]{aastex}
@@
 \newcommand{\dd}{\ensuremath{\,\mathrm{d}}}
+\newcommand{\unit}[1]{{\ensuremath{\,\mathrm{#1}}}}
 \newcommand{\bvec}[1]{{\ensuremath{\boldsymbol{#1}}}}
@@
 % Notation for this paper.
-\newcommand{\period}{{\ensuremath{P}}}
-\newcommand{\unit}[1]{{\ensuremath{\,\mathrm{#1}}}}
+\newcommand{\meanpars}{{\ensuremath{\bvec{\theta}}}}
+\newcommand{\kernpars}{{\ensuremath{\bvec{\alpha}}}}
 
 \newcommand{\params}{{\ensuremath{\bvec{w}}}}
-\newcommand{\poppars}{{\ensuremath{\theta}}}
+\newcommand{\poppars}{{\ensuremath{\bvec{\beta}}}}
 
@@
 \title{%
-Single \& double transits discovered in the \kepler\ archive: \\
-the frequency of long-period exoplanets
+The population of long-period exoplanets I. --- \\
+Fully-automated discovery \& characterization of
+long-period transiting exoplanet candidates in the \kepler\ archive
 }
@@
 The first is that the transit probability for long-period planets is very low;
-scaling as $\propto\period^{-5/3}$ for orbital periods longer than the
+scaling as $\propto P^{-5/3}$ for orbital periods longer than the
 baseline of contiguous observations.
@@
 
-\section{The fully-automated search for long-period transiting exoplanets}
+\section{A fully-automated search method}
 
@@
 The following sections describe each of these steps in more detail.
-
-% The search for long-period planets presents several unique challenges.
-% Of these, the most important is the inevitable sensitively to signals falsely
-% identified as being caused by a transit exoplanet when it is actually a
-% systematic false alarm (noise) or an astrophysical false positive.
-% In the following paragraphs, we detail our method for addressing these
-% challenges and quantifying their effects.
-% In summary, we identify false alarms by developing a conservative automated
-% candidate vetting algorithm using the full light curve of each target star and
-% measure the incompleteness introduced by this procedure.
-% To account for astrophysical false positives, we discard candidates that fail
-% the standard transit centroid tests and then statistically incorporate
-% uncertainties introduced by false positives missed by this procedure at a
-% population level.
 
@@
 \subsection{Light curve-level vetting}
+
+In this step of the method, the goal is to discard any signals that are not
+sufficiently ``transit-like'' in shape.
+To quantify this decision, we perform a model comparison between a physical
+transit model and a set of other parameterized models for systematics.
+In order for a candidate to pass this vetting step, the transit model must be
+``preferred'' to any other model as measured using the Bayesian Information
+Criterion (BIC).
+The BIC is not the optimal choice for this model comparison but it is
+computationally intractable to compute thousands of precise marginalized
+likelihoods for each model.
+The BIC can be efficiently computed and it exhibits the desired
+behavior---increasing with the likelihood but flexible models are
+penalized---and we find that it performs sufficiently well in practice.
+
+For up to three candidate transit times per light curve, we select a
+contiguous chunk of light curve approximately centered on the proposed transit
+with no more than 500 cadences \dfmtodo{check me} and compute the BIC of each
+model for this data set.
+We will define the BIC for a model $k$ in the set of $K$ models is given by
+\begin{eqnarray}
+\mathrm{BIC}_k &=& \ln \mathcal{L}^* - \frac{J}{2}\,\log N
+\end{eqnarray}
+where the likelihood function $\mathcal{L}$ is evaluated at its maximum, $J$
+is the number of free parameters in the model, and $N$ is the number of
+data points in the data set.
+
+For each model, we describe the data using a Gaussian Process (GP;
+\dfmtodo{cite}) with a Mat\'ern-3/2 covariance and mean given by the chosen
+model $m_k(t;\,\meanpars)$ parameterized by the parameter vector \meanpars.
+This generative model is specified by the following likelihood function:
+\begin{eqnarray}
+\mathcal{L} = \ln p_k(\bvec{y}\,|\,\meanpars,\,\kernpars) &=&
+- \frac{1}{2}\,\bvec{r}_k(\meanpars)^\T\,K(\kernpars)^{-1}\,
+    \bvec{r}_k(\meanpars)
+- \frac{1}{2}\log\det K(\kernpars) - \frac{N}{2} \log{2\,\pi}
+\end{eqnarray}
+where \bvec{y} is the vector of flux measurements, \bvec{t} are the
+corresponding times, and
+\begin{eqnarray}
+\bvec{r}_k(\meanpars) &=& \bvec{y} - m_k(\bvec{t};\,\meanpars) \quad.
+\end{eqnarray}
+The covariance matrix $K(\kernpars)$ is parameterized by the parameters
+$\kernpars = (\alpha,\,\tau)$ and its elements are given by
+\begin{eqnarray}
+\left[ K(\kernpars) \right]_{ij} &=& \sigma_i^2\,\delta_{ij}
+    + \alpha^2 \left[ 1+\frac{|t_i - t_j|}{\sqrt{3}\,\tau} \right]
+      \exp \left(-\frac{|t_i - t_j|}{\sqrt{3}\,\tau}\right)
+\end{eqnarray}
+where $\sigma_i$ is the reported uncertainty on the $i$-th flux measurement.
+
+The gradients of the likelihood with respect to the parameters \meanpars\
+and \kernpars\ are given by
+\begin{eqnarray}
+\frac{\dd\ln p_k(\bvec{y}\,|\,\meanpars,\,\kernpars)}{\dd \meanpars} &=&
+\frac{\dd m_k(\bvec{t};\,\meanpars)}{\dd\meanpars}^\T \, K(\kernpars)^{-1} \,
+    m_k(\bvec{t};\,\meanpars)
+\end{eqnarray}
+and
+\begin{eqnarray}
+\frac{\dd\ln p_k(\bvec{y}\,|\,\meanpars,\,\kernpars)}{\dd \kernpars} &=&
+\frac{1}{2}\,\mathrm{Tr}\left(
+    \left[ \bvec{\phi}\,\bvec{\phi}^\T - K(\kernpars)^{-1} \right]
+    \,\frac{\dd K(\kernpars)}{\dd\kernpars}
+\right)
+\end{eqnarray}
+where
+\begin{eqnarray}
+\bvec{\phi} &=& K(\kernpars)^{-1}\,\bvec{r}_k(\meanpars) \quad.
+\end{eqnarray}
+Therefore, if we can compute the gradient of the model with respect to its
+parameters, we can efficiently optimize this function to find the maximum
+likelihood parameters using a gradient-based non-linear optimization method.
+To compute the gradients of the transit model, we use a compile-time automatic
+differentiation library \dfmtodo{cite Ceres} and for the other models, we
+choose models that can be easily differentiated analytically.
+
+The models are:
+\begin{itemize}
+{\item a limb-darkened, exposure time integrated transit light curve,}
+{\item a pure Gaussian Process model to capture stellar variability,}
+{\item a single outlier,}
+{\item an step function, and}
+{\item a box.}
+\end{itemize}
 

### 2016-02-27 document/ms.tex
nothin

@@
 For up to three candidate transit times per light curve, we select a
-contiguous chunk of light curve approximately centered on the proposed transit
-with no more than 500 cadences \dfmtodo{check me} and compute the BIC of each
-model for this data set.
+contiguous chunk of PDC light curve approximately centered on the proposed
+transit with no more than 500 cadences \dfmtodo{check me} and compute the BIC
+of each model for this data set.
 We will define the BIC for a model $k$ in the set of $K$ models is given by

### 2016-03-02 document/ms.tex
some words about injections

@@
 
+To measure the completeness of our long-period transit search method, we
+exploit the fact that transit signals are sparse and rare.
+Therefore, most light curves contain no transits and we can reliably measure
+the recovery rate of our method on synthetic transit signals---with known
+properties---injected into real light curves.
+This procedure is standard practice in the transit literature and it has been
+used to determine the completeness of the KOI catalog (\dfmtodo{cite}) and
+other independent transit searches (\dfmtodo{cite}).
+
+To reliably capture the full structure of the search completeness function,
+the simulations must sample the (high-dimensional) space of all properties
+that affect the probability of detecting a transit: the stellar properties
+(including variability amplitudes and time scales), the planet's physical
+properties and orbital elements, and any observational effects (noise,
+spacecraft pointing variations, \etc).
+For the modest goals of this paper, we only need a robust constraint on the
+transit detection efficiency \emph{integrated} across the target sample but,
+even so, many simulations per star are required.
+
+The procedure for measuring the recovery rate of simulated transits is as
+follows:
+\begin{enumerate}
+{\item First, a star is randomly selected from the target list, and the PDC
+light curve and stellar properties for that star are loaded.}
+{\item Planetary properties are sampled from the distributions listed in
+\dfmtodo{some table} with phase uniformly distributed across the baseline of
+observations. These properties are resampled until the transit is visible in
+at least one non-flagged cadence.}
+{\item The transit signal induced by this planet is computed and multiplied
+into the PDC light curve.}
+{\item The transit search method described in section \dfmtodo{some section}
+(including de-trending and all automated vetting) is applied to this light
+curve with the injected transit signal.}
+{\item This candidate is flagged as recovered if at least one transit (within
+\dfmtodo{some tolerance}) passes all the cuts imposed by the automated
+vetting.}
+\end{enumerate}
+
 \section{The occurrence rate of long-period exoplanets}
@@
 \begin{eqnarray}
-Q_{\mathrm{geom},k} (\params) &=& \frac{R_{\star,k}}{a_k(\params)} \\
-&=& \left[\frac{4\,\pi^2}{G\,M_{\star,k}}\right]^{1/3}\,R_{\star,k}\,P^{-2/3}
+Q_{\mathrm{geom},k} (\params) &=& \frac{R_{\star,k}}{a_k(\params)}
+    \, \frac{1 + e(\params)\,\sin\omega(\params)}{1-e(\params)^2} \\
+&=& \left[\frac{4\,\pi^2}{G\,M_{\star,k}}\right]^{1/3}\,R_{\star,k}
+    \, \left[\frac{1 + e(\params)\,\sin \omega(\params)}{1-e(\params)^2}\right]
+    \, P^{-2/3}
 \end{eqnarray}
@@
     \left[\frac{4\,\pi^2}{G\,M_{\star,k}}\right]^{1/3}\,
-    R_{\star,k}\,T_k\,P^{-5/3} \quad.
+    R_{\star,k}\,T_k
+    \, \left[\frac{1 + e(\params)\,\sin \omega(\params)}{1-e(\params)^2}\right]
+    \, P^{-5/3} \quad.
 \end{eqnarray}

### 2016-03-02 peerless/pool.py
adding rodrigo's pool

@@ -1,0 +1,826 @@
+# -*- coding: utf-8 -*-
+'''
+Author: Rodrigo Luger
+Included in this project and licensed under MIT with his permission.
+
+
+pool.py
+-------
+
+An implementation of four different types of pools:
+
+    - An MPI pool borrowed from ``emcee``. This pool passes Python objects
+      back and forth to the workers and communicates once per task.
+
+    - An attempt at an optimized version of the MPI pool, specifically for
+      passing arrays of numpy floats. If the length of the array passed
+      to the ``map`` method is larger than the number of processes, the iterable
+      is passed in chunks, which are processed *serially* on each processor.
+      This minimizes back-and-forth communication and should increase the speed
+      a bit.
+
+    - A multiprocessing for local parallelization, borrowed from ``emcee``
+
+    - A serial pool, which uses the built-in ``map`` function
+
+
+'''
+
+from __future__ import division, print_function, absolute_import, unicode_literals
+import numpy as np
+import sys
+try:
+    from mpi4py import MPI
+    MPI = MPI
+except ImportError:
+    MPI = None
+import signal
+import functools
+import multiprocessing
+import multiprocessing.pool
+import logging
+log = logging.getLogger(__name__)
+
+__all__ = ['MPIPool', 'MPIOptimizedPool', 'MultiPool', 'SerialPool']
+
+# Tags and messages
+TAG_TASK     = 0
+TAG_NEW_FUNC = 1
+TAG_NEW_DIMS = 2
+TAG_CLOSE    = 3
+MSG_EMPTY    = lambda : np.empty(1, dtype = 'float64')
+
+class _close_pool_message(object):
+    def __repr__(self):
+        return "<Close pool message>"
+
+class _function_wrapper(object):
+    def __init__(self, function):
+        self.function = function
+
+def _error_function(*args):
+    '''
+    The default worker function. Should be replaced
+    with the desired mapping function on the first
+    call.
+
+    '''
+
+    raise Exception("Pool was sent tasks before being told what "
+                    "function to apply.")
+
+def _test_function(x):
+    '''
+    Wastes a random amount of time, then
+    returns the average of ``x``.
+
+    '''
+
+    for i in range(np.random.randint(99999)):
+        j = i ** 2
+
+    return np.sum(x) / float(len(x))
+
+def _initializer_wrapper(actual_initializer, *rest):
+    """
+    We ignore SIGINT. It's up to our parent to kill us in the typical
[…]

### 2016-03-03 document/ms.tex

@@
 
-% \renewcommand{\eqref}[1]{\ref{eq:#1}}
-% \newcommand{\Eq}[1]{Equation~(\eqref{#1})}
-% \newcommand{\eq}[1]{\Eq{#1}}
-% \newcommand{\eqalt}[1]{Equation~\eqref{#1}}
+\renewcommand{\eqref}[1]{\ref{eq:#1}}
+\newcommand{\Eq}[1]{Equation~(\eqref{#1})}
+\newcommand{\eq}[1]{\Eq{#1}}
+\newcommand{\eqalt}[1]{Equation~\eqref{#1}}
 \newcommand{\eqlabel}[1]{\label{eq:#1}}
@@
 
+The fraction of recovered simulations as a function of the relevant parameters
+gives an estimate of the search completeness or the probability of detecting
+an exoplanet transit with a given set of parameters, \emph{conditioned on the
+fact that it transits}.
+We will call this function $Q_{\mathrm{det},k}(\params)$ where \params\ is the
+set of all parameters affecting the transit detectability and $k$ is an index
+running over target stars.
+
+This detection efficiency must then be combined with the geometric transit
+probability function and the window function.
+For the star $k$, the geometric transit probability is given by \dfmtodo{cite}
+\begin{eqnarray}
+Q_{\mathrm{geom},k} (\params) &=& \frac{R_{\star,k}}{a_k}
+    \, \frac{1 + e\,\sin\omega}{1-e^2} \\
+&=& \left[\frac{4\,\pi^2}{G\,M_{\star,k}}\right]^{1/3}\,R_{\star,k}
+    \, \left[\frac{1 + e\,\sin \omega}{1-e^2}\right]
+    \, P^{-2/3}
+\end{eqnarray}
+where the parameters $e$, $\omega$, and $P$ are included in \params.
+Approximating the window function using the binomial probability of observing
+at least one transit \dfmtodo{cite bm14} we find
+\begin{eqnarray}
+Q_{\mathrm{win},k} (\params) &=& 1 - (1 - f_{\mathrm{duty},k})^{T_k/P}
+\end{eqnarray}
+where $f_{\mathrm{duty},k}$ is the duty cycle and $T_k$ is the full
+observation baseline for target $k$.
+
+Combining these detection effects, the total detection efficiency is given by
+\begin{eqnarray}
+Q_k(\params) &=& Q_{\mathrm{det},k}(\params) \,
+                 Q_{\mathrm{win},k} (\params) \,
+                 Q_{\mathrm{geom},k} (\params) \quad.
+\end{eqnarray}
+For the purposes of this \paper, we are not considering the occurrence rate of
+exoplanets as a function of stellar properties; we will only measure an
+average rate across the target sample that we previously selected.
+Therefore, it is sufficient to estimate the marginalized detection efficiency
+integrated with respect to our prior distributions on the nuisance parameters.
+In this case, the only parameters that we will consider are planet radius and
+orbital period.
+Under this model, the relevant detection efficiency function for long-period
+transiting planets is
+\begin{eqnarray}\eqlabel{full-comp}
+Q(R,\,P) &=& \frac{1}{K} \sum_{k=1}^{K} \int Q_k(\params) \,
+    p(\params_{\{R,\,P\}}) \dd\params_{\{R,\,P\}}
+\end{eqnarray}
+where $\params_{\{R,\,P\}}$ indicates the set of all parameters except radius
+and period.
+
+Since the simulated parameters in the injection and recovery tests described
+above were sampled from the prior distribution $p(\params_{\{R,\,P\}})$, the
+easiest way to estimate \eq{full-comp} is to take the ratio of the weighted
+histogram of the recovered injections to the weighted histogram of all
+simulations where each simulation is weighted by
+$Q_{\mathrm{win},k} (\params) \, Q_{\mathrm{geom},k} (\params)$ evaluated at
+the parameters of the simulation.
+
 \section{The occurrence rate of long-period exoplanets}
@@
 Geometric:
-
-\begin{eqnarray}
-Q_{\mathrm{geom},k} (\params) &=& \frac{R_{\star,k}}{a_k(\params)}
-    \, \frac{1 + e(\params)\,\sin\omega(\params)}{1-e(\params)^2} \\
-&=& \left[\frac{4\,\pi^2}{G\,M_{\star,k}}\right]^{1/3}\,R_{\star,k}
-    \, \left[\frac{1 + e(\params)\,\sin \omega(\params)}{1-e(\params)^2}\right]
-    \, P^{-2/3}
-\end{eqnarray}
 

### 2016-03-17 document/ms.tex
a few words

@@
 \newcommand{\poppars}{{\ensuremath{\bvec{\beta}}}}
+
+\newcommand{\rate}{{\ensuremath{\Gamma}}}
 
@@
 the parameters of the simulation.
+\dfmtodo{Some figure} shows the measured completeness (\eq{full-comp}) as a
+function of planet radius and orbital period.
+
+\dfmtodo{Analytic fit?}
 
@@
 
-Geometric:
-
-Temporal:
-
+Using the catalog of exoplanet discoveries (\dfmtodo{some section}) and the
+measurement of the search completeness (\dfmtodo{some section}), we can now
+estimate the occurrence rate of long-period exoplanets.
+This inference can be simplified by making a few strong assumptions that are
+only weakly justified.
+First, we make the strong assumption that none of the candidates are
+astrophysical false positives (background eclipsing binaries, the secondary
+eclipse of a long-period binary system, \etc).
+We revisit this assumption and discuss its validity in \dfmtodo{some section}.
+Next, we model the occurrence of exoplanets as a Poisson process
+(\dfmtodo{CITE}) with a rate function $\rate_{\poppars} (R,\,P)$ parameterized
+by some parameters \poppars.
+This assumption leads to the commonly used likelihood function
+(\dfmtodo{CITE})
 \begin{eqnarray}
-Q_{\mathrm{temp},k} (\params) &=& \frac{T_k}{P}
+\ln p (\{w_j\}_{j=1}^J\,|\,\poppars) =
+    \sum_{j=1}^J \ln \rate_{\poppars} (R_j,\,P_j)
+    - \int \rate_{\poppars} (R,\,P)\,Q(R,\,P)\dd R\dd P
+    + \mathrm{constant} \quad.
 \end{eqnarray}
-where $T_k$ is the total observing baseline for target $k$.
-Combined with the detection efficiency $Q_{\mathrm{det}}(\params)$ (assumed to
-be constant for each target), the total completeness as a function of the
-parameters is
-\begin{eqnarray}
-Q_k(\params) &=& Q_{\mathrm{det},k}(\params) \,
-                 Q_{\mathrm{temp},k} (\params) \,
-                 Q_{\mathrm{geom},k} (\params) \\
-&=& Q_{\mathrm{det},k}(\params) \,
-    \left[\frac{4\,\pi^2}{G\,M_{\star,k}}\right]^{1/3}\,
-    R_{\star,k}\,T_k
-    \, \left[\frac{1 + e(\params)\,\sin \omega(\params)}{1-e(\params)^2}\right]
-    \, P^{-5/3} \quad.
-\end{eqnarray}
-
-The likelihood function for the catalog of planet candidates is
-\begin{eqnarray}
-p(\{\params_n\}\,|\,\poppars) &\propto&
-    \exp \left(
-        \int f_\poppars (\params)\,\sum_{k=1}^K Q_k(\params) \dd\params
-    \right) \, \prod_{n=1}^N f_\poppars (\params_n) \quad.
-\end{eqnarray}
-
-Therefore
-\begin{eqnarray}
-\int f_\poppars (\params)\,\sum_{k=1}^K Q_k(\params) \dd\ln P\dd\ln R &=&
-    \bar{Q}\,\int Q_{\mathrm{det}}(\params)\,f_\poppars(\params)\,P^{-5/3}
-        \dd\ln P\dd\ln R
-\end{eqnarray}
-where
-\begin{eqnarray}
-\bar{Q} &=& \sum_{k=1}^K
-    \left[\frac{4\,\pi^2}{G\,M_{\star,k}}\right]^{1/3}\,R_{\star,k}\,T_k
-\quad.
-\end{eqnarray}
-
-The easiest way to evaluate this integral in practice is to use Monte Carlo
-integration to find
-\begin{eqnarray}
-\int Q_{\mathrm{det}}(\params)\,f_\poppars(\params)\,P^{-5/3}\dd\ln P\dd\ln R
-&=& \frac{F}{J}\sum_{j=1}^J Q_{\mathrm{det}}(P^{(j)},\,R^{(j)})\,
-        f_\poppars(P^{(j)},\,R^{(j)})
-\end{eqnarray}
-where
-\begin{eqnarray}
-F &=& \frac{3}{5}\,[P_\mathrm{min}^{-5/3}-P_\mathrm{max}^{-5/3}]\,
-      [\ln R_\mathrm{max} - \ln R_\mathrm{min}]
-\end{eqnarray}
-and
-\begin{eqnarray}
-P^{(j)} \sim P^{-8/3} &\mathrm{and}&
-\ln R^{(j)} \sim \mathcal{U}(\ln R_\mathrm{min},\,\ln R_\mathrm{max})
-\end{eqnarray}
-
-\begin{eqnarray}
-f_\poppars (\params) &=& \frac{1}{f_0}\,C\,P^\alpha\,R^\beta
-\end{eqnarray}
-where
-\begin{eqnarray}
-f_0 &=&
-    \int_{P_\mathrm{min}}^{P_\mathrm{max}}
-    \int_{R_\mathrm{min}}^{R_\mathrm{max}}
-    P^\alpha\,R^\beta\dd\ln P\dd\ln R
-\end{eqnarray}
+Since our catalog of discoveries is small, we will only make limited
+inferences about the population.
+For the purposes of this paper, we will simply estimate the period of
+long-period planets ($2\,\mathrm{yr} \le P < 15\,\mathrm{yr}$) in two radius
+bins $0.1\,R_\mathrm{J} \le R < 0.5\,R_\mathrm{J}$ and $0.5\,R_\mathrm{J} \le
+R < R_\mathrm{J}$.
 

### 2016-04-19 document/figures/completeness.py
don't crash on init

@@ -2,7 +2,7 @@
 
 from __future__ import division, print_function
 
-from plot_setup import COLORS
+from plot_setup import COLORS, SQUARE_FIGSIZE
 
 import os
 import pickle
@@ -11,7 +11,39 @@ import pandas as pd
 import matplotlib.pyplot as pl
 
 inj = pd.read_hdf("../../results/injections.h5", "injections")
-print(inj)
+inj = inj[inj.ncadences > 0]
+rec = inj[inj.recovered]
 
+# n_all, bins = np.histogram(np.log10(inj.radius), 20)
+# n_rec, _ = np.histogram(np.log10(rec.radius), bins)
+# n = n_rec / n_all
+# n_err = n / np.sqrt(n_all)
+# print(n)
 
-# fig.savefig("completeness.pdf", bbox_inches="tight")
+n_all, ln_radius_bins, ln_period_bins = np.histogram2d(
+    np.log(inj.radius), np.log(inj.period), (10, 5),
+)
+n_rec, _, _ = np.histogram2d(
+    np.log(rec.radius), np.log(rec.period), (ln_radius_bins, ln_period_bins),
+)
+n = n_rec / n_all
+n_err = n / np.sqrt(n_all)
+
+X, Y = np.meshgrid(np.exp(ln_period_bins) / 365.25,
+                   np.exp(ln_radius_bins) / 0.0995,
+                   indexing="ij")
+
+fig, ax = pl.subplots(1, 1, figsize=SQUARE_FIGSIZE)
+cax = ax.pcolor(X, Y, 100*n.T, cmap="viridis", vmin=0, vmax=100)
+ax.set_xscale("log")
+ax.set_yscale("log")
+ax.set_xlim(X.min(), X.max())
+ax.set_ylim(Y.min(), Y.max())
+ax.set_xlabel("period [years]")
+ax.set_ylabel("$R_\mathrm{P} / R_\mathrm{J}$")
+ax.set_xticks([3, 5, 10, 20])
+ax.get_xaxis().set_major_formatter(pl.ScalarFormatter())
+ax.set_yticks([0.1, 0.2, 0.5, 1, 2])
+ax.get_yaxis().set_major_formatter(pl.ScalarFormatter())
+
+fig.savefig("completeness.pdf", bbox_inches="tight")

### 2016-04-19 peerless/fit.py
less verbosity

@@ -57,7 +57,6 @@ class TransitModel(object):
                                 ll, blob = self.lnlike(compute_blob=True)
                                 if blob[0] == 0:
                                     mx = (ll, (b, rad, per, ecc, w))
-        print(mx)
         body.e = mx[1][3]
         body.omega = mx[1][4]
         body.period = mx[1][2]
@@ -181,7 +180,6 @@ class TransitModel(object):
             # Final optimization.
             p0 = self.system.get_vector()
             r = minimize(self._nlp, p0, method="L-BFGS-B")
-            print(r)
 
             return
 

### 2016-04-19 document/figures/completeness.py
completeness figure

@@ -2,26 +2,19 @@
 
 from __future__ import division, print_function
 
-from plot_setup import COLORS, SQUARE_FIGSIZE
+from plot_setup import SQUARE_FIGSIZE, COLORS
 
-import os
-import pickle
 import numpy as np
 import pandas as pd
+from itertools import product
 import matplotlib.pyplot as pl
 
 inj = pd.read_hdf("../../results/injections.h5", "injections")
 inj = inj[inj.ncadences > 0]
 rec = inj[inj.recovered]
 
-# n_all, bins = np.histogram(np.log10(inj.radius), 20)
-# n_rec, _ = np.histogram(np.log10(rec.radius), bins)
-# n = n_rec / n_all
-# n_err = n / np.sqrt(n_all)
-# print(n)
-
 n_all, ln_radius_bins, ln_period_bins = np.histogram2d(
-    np.log(inj.radius), np.log(inj.period), (10, 5),
+    np.log(inj.radius), np.log(inj.period), (8, 4),
 )
 n_rec, _, _ = np.histogram2d(
     np.log(rec.radius), np.log(rec.period), (ln_radius_bins, ln_period_bins),
@@ -33,8 +26,20 @@ X, Y = np.meshgrid(np.exp(ln_period_bins) / 365.25,
                    np.exp(ln_radius_bins) / 0.0995,
                    indexing="ij")
 
-fig, ax = pl.subplots(1, 1, figsize=SQUARE_FIGSIZE)
-cax = ax.pcolor(X, Y, 100*n.T, cmap="viridis", vmin=0, vmax=100)
+fig = pl.figure(figsize=2*np.array(SQUARE_FIGSIZE))
+
+ax = pl.axes([0.1, 0.1, 0.6, 0.6])
+ax.pcolor(X, Y, 100*n.T, cmap="viridis", vmin=0, vmax=100)
+
+# Label the bins with their completeness percentages.
+for i, j in product(range(len(ln_period_bins)-1),
+                    range(len(ln_radius_bins)-1)):
+    x = np.exp(0.5 * (ln_period_bins[i] + ln_period_bins[i+1])) / 365.25
+    y = np.exp(0.5 * (ln_radius_bins[j] + ln_radius_bins[j+1])) / 0.0995
[…]

### 2016-04-19 document/ms.tex
words

@@
 % \documentclass[twocolumn]{aastex6}
-\documentclass[onecolumn]{aastex6}
-% \documentclass[preprint]{aastex}
+% \documentclass[onecolumn]{aastex6}
+\documentclass[preprint,12pt]{aastex}
 
@@
 \title{%
-The population of long-period exoplanets I. --- \\
+The population of long-period exoplanets --- \\
 Fully-automated discovery \& characterization of
@@
 still be underrepresented in a transiting sample.
-The second challenge is that there are substantial signals in the observed
+The second challenge is that there are many signals in the observed
 light curves caused by stochastic processes---both instrumental
 (pointing jitter, temperature variations, \etc) and astrophysical (stellar
-variability, \etc)---that can masquerade as transit signals.
-In practice, even using the most sophisticated systematics removal methods,
-these false signal far outnumber the true single transits.
+variability, \etc)---that can masquerade as transits.
+Even using the most sophisticated methods for removing this variability, false
+signal far outnumber the true single transits.
 
@@
 One shortcoming of the PH method is that it can be difficult to fully quantify
-the performance (completeness and reliability) of the search and PH does not
-evaluate their users using synthetic transit signals as is now common practice
-in the transit search literature \dfmtodo{is this still true?}.
-This means that the PH sample of candidates cannot be used for robust
+the performance (completeness and reliability) of the search results.
+% and PH does not
+% evaluate their users using synthetic transit signals as is now common practice
+% in the transit search literature \dfmtodo{is this still true?}.
+This means that the PH sample of candidates cannot be reliably used for robust
 population inference.
 
+Visual inspection and hand-curation by experts has also been used to find the
+transits of long-period planets in previously known planetary systems
+(\dfmtodo{CITE single transit KOIs}).
+All light curves in the \kepler\ archive with \kepler\ Objects of Interest
+(KOIs) were visually inspected to find candidate single transits.
+This is a reasonable idea because long-period planets with transiting inner
+planets are expected to have a higher geometric transit probability.
+The selection effects introduced by restricting the target sample like this
+are difficult to take into account when making inferences about the population
+of long-period planets.
+
 To study the occurrence rate of long-period exoplanets, we have developed a
-fully-automated method for searching the archival \kepler\ light curves for
-these systems with only one or two transits.
-Using this method, we detect XXX long-period transiting planet candidates and
-YYY long-period eclipsing binary candidates.
-We estimate that the population level false positive rate in this exoplanet
-candidate sample is about ZZZ\%.
+fully-automated method to search the archival \kepler\ light curves and
+reliably discover long-period planets with only one or two transits.
+Using this method, we search the 40,000 brightest Sun-like stars and detect
+XXX long-period astrophysical transit candidates.
+Of these, YYY are likely to be exoplanets with radii equal to or smaller than
+Jupiter's radius.
+Using transit injection and recovery, we measure the completeness of our
+search procedure.
+We estimate that the population level astrophysical false positive rate in
+this candidate sample is about ZZZ\%.
 By injecting synthetic transit signals into the \kepler\ light curves, we
@@
 than their larger counterparts even at long orbital periods.
-
-Data from the \kepler\ Mission has been used to discover a diverse zoo of
-thousands of exoplanets of all sizes orbiting stars of all types.
-It has be demonstrated that these catalogs of exoplanet discoveries can be
-used to place constraints on the occurrence rate of exoplanets \dfmtodo{CITE}.
-These results are sensitive to the detection efficiency and reliability of the
-discovery methodology \dfmtodo{CITE Burke}.
 
@@
 
+The model comparison step is computationally expensive because we estimate the
+marginalized likelihoods for the light curve data under several different
+models describing a transit and many other processes that ``look'' like
+transits but are actually caused by noise.
+This step is also conservative; unless a signal is a very convincing transit,
+it won't pass the test.
+In practice, this means that all but the highest signal-to-noise events will
+be rejected at this step.
+Therefore, in the inexpensive first step---the initial candidate search---we
+can restrict the candidate list to high signal-to-noise events without a
+substantial loss in detection efficiency.
+
 \subsection{Finding box-shaped candidate events}
 
-It is not feasible to compute a full model comparison at every time in the
-light curve so we must first find potentially interesting events.
+It is not computationally feasible to run a full model comparison at every
+time in the light curve so we must first find potentially interesting events.
+For our purposes, ``interesting'' means high signal-to-noise and previously
+unknown.
+We restrict our search to high signal-to-noise transits since the
+
 To generate this list, we apply a standard ``box least squares'' (BLS;
@@
 a grid of times spanning the full \kepler\ baseline.
+We only need to use a single transit duration because the following steps in
+this procedure are only sensitive to transits with very high signal-to-noise
+so, in practice, the results of this step are insensitive to the specific
+choice of duration.
+
+As previously mentioned, the following steps will only detect high
+signal-to-noise transits.
+Therefore, we use this
 To avoid edge effects, we apodize this detection scalar near any large gaps in
@@
 
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\textwidth]{figures/completeness.pdf}
+\end{center}
+\caption{%
+\figlabel{completeness}}
+\end{figure*}
+
 \section{The occurrence rate of long-period exoplanets}

### 2016-04-19 document/ms.tex
nothing really

@@
 
-The model comparison step is computationally expensive because we estimate the
-marginalized likelihoods for the light curve data under several different
-models describing a transit and many other processes that ``look'' like
-transits but are actually caused by noise.
+The model comparison step (step 2) is the key component of our method that
+enables robust automation but it is also computationally expensive because we
+must estimate the marginalized likelihoods for the light curve under several
+different models describing a transit and many other processes that ``look''
+like transits but are actually caused by noise.
 This step is also conservative; unless a signal is a very convincing transit,

### 2016-04-29 document/ms.tex
moving GP to appendix

@@
 \sloppy\sloppypar
+\widowpenalty10000
+\clubpenalty500
 
@@
 limit on the detectable periods of about two years.
-In the Solar System, Jupiter---with a period of 12 years---dominates the
+In the Solar System, Jupiter~--~with a period of 12 years~--~dominates the
 planetary dynamics and, since it would only exhibit at most one transit in the
@@
 The second challenge is that there are many signals in the observed
-light curves caused by stochastic processes---both instrumental
+light curves caused by stochastic processes~--~both instrumental
 (pointing jitter, temperature variations, \etc) and astrophysical (stellar
-variability, \etc)---that can masquerade as transits.
+variability, \etc)~--~that can masquerade as transits.
 Even using the most sophisticated methods for removing this variability, false
@@
 long-period, giant planet occurrence rates based on radial velocity surveys
-and we demonstrate that small---and possibly rocky---planets are more common
+and we demonstrate that small~--~and possibly rocky~--~planets are more common
 than their larger counterparts even at long orbital periods.
@@
 be rejected at this step.
-Therefore, in the inexpensive first step---the initial candidate search---we
+Therefore, in the inexpensive first step~--~the initial candidate search~--~we
 can restrict the candidate list to high signal-to-noise events without a
@@
 
-\subsection{Finding box-shaped candidate events}
+\subsection{Initial candidate events}
 
@@
 unknown.
-We restrict our search to high signal-to-noise transits since the
 
@@
 signal-to-noise transits.
-Therefore, we use this
 To avoid edge effects, we apodize this detection scalar near any large gaps in
@@
 The BIC can be efficiently computed and it exhibits the desired
-behavior---increasing with the likelihood but flexible models are
-penalized---and we find that it performs sufficiently well in practice.
+behavior~--~increasing with the likelihood but flexible models are
+penalized~--~and we find that it performs sufficiently well in practice.
 
@@
 model $m_k(t;\,\meanpars)$ parameterized by the parameter vector \meanpars.
-This generative model is specified by the following likelihood function:
-\begin{eqnarray}
-\mathcal{L} = \ln p_k(\bvec{y}\,|\,\meanpars,\,\kernpars) &=&
-- \frac{1}{2}\,\bvec{r}_k(\meanpars)^\T\,K(\kernpars)^{-1}\,
-    \bvec{r}_k(\meanpars)
-- \frac{1}{2}\log\det K(\kernpars) - \frac{N}{2} \log{2\,\pi}
-\end{eqnarray}
-where \bvec{y} is the vector of flux measurements, \bvec{t} are the
-corresponding times, and
-\begin{eqnarray}
-\bvec{r}_k(\meanpars) &=& \bvec{y} - m_k(\bvec{t};\,\meanpars) \quad.
-\end{eqnarray}
-The covariance matrix $K(\kernpars)$ is parameterized by the parameters
-$\kernpars = (\alpha,\,\tau)$ and its elements are given by
-\begin{eqnarray}
-\left[ K(\kernpars) \right]_{ij} &=& \sigma_i^2\,\delta_{ij}
-    + \alpha^2 \left[ 1+\frac{|t_i - t_j|}{\sqrt{3}\,\tau} \right]
-      \exp \left(-\frac{|t_i - t_j|}{\sqrt{3}\,\tau}\right)
-\end{eqnarray}
-where $\sigma_i$ is the reported uncertainty on the $i$-th flux measurement.
-
-The gradients of the likelihood with respect to the parameters \meanpars\
-and \kernpars\ are given by
-\begin{eqnarray}
-\frac{\dd\ln p_k(\bvec{y}\,|\,\meanpars,\,\kernpars)}{\dd \meanpars} &=&
-\frac{\dd m_k(\bvec{t};\,\meanpars)}{\dd\meanpars}^\T \, K(\kernpars)^{-1} \,
-    m_k(\bvec{t};\,\meanpars)
-\end{eqnarray}
-and
-\begin{eqnarray}
-\frac{\dd\ln p_k(\bvec{y}\,|\,\meanpars,\,\kernpars)}{\dd \kernpars} &=&
-\frac{1}{2}\,\mathrm{Tr}\left(
-    \left[ \bvec{\phi}\,\bvec{\phi}^\T - K(\kernpars)^{-1} \right]
-    \,\frac{\dd K(\kernpars)}{\dd\kernpars}
-\right)
-\end{eqnarray}
-where
-\begin{eqnarray}
-\bvec{\phi} &=& K(\kernpars)^{-1}\,\bvec{r}_k(\meanpars) \quad.
-\end{eqnarray}
-Therefore, if we can compute the gradient of the model with respect to its
-parameters, we can efficiently optimize this function to find the maximum
-likelihood parameters using a gradient-based non-linear optimization method.
-To compute the gradients of the transit model, we use a compile-time automatic
-differentiation library \dfmtodo{cite Ceres} and for the other models, we
-choose models that can be easily differentiated analytically.
 
@@
 Therefore, when studying the light curve of an eclipsing binary star or a star
-with known transiting planet candidates---on shorter periods---we also remove
+with known transiting planet candidates~--~on shorter periods~--~we also remove
 all the in-transit data for the candidate using the parameters provided by the
@@
 Therefore, most light curves contain no transits and we can reliably measure
-the recovery rate of our method on synthetic transit signals---with known
-properties---injected into real light curves.
+the recovery rate of our method on synthetic transit signals~--~with known
+properties~--~injected into real light curves.
 This procedure is standard practice in the transit literature and it has been
@@
 transit event is crucial for the future of transiting exoplanet surveys.
-Many of the most dynamically influential planets---like Jupiter in our Solar
-system---exhibit only a single transit in the full observational baseline of
+Many of the most dynamically influential planets~--~like Jupiter in our Solar
+system~--~exhibit only a single transit in the full observational baseline of
 the \kepler.
@@
 
-\section{Supervised classification}
+\section{Gaussian process regression}
+
+Gaussian Processes (GPs) are a class of non-parametric, stochastic models that
+have been demonstrated to be good effective models for the variability in
+\kepler\ light curves.
+A simple GP model can be used to capture residual non-transit variability in
+light curves.
+In this \paper, we use a GP model for two steps: light curve--level transit
+shape vetting and parameter estimation.
+A full discussion of GPs is beyond the scope of this \paper, so we will only
+summarize the most relevant points here and direct an interested reader to
+\dfmtodo{cite RW} for more details.
+
+A GP model is specified by the following likelihood function
+\begin{eqnarray}\eqlabel{gplike}
+\mathcal{L} = \ln p(\bvec{y}\,|\,\meanpars,\,\kernpars) &=&
+- \frac{1}{2}\,\bvec{r}(\meanpars)^\T\,K(\kernpars)^{-1}\,
+    \bvec{r}(\meanpars)
+- \frac{1}{2}\log\det K(\kernpars) - \frac{N}{2} \log{2\,\pi}
+\end{eqnarray}
+where \bvec{y} is a list of measurements in a scalar time series~--~in this
+case, fluxes~--~measured at the times \bvec{t}, and
+\begin{eqnarray}
+\bvec{r}(\meanpars) &=& \bvec{y} - m(\bvec{t};\,\meanpars)
+\end{eqnarray}
+is the vector of residuals away from the mean model $m(\bvec{t};\,\meanpars)$.
+For the purposes of this paper, we model the covariance matrix $K(\kernpars)$
+using the Mat\'ern-3/2 kernel.
+Under this model, the elements of $K(\kernpars)$ are given by
+\begin{eqnarray}\eqlabel{matern}
+\left[ K(\kernpars) \right]_{ij} &=& \sigma_i^2\,\delta_{ij}
+    + \alpha^2 \left[ 1+\frac{|t_i - t_j|}{\sqrt{3}\,\tau} \right]
+      \exp \left(-\frac{|t_i - t_j|}{\sqrt{3}\,\tau}\right)
+\end{eqnarray}
+where $\sigma_i$ is the reported uncertainty on the $i$-th measurement in the
+time series and $\delta_{ij}$ is the Kronecker delta.
+
+This covariance function (\eqalt{matern}) is specified by an amplitude
+$\alpha$ and a time scale $\tau$ and we will simultaneously fit for these
+hyperparameters $\kernpars=(\alpha,\,\tau)$ and the parameters of the mean
+model \meanpars.
+To efficiently find the parameter set that maximizes \eq{gplike} using a
+non-linear optimization routine\footnote{We use the L-BFGS-B method as
+implemented in SciPy \url{%
+http://docs.scipy.org/doc/scipy/reference/generated/%
+scipy.optimize.minimize.html}.},
+it is useful to be able to compute the gradient of \eq{gplike} with respect to
+the parameters \meanpars\ and \kernpars.
+These gradients are given by
+\begin{eqnarray}\eqlabel{gpmeangrad}
+\frac{\dd\ln p(\bvec{y}\,|\,\meanpars,\,\kernpars)}{\dd \meanpars} &=&
+\frac{\dd m(\bvec{t};\,\meanpars)}{\dd\meanpars}^\T \, K(\kernpars)^{-1} \,
+    m(\bvec{t};\,\meanpars)
+\end{eqnarray}
+and
+\begin{eqnarray}
+\frac{\dd\ln p(\bvec{y}\,|\,\meanpars,\,\kernpars)}{\dd \kernpars} &=&
+\frac{1}{2}\,\mathrm{Tr}\left(
+    \left[ \bvec{\phi}\,\bvec{\phi}^\T - K(\kernpars)^{-1} \right]
+    \,\frac{\dd K(\kernpars)}{\dd\kernpars}
+\right)
+\end{eqnarray}
+where
+\begin{eqnarray}
+\bvec{\phi} &=& K(\kernpars)^{-1}\,\bvec{r}(\meanpars) \quad.
+\end{eqnarray}
+
+To evaluate \eq{gpmeangrad}, we must also evaluate the derivative of the mean
+model with respect to its parameters.
+For this \paper, the model $m(\bvec{t};\,\meanpars)$ will sometimes be the
+limb-darkened, exposure time-integrated transit of a planet on a Keplerian
+orbit and the parameters \meanpars\ are the physical and orbital parameters of
+the planet and star.
+Analytically computing the gradient of a simple transit model is possible
+\citep{Pal:2008} but it becomes substantially more tedious as the model
+becomes more realistic.
+Therefore, we use a compile-time automatic differentiation library\footnote{%
+More specifically, we use the \texttt{Jet} object from the BSD-licensed Ceres
+Solver \url{http://ceres-solver.org}} \citep{Agarwal:2016} to compute first
+derivatives of the full transit model to machine precision.
 

### 2016-05-14 document/ms.tex
writing

@@
-% This paper is part of the single transits project.
-% Copyright 2015 Dan Foreman-Mackey (NYU) and the co-authors listed below.
-%
-%  RULES OF THE GAME
-%
-%  * 80 characters
-%  * line breaks at the ends of sentences
-%  * eqnarrys ONLY
-%  * ``light curve'' not ``light-curve'' or ``lightcurve''
-%  * that is all.
-%
+% Copyright 2015-2016 Dan Foreman-Mackey and the co-authors listed below.
 
-% \documentclass[twocolumn]{aastex6}
-% \documentclass[onecolumn]{aastex6}
-\documentclass[preprint,12pt]{aastex}
+\documentclass[manuscript, letterpaper]{aastex6}
 
@@
 
-\usepackage{color,hyperref}
-\definecolor{linkcolor}{rgb}{0,0,0.5}
-\hypersetup{colorlinks=true,linkcolor=linkcolor,citecolor=linkcolor,
-            filecolor=linkcolor,urlcolor=linkcolor}
 \usepackage{url}
 \usepackage{amssymb,amsmath}
-\usepackage{subfigure}
-\usepackage{booktabs}
-
 \usepackage{natbib}
@@
 
+% omg AASTEX 6.0 -- modifications from HOGG
+\setlength{\voffset}{0in}
+\setlength{\hoffset}{0in}
+\setlength{\textwidth}{6.5in}
+\setlength{\textheight}{9in}
+\setlength{\headheight}{0ex}
+\setlength{\headsep}{\baselinestretch\baselineskip} % this is 2 lines in ``manuscript''
+\setlength{\topmargin}{-\headsep}
+
+\setlength{\skip\footins}{24pt}
+\linespread{0.54} % close to 10/13 spacing in ``manuscript''
+\setlength{\parindent}{0.54\baselineskip}
+\hypersetup{colorlinks = false}
+\makeatletter % you know you are living your life wrong when you need to do this
+\long\def\frontmatter@title@above{
+\vspace*{-\headsep}\vspace*{\headheight}
+\noindent\footnotesize
+{\noindent\footnotesize\textsc{\@journalinfo}}\par
+{\noindent\scriptsize Preprint typeset using \LaTeX\ style AASTeX6 with
+modifications by David W. Hogg and Daniel Foreman-Mackey.
+}\par\vspace*{-\baselineskip}\vspace*{0.625in}
+}%
+\makeatother
+
 \newcommand{\project}[1]{\textsl{#1}}
+
 \newcommand{\kepler}{\project{Kepler}}
@@
 \newcommand{\pdc}{\project{PDC}}
+\newcommand{\bls}{\project{BLS}}
+
 \newcommand{\license}{MIT License}
 
-\newcommand{\paper}{article}
+\newcommand{\paper}{paper}
 
@@
 
-\newcommand{\datareleaseurl}{{\url{http://bbq.dfm.io/ketu}}}
+\shorttitle{The population of long-period exoplanets}
+\shortauthors{Foreman-Mackey, Hogg, Morton, \etal}
+% \submitted{Submitted to \textit{The Astrophysical Journal}}
 
@@
 \clubpenalty500
-
-% \slugcomment{Not to appear in Nonlearned J., 45.}
 
@@
 long-period transiting exoplanet candidates in the \kepler\ archive
+\vspace{-3\baselineskip}  % OMG AASTEX6 IS SO BROKEN
 }
@@
 
-The transit method of exoplanet detection and characterization has been
-demonstrated as a powerful method for building systematic catalogs of
-exoplanets.
-Despite the great success of the \kepler\ Mission with thousands of planet
-discoveries \citep{Burke:2014, Rowe:2015}, current methods for exoplanet
-discoveries are currently limited in the range of orbital periods that can be
-studied.
-Specifically, the standard transit search procedures only discover signals
-with at least three observed transits \citep[for example][]{Petigura:2013,
-Burke:2014, Rowe:2015}.
+Data from the \kepler\ Mission has been used to discover thousands of
+transiting exoplanets.
+The systematic nature of these discoveries and careful quantification of
+survey selection effects, search completeness, and catalog reliability has
+enabled many diverse studies of the detailed frequency and distribution of
+exoplanets \citep[for example,][]{Howard:2012, Petigura:2013,
+Foreman-Mackey:2014, Dressing:2015, Burke:2015, Mulders:2015}.
+So far, these results have been limited to relatively short orbital periods
+because existing transit search methods require the observation of multiple
+transits within the baseline of the data.
 For \kepler, with a baseline of about four years, this sets an absolute upper
@@
 planetary dynamics and, since it would only exhibit at most one transit in the
-\kepler\ data, it would be missed by most existing transit search procedures.
+\kepler\ data, an exo-Jupiter would be missed by most existing transit search
+procedures.
 It is possible to discover long-period planets like this using targeted radial
-velocity (RV) surveys \citep[for example][]{Butler:2006, Knutson:2014}
-\dfmtodo{CITE Bryan \etal} but the cost of implementing a systematic RV search
-is substantially higher than searching the existing and forthcoming
-photometric data for single transits.
+velocity (RV) surveys \citep[for example][]{Butler:2006, Knutson:2014,
+Bryan:2016} but the cost of implementing a systematic RV search is
+substantially higher than searching the existing and forthcoming photometric
+data for single transits.
 
-There are two main technical barriers to a search for single transit events.
+There are two main technical barriers to a systematic search for single
+transit events.
 The first is that the transit probability for long-period planets is very low;
@@
 Therefore, even if long-period planets are intrinsically common, they will
-still be underrepresented in a transiting sample.
-The second challenge is that there are many signals in the observed
-light curves caused by stochastic processes~--~both instrumental
-(pointing jitter, temperature variations, \etc) and astrophysical (stellar
-variability, \etc)~--~that can masquerade as transits.
-Even using the most sophisticated methods for removing this variability, false
-signal far outnumber the true single transits.
+be underrepresented in a transiting sample.
+The second challenge is that there are many signals in the observed light
+curves caused by stochastic processes~--~both instrumental and
+astrophysical~--~that can masquerade as transits.
+Even when the most sophisticated methods for removing this variability are
+used, false signals far outnumber the true single transits in any traditional
+search.
 
-Nearly every transit search algorithm is built on the same principles and many
-of the same decisions are made.
-In particular, at the heart of most methods is a matched filtering step where
-the likelihood of an approximate transit model is computed on a grid in the
-physical parameters \citep[\kepler\ Data Processing
-Handbook\footnote{\url{https://archive.stsci.edu/kepler/manuals/KSCI-19081-001_Data_Processing_Handbook.pdf}};][]{%
-Petigura:2013, Huang:2013, Dressing:2015, Foreman-Mackey:2015}.
-Using these methods, and substantial hand-curation, some long-period
-transiting candidates have been published \citep[for example][]{Batalha:2013,
-Huang:2013, Kipping:2014a}.
-For more recent data releases, the community has settled on more conservative
-selection criteria where candidates are required to have multiple transits
-\citep[for example][]{Petigura:2013, Burke:2014, Rowe:2015}.
-Even the \project{QATS} algorithm \citep{Carter:2013} for finding
-quasiperiodic transits builds on much the same infrastructure.
-This means that there has never been a systematic search for single transits
-in the full \kepler\ dataset.
+At the heart of all periodic transit search procedures is a filtering step
+based on ``box least squares'' \citep[\bls;][]{Kovacs:2002}.
+This step produces a list of candidate transit times that is then vetted to
+remove the substantial fraction of false signals using some combination of
+automated heuristics and expert curation.
+In practice, the fraction of false signals can be substantially reduced by
+requiring that at least three self-consistent transits be observed \citep[The
+\kepler\ Data Processing Handbook%
+\footnote{\url{https://archive.stsci.edu/kepler/manuals/KSCI-19081-001_Data_Processing_Handbook.pdf}};][]{Petigura:2013,
+Burke:2014, Rowe:2015, Coughlin:2015}.
 
-A qualitatively different approach to planet search is employed by the
-\project{Planet Hunters} (PH)
-project\footnote{\url{http://www.planethunters.org/}} \citep{Fischer:2012}.
-PH is a ``citizen science'' project where visitors to the website look at
-sections of light curve and mark the locations of transits that can be
-identified visually.
-Visual inspection can be a useful search technique for large single transits
-because humans are able to robustly distinguish transit signals from the noise
-and this project has yielded some promising long-period candidates and
-confirmed planets \citep[for example][]{Wang:2013} \dfmtodo{CITE Wang 2015}.
-One shortcoming of the PH method is that it can be difficult to fully quantify
-the performance (completeness and reliability) of the search results.
-% and PH does not
-% evaluate their users using synthetic transit signals as is now common practice
-% in the transit search literature \dfmtodo{is this still true?}.
-This means that the PH sample of candidates cannot be reliably used for robust
-population inference.
+Recent work has yielded discoveries of long-period transiting planets with
+only one or two transits identified in archival \kepler\ and \KT\ light curves
+by visual inspection \citep{Wang:2013, Kipping:2014a, Osborn:2016,
+Kipping:2016, Uehara:2016, Wang:2015}.
+Since all of these discoveries rely on human interaction, it is intractable to
+reliably constrain the completeness of these catalogs and they cannot be used
+to measure the occurrence rate of long-period planets.
 
-Visual inspection and hand-curation by experts has also been used to find the
-transits of long-period planets in previously known planetary systems
-(\dfmtodo{CITE single transit KOIs}).
-All light curves in the \kepler\ archive with \kepler\ Objects of Interest
-(KOIs) were visually inspected to find candidate single transits.
-This is a reasonable idea because long-period planets with transiting inner
-planets are expected to have a higher geometric transit probability.
-The selection effects introduced by restricting the target sample like this
-are difficult to take into account when making inferences about the population
-of long-period planets.
-
-To study the occurrence rate of long-period exoplanets, we have developed a
-fully-automated method to search the archival \kepler\ light curves and
-reliably discover long-period planets with only one or two transits.
-Using this method, we search the 40,000 brightest Sun-like stars and detect
-XXX long-period astrophysical transit candidates.
-Of these, YYY are likely to be exoplanets with radii equal to or smaller than
-Jupiter's radius.
-Using transit injection and recovery, we measure the completeness of our
-search procedure.
-We estimate that the population level astrophysical false positive rate in
-this candidate sample is about ZZZ\%.
-By injecting synthetic transit signals into the \kepler\ light curves, we
-measure the completeness of our search method.
-Based on this catalog of exoplanet candidates and the search completeness, we
-constrain the occurrence rate of long-period exoplanets.
-For large planets, these results are consistent with previous measurements of
-long-period, giant planet occurrence rates based on radial velocity surveys
-and we demonstrate that small~--~and possibly rocky~--~planets are more common
-than their larger counterparts even at long orbital periods.
+In this \paper, we develop a systematic method of reliably discovering the
+transits of large long-period companions in photometric time series
+\emph{without human intervention}.
+Since the search methodology is fully-automated, we can robustly measure the
+search completeness~--~using injection and recovery tests~--~and use these
+products to place probabilistic constraints on the occurrence rate of
+long-period planets.
+We apply this method to a subset of the archival data from the \kepler\
+Mission and produce a catalog of discoveries.
 
@@
 \begin{figure*}
+\vspace{\baselineskip}
 \begin{center}
@@
 
-\begin{figure*}
+\begin{figure}
+\vspace{\baselineskip}
 \begin{center}
@@
 \figlabel{targets}}
-\end{figure*}
+\end{figure}
 
@@
 \figlabel{full-sample}}
-\end{figure*}
+\end{figure}
 
@@
 \figlabel{completeness}}
-\end{figure*}
+\end{figure}
 
@@
 
-\acknowledgments
+% \acknowledgments
 It is a pleasure to thank
@@
 for helpful contributions to the ideas and code presented here.
-DFM and DWH were partially supported by the National Science Foundation
-(grant IIS-1124794),
-the National Aeronautics and Space Administration
-(grant NNX12AI50G), and the Moore--Sloan Data Science Environment at NYU.
+
+DWH was partially supported by the National Science Foundation (grant
+IIS-1124794), the National Aeronautics and Space Administration (grant
+NNX12AI50G), and the Moore--Sloan Data Science Environment at NYU.
 
@@
 NASA Exoplanet Archive.
-The Archive is operated by the California Institute of Technology, under
-contract with NASA under the Exoplanet Exploration Program.
+The Exoplanet Archive is operated by the California Institute of Technology,
+under contract with NASA under the Exoplanet Exploration Program.
 This \paper\ includes data collected by the \kepler\ mission. Funding for the
@@
 We are grateful to the entire \kepler\ team, past and present.
-Their tireless efforts were all essential to the tremendous success of the mission
-and the successes of \KT, present and future.
+Their tireless efforts were all essential to the tremendous success of the
+mission and the successes of \KT, present and future.
+
 These data were obtained from the Mikulski Archive for Space Telescopes
@@
 NNX13AC07G and by other grants and contracts.
-Computing resources were provided by High Performance Computing (HPC) at New
-York University (NYU).
+
+Computing resources were provided by High Performance Computing at New York
+University.
 
 \facility{Kepler}
+\software{%
+    \project{ceres} \citep{Agarwal:2016},
+    \project{corner.py} \citep{Foreman-Mackey:2016},
+    \project{emcee} \citep{Foreman-Mackey:2013},
+    \project{george} \citep{Ambikasaran:2016},
+	\project{matplotlib} \citep{Hunter:2007},
+	\project{numpy} \citep{Van-Der-Walt:2011},
+	\project{scipy} \citep{Jones:2001}}.
 
+\newpage
 \appendix
@@
 \bibliography{peerless}
-\clearpage
-
-% \begin{figure}[p]
-% \begin{center}
-% \includegraphics{figures/pca.pdf}
-% \end{center}
-% \caption{%
-% The top 10 eigen light curves (ELCs) generated by running principal component
-% analysis on all the aperture photometry from Campaign~1.
-% \figlabel{pca}}
-% \end{figure}
 

### 2016-05-15 document/ms.tex
cleaning

@@
 
-\subsection{Discussion of some interesting systems}
-
 \section{Empirical search completeness}
@@
 
-The discovery and characterization of transiting planets based on a single
-transit event is crucial for the future of transiting exoplanet surveys.
-Many of the most dynamically influential planets~--~like Jupiter in our Solar
-system~--~exhibit only a single transit in the full observational baseline of
-the \kepler.
-This will become even more of a problem as upcoming surveys move to shorter
-contiguous observations.
-For example, the \tess\ Mission is planned to get full-sky coverage at
-half-hour cadence but most of the sky will only be targeted for a month.
-This means that even habitable zone planets orbiting cool stars will transit
-their host \emph{at most once in the entire lifetime of the Mission}!
-
-To date, no methods exist for systematically and robustly discovering single
-transit events based on large photometric surveys.
-In this \paper, we present a novel and conceptually unique solution to this
-problem drawing on machine learning methods for supervised classification.
-This method has immense potential because it can be designed to be very robust
-to false positives and it can exploit the detailed shape of physical transits.
-
-Despite the fact that single transits are unlikely even if these long-period
-planets are intrinsically common, we estimate that $\sim 60$ events should be
-detectable in the \kepler\ archival dataset by extrapolating recent models of
-planet occurrence rates and taking selection effects into account.
-When applied to 3500 light curves from the \kepler\ dataset, this method
-recovers one previously unknown single transit event at
-$830.8093\pm0.0002$~KBJD in the light curve of KIC 10602068.
-This rate is consistent with the predicted yield of 60 events in the full
-dataset of 190,000 light curves.
-
-Assuming a bound Keplerian orbit, we place constraints on the physical
-properties of this transit candidate KIC 10602068.01.
-Using photometrically derived stellar properties, we find that this candidate
-has a radius of $2.1 \pm 0.4\,R_\mathrm{J}$ placing it as a very large planet
-or brown dwarf or a small star.
-
-This method for transit search is built using supervised classification and
-its performance relies on several strong assumptions about the datasets and
-these assumptions are sometimes violated leading to some transit-like signals
-that appear to be caused by noise to be misclassified as transits.
-The most severe assumption is that the noise properties of the data are
-stationary.
-In other words, we assume that variability in one subset of a light curve is
-completely spanned by the variability in the other sections.
-This assumption is, in general, false because the stochastic processes that
-cause stellar variability are complicated and non-stationary and the detector
-is plagued by non-negligible catastrophic changes in sensitivity and response.
-We attempt to mitigate this problem by using light curves that have been
-preprocessed to remove most of the instrumental effects and carefully dividing
-the data into subsets but some false positives are still incorrectly
-identified as candidates.
-
-One possible method for reducing the false positive rate would be to augment
-the training dataset using heuristic simulations of common false positives or
-the light curves of ``similar'' stars.
-Another option is to recognize that this search drastically reduces the
-parameter space requiring evaluation and comparing the predictive power of
-a transit model to other heuristic models including stellar variability or
-instrumental effects.
-
 % \acknowledgments

### 2016-05-19 document/ms.tex
plot fonts

@@
 
-% omg AASTEX 6.0 -- modifications from HOGG
+% ----------------------------------- %
+% start of AASTeX mods by DWH and DFM %
+% ----------------------------------- %
+
 \setlength{\voffset}{0in}
@@
 
-\setlength{\skip\footins}{24pt}
 \linespread{0.54} % close to 10/13 spacing in ``manuscript''
@@
 
+% Section spacing:
+\makeatletter
+\let\origsection\section
+\renewcommand\section{\@ifstar{\starsection}{\nostarsection}}
+\newcommand\nostarsection[1]{\sectionprelude\origsection{#1}}
+\newcommand\starsection[1]{\sectionprelude\origsection*{#1}}
+\newcommand\sectionprelude{\vspace{1em}}
+\makeatother
+
+\sloppy\sloppypar
+
+% ------------------ %
+% end of AASTeX mods %
+% ------------------ %
+
+% Projects:
 \newcommand{\project}[1]{\textsl{#1}}
-
 \newcommand{\kepler}{\project{Kepler}}
@@
 \newcommand{\tess}{\project{TESS}}
-\newcommand{\plato}{\project{PLATO}}
-\newcommand{\jwst}{\project{JWST}}
-\newcommand{\terra}{\project{TERRA}}
 \newcommand{\pdc}{\project{PDC}}
 \newcommand{\bls}{\project{BLS}}
-
-\newcommand{\license}{MIT License}
-
-\newcommand{\paper}{paper}
 
@@
 
-% \newcommand{\figref}[1]{\ref{fig:#1}}
-% \newcommand{\Fig}[1]{\figurename~\figref{#1}}
-% \newcommand{\fig}[1]{\Fig{#1}}
-\newcommand{\figlabel}[1]{\label{fig:#1}}
+\newcommand{\dfmfigref}[1]{\ref{fig:#1}}
+\newcommand{\dfmFig}[1]{Figure~\dfmfigref{#1}}
+\newcommand{\dfmfig}[1]{\dfmFig{#1}}
+\newcommand{\dfmfiglabel}[1]{\label{fig:#1}}
 
@@
 
-% Notation for this paper.
+% Helpers for this paper:
+\newcommand{\license}{MIT License}
+\newcommand{\paper}{paper}
+
+% Notation for this paper:
 \newcommand{\meanpars}{{\ensuremath{\bvec{\theta}}}}
 \newcommand{\kernpars}{{\ensuremath{\bvec{\alpha}}}}
-
 \newcommand{\params}{{\ensuremath{\bvec{w}}}}
 \newcommand{\poppars}{{\ensuremath{\bvec{\beta}}}}
-
 \newcommand{\rate}{{\ensuremath{\Gamma}}}
@@
 % \submitted{Submitted to \textit{The Astrophysical Journal}}
-
-% no more bad lines!
-\sloppy\sloppypar
-\widowpenalty10000
-\clubpenalty500
 
@@
 In practice, the fraction of false signals can be substantially reduced by
-requiring that at least three self-consistent transits be observed \citep[The
-\kepler\ Data Processing Handbook%
-\footnote{\url{https://archive.stsci.edu/kepler/manuals/KSCI-19081-001_Data_Processing_Handbook.pdf}};][]{Petigura:2013,
-Burke:2014, Rowe:2015, Coughlin:2015}.
+requiring that at least three self-consistent transits be observed
+\citep{Petigura:2013, Burke:2014, Rowe:2015, Coughlin:2015}.
 
@@
 
-\begin{figure*}
-\vspace{\baselineskip}
+\begin{figure*}[p]~\\
 \begin{center}
@@
 transit.
-\figlabel{model-comp}}
+\dfmfiglabel{model-comp}}
 \end{figure*}
+
+\dfmfig{model-comp}
 
@@
 
-\begin{figure}
-\vspace{\baselineskip}
+\begin{figure}~\\
 \begin{center}
@@
 Blah.
-\figlabel{targets}}
+\dfmfiglabel{targets}}~\\
 \end{figure}
@@
 
-\begin{figure}
-\vspace{\baselineskip}
+\begin{figure*}~\\
 \begin{center}
@@
 Blah.
-\figlabel{full-sample}}
-\end{figure}
+\dfmfiglabel{full-sample}}~\\
+\end{figure*}
 
@@
 
-\begin{figure}
-\vspace{\baselineskip}
+\begin{figure*}[p]~\\
 \begin{center}
@@
 \caption{%
-\figlabel{completeness}}
-\end{figure}
+\dfmfiglabel{completeness}}
+\end{figure*}
 
@@
 
-% \acknowledgments
+We have developed a fully-automated method to search for the transits and
+eclipses of long-period companions in photometric time series.
+Applying this method to a subset of the \kepler\ archival light curves, we
+discovered XX astrophysical transits.
+Of these discoveries, at least about YY are likely to be planetary in nature.
+Combining this catalog of discoveries with a measurement of the completeness
+of our search method, we place a constraint on the occurrence rate of
+long-period exoplanets.
+
+Our method for transit detection finds convincing transit-shaped signals does
+a model comparison between a physical transit model.
+
+\acknowledgments
 It is a pleasure to thank

### 2016-05-19 document/figures/plot_setup.py

@@ -2,15 +2,16 @@
 
 from __future__ import division, print_function
 
+from cycler import cycler
+from matplotlib import rcParams
+
 __all__ = ["COLORS"]
 
-from cycler import cycler
-
-from matplotlib import rcParams
-rcParams["font.size"] = 20
-rcParams["font.family"] = "serif"
-rcParams["font.serif"] = "Computer Sans"
+rcParams["font.size"] = 16
+rcParams["font.family"] = "sans-serif"
+rcParams["font.sans-serif"] = ["Computer Modern Sans"]
 rcParams["text.usetex"] = True
+rcParams["text.latex.preamble"] = r"\usepackage{cmbright}"
 rcParams["figure.autolayout"] = True
 rcParams["axes.prop_cycle"] = cycler("color", (
     "#1f77b4", "#ff7f0e", "#2ca02c", "#d62728", "#9467bd", "#8c564b",

### 2016-06-02 peerless/fit.py
harder period prior

@@ -150,6 +150,10 @@ class TransitModel(object):
         if not np.isfinite(ll):
             return -np.inf, blob
 
+        # reject samples with other transits.
+        if blob[1] > 0:
+            return -np.inf, blob
+
         return lp + ll, blob
 
     def __call__(self, theta):

### 2016-06-06 document/figures/full_sample.py
fits collection

@@ -21,7 +21,7 @@ for f in np.exp(np.linspace(np.log(0.001), np.log(100), 8)):
     ax.plot(x0, y0, "k", lw=0.5, alpha=0.5)
 
 ax.loglog(x, y, ".", color=COLORS["DATA"], ms=4)
-ax.set_xlim(1.1, 450.)
+ax.set_xlim(0.5, 450.)
 ax.set_ylim(0.3, 30)
 ax.set_xlabel("orbital period [days]")
 ax.set_ylabel("planet radius [$R_\oplus$]")
@@ -43,17 +43,23 @@ period = np.array("0.2408467 0.61519726 1.0000174 1.8808476 11.862615 "
                   "29.447498 84.016846 164.79132".split(), dtype=float)
 ax.plot(period * 365, rad / rad[2], "o",  # color=COLORS["MODEL_2"],
         ms=4, mec="none")
-ax.set_xlim(0.5, max(x0))
 ax.axvline(4.2*365 / 2., color="k", alpha=0.6)
 ax.axvline(4.2*365, color="k", ls="dashed", alpha=0.6)
 
-fits = pd.read_csv("fits.csv")
+fig.set_tight_layout(True)
+fig.savefig("full_sample_zoom.pdf", bbox_inches="tight")
 
-xerr = np.array(fits[["period_err_1", "period_err_2"]]).T
-yerr = np.array(fits[["radius_err_1", "radius_err_2"]]).T / 0.01
-x = np.array(fits.period)
-y = np.array(fits.radius) / 0.01
+ax.set_xlim(0.5, max(x0))
+fig.savefig("full_sample.pdf", bbox_inches="tight")
+
+fits = pd.read_csv("../../results/fits.csv")
+
+pf = 365.25
+rf = 0.0995 / 0.00915
+xerr = np.array(fits[["period_uncert_minus", "period_uncert_plus"]]).T * pf
+yerr = np.array(fits[["radius_uncert_minus", "radius_uncert_plus"]]).T * rf
+x = np.array(fits.period) * pf
+y = np.array(fits.radius) * rf
 ax.errorbar(x, y, xerr=xerr, yerr=yerr, fmt=".g", capsize=0)
 
-fig.set_tight_layout(True)
-fig.savefig("full_sample.pdf", bbox_inches="tight")
+fig.savefig("full_sample_plus_cands.pdf", bbox_inches="tight")

### 2016-06-06 document/figures/model_comp.py
back to correct model comparison plot

@@ -54,6 +54,4 @@ for a, ax, (disp, name, kicid, peak_id) in zip("abcd", axes.flatten(), models):
     ax.set_xlabel("hours since event")
     ax.set_title("KIC {0}".format(kicid, disp))
 
-    break
-
 fig.savefig("model_comp.pdf", bbox_inches="tight")

### 2016-06-06 document/figures/model_comp.py
gp pred in model comp figure

@@ -23,7 +23,7 @@ fig, axes = pl.subplots(2, 2, figsize=(8, 8))
 os.makedirs("cache", exist_ok=True)
 for a, ax, (disp, name, kicid, peak_id) in zip("abcd", axes.flatten(), models):
     fn = os.path.join("cache", "{0}.pkl".format(kicid))
-    if False and os.path.exists(fn):
+    if os.path.exists(fn):
         print("using cached file: {0}".format(fn))
         with open(fn, "rb") as f:
             results = pickle.load(f)
@@ -43,8 +43,8 @@ for a, ax, (disp, name, kicid, peak_id) in zip("abcd", axes.flatten(), models):
     x0 = np.linspace(rng[0], rng[1], 500)
     ax.plot(24*(x[m] - t0), y[m], ".", color=COLORS["DATA"])
 
-    # mu = gp.predict(y0, x0, return_cov=False)
-    mu = gp.mean.get_value(x0)
+    mu = gp.predict(y0, x0, return_cov=False)
+    # mu = gp.mean.get_value(x0)
     ax.plot(24*(x0 - t0), mu, color=COLORS["MODEL_2"], lw=2.5, alpha=0.8)
     ax.annotate("({0})".format(a), xy=(0, 0), xycoords="axes fraction",
                 xytext=(5, 12), textcoords="offset points")

### 2016-06-07 document/figures/full_sample.py
no solar system plot

@@ -1,6 +1,6 @@
 # -*- coding: utf-8 -*-
 
-from plot_setup import COLORS
+from peerless.plot_setup import COLORS
 
 import matplotlib
 import numpy as np
@@ -36,6 +36,9 @@ x, y = kois[m].koi_period, kois[m].koi_prad
 ax.plot(x, y, ".",  # color=COLORS["MODEL_1"],
         ms=3, alpha=0.3, zorder=-1)
 
+fig.set_tight_layout(True)
+fig.savefig("full_sample_no_ss_zoom.pdf", bbox_inches="tight")
+
 # Plot the solar system.
 rad = np.array("2439.7 6051.8 6371.00 3389.5 69911 58232 25362 24622"
                .split(), dtype=float)
@@ -46,7 +49,6 @@ ax.plot(period * 365, rad / rad[2], "o",  # color=COLORS["MODEL_2"],
 ax.axvline(4.2*365 / 2., color="k", alpha=0.6)
 ax.axvline(4.2*365, color="k", ls="dashed", alpha=0.6)
 
-fig.set_tight_layout(True)
 fig.savefig("full_sample_zoom.pdf", bbox_inches="tight")
 
 ax.set_xlim(0.5, max(x0))

### 2016-06-29 document/ms.tex
refs
some words about vetting and candidate selection

@@
 \pdfoutput=1
+
+\usepackage{microtype}
 
@@
 
+EB catalog: \citep{Kirk:2016}
+
+Microlensing OR: \citep{Shvartzvald:2016}
+
 Data from the \kepler\ Mission has been used to discover thousands of
@@
 
-\subsection{Initial candidate events}
+\subsection{Step 1 -- Initial candidate events}
 
@@
 
-To generate this list, we apply a standard ``box least squares'' (BLS;
-\dfmtodo{CITE}) method with a single (non-periodic) box.
+To generate this list, we use a method much like the standard ``box least
+squares'' (BLS; \dfmtodo{CITE}) procedure with a single (non-periodic) box.
 First, we filter the PDC (\dfmtodo{CITE}) light curves using a running
@@
 variability.
-We then compute the signal-to-noise of the depth of a 0.6~day long transit on
-a grid of times spanning the full \kepler\ baseline.
-We only need to use a single transit duration because the following steps in
-this procedure are only sensitive to transits with very high signal-to-noise
-so, in practice, the results of this step are insensitive to the specific
-choice of duration.
+We then compute the signal-to-noise of the depth of a 0.6~day long
+transit on a grid of times spanning the full baseline of observations.
 
-As previously mentioned, the following steps will only detect high
-signal-to-noise transits.
+In detail, at each proposal time $t_0$, we hypothesize a box-shaped transit
+with duration $\tau$
+\begin{eqnarray}
+m(t) &=& \left\{\begin{array}{ll}
+    \mu, & \mbox{\,if $|t - t_0| < \tau/2$} \\
+    \mu - \delta, & \mbox{\,otherwise}
+\end{array}\right. \quad.
+\end{eqnarray}
+Assuming that the uncertainties on the observed fluxes $f(t)$ are Gaussian
+with known variance ${\sigma_f}^2$, the likelihood function for the mean flux
+$\mu$ and transit depth $\delta$ can be analytically computed to be a
+two-dimensional Gaussian with mean and covariance given by linear
+least-squares.
+This likelihood function provides a natural scalar objective: the
+signal-to-noise of the measured depth $\delta / \sigma_\delta$ computed a
+function of time.
+In principle this scalar is also a function of duration but we only use a
+single transit duration because the following steps in this procedure are only
+sensitive to transits with very high signal-to-noise.
+In practice, the final results are insensitive to the specific choice of
+duration.
+
 To avoid edge effects, we apodize this detection scalar near any large gaps in
@@
 duration.
-Finally, we estimate the noise in the time series using a robust running
-windowed variance estimate of the detection scalar and accepting peaks more
-than 25-times this noise as candidates.
+Finally, we estimate the background noise level in the detection scalar time
+series using a robust running windowed variance estimate of the detection
+scalar and accepting peaks more than 25-times this noise as candidates.
 
-\subsection{Light curve-level vetting}
+For the \kepler\ light curves, this procedure yields at least one candidate
+event in about 10~percent of targets and the three highest signal-to-noise
+events are investigated in the following step.
+
+\subsection{Step 2 -- Light curve vetting}
 
@@
 of each model for this data set.
-We will define the BIC for a model $k$ in the set of $K$ models is given by
+The BIC for a model $k$ in the set of $K$ models is given by
 \begin{eqnarray}
@@
 
-The models are:
+We consider the following mean models and this list provides a qualitative
+justification for each model:
 \begin{itemize}
@@
 {\item a pure Gaussian Process model to capture stellar variability,}
-{\item a single outlier,}
-{\item an step function, and}
-{\item a box.}
+{\item a single outlier to account for a bad data point,}
+{\item a step function to describe sudden pixel sensitivity dropouts (SPSDs;
+\dfmtodo{CITE}), and}
+{\item a box to catch signals that are well fit by the search scalar but
+insufficiently transit-like to be convincing.}
 \end{itemize}
+The functional forms of these models are given in Appendix \dfmtodo{SOME APP}.
+
+This method of automated vetting is clearly limited by the specific models
+selected in this step.
+We find that these are sufficient for the targets discussed below but other
+target lists might require additional models to be included for robust
+selection.
 
@@
 
+\begin{figure*}[p]~\\
+\begin{center}
+\include{lcfig}
+\end{center}
+\caption{%
+\dfmfiglabel{lightcurves}}
+\end{figure*}
+
 \begin{figure*}~\\
 \begin{center}
-\includegraphics{figures/full_sample.pdf}
+\includegraphics{figures/full_sample_plus_cands.pdf}
 \end{center}
@@
 \end{figure*}
+
+\begin{deluxetable}{cccccl}
+\tabletypesize{\footnotesize}
+\tablecaption{caption\label{tab:table}}
+\include{paramtab}
+% \tablenotetext{a}{Adjusted for inflation}
+% \tablenotetext{b}{Accounts for the change from page charges to digital quanta in April, 2011}
+% \tablecomments{Note that {\tt \string \colnumbers} does not work with the
+% vertical line alignment token. If you want vertical lines in the headers you
+% can not use this command at this time.}
+\end{deluxetable}
 

### 2016-06-29 document/ms.tex
model comparison times

@@
 
-This method of automated vetting is clearly limited by the specific models
-selected in this step.
+\dfmfig{model-comp} shows representative events that fall into different
+classes and the corresponding maximum-likelihood model.
+
+The reliability of this method of automated vetting is limited by the specific
+models selected in this step.
 We find that these are sufficient for the targets discussed below but other
@@
 selection.
-
-\subsection{Pixel-level vetting}
 
@@
 
-\dfmfig{model-comp}
+\subsection{Pixel-level vetting}
 

### 2016-06-29 document/figures/model_comp.py

@@ -2,7 +2,7 @@
 
 from __future__ import division, print_function
 
-from plot_setup import COLORS
+from peerless.plot_setup import COLORS
 
 import os
 import pickle
@@ -35,8 +35,12 @@ for a, ax, (disp, name, kicid, peak_id) in zip("abcd", axes.flatten(), models):
 
     peak = results.peaks[peak_id]
     t0 = peak["transit_time"]
-    rng = t0 + np.array([-2, 2])
     gp, y0 = peak["gps"][name]
+    if disp == "step":
+        t0 = gp.mean["t0"]
+    elif disp == "box":
+        t0 = 0.5 * (gp.mean.mn + gp.mean.mx)
+    rng = t0 + np.array([-2, 2])
 
     x, y = peak["data"][:2]
     m = (rng[0] < x) & (x < rng[1])

### 2016-06-29 document/figures/model_comp.py
model comparison names

@@ -48,9 +48,9 @@ for a, ax, (disp, name, kicid, peak_id) in zip("abcd", axes.flatten(), models):
     ax.plot(24*(x[m] - t0), y[m], ".", color=COLORS["DATA"])
 
     mu = gp.predict(y0, x0, return_cov=False)
-    # mu = gp.mean.get_value(x0)
     ax.plot(24*(x0 - t0), mu, color=COLORS["MODEL_2"], lw=2.5, alpha=0.8)
-    ax.annotate("({0})".format(a), xy=(0, 0), xycoords="axes fraction",
+    ax.annotate("({0}) {1}".format(a, disp),
+                xy=(0, 0), xycoords="axes fraction",
                 xytext=(5, 12), textcoords="offset points")
 
     ax.set_xlim(24*(rng - t0))

### 2016-06-29 document/ms.tex
words about vetting models

@@
 \newcommand{\rate}{{\ensuremath{\Gamma}}}
+
+\newcommand{\modelname}[1]{{\textsf{#1}}}
 
@@
 For the \kepler\ light curves, this procedure yields at least one candidate
-event in about 10~percent of targets and the three highest signal-to-noise
+event in about 1~percent of targets and the three highest signal-to-noise
 events are investigated in the following step.
@@
 \begin{itemize}
-{\item a limb-darkened, exposure time integrated transit light curve,}
-{\item a pure Gaussian Process model to capture stellar variability,}
-{\item a single outlier to account for a bad data point,}
-{\item a step function to describe sudden pixel sensitivity dropouts (SPSDs;
-\dfmtodo{CITE}), and}
-{\item a box to catch signals that are well fit by the search scalar but
-insufficiently transit-like to be convincing.}
+{\item \modelname{transit} -- a limb-darkened, exposure time integrated
+transit light curve,}
+{\item \modelname{variability} -- a pure Gaussian Process model to capture
+stellar variability,}
+{\item \modelname{outlier} -- a single outlier to account for a bad data
+point,}
+{\item \modelname{step} -- a step function to describe sudden pixel
+sensitivity dropouts (SPSDs; \dfmtodo{CITE}), and}
+{\item \modelname{box} -- a box to catch signals that are well fit by the
+search scalar but insufficiently transit-like to be convincing.}
 \end{itemize}
@@
 classes and the corresponding maximum-likelihood model.
+For each candidate event, the BIC of each of these models is computed and the
+event is only passed as a candidate if the \modelname{transit} model is
+preferred to all the other models.
+The \modelname{box} model is the most restrictive comparison, vetoing about
+half of the candidate events in the \kepler\ light curves, followed by the
+\modelname{variability} model.
+To further restrict to non-grazing transits, we also reject events where the
+best fit impact parameter is less than $1 - R_\mathrm{P} / R_\star$.
 

### 2016-06-29 document/ms.tex
words about centroid offsets

@@
 
-\subsection{Pixel-level vetting}
+\subsection{Step 3 -- Pixel-level vetting}
 
-\section{A catalog of exoplanet \& binary candidates}
+To minimize contamination from background eclipsing binary systems, we require
+candidate events to pass a centroid shift test similar to the one used in the
+official \kepler\ transit search pipeline \citep{Bryson:2013}.
+To measure the centroid shift, we model the flux-weighted centroid traces
+independently in each coordinate as a multiple of the best-fit transit model
+and a GP noise model.
+By properly normalizing the transit model, we  measure the in-transit centroid
+shift $\Delta_\mathrm{centroid}$ in pixels.
+We reject any candidate event where the estimated transit location is more
+than half a pixel from the out-of-transit centroid
+\begin{eqnarray}
+\Delta_\mathrm{centroid}\,\left(\frac{1}{\delta} - 1\right) &>& 0.5
+\end{eqnarray}
+where $\delta$ is the observed transit depth \citep{Bryson:2013}.
+
+\section{Results: a catalog of long-period transiting exoplanet candidates}
 

### 2016-06-29 document/ms.tex
updating eb table; words about target selection

@@
 
-\subsection{Target selection}\sectlabel{data}
+To limit the scope of this paper while still demonstrating the applicability
+of our method, we search the \kepler\ archival light curves of the brightest
+and quietest Sun-like stars for long-period transiting exoplanets.
+In this section, we describe the target selection process, the parameter
+estimation procedure, and present the catalog of discoveries.
 
-For the purposes of this \paper, we select the $\sim40,000$ brightest and
-quietest G and K dwarfs from the \kepler\ catalog using the following
-parameters:
+\subsection{Target selection}\sectlabel{target-selection}
+
+We select the $\sim40,000$ brightest and quietest G and K dwarfs from the
+\kepler\ catalog using the most recent catalog of stellar parameters%
+\footnote{Parameters from the \textsf{q1\_q17\_dr24\_stellar} table from the
+NASA Exoplanet Archive \citep[][with updates]{Huber:2014}.} and the cuts used
+by \citet{Burke:2015}:
 \begin{itemize}
@@
 {\item $R_\star \le 1.15\,R_\odot$,}
+{\item $\mathrm{data\,span} \ge 2\,\mathrm{years}$,}
+{\item $\mathrm{duty\,cycle} \ge 0.6$,}
 {\item $K_p \le 15\unit{mag}$, and}
@@
 \end{itemize}
+We continue by excluding the light curves of known eclipsing
+binaries\footnote{\url{http://keplerebs.villanova.edu/}} \citep{Kirk:2016} and
+other known false positives \citep{Coughlin:2016}.
+The final catalog contains 39,518 targets and the parameter distribution is
+shown in \dfmfig{targets}.
+
 We also restrict the sample to only include targets with a data span of more

### 2016-06-29 document/ms.tex
updated EB table

@@
 We continue by excluding the light curves of known eclipsing
-binaries\footnote{\url{http://keplerebs.villanova.edu/}} \citep{Kirk:2016} and
-other known false positives \citep{Coughlin:2016}.
+binaries\footnote{\url{http://keplerebs.villanova.edu/}} \citep{Kirk:2016},
+other known false positives \citep{Coughlin:2016}, and seven extra blacklisted
+stars.
 The final catalog contains 39,518 targets and the parameter distribution is
@@
 within 2 transit durations of the known candidates.
+
+\begin{deluxetable}{cl}
+\tabletypesize{\footnotesize}
+\tablecaption{caption\label{tab:blacklist}}
+\tablehead{\colhead{kic id} & \colhead{comments}}
+\startdata
+3323887  & A known system with transit timing variations (Kepler-9) \\
+4482348	 & Crazy crosstalk outliers \\
+4450472	 & noise \\
+4586468	 & EB not in list \\
+5438845	 & noise \\
+8009496	 & ephemeris match \\
+10068041 & AMS \\
+\enddata
+\end{deluxetable}
 

### 2016-06-29 document/ms.tex
smaller blacklist

--- 2016-06-29 document/ms.tex
@@
 We continue by excluding the light curves of known eclipsing
-binaries\footnote{\url{http://keplerebs.villanova.edu/}} \citep{Kirk:2016} and
-other known false positives \citep{Coughlin:2016}.
-The final catalog contains 39,518 targets and the parameter distribution is
+binaries\footnote{\url{http://keplerebs.villanova.edu/}} \citep{Kirk:2016},
+other known false positives \citep{Coughlin:2016}, a planet with known transit
+timing variations (Kepler-9), and four especially noisy stars (KIC~4482348,
+KIC~4450472, KIC~5438845, and KIC~10068041).
+The final catalog contains 39,036 targets and the parameter distribution is
 shown in \dfmfig{targets}.

### 2016-06-29 document/ms.tex
masking transits

@@
 
-We also restrict the sample to only include targets with a data span of more
-than two years and a duty cycle of better than $0.6$.
-Since the \kepler\ data have been searched for shorter period planets
-\dfmtodo{CITE Coughlin} and eclipsing binaries \dfmtodo{CITE EB catalog} than
-targeted by this project, we censor these previously known targets.
-For the known EBs, we simply remove these targets from the candidate list.
-For the confirmed and candidate KOIs from \dfmtodo{Coughlin}, we remove data
-within 2 transit durations of the known candidates.
+Since these data have already been searched for short-period planets, we
+assume that all high signal-to-noise candidates with three or more transits
+have been previously found \citep{Coughlin:2016}.
+To remove these candidates from consideration, we mask the cadences within two
+transit durations of the time when a short-period planet candidate is known to
+transit.
 

### 2016-06-29 document/ms.tex
updating coughlin ref

@@
 requiring that at least three self-consistent transits be observed
-\citep{Petigura:2013, Burke:2014, Rowe:2015, Coughlin:2015}.
+\citep{Petigura:2013, Burke:2014, Rowe:2015, Coughlin:2016}.
 
@@
 transit durations of the time when a short-period planet candidate is known to
-transit.
+transit\footnote{We specifically use the \textsf{q1\_q17\_dr24\_koi} from the
+NASA Exoplanet Archive \url{http://exoplanetarchive.ipac.caltech.edu/}.}.
 
@@
 \end{figure}
-
-We start with the PDC-MAP light curves downloaded from
-MAST\footnote{\url{https://archive.stsci.edu/kepler/}}.
-
-The \kepler\ Mission measured photometric time series for about 190,000 stars
-at half-hour cadence for a baseline of over four years.
-We aim to search these light curves for single transits of long-period planets
-and single eclipses of binary stars.
-These data are made available on
-MAST\footnote{\url{https://archive.stsci.edu/kepler/}} and, for each target,
-we downloaded the full set of long cadence light curve files provided by Data
-Release 24 \citep{Thompson:2015}.
-From these files, we extracted the PDC time series and split them into
-``sections'' with no more than ten contiguous missing or flagged data points.
-The PDC light curves have been corrected for the instrumental effects caused
-by the spacecraft using a data-driven model of the focal plane
-\citep{Stumpe:2012, Smith:2012}.
-Crucially, an attempt is also made by the PDC procedure to remove sharp
-instrumental artifacts like ``sudden pixel sensitivity dropouts (SPSDs)''.
-The success rate of this correction procedure is much higher than in earlier
-data releases but, as discussed in \sect{demo}, there remain some cases that
-are not properly accounted for.
-
-The goal of this project is to discover the transits of long-period planets
-that have not yet been discovered.
-Therefore, when studying the light curve of an eclipsing binary star or a star
-with known transiting planet candidates~--~on shorter periods~--~we also remove
-all the in-transit data for the candidate using the parameters provided by the
-\project{NASA Exoplanet
-Archive}\footnote{\url{http://exoplanetarchive.ipac.caltech.edu/}; We
-downloaded the \texttt{cumulative} table of \kepler\ Objects of Interest on
-2015-03-25.}.
 

### 2016-06-29 document/ms.tex
updating corner ref

@@
 \pdfoutput=1
+
+\include{vc}
 
@@
 
+All of the code used in this project is available from
+\url{https://github.com/dfm/peerless} under the MIT open-source software
+license.
+This code (plus some dependencies) can be run to re-generate all of the
+figures and results in this \paper; this version of the paper was generated
+with git commit \texttt{\githash} (\gitdate).
+
 \acknowledgments

### 2016-06-29 document/ms.tex
listing the models

@@
 
-\subsection{Step 2 -- Light curve vetting}
+\subsection{Step 2 -- Light curve vetting}\sectlabel{light-curve-vetting}
 
@@
 \end{itemize}
-The functional forms of these models are given in Appendix \dfmtodo{SOME APP}.
+The functional forms of these models are given in \app{model-details}.
 
@@
 
-\section{Gaussian process regression}
+\section{Details of the light curve models}\sectlabel{model-details}
+
+In \sect{light-curve-vetting}, the five light curve models were listed.
+In this section, we give the mathematical details of each model and list the
+parameters that are fit.
+Each model~--~except the \modelname{transit} model~--~can be easily
+differentiated with respect to its parameters.
+As discussed in the following section, this feature is crucial for efficient
+and robust likelihood maximization.
+
+\begin{itemize}
+
+{\item
+The \modelname{box} model is given by
+\begin{eqnarray}
+m_\mathrm{box}(t) &=& \left\{\begin{array}{ll}
+a, & \mbox{if $t \le t_\mathrm{min}$} \\
+b, & \mbox{if $t_\mathrm{min} < t \le t_\mathrm{max}$} \\
+c, & \mbox{if $t_\mathrm{max} < t$}
+\end{array}\right.
+\end{eqnarray}
+where $a$, $b$, and $c$ are free parameters, and $t_\mathrm{min}$ and
+$t_\mathrm{max}$ are fixed.
+In practice, we include two different \modelname{box} models where
+$t_\mathrm{min}$ and $t_\mathrm{max}$ are set using different heuristics.
+The first \modelname{box} has the bounds set to match the ingress and
+egress of the best fit \modelname{transit}.
+The second \modelname{box} is chosen based on the largest change points in the
+light curve.
+}
+
+{\item
+The \modelname{step} model is given by
+\begin{eqnarray}
+m_\mathrm{step}(t) &=& \left\{\begin{array}{ll}
+m_1 + h_1\,\exp\left([t - t_0] / w_1\right), & \mbox{if $t < t_0$} \\
+m_2 + h_2\,\exp\left([t_0 - t] / w_2\right), & \mbox{if $t_0 \le t$}
+\end{array}\right.
+\end{eqnarray}
+where all of the parameters~--~including $t_0$~--~are included in the fit.
+To ensure that the widths $w_*$ remain positive, we fit for $\log w_*$.
+}
+
+{\item
+For the \modelname{outlier} model, we iterate through all cadences $t_n$
+within 0.3~days of the candidate transit time and evaluate the model as
+\begin{eqnarray}
+m_\mathrm{outlier}(t) &=& \left\{\begin{array}{ll}
+f(t_0), & \mbox{if $t = t_0$} \\
+\mathrm{median}[f(t \ne t_0)], & \mbox{if $t \ne t_0$}
+\end{array}\right.
+\end{eqnarray}
+where $f(t)$ is the observed time series.
+With this model, no non-linear optimization is required and the final value of
+$t_0$ is the one with the maximum likelihood in this grid search.
+}
+
+{\item
+The \modelname{variability} model only has one parameter, the flux $m_0$ and
+$m_\mathrm{variability}(t) = m_0$ at all times.
+The variability is captured by the Gaussian Process residual model.
+}
+
+{\item
+Finally, the \modelname{transit} model is an exposure time integrated,
+limb darkened light curve \citep{Mandel:2002, Kipping:2010} parameterized by
+the radius ratio between the planet and star, the transit duration, the
+transit time, the impact parameter, and two quadratic limb darkening
+coefficients \citep{Kipping:2013}.
+Analytically computing the gradient of a simple transit model is possible
+\citep{Pal:2008} but it becomes substantially more tedious as the model
+becomes more realistic.
+Therefore, we instead use a compile-time automatic differentiation
+library\footnote{More specifically, we use the \texttt{Jet} object from the
+BSD-licensed Ceres Solver \url{http://ceres-solver.org}} \citep{Agarwal:2016}
+to efficiently compute first derivatives of the full transit model with
+respect to the orbital and physical parameters to machine precision.
+}
+
+\end{itemize}
+
+\section{Gaussian process regression}\sectlabel{gp-regression}
 

### 2016-06-29 document/ms.tex
not much

@@
 model with respect to its parameters.
-For this \paper, the model $m(\bvec{t};\,\meanpars)$ will sometimes be the
-limb-darkened, exposure time-integrated transit of a planet on a Keplerian
-orbit and the parameters \meanpars\ are the physical and orbital parameters of
-the planet and star.
-Analytically computing the gradient of a simple transit model is possible
-\citep{Pal:2008} but it becomes substantially more tedious as the model
-becomes more realistic.
-Therefore, we use a compile-time automatic differentiation library\footnote{%
-More specifically, we use the \texttt{Jet} object from the BSD-licensed Ceres
-Solver \url{http://ceres-solver.org}} \citep{Agarwal:2016} to compute first
-derivatives of the full transit model to machine precision.
 

### 2016-06-29 peerless/catalogs.py
adding cumulative table

@@ -18,7 +18,8 @@ from .settings import PEERLESS_DATA_DIR
 
 __all__ = [
     "KOICatalog", "KICatalog", "EBCatalog", "BlacklistCatalog",
-    "TargetCatalog", "DatasetsCatalog",
+    "TargetCatalog", "DatasetsCatalog", "CumulativeCatalog", "UeharaCatalog",
+    "WangCatalog",
 ]
 
 
@@ -109,6 +110,10 @@ class KOICatalog(ExoplanetArchiveCatalog):
 
 class KICatalog(ExoplanetArchiveCatalog):
     name = "q1_q17_dr24_stellar"
+
+
+class CumulativeCatalog(ExoplanetArchiveCatalog):
+    name = "cumulative"
 
 
 class CatalogDownloadError(Exception):

### 2016-06-29 document/ms.tex
captions

@@
 \caption{%
-Blah.
+The distribution of stellar parameters for \kepler\ targets selected for this
+search (orange) compared to the distribution of the full \kepler\ target
+catalog (black).
 \dfmfiglabel{targets}}~\\
@@
 \subsection{Parameter estimation}
+
+\subsection{Catalog of candidates}
+
+\begin{deluxetable}{cccccl}
+\tabletypesize{\footnotesize}
+\tablecaption{The inferred parameters for the long-period transiting exoplanet
+candidates
+\label{tab:table}}
+\include{paramtab}
+\tablenotetext{\dagger}{Candidate has two observed transits.}
+\tablenotetext{a}{Included in the \citet{Wang:2015} catalog.}
+\tablenotetext{b}{Included in the \citet{Uehara:2016} catalog.}
+\end{deluxetable}
 
@@
 \caption{%
-\dfmfiglabel{lightcurves}}
+Sections of PDC light curve centered on each candidate (black) with the
+posterior-median transit model over-plotted (orange).
+Candidates with two transits are folded on the posterior-median period.
+\dfmfiglabel{light-curves}}
 \end{figure*}
@@
 \caption{%
-Blah.
+The catalog of long-period transiting exoplanet candidates (green) compared to
+the \kepler\ candidates (blue) and confirmed planets (black), and the Solar
+System (orange).
+The vertical dashed line indicates the full lifetime of the \kepler\ Mission;
+planets with orbital periods longer than this will show at most one transit.
+The vertical solid line shows the absolute maximum period accessible to
+transit searches that require at least three transits.
 \dfmfiglabel{full-sample}}~\\
 \end{figure*}
-
-\begin{deluxetable}{cccccl}
-\tabletypesize{\footnotesize}
-\tablecaption{caption\label{tab:table}}
-\include{paramtab}
-% \tablenotetext{a}{Adjusted for inflation}
-% \tablenotetext{b}{Accounts for the change from page charges to digital quanta in April, 2011}
-% \tablecomments{Note that {\tt \string \colnumbers} does not work with the
-% vertical line alignment token. If you want vertical lines in the headers you
-% can not use this command at this time.}
-\end{deluxetable}
 

### 2016-06-29 document/ms.tex
rotate table

@@
 To generate this list, we use a method much like the standard ``box least
-squares'' (BLS; \dfmtodo{CITE}) procedure with a single (non-periodic) box.
-First, we filter the PDC (\dfmtodo{CITE}) light curves using a running
-windowed median with a half-width of \dfmtodo{how many} to remove stellar
+squares'' \citep[\bls;][]{Kovacs:2002} procedure with a single (non-periodic)
+box.
+First, we filter the \pdc\ light curves \citep{Stumpe:2012, Smith:2012}
+using a running windowed median with a half-width of 2~days to remove stellar
 variability.
@@
 For up to three candidate transit times per light curve, we select a
-contiguous chunk of PDC light curve approximately centered on the proposed
-transit with no more than 500 cadences \dfmtodo{check me} and compute the BIC
-of each model for this data set.
+contiguous chunk of \pdc\ light curve approximately centered on the proposed
+transit with no more than 500 cadences and compute the BIC of each model for
+this data set.
 The BIC for a model $k$ in the set of $K$ models is given by
@@
 
-For each model, we describe the data using a Gaussian Process (GP;
-\dfmtodo{cite}) with a Mat\'ern-3/2 covariance and mean given by the chosen
-model $m_k(t;\,\meanpars)$ parameterized by the parameter vector \meanpars.
+For each model, we describe the data using a Gaussian Process
+\citep[GP;][]{Rasmussen:2006} with a Mat\'ern-3/2 covariance and mean given by
+the chosen model $m_k(t;\,\meanpars)$ parameterized by the parameter vector
+\meanpars.
 
@@
 
+\begin{floattable}
 \begin{deluxetable}{cccccl}
@@
 \tablenotetext{b}{Included in the \citet{Uehara:2016} catalog.}
+% \tablecomments{For the candidates with multiple transits, the
+% period uncertainty is given in concise notation to be more readable}
 \end{deluxetable}
+\end{floattable}
 
@@
 \caption{%
-Sections of PDC light curve centered on each candidate (black) with the
+Sections of \pdc\ light curve centered on each candidate (black) with the
 posterior-median transit model over-plotted (orange).
@@
 \begin{enumerate}
-{\item First, a star is randomly selected from the target list, and the PDC
+{\item First, a star is randomly selected from the target list, and the \pdc\
 light curve and stellar properties for that star are loaded.}
@@
 {\item The transit signal induced by this planet is computed and multiplied
-into the PDC light curve.}
+into the \pdc\ light curve.}
 {\item The transit search method described in section \dfmtodo{some section}
@@
 \caption{%
+The completeness of the search procedure described here as a function of
+period and radius.
+In each bin, the completeness (in percent) is given with the associated
+sampling uncertainty.
+The projected histograms show the integrated completeness as independent
+functions of period and radius.
 \dfmfiglabel{completeness}}

### 2016-06-30 document/ms.tex
table comment
albedo
parameters and priors

@@
 \usepackage{natbib}
+\usepackage{multirow}
 \bibliographystyle{aasjournal}
@@
 
+For each transit candidate, we constrain the physical parameters of the system
+by fitting the signal using a Keplerian orbit and a quadratic limb darkening
+law for the central body.
+
+\begin{floattable}
+\begin{deluxetable}{lccc}
+\tabletypesize{\footnotesize}
+\tablecaption{The inferred parameters and priors used in the inference
+\label{tab:parameters}}
+
+\tablehead{%
+    \colhead{name} & \colhead{symbol} & \colhead{units} &
+    \colhead{prior}
+}
+
+\startdata
+mean flux & $\log f_\star$ & \nodata &
+    $\log f_\star \sim \mathcal{U}(-1,\,1)$ \\
+stellar mass\tablenotemark{a} & $M_\star$ & $M_\odot$ &
+    $M_\star \sim \mathcal{N}(M_{\star,\mathrm{cat}},\,
+        \sigma_{M,\star,\mathrm{cat}})$ \\
+stellar radius\tablenotemark{a} & $R_\star$ & $R_\odot$ &
+    $R_\star \sim \mathcal{N}(R_{\star,\mathrm{cat}},\,
+        \sigma_{R,\star,\mathrm{cat}})$ \\
+\multirow{2}{*}{limb darkening} & $q_1$ & \nodata &
+    $q_1 \sim \mathcal{U}(0,\,1)$ \\
+ & $q_2$ & \nodata & $q_2 \sim \mathcal{U}(0,\,1)$ \\
+\hline
+planet radius & $\log R_\mathrm{P}$ & $R_\odot$ &
+    $\log R_\mathrm{P} \sim \mathcal{U}(-10,\,2)$ \\
+reference time & $t_0$ & days &
+    $t_0 \sim \mathcal{U}(t_\mathrm{cand}-0.5,\,t_\mathrm{cand}+0.5)$%
+    \tablenotemark{b} \\
+\multirow{2}{*}{\begin{minipage}{1in}semi-major axis \ \& inclination\end{minipage}}
+    & $\sqrt{a}\sin i$ & ${R_\odot}^{1/2}$ &
+    $\sqrt{a}\sin i \sim \mathcal{U}(-10^3,\,10^3) / \sqrt{a}$ \\
+    & $\sqrt{a}\cos i$ & ${R_\odot}^{1/2}$ &
+    $\sqrt{a}\cos i \sim \mathcal{U}(0,\,10^3) / \sqrt{a}$ \\
+\multirow{2}{*}{eccentricity}
+    & $\sqrt{e}\sin \omega$ & \nodata & $e \sim \beta(1.12,\,3.09)$%
+    \tablenotemark{c} \\
+    & $\sqrt{e}\cos \omega$ & \nodata & $\omega \sim \mathcal{U}(-\pi,\,\pi)$\\
+\enddata
+
+\tablenotetext{a}{Stellar parameters and uncertainties taken from the \kepler\
+catalog \citep{Huber:2014}}
+\tablenotetext{b}{The reference time is constrained to be within half a day of
+the candidate transit time}
+\tablenotetext{c}{\citet{Kipping:2013a}}
+\tablecomments{There is one further constraint that complicates these priors:
+the period of the orbit must be longer than some minimum period
+$P_\mathrm{min}$ set by the transit time and the full baseline of \kepler\
+observations.}
+\end{deluxetable}
+\end{floattable}
+
 \subsection{Catalog of candidates}
@@
 \include{paramtab}
+\tablenotetext{*}{The equilibrium temperature is computed assuming zero
+albedo.}
 \tablenotetext{\dagger}{Candidate has two observed transits.}
@@
 \tablenotetext{b}{Included in the \citet{Uehara:2016} catalog.}
-% \tablecomments{For the candidates with multiple transits, the
-% period uncertainty is given in concise notation to be more readable}
+\tablecomments{The values and uncertainties indicate the 16-th, 50-th, and
+84-th percentiles of the posterior samples for each parameter.}
 \end{deluxetable}

### 2016-06-30 document/ms.tex
stupid formatting
words about parameter estimation

@@
 \setlength{\headsep}{\baselinestretch\baselineskip} % this is 2 lines in ``manuscript''
+\setlength{\footnotesep}{0in}
 \setlength{\topmargin}{-\headsep}
@@
 \newcommand\sectionprelude{\vspace{1em}}
+\let\origsubsection\subsection
+\renewcommand\subsection{\@ifstar{\starsubsection}{\nostarsubsection}}
+\newcommand\nostarsubsection[1]{\subsectionprelude\origsubsection{#1}}
+\newcommand\starsubsection[1]{\subsectionprelude\origsubsection*{#1}}
+\newcommand\subsectionprelude{\vspace{1em}}
 \makeatother
+
+\widowpenalty=1000
+\clubpenalty=1000
 
@@
 \newcounter{affilcounter}
+\altaffiltext{1}{\textsf{danfm@uw.edu}; Sagan Fellow}
+
 \setcounter{affilcounter}{2}
-\altaffiltext{1}{\url{danfm@uw.edu}; Sagan Fellow}
-
 \edef \uw {\arabic{affilcounter}}\stepcounter{affilcounter}
@@
 For each transit candidate, we constrain the physical parameters of the system
-by fitting the signal using a Keplerian orbit and a quadratic limb darkening
-law for the central body.
+by fitting a section of light curve around each transit using an exposure time
+integrated  Keplerian orbit with a quadratic limb darkening law for the
+central body\footnote{Implemented at \url{https://github.com/dfm/transit};
+this \paper\ uses git commit \textsf{482d99b} of that repository.}.
+It has previously been established that the orbital period of a transiting
+planet with only one transit can still be constrained given a measurement of
+the stellar density and an assumption about the orbital eccentricity \cite[for
+example][]{Wang:2015, Osborn:2016}.
+Qualitatively this works because the transit of a bound body cannot have an
+arbitrary period for a given duration.
+This is the same argument used to justify the ``photoeccentric effect''
+\citep{Dawson:2012} and the method of ``asterodensity profiling''
+\citep{Kipping:2014b}.
+In particular, this suggests that the periods of single transits in systems
+with multiple inner planets will be especially well constrained
+\citep{Kipping:2012}.
+In this \paper, we do not take advantage of the extra constraints provided by
+the inner planets, instead treating each long-period transiting system in
+isolation, but this would be a good follow-up project.
 

### 2016-06-30 document/ms.tex
words about likelihood function

@@
 \newcommand{\bls}{\project{BLS}}
+\newcommand{\emcee}{\project{emcee}}
 
@@
 {\item \modelname{step} -- a step function to describe sudden pixel
-sensitivity dropouts (SPSDs; \dfmtodo{CITE}), and}
+sensitivity dropouts \citep[SPSDs; for example][]{Christiansen:2013}, and}
 {\item \modelname{box} -- a box to catch signals that are well fit by the
@@
 isolation, but this would be a good follow-up project.
+
+In the following paragraphs, we describe the components of the probabilistic
+model.
+To perform parameter estimation under this model, we use the Markov Chain
+Monte Carlo (MCMC) package \emcee\footnote{\url{http://dfm.io/emcee}}
+\citep{Foreman-Mackey:2013} with an ensemble of 40 walkers.
+We run each chain until the.
+
+\paragraph{Priors}
+
+For each candidate in our sample, we take the constraints on the stellar
+parameters from the \kepler\ stellar properties catalog\footnote{The
+\textsf{q1\_q17\_dr24\_stellar} table from the NASA Exoplanet Archive
+\citep{Huber:2014}} and assume an empirical beta function prior on the
+eccentricities based on the observed eccentricity distribution of long-period
+planets discovered using radial velocities \citep{Kipping:2013}.
+Table~\ref{tab:parameters} lists all the fit parameters and their prior
+distributions.
+Besides these listed priors, we add the extra constraint that no other
+transits can occur in the baseline of the \kepler\ observations.
+This constraint is overly conservative because there is some probability that
+a second transit could occur in a data gap but we find that, in practice, most
+of the posterior mass is at longer periods and the period inferences are not
+significantly affected.
+
+\paragraph{Likelihood function}
+
+As above, we model the light curve as GP with a physical transit model as the
+mean and a covariance matrix described by a Mat\'ern-3/2 kernel function.
+The full likelihood function and some details of GP regression are given in
+\app{gp-regression}.
+For computational efficiency, we first perform a joint optimization of the
+orbital parameters and GP hyperparameters to find the maximum \foreign{a
+posteriori} model then keep these.
 

### 2016-06-30 document/ms.tex

--- 2016-06-30 document/ms.tex
@@
 isolation, but this would be a good follow-up project.
+
+\paragraph{Priors}
+
+For each candidate in our sample, we take the constraints on the stellar
+parameters from the \kepler\ stellar properties catalog\footnote{The
+\textsf{q1\_q17\_dr24\_stellar} table from the NASA Exoplanet Archive
+\citep{Huber:2014}} and assume an empirical beta function prior on the
+eccentricities based on the observed eccentricity distribution of long-period
+planets discovered using radial velocities \citep{Kipping:2013}.
+Table~\ref{tab:parameters} lists all the fit parameters and their prior
+distributions.
+Besides these listed priors, we add the extra constraint that no other
+transits can occur in the baseline of the \kepler\ observations.
+This constraint is overly conservative because there is some probability that
+a second transit could occur in a data gap but we find that, in practice, most
+of the posterior mass is at longer periods and the period inferences are not
+significantly affected.
+
+\paragraph{Likelihood function}
 

### 2016-06-30 document/ms.tex
footnote about autocorraltion times
words about results

--- 2016-06-30 document/ms.tex
@@
 
-\section{A fully-automated search method}
+\section{A fully-automated search method}\sectlabel{search}
 
@@
 \citep{Foreman-Mackey:2013} with an ensemble of 40 walkers.
-We run each chain until the.
+We run each chain until at least 750 independent samples~--~in most cases, we
+actually produce thousands of independent samples~--~are obtained\footnote{The
+integrated autocorrelation time is estimated using a robust iterative method
+as suggested by Alan Sokal:
+\url{http://www.stat.unc.edu/faculty/cji/Sokal.pdf}.} and discard the first
+third of the chain as burn-in.
 
@@
 For computational efficiency, we first perform a joint optimization of the
-orbital parameters and GP hyperparameters to find the maximum \foreign{a
-posteriori} model then keep these.
+physical parameters and GP hyperparameters to find the maximum \foreign{a
+posteriori} model then keep the hyperparameters fixed and run MCMC sampling
+for the 11 physical parameters alone.
 
@@
 
-\subsection{Catalog of candidates}
+\subsection{Catalog of transit candidates}
+
+Applying the search procedure described in \sect{search} to the \kepler\ light
+curves of the targets selected in \sect{target-selection}, we find 16
+convincing transit candidates.
+Visual inspection of each candidate confirms the reliability of the
+classification and no candidates are manually removed from the catalog.
+Of these, three candidates have two transits in the \kepler\ baseline and the
+remainder have only one observable transit.
+The candidates and their inferred physical parameters are listed in
+Table~\ref{tab:catalog} and the light curves are plotted in
+\fig{light-curves}.
 
@@
 candidates
-\label{tab:table}}
+\label{tab:catalog}}
 \include{paramtab}
@@
 Candidates with two transits are folded on the posterior-median period.
+The plots are ordered by increasing planetary radius from the top-left to the
+bottom-right.
 \dfmfiglabel{light-curves}}

### 2016-06-30 document/ms.tex
table refs

@@
 \tabletypesize{\footnotesize}
-\tablecaption{The inferred parameters and priors used in the inference
+\caption{The inferred parameters and priors used in the inference
 \label{tab:parameters}}
@@
 Table~\ref{tab:catalog} and the light curves are plotted in
-\fig{light-curves}.
+\dfmfig{light-curves}.
 
@@
 \tabletypesize{\footnotesize}
-\tablecaption{The inferred parameters for the long-period transiting exoplanet
-candidates
-\label{tab:catalog}}
+\caption{The inferred parameters for the long-period transiting exoplanet
+candidates \label{tab:catalog}}
 \include{paramtab}

### 2016-07-02 document/ms.tex
words about the catalog of candidates

@@
 Applying the search procedure described in \sect{search} to the \kepler\ light
-curves of the targets selected in \sect{target-selection}, we find 16
+curves of the 39,036 targets selected in \sect{target-selection}, we find 16
 convincing transit candidates.
@@
 \dfmfig{light-curves}.
+
+Two of the shortest period candidates~--~both with two observed
+transits~--~have previously been studied in detail \citep[KIC~8800954 and
+KIC~3239945;][]{Kipping:2014a, Kipping:2016}.
+Table~\ref{tab:catalog} indicates the candidates that were also discovered by
+earlier searches for long-period transiting systems using visual inspection
+\citep{Wang:2015, Uehara:2016}.
+The consistency between our results and the earlier catalogs is reassuring.
+Our automated search did not find any more candidates than visual inspection
+of the light curves of known KOIs \citep{Uehara:2016} and one candidate
+(KIC~3230491) reported by the human analysis was discarded as grazing by our
+search.
+The PH citizen science project reported five long-period candidates with one
+or two observed transits in our target list \citep{Wang:2015}.
+Of these, we also find two (KIC~8410697 and KIC~10842718) although we find a
+second transit in the KIC~8410697 system that was not previously reported.
+The three other candidates reported by \citet{Wang:2015} that we miss
+(KIC~5536555, KIC~9662267, and KIC~12454613) are have low signal-to-noise
+transits that do not pass our initial signal-to-noise threshold.
+Six of the candidates in Table~\ref{tab:catalog} have not been previously
+published.
+
+The candidate in the light curve of KIC~4754460 as an individual transit
+candidate but another deeper eclipse can be found at a KBJD of 1587.13; right
+at the beginning of Quarter 17.
+This eclipse was missed by the automated search because only the second half
+of the eclipse is observed.
+The most likely explanation of this system is that the listed candidate is the
+secondary eclipse of a binary system but we will keep the candidate is the
+list and treat this effect statistically in \sect{false-positives}.
 
@@
 
-\section{Astrophysical false positives}
+\section{Astrophysical false positives}\sectlabel{false-positives}
 

### 2016-07-02 document/ms.tex
words about injections

@@
 \dfmfig{light-curves}.
+The inferred radius and orbital periods of the candidates are compared to the
+short-period \kepler\ sample and the Solar System in \dfmfig{full-sample}.
 
@@
 
-To measure the completeness of our long-period transit search method, we
+To measure the completeness of search procedure described in \sect{search}, we
 exploit the fact that transit signals are sparse and rare.
@@
 This procedure is standard practice in the transit literature and it has been
-used to determine the completeness of the KOI catalog (\dfmtodo{cite}) and
-other independent transit searches (\dfmtodo{cite}).
+used to determine the completeness of the KOI catalog
+\citep{Christiansen:2013, Christiansen:2015} and other independent transit
+searches \citep{Petigura:2013, Dressing:2015, Foreman-Mackey:2015}.
 
@@
 {\item Planetary properties are sampled from the distributions listed in
-\dfmtodo{some table} with phase uniformly distributed across the baseline of
-observations. These properties are resampled until the transit is visible in
-at least one non-flagged cadence.}
+Table~\ref{tab:simulations} with phase uniformly distributed across the
+baseline of observations. These properties are re-sampled until the transit is
+visible in at least one non-flagged cadence.}
 {\item The transit signal induced by this planet is computed and multiplied
 into the \pdc\ light curve.}
-{\item The transit search method described in section \dfmtodo{some section}
-(including de-trending and all automated vetting) is applied to this light
+{\item The transit search method described in \sect{search}~--~including
+de-trending and all automated vetting~--~is applied to this light
 curve with the injected transit signal.}
-{\item This candidate is flagged as recovered if at least one transit (within
-\dfmtodo{some tolerance}) passes all the cuts imposed by the automated
-vetting.}
+{\item This candidate is flagged as recovered if at least one transit within
+one transit duration passes all the cuts imposed by the automated vetting.}
 \end{enumerate}
@@
 \dfmtodo{Analytic fit?}
+
+\begin{floattable}
+\begin{deluxetable}{lc}
+\tabletypesize{\footnotesize}
+\caption{Distributions of physical parameters for transit simulations
+\label{tab:simulations}}
+
+\tablehead{%
+    \colhead{name} & \colhead{distribution}
+}
+\startdata
+period & $\log P \sim \mathcal{U}(\log 2\unit{yr},\,\log 25\unit{yr})$ \\
+radius ratio & $\log R_\mathrm{P}/R_\star \sim
+    \mathcal{U}(\log 0.02,\,\log 0.2)$ \\
+impact parameter & $b \sim \mathcal{U}(0,\,1+R_\mathrm{P}/R_\star)$ \\
+\multirow{2}{*}{eccentricity} & $e \sim \beta(1.12,\,3.09)$\tablenotemark{a} \\
+    & $\omega \sim \mathcal{U}(-\pi,\,\pi)$\\
+\multirow{2}{*}{limb darkening} & $q_1 \sim \mathcal{U}(0,\,1)$ \\
+                                & $q_2 \sim \mathcal{U}(0,\,1)$ \\
+\enddata
+
+\tablenotetext{a}{\citet{Kipping:2013a}}
+\end{deluxetable}
+\end{floattable}
 

### 2016-07-02 document/ms.tex
words about completeness

@@
 \include{vc}
+\include{numbers}
 
@@
 
-\subsection{Step 1 -- Initial candidate events}
+\subsection{Step 1 -- Initial candidate events}\sectlabel{stepone}
 
@@
 KIC~4450472, KIC~5438845, and KIC~10068041).
-The final catalog contains 39,036 targets and the parameter distribution is
-shown in \dfmfig{targets}.
+The final catalog contains \numtargets\ targets and the parameter distribution
+is shown in \dfmfig{targets}.
 
@@
 Applying the search procedure described in \sect{search} to the \kepler\ light
-curves of the 39,036 targets selected in \sect{target-selection}, we find 16
-convincing transit candidates.
+curves of the \numtargets\ targets selected in \sect{target-selection}, we
+find \numcands\ convincing transit candidates.
 Visual inspection of each candidate confirms the reliability of the
@@
 
+\dfmfig{completeness} shows the fraction of recovered simulations as a
+function of planet radius and orbital period based on \numinjs\ injected
+signals.
+This figure shows the transit detection efficiency falling with decreasing
+planet radius.
+This is the expected behavior because the depth (and signal strength) of a
+transit scales with the area ratio between the planet and the star.
+The decreasing completeness with orbital period is less intuitive because, on
+average, the signal strength should increase as the duration of the transit
+increases.
+In this case, this simplistic treatment misses two important factors.
+First, in step 1 of the search procedure (\sect{stepone}) only a single
+transit duration is used and second, longer transits are less easily
+distinguished from stellar variability and they will, therefore, be discarded
+in the conservative light curve vetting step (\sect{light-curve-vetting}).
+
 This detection efficiency must then be combined with the geometric transit
@@
 Approximating the window function using the binomial probability of observing
-at least one transit \dfmtodo{cite bm14} we find
+at least one transit \citep{Burke:2014a} we find
 \begin{eqnarray}
@@
 \caption{%
-The completeness of the search procedure described here as a function of
-period and radius.
+An empirical estimate of the search completeness as a function of planet
+radius and orbital period.
 In each bin, the completeness (in percent) is given with the associated

### 2016-07-02 document/figures/completeness.py
updated completeness plot

@@ -13,8 +13,11 @@ inj = pd.read_hdf("../../results/injections.h5", "injections")
 inj = inj[inj.ncadences > 0]
 rec = inj[inj.recovered]
 
+# Histograms.
+ln_radius_bins = np.linspace(np.log(0.15), np.log(2.2), 8) + np.log(0.0995)
+ln_period_bins = np.linspace(np.log(2), np.log(25), 5) + np.log(365.25)
 n_all, ln_radius_bins, ln_period_bins = np.histogram2d(
-    np.log(inj.radius), np.log(inj.period), (8, 4),
+    np.log(inj.radius), np.log(inj.period), (ln_radius_bins, ln_period_bins),
 )
 n_rec, _, _ = np.histogram2d(
     np.log(rec.radius), np.log(rec.period), (ln_radius_bins, ln_period_bins),
@@ -26,6 +29,29 @@ X, Y = np.meshgrid(np.exp(ln_period_bins) / 365.25,
                    np.exp(ln_radius_bins) / 0.0995,
                    indexing="ij")
 
+# Plot 1
+fig, ax = pl.subplots(1, 1, figsize=2*np.array(SQUARE_FIGSIZE))
+
+ax.plot(inj[~inj.recovered].period/365.25, inj[~inj.recovered].radius/0.0995,
+        ".", color=COLORS["DATA"], alpha=0.3, rasterized=True)
+ax.plot(rec.period / 365.25, rec.radius / 0.0995, ".", color=COLORS["MODEL_1"],
+        alpha=0.3, rasterized=True)
+
+ax.set_xscale("log")
+ax.set_yscale("log")
+ax.set_xlim(X.min(), X.max())
+ax.set_ylim(Y.min(), Y.max())
+ax.set_xlabel("period [years]")
+ax.set_ylabel("$R_\mathrm{P} / R_\mathrm{J}$")
+ax.set_xticks([3, 5, 10, 20])
+ax.get_xaxis().set_major_formatter(pl.ScalarFormatter())
+ax.set_yticks([0.2, 0.5, 1, 2])
+ax.get_yaxis().set_major_formatter(pl.ScalarFormatter())
+
+fig.savefig("completeness0.pdf", bbox_inches="tight")
+pl.close(fig)
+
+# Plot 2
[…]

### 2016-07-02 document/ms.tex
words about completeness

@@
 probability function and the window function.
-For the star $k$, the geometric transit probability is given by \dfmtodo{cite}
-\begin{eqnarray}
-Q_{\mathrm{geom},k} (\params) &=& \frac{R_{\star,k}}{a_k}
+For the star $k$, the geometric transit probability is given by
+\citep{Winn:2010}
+\begin{eqnarray}
+Q_{\mathrm{geom},k} (\params) &=& \frac{R_{\star,k} + R}{a_k}
     \, \frac{1 + e\,\sin\omega}{1-e^2} \\
-&=& \left[\frac{4\,\pi^2}{G\,M_{\star,k}}\right]^{1/3}\,R_{\star,k}
+&=& \left[\frac{4\,\pi^2}{G\,M_{\star,k}}\right]^{1/3}\,(R_{\star,k}+R)
     \, \left[\frac{1 + e\,\sin \omega}{1-e^2}\right]
@@
 \end{eqnarray}
-where the parameters $e$, $\omega$, and $P$ are included in \params.
-Approximating the window function using the binomial probability of observing
-at least one transit \citep{Burke:2014a} we find
+where $R$ is the planet radius, $P$ is the orbital period, $e$ is the orbital
+eccentricity, $\omega$ is the argument of periastron, $R_{\star,k}$ is
+the radius of star $k$, and $M_{\star,k}$ is the star's mass.
+All of these parameters are included in \params.
+
+Approximating the window function using a binomial probability of observing
+at least one transit, we find \citep[following][]{Burke:2014a}
 \begin{eqnarray}
@@
 \end{eqnarray}
-For the purposes of this \paper, we are not considering the occurrence rate of
-exoplanets as a function of stellar properties; we will only measure an
-average rate across the target sample that we previously selected.
-Therefore, it is sufficient to estimate the marginalized detection efficiency
-integrated with respect to our prior distributions on the nuisance parameters.
-In this case, the only parameters that we will consider are planet radius and
-orbital period.
-Under this model, the relevant detection efficiency function for long-period
-transiting planets is
-\begin{eqnarray}\eqlabel{full-comp}
-Q(R,\,P) &=& \frac{1}{K} \sum_{k=1}^{K} \int Q_k(\params) \,
-    p(\params_{\{R,\,P\}}) \dd\params_{\{R,\,P\}}
-\end{eqnarray}
-where $\params_{\{R,\,P\}}$ indicates the set of all parameters except radius
-and period.
-
-Since the simulated parameters in the injection and recovery tests described
-above were sampled from the prior distribution $p(\params_{\{R,\,P\}})$, the
-easiest way to estimate \eq{full-comp} is to take the ratio of the weighted
-histogram of the recovered injections to the weighted histogram of all
-simulations where each simulation is weighted by
-$Q_{\mathrm{win},k} (\params) \, Q_{\mathrm{geom},k} (\params)$ evaluated at
-the parameters of the simulation.
-\dfmtodo{Some figure} shows the measured completeness (\eq{full-comp}) as a
-function of planet radius and orbital period.
-
-\dfmtodo{Analytic fit?}
+\dfmtodo{Talk about doing integrals with this.}
+
+% For the purposes of this \paper, we are not considering the occurrence rate of
+% exoplanets as a function of stellar properties; we will only measure an
+% average rate across the target sample that we previously selected.
+% Therefore, it is sufficient to estimate the marginalized detection efficiency
+% integrated with respect to our prior distributions on the nuisance parameters.
+% In this case, the only parameters that we will consider are planet radius and
+% orbital period.
+% Under this model, the relevant detection efficiency function for long-period
+% transiting planets is
+% \begin{eqnarray}\eqlabel{full-comp}
+% Q(R,\,P) &=& \frac{1}{K} \sum_{k=1}^{K} \int Q_k(\params) \,
+%     p(\params_{\{R,\,P\}}) \dd\params_{\{R,\,P\}}
+% \end{eqnarray}
+% where $\params_{\{R,\,P\}}$ indicates the set of all parameters except radius
+% and period.
+
+% Since the simulated parameters in the injection and recovery tests described
+% above were sampled from the prior distribution $p(\params_{\{R,\,P\}})$, the
+% easiest way to estimate \eq{full-comp} is to take the ratio of the weighted
+% histogram of the recovered injections to the weighted histogram of all
+% simulations where each simulation is weighted by
+% $Q_{\mathrm{win},k} (\params) \, Q_{\mathrm{geom},k} (\params)$ evaluated at
+% the parameters of the simulation.
+% \dfmtodo{Some figure} shows the measured completeness (\eq{full-comp}) as a
+% function of planet radius and orbital period.
+
+% \dfmtodo{Analytic fit?}
 

### 2016-07-02 document/ms.tex
words about occurrence rates

@@
 
-\subsection{Catalog of transit candidates}
+\subsection{Catalog of transit candidates}\sectlabel{catalog}
 
@@
 
-\section{Empirical search completeness}
+\section{Empirical search completeness}\sectlabel{completeness}
 
@@
 radius and orbital period.
-In each bin, the completeness (in percent) is given with the associated
-sampling uncertainty.
+In each bin, the completeness is estimated by the fraction of recovered
+simulations.
 The projected histograms show the integrated completeness as independent
@@
 
-Using the catalog of exoplanet discoveries (\dfmtodo{some section}) and the
-measurement of the search completeness (\dfmtodo{some section}), we can now
+Using the catalog of exoplanet discoveries (\sect{catalog}) and the
+measurement of the search completeness (\sect{completeness}), we can now
 estimate the occurrence rate of long-period exoplanets.
-This inference can be simplified by making a few strong assumptions that are
-only weakly justified.
-First, we make the strong assumption that none of the candidates are
-astrophysical false positives (background eclipsing binaries, the secondary
-eclipse of a long-period binary system, \etc).
-We revisit this assumption and discuss its validity in \dfmtodo{some section}.
-Next, we model the occurrence of exoplanets as a Poisson process
-(\dfmtodo{CITE}) with a rate function $\rate_{\poppars} (R,\,P)$ parameterized
-by some parameters \poppars.
-This assumption leads to the commonly used likelihood function
-(\dfmtodo{CITE})
-\begin{eqnarray}
-\ln p (\{w_j\}_{j=1}^J\,|\,\poppars) =
-    \sum_{j=1}^J \ln \rate_{\poppars} (R_j,\,P_j)
-    - \int \rate_{\poppars} (R,\,P)\,Q(R,\,P)\dd R\dd P
-    + \mathrm{constant} \quad.
-\end{eqnarray}
-Since our catalog of discoveries is small, we will only make limited
-inferences about the population.
-For the purposes of this paper, we will simply estimate the period of
-long-period planets ($2\,\mathrm{yr} \le P < 15\,\mathrm{yr}$) in two radius
-bins $0.1\,R_\mathrm{J} \le R < 0.5\,R_\mathrm{J}$ and $0.5\,R_\mathrm{J} \le
-R < R_\mathrm{J}$.
+To simplify the analysis, we will make the strong assumption that none of the
+candidates are astrophysical false positives (the eclipse of a stellar mass
+companion, a background eclipsing binary, or the secondary eclipse of a
+long-period binary system).
+We revisit this assumption and discuss its validity in the following section.
+As a further simplification, we also neglect the measurement uncertainties on
+the planet parameters (including orbital period).
+This assumption is only justified because we are only making high-level
+measurements of the mean occurrence rate in large bins.
 

### 2016-07-05 document/figures/method_comp.py
no qa

@@ -8,7 +8,7 @@ import pandas as pd
 import matplotlib
 import matplotlib.pyplot as pl
 
-from peerless.plot_setup import COLORS
+from peerless import plot_setup  # NOQA
 
 names = ["id", "binary", "mass", "radius", "period", "a", "e", "per", "long",
          "asc", "incl", "teq", "age", "method", "year", "updated", "ra", "dec",

### 2016-07-05 document/ms.tex
a few comments from @davidwhogg

@@
 \title{%
-The population of long-period exoplanets --- \\
-Fully-automated discovery \& characterization of
-long-period transiting exoplanet candidates in the \kepler\ archive
+The population of long-period transiting exoplanets
 \vspace{-3\baselineskip}  % OMG AASTEX6 IS SO BROKEN
@@
 This large, homogeneous catalog of discoveries has enabled rigorous studies of
-the occurrence rate of exoplanets and extra-Solar planetary systems as a
-function of their physical properties.
-Transit survey like \kepler\ are most sensitive to planets with shorter
+the occurrence rate of exoplanets and planetary systems as a function of their
+physical properties.
+Transit surveys like \kepler\ are most sensitive to planets with shorter
 orbital periods than the gas giant planets that dominate the dynamics of our
 Solar System.
-We performed a fully-automated search for the transits of long-period
+We performed a fully automated search for the transits of long-period
 exoplanets in the archival \kepler\ light curves and announce XXX planet
@@
 \emph{without human intervention}.
-Since the search methodology is fully-automated, we can robustly measure the
+Since the search methodology is fully automated, we can robustly measure the
 search completeness~--~using injection and recovery tests~--~and use these
@@
 
-\section{A fully-automated search method}\sectlabel{search}
+\section{A fully automated search method}\sectlabel{search}
 
 To find long-period exoplanets in the \kepler\ light curves, we search for
-individual, high signal-to-noise transit signals using a fully-automated
+individual, high signal-to-noise transit signals using a fully automated
 procedure that can be broken into three main steps:
@@
 
-We have developed a fully-automated method to search for the transits and
+We have developed a fully automated method to search for the transits and
 eclipses of long-period companions in photometric time series.

### 2016-07-05 document/ms.tex
more comments from @davidwhogg

@@
 
-\shorttitle{The population of long-period exoplanets}
+\shorttitle{The population of long-period transiting exoplanets}
 \shortauthors{Foreman-Mackey, Hogg, Morton, \etal}
@@
 Kipping:2016, Uehara:2016, Wang:2015}.
-Since all of these discoveries rely on human interaction, it is intractable to
-reliably constrain the completeness of these catalogs and they cannot be used
-to measure the occurrence rate of long-period planets.
-
-In this \paper, we develop a systematic method of reliably discovering the
+Since all of these discoveries rely on human interaction, it is prohibitively
+expensive to reliably measure the completeness of these catalogs and they
+cannot be used to constrain the occurrence rate of long-period planets.
+
+In this \paper, we develop a systematic method for reliably discovering the
 transits of large long-period companions in photometric time series
@@
 enables robust automation but it is also computationally expensive because we
-must estimate the marginalized likelihoods for the light curve under several
-different models describing a transit and many other processes that ``look''
-like transits but are actually caused by noise.
+must estimate the marginalized likelihoods of several different models
+describing a transit and many other processes that ``look'' like transits but
+are actually caused by noise.
 This step is also conservative; unless a signal is a very convincing transit,
@@
 It is not computationally feasible to run a full model comparison at every
-time in the light curve so we must first find potentially interesting events.
+conceivable transit time possible in the light curve so we must first find
+potentially interesting events.
 For our purposes, ``interesting'' means high signal-to-noise and previously
@@
 box.
-First, we filter the \pdc\ light curves \citep{Stumpe:2012, Smith:2012}
-using a running windowed median with a half-width of 2~days to remove stellar
-variability.
+After masking any known transits, we filter the \pdc\ light curves
+\citep{Stumpe:2012, Smith:2012} using a running windowed median with a
+half-width of 2~days to remove stellar variability.
 We then compute the signal-to-noise of the depth of a 0.6~day long
@@
 This likelihood function provides a natural scalar objective: the
-signal-to-noise of the measured depth $\delta / \sigma_\delta$ computed a
-function of time.
+signal-to-noise of the measured depth computed a function of time.
 In principle this scalar is also a function of duration but we only use a
@@
 The BIC can be efficiently computed and it exhibits the desired
-behavior~--~increasing with the likelihood but flexible models are
+behavior~--~decreasing with increasing likelihood but flexible models are
 penalized~--~and we find that it performs sufficiently well in practice.
@@
 contiguous chunk of \pdc\ light curve approximately centered on the proposed
-transit with no more than 500 cadences and compute the BIC of each model for
-this data set.
+transit with no more than 500 cadences (about 10 days) and compute the BIC of
+each model for this data set.
 The BIC for a model $k$ in the set of $K$ models is given by
 \begin{eqnarray}
-\mathrm{BIC}_k &=& \ln \mathcal{L}^* - \frac{J}{2}\,\log N
+\mathrm{BIC}_k &=& -2\,\ln \mathcal{L}^* + J\,\ln N
 \end{eqnarray}

### 2016-07-05 document/ms.tex
words about ORs

@@
 
+Assuming a Poisson likelihood, the occurrence rate density in a volume
+$V$~--~defined as $P_\mathrm{min} \le P < P_\mathrm{max}$ and
+$R_\mathrm{min} \le R < R_\mathrm{max}$~--~is
+\begin{eqnarray}
+\frac{\dd N}{\dd\ln P\dd\ln R} &=&
+    \frac{N(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max})}
+         {Z(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max})}
+\end{eqnarray}
+where $N(\cdots)$ is the number of planets in the volume and
+\begin{eqnarray}
+Z(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max}) &=&
+    \sum_{k=1}^{K} \int p(w_{P,\,R})\,Q_k(w)\,\bvec{1}[P,\,R\in V]\dd w
+\end{eqnarray}
+where $p(w_{P,\,R})$ is the prior distribution of all the parameters except
+the period and radius.
+Using the $J$ injections sampled uniformly in period and radius and other
+parameters from $p(w_{P,\,R})$,
+\begin{eqnarray}
+Z(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max}) &\approx&
+    \frac{K}{J}\,\sum_{j=1}^{J} Q_k(w^{(j)})
+\end{eqnarray}
+where the sum is over all injections in the volume $V$.
+
 \section{Astrophysical false positives}\sectlabel{false-positives}

### 2016-07-05 peerless/occurrence.py
breaking occ calc out into module

@@ -1,0 +1,81 @@
+# -*- coding: utf-8 -*-
+
+import numpy as np
+import pandas as pd
+from itertools import product
+from collections import OrderedDict
+
+from peerless.catalogs import TargetCatalog
+
+__all__ = ["compute_occurrence"]
+
+# Newton's constant in $R_\odot^3 M_\odot^{-1} {days}^{-2}$.
+_G = 2945.4625385377644
+
+
+def compute_occurrence(inj, fits0, rbins, pbins):
+    """
+    Compute the occurrence rate density in a grid of period
+
+    """
+    # Only select injections from the corresponding target list.
+    targets = TargetCatalog().df
+    targets = targets[np.isfinite(targets.mass)]
+    inj0 = pd.merge(inj, targets, left_on="kicid", right_on="kepid",
+                    suffixes=["", "_stlr"])
+    inj0 = pd.DataFrame(inj0[np.isfinite(inj0.mass)])
+
+    # Note this only works because we injected uniformly in log-period.
+    results = []
+    for (rmin, rmax), (pmin, pmax) in product(rbins, pbins):
+        m = (rmin * 0.0995 <= inj0.radius) & (inj0.radius <= rmax * 0.0995)
+        m &= (pmin * 365.25 <= inj0.period) & (inj0.period <= pmax * 365.25)
+        inj = pd.DataFrame(inj0[m])
+        rec = inj.accept
+
+        # Geometric.
+        fk = inj.dutycycle
+        Tk = inj.dataspan
+        Mk = inj.mass
+        Rk = inj.radius_stlr
+        Qk = (4*np.pi/(_G * Mk))**(1./3) * (Rk + inj.radius * 0.0995)
+        period = inj.period
+
+        # Eccentric contribution to geometric transit probability.
+        eccen = inj.e
+        omega = inj.omega
+        Qe = (1.0 + eccen * np.sin(omega)) / (1.0 - eccen**2)
+
+        # Window function.
+        Qt = period**(-2./3) * (1.0 - (1.0 - fk)**(Tk / period))
+
+        # Re-weight the samples based on the injected radius distribution.
+        radius = inj.radius
+        bins = np.log(0.0995) + np.linspace(np.log(rmin), np.log(rmax), 10)
+        n, _ = np.histogram(np.log(np.array(radius)), bins, density=True)
+        w = n[np.digitize(np.log(np.array(radius)), bins) - 1]
+
+        # Combine all the effects and integrate.
[…]

### 2016-07-05 peerless/occurrence.py
makign OR table

@@ -13,11 +13,14 @@ __all__ = ["compute_occurrence"]
 _G = 2945.4625385377644
 
 
-def compute_occurrence(inj, fits0, rbins, pbins):
+def compute_occurrence(inj, fits0, rgrid, pgrid):
     """
     Compute the occurrence rate density in a grid of period
 
     """
+    rbins = [(float(rgrid[i]), float(rgrid[i+1])) for i in range(len(rgrid)-1)]
+    pbins = [(float(pgrid[i]), float(pgrid[i+1])) for i in range(len(pgrid)-1)]
+
     # Only select injections from the corresponding target list.
     targets = TargetCatalog().df
     targets = targets[np.isfinite(targets.mass)]

### 2016-07-06 document/ms.tex
Adding occurrence rate table into ms
gamma

@@
 $R_\mathrm{min} \le R < R_\mathrm{max}$~--~is
-\begin{eqnarray}
-\frac{\dd N}{\dd\ln P\dd\ln R} &=&
-    \frac{N(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max})}
+\begin{eqnarray}\eqlabel{rate-density}
+\Gamma_V \equiv \frac{\dd N}{\dd\ln P\dd\ln R} &=&
+    \frac{C(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max})}
          {Z(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max})}
 \end{eqnarray}
-where $N(\cdots)$ is the number of planets in the volume and
+where $N$ is the expected number of planets per G/K dwarf, $C(\cdots)$ is the
+number of planets in the volume, and
 \begin{eqnarray}
@@
 where the sum is over all injections in the volume $V$.
+
+\begin{floattable}
+\begin{deluxetable}{ccc}
+\tabletypesize{\footnotesize}
+\caption{The occurrence rate density in two radius bins \label{tab:occurrence}}
+\include{ortab}
+\tablenotetext{a}{See \eq{rate-density}}
+\tablecomments{These values are computed in the period range 2--25~years.}
+\end{deluxetable}
+\end{floattable}
 

### 2016-07-06 document/ms.tex
words about ors

@@
 \end{eqnarray}
-\dfmtodo{Talk about doing integrals with this.}
-
-% For the purposes of this \paper, we are not considering the occurrence rate of
-% exoplanets as a function of stellar properties; we will only measure an
-% average rate across the target sample that we previously selected.
-% Therefore, it is sufficient to estimate the marginalized detection efficiency
-% integrated with respect to our prior distributions on the nuisance parameters.
-% In this case, the only parameters that we will consider are planet radius and
-% orbital period.
-% Under this model, the relevant detection efficiency function for long-period
-% transiting planets is
-% \begin{eqnarray}\eqlabel{full-comp}
-% Q(R,\,P) &=& \frac{1}{K} \sum_{k=1}^{K} \int Q_k(\params) \,
-%     p(\params_{\{R,\,P\}}) \dd\params_{\{R,\,P\}}
-% \end{eqnarray}
-% where $\params_{\{R,\,P\}}$ indicates the set of all parameters except radius
-% and period.
-
-% Since the simulated parameters in the injection and recovery tests described
-% above were sampled from the prior distribution $p(\params_{\{R,\,P\}})$, the
-% easiest way to estimate \eq{full-comp} is to take the ratio of the weighted
-% histogram of the recovered injections to the weighted histogram of all
-% simulations where each simulation is weighted by
-% $Q_{\mathrm{win},k} (\params) \, Q_{\mathrm{geom},k} (\params)$ evaluated at
-% the parameters of the simulation.
-% \dfmtodo{Some figure} shows the measured completeness (\eq{full-comp}) as a
-% function of planet radius and orbital period.
-
-% \dfmtodo{Analytic fit?}
 
@@
 $R_\mathrm{min} \le R < R_\mathrm{max}$~--~is
+\citep[see, for example, the Appendix of][]{Foreman-Mackey:2014}
 \begin{eqnarray}\eqlabel{rate-density}
@@
 Z(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max}) &=&
-    \sum_{k=1}^{K} \int p(w_{P,\,R})\,Q_k(w)\,\bvec{1}[P,\,R\in V]\dd w
-\end{eqnarray}
-where $p(w_{P,\,R})$ is the prior distribution of all the parameters except
-the period and radius.
+    \sum_{k=1}^{K} \int p(w_{\{P,\,R\}})\,Q_k(w)\,\bvec{1}[P,\,R\in V]\dd w
+\end{eqnarray}
+where $p(w_{\{P,\,R\}})$ is the prior distribution of all the parameters except
+the period and radius and $\bvec{1}[\cdot]$ is 1 if the argument is satisfied
+and 0 otherwise.
 Using the $J$ injections sampled uniformly in period and radius and other
-parameters from $p(w_{P,\,R})$,
+parameters from $p(w_{\{P,\,R\}})$,
 \begin{eqnarray}

### 2016-07-06 document/figures/completeness.py
adding analytic fit to completeness model

@@ -4,14 +4,82 @@ from __future__ import division, print_function
 
 from peerless.plot_setup import SQUARE_FIGSIZE, COLORS
 
-import numpy as np
+# import numpy as np
 import pandas as pd
 from itertools import product
 import matplotlib.pyplot as pl
+from scipy.optimize import minimize
+
+from autograd import grad
+import autograd.numpy as np
+
 
 inj = pd.read_hdf("../../results/injections.h5", "injections")
 inj = inj[inj.ncadences > 0]
 rec = inj[inj.recovered]
+
+
+def analytic_model(params, ln_radius, ln_period):
+    b1, b2, a1, a2, k1, k2, x1, x2 = params
+    a = (a1 * ln_period + a2) * (b1 * ln_radius + b2)
+    a = a * (a > 0.0) * (a < 1.0) + 1.0 * (a > 1.0)
+    k = k1 * ln_period + k2
+    x = x1 * ln_period + x2
+    return a / (1.0 + np.exp(-k * (ln_radius - x)))
+
+
+def nll(params, ln_radius, ln_period, flag):
+    m = analytic_model(params, ln_radius, ln_period)
+    return np.mean((flag - m)**2)
+
+
+def error(params, ln_radius, ln_period, flag):
+    m = analytic_model(params, ln_radius, ln_period)
+    pred = m > 0.5
+    return np.sum(pred != flag)
+
+
+x, y = np.log(np.array(inj.radius)), np.log(np.array(inj.period))
+flag = np.array(inj.recovered, dtype=int)
+params = np.array([0.0, 1.0, 0.0, 0.6, 0.0, 10.0, 0.0, -3.0])
+r = minimize(nll, params, jac=grad(nll), args=(x, y, flag))
+with open("../completenessfit.tex", "w") as f:
+    f.write(r"""\newcommand{{\parama}}{{{0[0]:.2f}}}
+\newcommand{{\paramb}}{{{0[1]:.2f}}}
+\newcommand{{\paramc}}{{{0[2]:.2f}}}
+\newcommand{{\paramd}}{{{0[3]:.2f}}}
+\newcommand{{\parame}}{{{0[4]:.2f}}}
+\newcommand{{\paramf}}{{{0[5]:.2f}}}
[…]

### 2016-07-06 document/ms.tex
words about the analytic fit

@@
 \include{numbers}
+\include{completenessfit}
 
@@
 
+So that our planet candidate catalog can be easily used for other projects, we
+also provide an analytic approximation to the relevant integrated detection
+efficiency function
+\begin{eqnarray}
+Q_\mathrm{det}(P,\,R) &=& \sum_{k=1}^{K} \int Q_\mathrm{det,k}(\params)\,
+    p(\params_{\{P,\,R\}}) \dd\params_{\{P,\,R\}}
+\end{eqnarray}
+where $p(\params_{\{P,\,R\}})$ is the prior distribution of all the parameters
+except the period and radius.
+We find that a good fit to this integrated completeness is given by the
+function
+\begin{eqnarray}
+Q_\mathrm{det}(P,\,R) &\approx&
+    \frac{a(P)\,b(R)}{1+\exp\left[-k(P)\,(\ln R-x(P))\right]}
+\end{eqnarray}
+where
+\begin{eqnarray}
+a(P) = a_1\,\ln P + a_2 \,,\quad
+b(R) = b_1\,\ln R + b_2 \,,\quad \\
+k(P) = k_1\,\ln P + k_2 \,,\,\mathrm{and}\quad
+x(P) = x_1\,\ln P + x_2 \,.
+\end{eqnarray}
+When fit to the set of \numinjs\ injected transits, the best fit parameters
+are given in Table~\ref{tab:completeness} and the approximation is plotted
+in \dfmfig{completeness-analytic}.
+Note that we do not use this approximation in the following analysis but
+instead compute the relevant integrals using the injection catalog directly.
+
 \begin{floattable}
@@
 
+\begin{figure*}[htbp]~\\
+\begin{center}
+\includegraphics[width=0.6\textwidth]{figures/completeness_analytic.pdf}
+\end{center}
+\caption{%
+An analytic approximation to \dfmfig{completeness} with the same color scale.
+The contours indicate the 0.1, 0.3, 0.5, and 0.7 levels.
+\dfmfiglabel{completeness-analytic}}
+\end{figure*}
+
+\begin{floattable}
+\begin{deluxetable}{cc|cc}
+\tabletypesize{\footnotesize}
+\caption{The fit parameters for the analytic approximation to the completeness
+function
+\label{tab:completeness}}
+\tablehead{%
+    \colhead{parameter} & \colhead{value} &
+    \colhead{parameter} & \colhead{value}
+}
+\startdata
+$a_1$ & $\paramc$ & $k_1$ & $\parame$ \\
+$a_2$ & $\paramd$ & $k_2$ & $\paramf$ \\
+$b_1$ & $\parama$ & $x_1$ & $\paramg$ \\
+$b_2$ & $\paramb$ & $x_2$ & $\paramh$ \\
+\enddata
+\end{deluxetable}
+\end{floattable}
+
 \section{The occurrence rate of long-period exoplanets}
@@
 Z(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max}) &=&
-    \sum_{k=1}^{K} \int p(w_{\{P,\,R\}})\,Q_k(w)\,\bvec{1}[P,\,R\in V]\dd w
-\end{eqnarray}
-where $p(w_{\{P,\,R\}})$ is the prior distribution of all the parameters except
-the period and radius and $\bvec{1}[\cdot]$ is 1 if the argument is satisfied
-and 0 otherwise.
+    \sum_{k=1}^{K} \int p(\params_{\{P,\,R\}})\,
+    Q_k(\params)\,\bvec{1}[P,\,R\in V]\dd \params
+\end{eqnarray}
+where $p(\params_{\{P,\,R\}})$ is the prior distribution of all the parameters
+except the period and radius and $\bvec{1}[\cdot]$ is 1 if the argument is
+satisfied and 0 otherwise.
 Using the $J$ injections sampled uniformly in period and radius and other

### 2016-07-07 document/ms.tex
cleaning up some to dos
bounding analytic model
words about occurrence rates

@@
 Q_\mathrm{det}(P,\,R) &\approx&
-    \frac{a(P)\,b(R)}{1+\exp\left[-k(P)\,(\ln R-x(P))\right]}
+    \frac{\mathrm{min}[\mathrm{max}[a(P)\,b(R),\,0],\,1]}
+         {1+\exp\left[-k(P)\,(\ln R-x(P))\right]}
 \end{eqnarray}
@@
 where $N$ is the expected number of planets per G/K dwarf, $C(\cdots)$ is the
-number of planets in the volume, and
+number of detected planets in the volume, and
 \begin{eqnarray}
@@
 where the sum is over all injections in the volume $V$.
+
+Using the injection results from \sect{completeness} and the catalog of
+discoveries from \sect{catalog}, we compute the occurrence rate in the period
+range 2 to 25 years and in two radius bins between 0.1 and
+$1.0\,R_\mathrm{J}$.
+The calculated occurrence rates are listed in Table~\ref{tab:occurrence}.
 
@@
 under contract with NASA under the Exoplanet Exploration Program.
+
 This \paper\ includes data collected by the \kepler\ mission. Funding for the
@@
 summarize the most relevant points here and direct an interested reader to
-\dfmtodo{cite RW} for more details.
+\citet{Rasmussen:2006} for more details.
 
@@
 
-To evaluate \eq{gpmeangrad}, we must also evaluate the derivative of the mean
-model with respect to its parameters.
-
-\clearpage
+% To evaluate \eq{gpmeangrad}, we must also evaluate the derivative of the mean
+% model with respect to its parameters.
+
 \bibliography{peerless}

### 2016-07-07 document/ms.tex
extrapolation

@@
 
+For comparison, we repeated the analysis of \citet{Burke:2015} and fit a
+double power-law occurrence rate to the short-period \kepler\ planet
+candidates\footnote{The analysis was adapted from publicly available code that
+was demonstrated to reproduce the same results as \citet{Burke:2015} by
+\citet{Foreman-Mackey:2015a}.} and extrapolated to the center of the two
+bins where we computed the occurrence rate.
+At a period of 7~years and a radius of $0.2\,R_\mathrm{J}$, the extrapolated
+occurrence is $0.73\pm0.28$ and at a radius of $0.6\,R_\mathrm{J}$, the
+extrapolated rate is $0.15\pm0.05$.
+
 \begin{floattable}

### 2016-07-12 document/ms.tex
updated fit table
some literature citations

@@
 Solar System.
-We performed a fully automated search for the transits of long-period
-exoplanets in the archival \kepler\ light curves and announce XXX planet
-candidates.
+We performed a fully automated search for long-period exoplanets with only one
+or two transits in the archival \kepler\ light curves.
+When applied to the 40,000 brightest Sun-like target stars, this search
+produces \numcands\ long-period exoplanet candidates.
 Since our method involves no human intervention, we empirically characterize
@@
 Based on these results, we measure the average occurrence rate of exoplanets
-smaller than Jupiter and with orbital periods longer than 700 days to be $\dd
-N = YYY \pm ZZZ\dd \ln P \dd \ln R$.
+smaller than Jupiter with orbital periods longer than two years.
 
@@
 
-EB catalog: \citep{Kirk:2016}
-
-Microlensing OR: \citep{Shvartzvald:2016}
+% EB catalog: \citep{Kirk:2016}
+
+% Microlensing OR: \citep{Shvartzvald:2016}
 
@@
 procedures.
+
+A study of the population of long-period transiting planets complements
+parallel radial velocity \citep[RV; for example][]{Cumming:2008,
+Knutson:2014, Bryan:2016}, microlensing \citep[for
+example][]{Gould:2010, Cassan:2012, Clanton:2014, Shvartzvald:2016}, and
+direct imaging \citep[for example][]{Bowler:2016}.
+
 It is possible to discover long-period planets like this using targeted radial
-velocity (RV) surveys \citep[for example][]{Butler:2006, Knutson:2014,
-Bryan:2016} but the cost of implementing a systematic RV search is
+velocity (RV) surveys
+
+but the cost of implementing a systematic RV search is
 substantially higher than searching the existing and forthcoming photometric
@@
 \begin{floattable}
-\begin{deluxetable}{cccccl}
+\begin{deluxetable}{ccccccccl}
 \tabletypesize{\footnotesize}

### 2016-07-12 peerless/mr.py
adding probabilistic mass-radius relation

@@ -1,0 +1,55 @@
+# -*- coding: utf-8 -*-
+
+from __future__ import division, print_function
+
+import logging
+import numpy as np
+
+from .catalogs import LocalCatalog, singleton
+
+__all__ = ["WolfgangMRRelation"]
+
+
+class WolfgangMRRelation(LocalCatalog):
+    filename = "wolfgang.csv"
+
+    def predict_mass(self, radius_samples, num_hyper=None, maxiter=500):
+        radius_samples = np.atleast_1d(radius_samples)
+        shape = radius_samples.shape
+        flat_radii = radius_samples.flatten()
+        params = self.df
+
+        inds = np.ones(len(params), dtype=bool)
+        if num_hyper is not None:
+            inds = np.random.randint(len(params), size=num_hyper)
+
+        # Grab the parameter samples.
+        lnc = np.array(params["normconst"])[inds]
+        gamma = np.array(params["powindex"])[inds]
+        sigm = np.sqrt(np.array(params["varMR"]))[inds]
+
+        # Use Wolfgang+ (2016) Equation (2).
+        mu = lnc[:, None] + gamma[:, None] * np.log(flat_radii)[None, :]
+        std = sigm[:, None] + np.zeros_like(mu)
+        mass = np.exp(mu) + std * np.random.randn(*(mu.shape))
+
+        # Iterate until none of the masses are < 0.0.
+        for i in range(maxiter):
+            m = mass < 0.0
+            if not np.any(m):
+                break
+            mass[m] = np.exp(mu[m]) + std[m] * np.random.randn(m.sum())
+        if i == maxiter - 1:
+            logging.warn("Some masses still incorrect after 'maxiter'")
+
+        # For R > 9 R_E, use a log-normal distribution.
+        mask = flat_radii > 9.0
+        lnm = 0.04590711 + 0.3919828*np.random.randn(len(mass), mask.sum())
+        mass[:, mask] = np.exp(lnm + np.log(317.828))
+
+        # Reshape the samples into the correct (num_hyper, ...) shape.
+        final_shape = [len(lnc)] + list(shape)
+        return mass.reshape(final_shape)
+
+
+WolfgangMRRelation = singleton(WolfgangMRRelation)

### 2016-07-12 peerless/mr.py
chen mr relation

@@ -2,10 +2,11 @@
 
 from __future__ import division, print_function
 
+import h5py
 import logging
 import numpy as np
 
-from .catalogs import LocalCatalog, singleton
+from .catalogs import Catalog, LocalCatalog, singleton
 
 __all__ = ["WolfgangMRRelation"]
 
@@ -13,15 +14,15 @@ __all__ = ["WolfgangMRRelation"]
 class WolfgangMRRelation(LocalCatalog):
     filename = "wolfgang.csv"
 
-    def predict_mass(self, radius_samples, num_hyper=None, maxiter=500):
+    def predict_mass(self, radius_samples, num_mass=None, maxiter=500):
         radius_samples = np.atleast_1d(radius_samples)
         shape = radius_samples.shape
         flat_radii = radius_samples.flatten()
         params = self.df
 
         inds = np.ones(len(params), dtype=bool)
-        if num_hyper is not None:
-            inds = np.random.randint(len(params), size=num_hyper)
+        if num_mass is not None:
+            inds = np.random.randint(len(params), size=num_mass)
 
         # Grab the parameter samples.
         lnc = np.array(params["normconst"])[inds]
@@ -47,9 +48,118 @@ class WolfgangMRRelation(LocalCatalog):
         lnm = 0.04590711 + 0.3919828*np.random.randn(len(mass), mask.sum())
         mass[:, mask] = np.exp(lnm + np.log(317.828))
 
-        # Reshape the samples into the correct (num_hyper, ...) shape.
+        # Reshape the samples into the correct (num_mass, ...) shape.
         final_shape = [len(lnc)] + list(shape)
         return mass.reshape(final_shape)
 
 
+class ChenMRRelation(Catalog):
+    url = ("https://github.com/chenjj2/forecaster/blob/master/"
+           "fitting_parameters.h5?raw=true")
+    name = "chen"
+    _grid = None
+
+    def _save_fetched_file(self, file_handle):
+        with open(self.filename, "wb") as f:
+            f.write(file_handle.read())
+        with h5py.File(self.filename, "r") as f:
+            log_r, log_m, grid = self.make_grid(f["hyper_posterior"][...])
+        with h5py.File(self.filename, "w") as f:
+            f.create_dataset("log10_radius_bins", data=log_r)
+            f.create_dataset("log10_mass_bins", data=log_m)
+            f.create_dataset("cumulative_probability", data=grid)
+
+    def make_grid(self, samples):
[…]

### 2016-07-12 document/ms.tex
more prediction work, intro FP sentences

@@
 
-Tim to write some words here.
+Various configurations of grazing or blended eclipsing binaries can mimic the
+signal of a transiting planet \citep{}. The occurrence rate calculation
+presented in the preceding section assumes that none of the planet
+candidates identified in this work are caused by such astrophysical false
+positives.  In this Section we explore the validity of this assumption.
 

### 2016-07-13 peerless/mr.py
working chen MR

@@ -133,7 +133,7 @@ class ChenMRRelation(Catalog):
                 )
         return self._grid
 
-    def predict_mass(self, radius_samples, num_mass=1000):
+    def predict_mass(self, radius_samples, num_mass=10000):
         radius_samples = np.atleast_1d(radius_samples)
         shape = radius_samples.shape
         flat_log_r = np.log10(radius_samples.flatten())

### 2016-07-13 peerless/mr.py
adding script to predict injected masses

@@ -145,7 +145,9 @@ class ChenMRRelation(Catalog):
 
         r_inds = np.digitize(flat_log_r, log_r) - 1
         if np.any(r_inds < 0) or np.any(r_inds >= len(log_r) - 1):
-            raise ValueError("Invalid radii")
+            logging.warn("Radii outside of grid")
+            r_inds[r_inds < 0] = 0
+            r_inds[r_inds >= len(log_r) - 1] = len(log_r) - 2
 
         # Sample the masses.
         cp = grid[r_inds]

### 2016-07-13 document/figures/completeness.py
adding mass-semimajor completeness plot

@@ -14,7 +14,7 @@ from autograd import grad
 import autograd.numpy as np
 
 
-inj = pd.read_hdf("../../results/injections.h5", "injections")
+inj = pd.read_hdf("../../results/injections-with-mass.h5", "injections")
 inj = inj[inj.ncadences > 0]
 rec = inj[inj.recovered]
 
@@ -163,3 +163,91 @@ ax.set_yticklabels([])
 ax.xaxis.set_major_locator(pl.MaxNLocator(3))
 
 fig.savefig("completeness.pdf", bbox_inches="tight")
+pl.close(fig)
+
+
+# Histograms.
+ln_mass_bins = np.linspace(np.log(2.0), np.log(1e5), 8)
+ln_semimajor_bins = np.linspace(np.log(1.5), np.log(9), 5) + np.log(215.1)
+n_all, ln_mass_bins, ln_semimajor_bins = np.histogram2d(
+    inj.log10_mass*np.log(10), np.log(inj.semimajor),
+    (ln_mass_bins, ln_semimajor_bins),
+)
+n_rec, _, _ = np.histogram2d(
+    rec.log10_mass*np.log(10), np.log(rec.semimajor),
+    (ln_mass_bins, ln_semimajor_bins),
+)
+n = n_rec / n_all
+n_err = n / np.sqrt(n_all)
+
+X, Y = np.meshgrid(np.exp(ln_semimajor_bins) / 215.1,
+                   np.exp(ln_mass_bins) / 317.828,
+                   indexing="ij")
+
+
+# Plot 2
+fig = pl.figure(figsize=2*np.array(SQUARE_FIGSIZE))
+
+ax = pl.axes([0.1, 0.1, 0.6, 0.6])
+ax.pcolor(X, Y, 100*n.T, cmap="viridis", vmin=0, vmax=100)
+
+# Label the bins with their completeness percentages.
+for i, j in product(range(len(ln_semimajor_bins)-1),
+                    range(len(ln_mass_bins)-1)):
+    x = np.exp(0.5 * (ln_semimajor_bins[i] + ln_semimajor_bins[i+1])) / 215.1
+    y = np.exp(0.5 * (ln_mass_bins[j] + ln_mass_bins[j+1])) / 317.828
+    ax.annotate(r"${0:.3f}$".format(n[j, i]),
[…]

### 2016-07-13 document/ms.tex
masstab

@@
 
+\section{Comparison with the literature}\sectlabel{comparison}
+
+\begin{floattable}
+\begin{deluxetable}{cccc}
+\tabletypesize{\footnotesize}
+\caption{The inferred parameters for the long-period transiting exoplanet
+candidates \label{tab:masses}}
+\include{masstab}
+\tablenotetext{*}{The equilibrium temperature is computed assuming zero
+albedo.}
+\end{deluxetable}
+\end{floattable}
+
+\begin{figure*}[p]~\\
+\begin{center}
+\includegraphics[width=\textwidth]{figures/completeness-am.pdf}
+\end{center}
+\caption{%
+The same as \dfmfig{completeness} converted into the planet mass and
+semi-major axis plane.
+Since the completeness function depends on the planet's radius and not its
+mass, a probabilistic mass--radius relation \citep{Chen:2016} was used to
+convert radius to mass.
+\dfmfiglabel{completeness-am}}
+\end{figure*}
+
 \section{Discussion}\sectlabel{discussion}

### 2016-07-13 document/figures/mr.py
make

@@ -2,7 +2,7 @@ import numpy as np
 import matplotlib.pyplot as pl
 from peerless.mr import WolfgangMRRelation, ChenMRRelation
 
-radii = np.linspace(1.0, 12, 100)
+radii = np.linspace(1.0, 24, 100)
 for r, c in zip((ChenMRRelation(), WolfgangMRRelation()), "gk"):
     masses = r.predict_mass(radii)
     q = np.percentile(masses, [16, 50, 84], axis=0)

### 2016-07-13 document/ms.tex

@@
 \tabletypesize{\footnotesize}
-\caption{The inferred parameters for the long-period transiting exoplanet
-candidates \label{tab:masses}}
+\caption{The mass and semi-major axis estimates for the candidates from
+Table~\ref{tab:catalog} \label{tab:masses}}
 \include{masstab}
-\tablenotetext{*}{The equilibrium temperature is computed assuming zero
-albedo.}
+\tablenotetext{*}{The mass is estimated based on the measured radius using a
+probabilistic mass--radius relation \citep{Chen:2016}.}
 \end{deluxetable}

### 2016-07-13 document/ms.tex
updated mass pred table
some words of caution about extrapolation

@@
 extrapolated rate is $0.15\pm0.05$.
+These extrapolated values are qualitatively consistent with the rates listed
+in Table~\ref{tab:occurrence} but we note that extrapolations and their
+statistical uncertainties should not be taken too seriously.
 
@@
 \begin{floattable}
-\begin{deluxetable}{cccc}
+\begin{deluxetable}{cccccccc}
 \tabletypesize{\footnotesize}
@@
 \include{masstab}
-\tablenotetext{*}{The mass is estimated based on the measured radius using a
-probabilistic mass--radius relation \citep{Chen:2016}.}
+\tablecomments{The masses and radial velocity amplitudes are estimated based
+on the measured radius using a probabilistic mass--radius relation
+\citep{Chen:2016}.}
 \end{deluxetable}

### 2016-07-13 peerless/occurrence.py
making occ rate calc more flexible

@@ -13,7 +13,9 @@ __all__ = ["compute_occurrence"]
 _G = 2945.4625385377644
 
 
-def compute_occurrence(inj, fits0, rgrid, pgrid):
+def compute_occurrence(inj, fits0, rgrid, pgrid,
+                       x_name="period", x_factor=365.25,
+                       y_name="radius", y_factor=0.0995):
     """
     Compute the occurrence rate density in a grid of period
 
@@ -31,8 +33,8 @@ def compute_occurrence(inj, fits0, rgrid, pgrid):
     # Note this only works because we injected uniformly in log-period.
     results = []
     for (rmin, rmax), (pmin, pmax) in product(rbins, pbins):
-        m = (rmin * 0.0995 <= inj0.radius) & (inj0.radius <= rmax * 0.0995)
-        m &= (pmin * 365.25 <= inj0.period) & (inj0.period <= pmax * 365.25)
+        m = (rmin*y_factor <= inj0[y_name]) & (inj0[y_name] <= rmax*y_factor)
+        m &= (pmin*x_factor <= inj0[x_name]) & (inj0[x_name] <= pmax*x_factor)
         inj = pd.DataFrame(inj0[m])
         rec = inj.accept
 
@@ -53,16 +55,20 @@ def compute_occurrence(inj, fits0, rgrid, pgrid):
         Qt = period**(-2./3) * (1.0 - (1.0 - fk)**(Tk / period))
 
         # Re-weight the samples based on the injected radius distribution.
-        radius = inj.radius
-        bins = np.log(0.0995) + np.linspace(np.log(rmin), np.log(rmax), 10)
-        n, _ = np.histogram(np.log(np.array(radius)), bins, density=True)
-        w = n[np.digitize(np.log(np.array(radius)), bins) - 1]
+        x_samp = np.log(np.array(inj[x_name]))
+        x_bins = np.log(x_factor) + np.linspace(np.log(pmin), np.log(pmax), 20)
+        y_samp = np.log(np.array(inj[y_name]))
+        y_bins = np.log(y_factor) + np.linspace(np.log(rmin), np.log(rmax), 22)
+        n, _, _ = np.histogram2d(x_samp, y_samp, (x_bins, y_bins),
+                                 normed=True)
+        w = n[np.digitize(x_samp, x_bins) - 1,
+              np.digitize(y_samp, y_bins) - 1]
 
         # Combine all the effects and integrate.
         Q = (Qk * Qt * Qe * w)[rec].sum() / w.sum()
 
[…]

### 2016-07-13 peerless/occurrence.py
computing mass/semimajor occ rate

@@ -13,7 +13,7 @@ __all__ = ["compute_occurrence"]
 _G = 2945.4625385377644
 
 
-def compute_occurrence(inj, fits0, rgrid, pgrid,
+def compute_occurrence(inj, fits0, pgrid, rgrid,
                        x_name="period", x_factor=365.25,
                        y_name="radius", y_factor=0.0995):
     """

### 2016-07-14 document/ms.tex
words about comparisons

@@
 \setlength{\hoffset}{0in}
-\setlength{\textwidth}{6.5in}
+\setlength{\textwidth}{6in}
 \setlength{\textheight}{9in}
@@
 \setlength{\topmargin}{-\headsep}
+\setlength{\oddsidemargin}{0.25in}
+\setlength{\evensidemargin}{0.25in}
 
@@
 \shorttitle{The population of long-period transiting exoplanets}
-\shortauthors{Foreman-Mackey, Hogg, Morton, \etal}
+\shortauthors{Foreman-Mackey, Morton, Hogg, \etal}
 % \submitted{Submitted to \textit{The Astrophysical Journal}}
@@
 
+\edef \princeton {\arabic{affilcounter}}\stepcounter{affilcounter}
+\altaffiltext{\princeton}{Department of Astrophysics, Princeton University,
+                          Princeton, NJ, 08544, USA}
+
 \edef \scda {\arabic{affilcounter}}\stepcounter{affilcounter}
@@
 
-\edef \princeton {\arabic{affilcounter}}\stepcounter{affilcounter}
-\altaffiltext{\princeton}{Department of Astrophysics, Princeton University,
-                          Princeton, NJ, 08544, USA}
-
 \edef \mpis      {\arabic{affilcounter}}\stepcounter{affilcounter}
@@
     Daniel~Foreman-Mackey\altaffilmark{1,\uw},
+    Timothy~D.~Morton\altaffilmark{\princeton},
     David~W.~Hogg\altaffilmark{\scda,\nyu,\mpia,\cds},
-    Timothy~D.~Morton\altaffilmark{\princeton},
+    Eric~Agol\altaffilmark{\uw},
     Bernhard~Sch\"olkopf\altaffilmark{\mpis},
-    Eric~Agol\altaffilmark{\uw},
     and others
@@
 
+The population of long-period planets has been previously studied using radial
+velocity, microlensing, and direct imaging surveys.
+These methods all measure the occurrence rate in units of mass and semi-major
+axis instead of radius and period.
+Using the transit method, we do not directly measure the mass of the planet.
+Instead, we must rely on a mass--radius relationship constructed using
+exoplanets with both mass and radius measurements \citep[for
+example]{Weiss:2014, Wolfgang:2016, Chen:2016} to predict the expected masses
+of the transiting planets.
+
+A detailed discussion of the systematic effects introduced by the use of a
+mass--radius relationship is beyond the scope of this \paper\ but it is worth
+noting that all published relationships are based on exoplanets much closer to
+their host star than any of the candidates discussed here.
+
+We find that the mean occurrence rate density in the range $0.01\,M_\mathrm{J}
+\le M < 20\,M_\mathrm{J}$ and $1.5\unit{au} \le a < 9\unit{au}$ is
+\begin{eqnarray}\eqlabel{massocc}
+\frac{\dd^2 N}{\dd\ln M\,\dd\ln a} &=& \massocc
+\end{eqnarray}
+where $N$ is the expected number of planets per G/K dwarf.
+The uncertainty in \eq{massocc} does not take into account the uncertainties
+in the semi-major axis or mass estimates or any systematic noise in the
+mass--radius relationship.
+Therefore, the specific result should be taken with the appropriate grain of
+salt but a result in this parameter space eases qualitative comparison with
+occurrence rates measured using different methods.
+
 \begin{floattable}

### 2016-07-14 peerless/occurrence.py
fixing occurrence bug with multiple mass columns

@@ -28,7 +28,7 @@ def compute_occurrence(inj, fits0, pgrid, rgrid,
     targets = targets[np.isfinite(targets.mass)]
     inj0 = pd.merge(inj, targets, left_on="kicid", right_on="kepid",
                     suffixes=["", "_stlr"])
-    inj0 = pd.DataFrame(inj0[np.isfinite(inj0.mass)])
+    inj0 = pd.DataFrame(inj0[np.isfinite(inj0.stlr_mass)])
 
     # Note this only works because we injected uniformly in log-period.
     results = []
@@ -41,10 +41,10 @@ def compute_occurrence(inj, fits0, pgrid, rgrid,
         # Geometric.
         fk = inj.dutycycle
         Tk = inj.dataspan
-        Mk = inj.mass
-        Rk = inj.radius_stlr
-        Qk = (4*np.pi/(_G * Mk))**(1./3) * (Rk + inj.radius * 0.0995)
+        Mk = inj.stlr_mass
+        Rk = inj.stlr_radius
         period = inj.period
+        Qk = period**(-2./3) * (4*np.pi/(_G * Mk))**(1./3) * (Rk + inj.radius)
 
         # Eccentric contribution to geometric transit probability.
         eccen = inj.e
@@ -52,17 +52,16 @@ def compute_occurrence(inj, fits0, pgrid, rgrid,
         Qe = (1.0 + eccen * np.sin(omega)) / (1.0 - eccen**2)
 
         # Window function.
-        Qt = period**(-2./3) * (1.0 - (1.0 - fk)**(Tk / period))
+        Qt = (1.0 - (1.0 - fk)**(Tk / period))
 
         # Re-weight the samples based on the injected radius distribution.
         x_samp = np.log(np.array(inj[x_name]))
-        x_bins = np.log(x_factor) + np.linspace(np.log(pmin), np.log(pmax), 20)
+        x_bins = np.log(x_factor) + np.linspace(np.log(pmin), np.log(pmax), 5)
         y_samp = np.log(np.array(inj[y_name]))
-        y_bins = np.log(y_factor) + np.linspace(np.log(rmin), np.log(rmax), 22)
-        n, _, _ = np.histogram2d(x_samp, y_samp, (x_bins, y_bins),
-                                 normed=True)
-        w = n[np.digitize(x_samp, x_bins) - 1,
-              np.digitize(y_samp, y_bins) - 1]
[…]

### 2016-07-14 peerless/occurrence.py
pep8

@@ -67,7 +67,7 @@ def compute_occurrence(inj, fits0, pgrid, rgrid,
         Q = (Qk * Qt * Qe * w)[rec].sum() / w.sum()
 
         m = ((pmin < fits0[x_name]) & (fits0[x_name] < pmax) &
-            (rmin < fits0[y_name]) & (fits0[y_name] < rmax))
+             (rmin < fits0[y_name]) & (fits0[y_name] < rmax))
         fits = fits0[m]
 
         N = len(fits)

### 2016-07-14 document/ms.tex

@@
 
-\section{The occurrence rate of long-period exoplanets}
+\section{The occurrence rate of long-period exoplanets}\sectlabel{occurrence}
 
@@
 \begin{eqnarray}\eqlabel{rate-density}
-\Gamma_V \equiv \frac{\dd N}{\dd\ln P\dd\ln R} &=&
+\Gamma_V \equiv \frac{\dd^2 N}{\dd\ln P\dd\ln R} &=&
     \frac{C(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max})}
@@
 parameters from $p(w_{\{P,\,R\}})$,
-\begin{eqnarray}
+\begin{eqnarray}\eqlabel{approxnorm}
 Z(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max}) &\approx&
@@
 Using the transit method, we do not directly measure the mass of the planet.
-Instead, we must rely on a mass--radius relationship constructed using
+Instead, we must rely on a mass--radius (M--R) relationship constructed using
 exoplanets with both mass and radius measurements \citep[for
@@
 
+Table~\ref{tab:masses} lists gives constraints on the predicted masses of the
+exoplanet candidates using the probabilistic M--R relationship from
+\citet{Chen:2016} and taking uncertainties in the planet radius and
+statistical uncertainties in the M--R parameters.
+We compared the predictions with the predictions from \citet{Wolfgang:2016}
+and found similar values with smaller uncertainties and chose to use the
+\citet{Chen:2016} relationship because it was more conservative in the
+relevant range of parameter space.
+
 A detailed discussion of the systematic effects introduced by the use of a
-mass--radius relationship is beyond the scope of this \paper\ but it is worth
+M--R relationship is beyond the scope of this \paper\ but it is worth
 noting that all published relationships are based on exoplanets much closer to
 their host star than any of the candidates discussed here.
-
-We find that the mean occurrence rate density in the range $0.01\,M_\mathrm{J}
-\le M < 20\,M_\mathrm{J}$ and $1.5\unit{au} \le a < 9\unit{au}$ is
+This effect would probably cause the masses of these cool planets to be
+systematically underestimated.
+
+Using the same M--R relationship, we can also compute the completeness of our
+transit search as a function of planet mass and orbital semi-major axis.
+This function is plotted in \dfmfig{completeness-am} with the same color
+scheme as \dfmfig{completeness}.
+These injections and the predicted masses and measured semi-major axes of the
+candidates can then be used to estimate the occurrence rate in
+mass--semi-major axis units using the method from \sect{occurrence}.
+One small change to \eq{approxnorm} is necessary to account for the fact that
+the injections were not made uniformly in $\ln M$ and $\ln a$.
+We numerically estimate the prior distribution in mass and semi-major axis
+from which the injections were drawn $\tilde{p}(\ln a,\,\ln M)$ and
+\eq{approxnorm} becomes
+\begin{eqnarray}
+Z(a_\mathrm{min},\,a_\mathrm{max};\,M_\mathrm{min},\,M_\mathrm{max}) &\approx&
+    \frac{K}{J}\,\sum_{j=1}^{J}
+    \frac{Q_k(w^{(j)})}{\tilde{p}(\ln a^{(j)},\,\ln M^{(j)})} \quad.
+\end{eqnarray}
+Using this result, we find that the mean occurrence rate density in the range
+$0.01\,M_\mathrm{J} \le M < 20\,M_\mathrm{J}$ and $1.5\unit{au} \le a <
+9\unit{au}$ is
 \begin{eqnarray}\eqlabel{massocc}
@@
 \tabletypesize{\footnotesize}
-\caption{The mass and semi-major axis estimates for the candidates from
-Table~\ref{tab:catalog} \label{tab:masses}}
+\caption{The predicted masses and radial velocity signals for the candidates
+from Table~\ref{tab:catalog} \label{tab:masses}}
 \include{masstab}

### 2016-07-14 document/ms.tex
FP text

@@
 \newcommand{\emcee}{\project{emcee}}
+\newcommand{\exosyspop}{\project{exosyspop}}
 
@@
 
-Various configurations of grazing or blended eclipsing binaries can mimic the
-signal of a transiting planet \citep{}. The occurrence rate calculation
-presented in the preceding section assumes that none of the planet
-candidates identified in this work are caused by such astrophysical false
-positives.  In this Section we explore the validity of this assumption.
+Various configurations of eclipsing binary stars can mimic the signal of a
+transiting planet \citep{}.  However, the occurrence rate calculation
+presented in the preceding section assumes no astrophysical false positives
+among the candidates identified in this work.  In this Section we explore the
+validity of this assumption.
+
+While an eclipsing binary (EB) typically produces a photometric dip much
+deeper than a transiting planet, the depth of the signal may be comparable to
+that of a planet if the eclipse is grazing, or if the EB only comprises a small
+fraction of the total light in the photometric aperture---a so-called blended
+eclipsing binary (BEB).  Additionally, if a binary star has an eccentric
+orbit, it may be oriented so as to present only a secondary occultation and
+not a primary eclipse, causing a shallow and potentially flat-bottomed
+photometric dip without an accompanying tell-tale deep primary signal.
+
+To determine to what extent the catalog of detections presented in this work
+may contain such false positives, we simulate populations of detected signals
+to predict how many we should expect.  To accomplish this, we use the python
+package \exosyspop\ \citep{Morton:2016b}, which we developed for this
+purpose.
+
+With \exosyspop\, one can define the parameters of a population model and
+generate synthetic catalogs according to the model (and the parameters of a
+survey) very efficiently.  For example, a population of EBs may be defined by
+a binary fraction, power-law distributions in mass ratio and period (within
+given bounds), and a beta distribution for eccentricity.  This population,
+initialized with a catalog of target stars (each of which has a duty cycle and
+total span of observation), may then be ``observed,'' returning a catalog of
+objects potentially detectable via either primary or secondary eclipse
+(according to randomly oriented orbital geometries).  This synthetic catalog
+includes signal-to-noise estimates of both the primary and secondary eclipses,
+the number of detected primary and secondary eclipses, and the trapezoidal
+shape parameters (depth, duration, and ingress-to-duration ratio, as defined
+in \citet{Morton:2012}) of each detection.
+
+In order to predict how many EBs or BEBs we might expect to detect in this 
+particular search of \kepler\ data, we first need to choose reasonable parameters
+for the binary star population.  To do this, we calibrate the population 
+parameters using the catalog of detected \kepler\ eclipsing binaries.  We
+find that a binary fraction of 15\% between periods of 20 days and 25 years, with
+periods distributed as $f(P) \sim P^{-1.1}$ and eccentrities distributed according
+to $\beta(0.8, 2.0)$ is able to reproduce well both the number and period 
+distribution of
+
+The \kepler\
+EB catalog contains 698 EBs with periods between 20 and 1000 days
+
+The first step in determining EBs and BEBs
+
+The scenarios typically considered in \kepler\ false positive analysis
+\citep[][e.g.]{Morton:2016} are unblended eclipsing binary stars (EB),
+background/foreground chance-aligned eclipsing binaries (BEB), and
+hierarchical triple eclipsing binaries (HEB).  In this work, where
+we are concerned with long-period signals, we do not consider the HEB
+scenario, as most known hierarchical stellar systems have two components on
+relatively short orbits \citep{}.
 

### 2016-07-15 peerless/occurrence.py
adding calc of or for N-1

@@ -72,6 +72,7 @@ def compute_occurrence(inj, fits0, pgrid, rgrid,
 
         N = len(fits)
         int_rate = N / (Q * len(targets))
+        int_rate_minus = (N - 1) / (Q * len(targets))
         vol = (np.log(pmax) - np.log(pmin)) * (np.log(rmax) - np.log(rmin))
 
         results.append(OrderedDict([
@@ -84,6 +85,8 @@ def compute_occurrence(inj, fits0, pgrid, rgrid,
             ("normalization", Q),
             ("rate_density", int_rate/vol),
             ("rate_density_uncert", int_rate/vol/np.sqrt(N)),
+            ("rate_density_minus", int_rate_minus/vol),
+            ("rate_density_minus_uncert", int_rate_minus/vol/np.sqrt(N)),
         ]))
 
     return pd.DataFrame(results)

### 2016-07-15 document/ms.tex

@@
 to $\beta(0.8, 2.0)$ is able to reproduce well both the number and period 
-distribution of
-
-The \kepler\
-EB catalog contains 698 EBs with periods between 20 and 1000 days
-
-The first step in determining EBs and BEBs
+distribution of observed \kepler\ EBs between 20 and 1000 days.  We thus fix these
+binary star population parameters for our subsequent EB and BEB simulations.
 

### 2016-07-15 document/ms.tex
intro words

@@
 \newcommand{\tess}{\project{TESS}}
+\newcommand{\plato}{\project{PLATO}}
 \newcommand{\pdc}{\project{PDC}}
@@
 
-% EB catalog: \citep{Kirk:2016}
-
-% Microlensing OR: \citep{Shvartzvald:2016}
-
-Data from the \kepler\ Mission has been used to discover thousands of
-transiting exoplanets.
+Data from the \kepler\ Mission \citep{Borucki:2011} has been used to discover
+thousands of transiting exoplanets.
 The systematic nature of these discoveries and careful quantification of
@@
 So far, these results have been limited to relatively short orbital periods
-because existing transit search methods require the observation of multiple
-transits within the baseline of the data.
+because existing transit search methods require the observation of at least
+three transits within the baseline of the data.
 For \kepler, with a baseline of about four years, this sets an absolute upper
@@
 
+Before the launch of the \kepler\ Mission, it was predicted that the nominal
+mission would discover at least 10 exoplanets with only one or two observed
+transits \citep{Yee:2008} and subsequent searches for these signals have
+already been more fruitful than expected \citep{Wang:2015, Uehara:2016}.
+However, the systematic study of the population of long-period exoplanets
+found in the \kepler\ data has, so far, been limited because of the
+substantial technical challenge and the subtleties of interpretation.
+Any single transit events discovered in the \kepler\ light curves are
+interesting in their own right but the development of a method for the
+discovery of planets with orbital periods longer than the survey baseline are
+crucial for the future of the study of exoplanets via the transit method.
+All future transit surveys have shorter observational baselines than the
+\kepler\ Mission (\KT, \citealt{Howell:2014}; \tess, \citealt{Ricker:2015};
+\plato, \citealt{Rauer:2014}).
+The methodology presented in the following pages can be modified to be applied
+to these forthcoming data sets as they are collecting in the upcoming years.
+
 A study of the population of long-period transiting planets complements
@@
 direct imaging \citep[for example][]{Bowler:2016}.
-
-It is possible to discover long-period planets like this using targeted radial
-velocity (RV) surveys
-
-but the cost of implementing a systematic RV search is
-substantially higher than searching the existing and forthcoming photometric
-data for single transits.
+Exoplanets with both mass and radius measurements can be used to study
+planetary compositions and the formation of planetary systems \citep[for
+example][]{Weiss:2014, Rogers:2015, Wolfgang:2016}.
+The existing catalog of exoplanets with measured densities is sparsely
+populated at long orbital periods and discoveries with the transit method are
+compelling targets for follow-up observations.
+Furthermore, even at long orbital periods, the \kepler\ light curves should be
+sensitive to smaller planets than the current state-of-the-art RV surveys.
 
@@
 \begin{floattable}
-\begin{deluxetable}{ccc}
+\begin{deluxetable}{cccc}
 \tabletypesize{\footnotesize}
@@
 \include{ortab}
-\tablenotetext{a}{See \eq{rate-density}}
+\tablenotetext{a}{$\Gamma_V = \dd^2 N/\dd\ln P\dd\ln R$; see \eq{rate-density}}
+\tablenotetext{b}{$\Gamma_V$ computed assuming that one candidate is a false
+positive}
 \tablecomments{These values are computed in the period range 2--25~years.}

### 2016-07-15 document/ms.tex
intro words and formatting

@@
 \bibliographystyle{aasjournal}
+
+\usepackage{endnotes}
+\let\footnote=\endnote
 
@@
 
-\widowpenalty=1000
-\clubpenalty=1000
+\widowpenalty=100000
+\clubpenalty=100000
 
@@
 We apply this method to a subset of the archival data from the \kepler\
-Mission and produce a catalog of discoveries.
+Mission, release a catalog of exoplanet candidates, and estimate the
+occurrence rate of long-period exoplanets.
+We finish by discussing the potential effects of false positives, the
+prospects for radial velocity follow-up of these candidates, and compare to
+calculated occurrence rate to results based on discoveries using different
+planet discovery methods.
 
@@
 
-\newpage
 \appendix
@@
 
+\theendnotes
+
 \end{document}

### 2016-07-15 document/ms.tex
updating solar system in sample plot

@@
 {\noindent\footnotesize\textsc{\@journalinfo}}\par
-{\noindent\scriptsize Preprint typeset using \LaTeX\ style AASTeX6 with
-modifications by David W. Hogg and Daniel Foreman-Mackey.
+{\noindent\scriptsize Preprint typeset using \LaTeX\ style AASTeX6\\
+With modifications by David W. Hogg and Daniel Foreman-Mackey\\
+See the last page for endnotes
 }\par\vspace*{-\baselineskip}\vspace*{0.625in}
@@
 \newcommand{\dfmtodo}[1]{\todo{DFM}{red}{#1}}
+\newcommand{\tdmtodo}[1]{\todo{TDM}{blue}{#1}}
 \newcommand{\hoggtodo}[1]{\todo{HOGG}{blue}{#1}}
@@
 
+\tdmtodo{Just a note that I've added your figure in at the end of this section
+--- DFM}
+
+In light of this result, we demonstrate the sensitivity of our measured
+occurrence rates on contamination by computing a second constraint on
+$\Gamma_V$ for each volume with one candidate removed.
+In this case, \eq{rate-density} would be replaced by
+\begin{eqnarray}
+\tilde{\Gamma}_V &\equiv&
+    \frac{C(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max})
+          - 1}
+         {Z(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max})}
+\quad.
+\end{eqnarray}
+These updated rates are listed in Table~\ref{tab:occurrence}.
+
+\begin{figure*}[htbp]~\\
+\begin{center}
+\includegraphics[width=\textwidth]{../prediction/shape_kdes.pdf}
+\end{center}
+\caption{%
+\dfmfiglabel{shape-kdes}}
+\end{figure*}
+
 \section{Comparison with the literature}\sectlabel{comparison}
@@
 It is a pleasure to thank
-\ldots
+So Hattori,
+Angie Wolfgang,
+and
+Hans-Walter Rix
 for helpful contributions to the ideas and code presented here.

### 2016-07-15 document/figures/full_sample.py

@@ -44,7 +44,7 @@ rad = np.array("2439.7 6051.8 6371.00 3389.5 69911 58232 25362 24622"
                .split(), dtype=float)
 period = np.array("0.2408467 0.61519726 1.0000174 1.8808476 11.862615 "
                   "29.447498 84.016846 164.79132".split(), dtype=float)
-ax.plot(period * 365, rad / rad[2], "o",  # color=COLORS["MODEL_2"],
+ax.plot(period * 365, rad / rad[2], "s",  # color=COLORS["MODEL_2"],
         ms=4, mec="none")
 ax.axvline(4.2*365 / 2., color="k", alpha=0.6)
 ax.axvline(4.2*365, color="k", ls="dashed", alpha=0.6)

### 2016-07-15 document/figures/completeness.py
completeness color map colors

@@ -64,10 +64,10 @@ ln_period_bins = np.linspace(np.log(2), np.log(25), 101)
 Y, X = np.meshgrid(ln_period_bins, ln_radius_bins, indexing="ij")
 Z = analytic_model(r.x, X + np.log(0.0995), Y + np.log(365.25))
 c = ax.pcolor(np.exp(ln_period_bins), np.exp(ln_radius_bins), Z.T,
-              cmap="viridis", vmin=0, vmax=1)
+              cmap="Blues", vmin=0, vmax=1)
 cbar = fig.colorbar(c)
 cbar.set_ticks([0.0, 0.2, 0.4, 0.6, 0.8, 1.0])
-ax.contour(np.exp(Y), np.exp(X), Z, [0.1, 0.3, 0.5, 0.7], colors="w")
+ax.contour(np.exp(Y), np.exp(X), Z, [0.1, 0.3, 0.5, 0.7], colors="k")
 ax.set_xscale("log")
 ax.set_yscale("log")
 ax.set_ylim(np.exp([X.min(), X.max()]))
@@ -102,7 +102,7 @@ X, Y = np.meshgrid(np.exp(ln_period_bins) / 365.25,
 fig = pl.figure(figsize=2*np.array(SQUARE_FIGSIZE))
 
 ax = pl.axes([0.1, 0.1, 0.6, 0.6])
-ax.pcolor(X, Y, 100*n.T, cmap="viridis", vmin=0, vmax=100)
+ax.pcolor(X, Y, 100*n.T, cmap="Blues", vmin=0, vmax=100)
 
 # Label the bins with their completeness percentages.
 for i, j in product(range(len(ln_period_bins)-1),
@@ -111,7 +111,7 @@ for i, j in product(range(len(ln_period_bins)-1),
     y = np.exp(0.5 * (ln_radius_bins[j] + ln_radius_bins[j+1])) / 0.0995
     ax.annotate(r"${0:.3f}$".format(n[j, i]),
                 (x, y), ha="center", va="center", alpha=1.0, fontsize=12,
-                color="white")
+                color="k")
 
 ax.set_xscale("log")
 ax.set_yscale("log")
@@ -189,7 +189,7 @@ X, Y = np.meshgrid(np.exp(ln_semimajor_bins) / 215.1,
 fig = pl.figure(figsize=2*np.array(SQUARE_FIGSIZE))
 
 ax = pl.axes([0.1, 0.1, 0.6, 0.6])
[…]

### 2016-07-15 document/ms.tex
a few words about FPs
describe point styles for dealing with B/W plots

@@
 \caption{%
-The catalog of long-period transiting exoplanet candidates (green) compared to
-the \kepler\ candidates (blue) and confirmed planets (black), and the Solar
-System (orange).
+The catalog of long-period transiting exoplanet candidates (green points with
+error bars) compared to the \kepler\ candidates (blue points) and confirmed
+planets (black points), and the Solar System (orange squares).
 The vertical dashed line indicates the full lifetime of the \kepler\ Mission;
@@
 These updated rates are listed in Table~\ref{tab:occurrence}.
+In each case, the results are consistent within the uncertainties but the
+difference can be used to get a qualitative sense of the systematic
+uncertainty introduced by false positives.
 

### 2016-07-15 document/figures/completeness.py
AU -> au

@@ -204,7 +204,7 @@ ax.set_xscale("log")
 ax.set_yscale("log")
 ax.set_xlim(X.min(), X.max())
 ax.set_ylim(Y.min(), Y.max())
-ax.set_xlabel("semi-major axis [AU]")
+ax.set_xlabel("semi-major axis [au]")
 ax.set_ylabel("$M_\mathrm{P} / M_\mathrm{J}$")
 ax.set_xticks([2, 4, 8])
 ax.get_xaxis().set_major_formatter(pl.ScalarFormatter())

### 2016-07-15 document/ms.tex
placeholder for follow-up section cc @davidwhogg

@@
 \tablenotetext{b}{$\Gamma_V$ computed assuming that one candidate is a false
-positive}
+positive; see \eq{rate-minus}}
 \tablecomments{These values are computed in the period range 2--25~years.}
@@
 In this case, \eq{rate-density} would be replaced by
-\begin{eqnarray}
+\begin{eqnarray}\eqlabel{rate-minus}
 \tilde{\Gamma}_V &\equiv&
@@
 exoplanets with both mass and radius measurements \citep[for
-example]{Weiss:2014, Wolfgang:2016, Chen:2016} to predict the expected masses
-of the transiting planets.
+example][]{Weiss:2014, Wolfgang:2016, Chen:2016} to predict the expected
+masses of the transiting planets.
 
@@
 
+\dfmtodo{COMPARE!}
+
 \begin{floattable}
@@
 \end{figure*}
+
+\section{Prospects for follow-up}\sectlabel{follow-up}
+
+A real concern about the detection of exoplanets from a single transit is that
+follow-up and confirmation is difficult.
+Since the period of the orbit is poorly constrained and transits are sparse,
+any prediction of a subsequent transit time will be too uncertain to schedule
+targeted photometric follow-up.
+Instead, follow-up using radial velocity and astrometry are more promising.
+
+\hoggtodo{Comments about GAIA follow-up}
 

### 2016-07-15 document/ms.tex
words about RV follow-up

@@
 A study of the population of long-period transiting planets complements
-parallel radial velocity \citep[RV; for example][]{Cumming:2008,
+parallel radial velocity \citep[for example][]{Cumming:2008,
 Knutson:2014, Bryan:2016}, microlensing \citep[for
@@
 Furthermore, even at long orbital periods, the \kepler\ light curves should be
-sensitive to smaller planets than the current state-of-the-art RV surveys.
+sensitive to smaller planets than the current state-of-the-art radial velocity
+surveys.
 
@@
 Instead, follow-up using radial velocity and astrometry are more promising.
+For both radial velocity and astrometry, there is information about the
+orbiting planets in measurements made at all times~--~not just during transit.
+This allows observations to be scheduled without a well constrained orbital
+period.
+Furthermore, follow-up of any of these candidates using radial velocity or
+astrometry would provide a measurement of the density of a planet that would
+be invaluable for the study of planetary compositions.
+
+Table~\ref{tab:masses} lists the posterior predictions for the semi-amplitude
+$K$ of the radial velocity signal produced by each candidate using the mass
+predictions from the previous section.
+Since the orbital periods are long, we also include a simple prediction for
+the slope of the radial velocity trend induced by this planet by taking the
+ratio of the semi-amplitude and the orbital period.
+Any radial velocity follow-up of the candidates presented here would be an
+ambitious undertaking because the stars are relatively faint and, in most
+cases, the radial velocity trends are small.
+Some candidates should, however, be within the reach of current
+state-of-the-art facilities.
 

### 2016-07-15 document/ms.tex
lots more FPP text

@@
 total span of observation), may then be ``observed,'' returning a catalog of
-objects potentially detectable via either primary or secondary eclipse
-(according to randomly oriented orbital geometries).  This synthetic catalog
-includes signal-to-noise estimates of both the primary and secondary eclipses,
-the number of detected primary and secondary eclipses, and the trapezoidal
-shape parameters (depth, duration, and ingress-to-duration ratio, as defined
-in \citet{Morton:2012}) of each detection.
+objects detectable via either primary or secondary eclipse (according to
+randomly oriented orbital geometries and accounting for observation duty cycle
+and data span).  This synthetic catalog includes signal-to-noise estimates of
+both the primary and secondary eclipses, the number of detected primary and
+secondary eclipses, and the trapezoidal shape parameters of each detection
+(depth, duration, and ingress-to-duration ratio, as defined in
+\citet{Morton:2012}).
 
@@
 parameters using the catalog of detected \kepler\ eclipsing binaries.  We
-find that a binary fraction of 15\% between periods of 20 days and 25 years, with
-periods distributed as $f(P) \sim P^{-1.1}$ and eccentrities distributed according
+find that a binary fraction of 25\% between periods of 20 days and 25 years with
+a log-flat period distribution and eccentrities distributed according
 to $\beta(0.8, 2.0)$ is able to reproduce well both the number and period
@@
 
-The scenarios typically considered in \kepler\ false positive analysis
-\citep[][e.g.]{Morton:2016} are unblended eclipsing binary stars (EB),
-background/foreground chance-aligned eclipsing binaries (BEB), and
-hierarchical triple eclipsing binaries (HEB).  In this work, where
-we are concerned with long-period signals, we do not consider the HEB
-scenario, as most known hierarchical stellar systems have two components on
-relatively short orbits \citep{}.
-
-\tdmtodo{Just a note that I've added your figure in at the end of this section
---- DFM}
+To simulate synthetic populations of EB detections, we assign binary stars  to
+the \kepler\ target list described in \sect{target-selection} according to the
+above EB population parameters.  We consider an EB to be detected if it
+presents fewer than three eclipses (either primary or secondary, but not
+both), if the signal-to-noise ratio is $>$15, and the duration of the
+detected eclipse is $<$2.5\,d.  In 100 realizations of these synthetic 
+observations, we see $7.2 \pm 2.5$ single- or double-eclipsing EB signals.
+
+To simulate BEBs, we assume an exponentially varying background field star
+density across the \kepler\ field, from 0.005\,arcsec$^{-2}$ at a Galactic
+latitude $b=20$ to 0.05\,arcsec$^{-2}$ at $b=5$ (matching up well with the
+simulations of \citep{Morton:2011} at many different Galactic latitudes). Each
+\kepler\ target star is then assigned a number of background stars drawn from
+a Poisson distribution with mean given by the expected number of stars to be
+found within a circle of 4\,arcsec radius, given the  appropriate density at
+its Galactic lattitude.   We draw the specific background stars from a
+TRILEGAL \citep{Girardi:2005}  field star simulation toward the center of the
+\kepler\ field.  Binary companions are then assigned to these background stars
+according to the same stellar binary population distribution as the EB
+population above, and synthetic detected populations  are ``observed''
+according to the same rules (accounting appropriately for the diluted eclipse
+depths in the \kepler\ bandpass).  In 100 synthetic observations, we see an
+average of only 0.41 detected BEBs.
+
+These results suggest that we might certainly expect to see some unblended
+eclipsing binary signals in our search.  However, this does not mean that  we
+should fear that $\sim$7 of the planet candidates might be EBs. Rather, we can
+instead inspect the synthetic observation simulations in more detail; in
+particular, we can analyze the shape distribution of the different scenarios and
+compare them with the observed shapes of the actual \kepler\ detections in order
+to quantify the probability that each of them may be a false positive.
+
+Following the method of \citet{Morton:2012} used to compute false positive
+probabilities for the regular \kepler\ KOI catalogs \citet{Morton:2016}, we
+can calculate the posterior probability for each of our candidates to belong
+to each of the three scenarios we consider (EB, BEB, or planet) as follows:
+\begin{eqnarray} 
+{\rm Pr}_i = \frac{\pi_i \mathcal L_i}{\sum_{j} \pi_j \mathcal L_j}, 
+\end{eqnarray} 
+where the $\pi$ factors are the hypothesis priors, $\mathcal L$ are
+the hypothesis likelihoods, and the sum over $j$ is over all the hypotheses.
+In this case, we determine the relative hypothesis priors from the synthetic 
+observations, using the mean numbers of ``observed'' EBs (7.2) and BEBs (0.4), 
+and choosing the expected number of planets to be 12.  We calculate the hypothesis
+likelihoods using the depth/duration distributions of synthetic populations
+of each scenario and evaluating these distributions at the observed depths and 
+durations of each candidate signal.  To estimate the expected shape distribution
+of the planet scenario, we define a custom \exosyspop\ population of planets
+according to the two-bin population model described by \ref{tab:occurrence} and 
+generate a population of 1000 detected signals.
+
+We list the probabilities for each of our candidates to belong to each
+hypothesis in \ref{tab:fpp}.  We find that the two deepest signals in our
+candidate catalog (9306307 and  10602068) are very likely to be EBs, though we
+note that this result may be dominated by the fact that our planet population
+is fixed to have a maximum radius of 1\,$R_{\rm J}$.  Most of the rest of the
+candidates  have false positive probabilities below 10\%.  We do note that as
+discussed in \sect{}, 4754460 (which we calculate to have a 5\% false positive
+probability) does show a partial deep eclipse right at the end of the \kepler\
+data that indicates that it is most likely an EB.  Apart from this, the expected 
+number of false positives among the candidates with $R < R_{\rm J}$, according
+to these calculations, is about one.
 

### 2016-07-16 document/ms.tex
Adding @davidwhogg's words becuase he's bad at git

--- 2016-07-15 document/ms.tex
@@
 \newcommand{\plato}{\project{PLATO}}
+\newcommand{\gaia}{\project{Gaia}}
 \newcommand{\pdc}{\project{PDC}}
@@
 
+In priniciple the \gaia\ Mission will be very sensitive to the astrometric
+wobble produced by a long-period exoplanet \citep{Perryman:2014}.
+To leading order, the astrometric signal strength is proportional to the
+semi-major axis of the stellar (primary) reflex motion in angular units.
+That is, detectability is related to the angle $\alpha$ given by
+\begin{eqnarray}
+alpha &=& \frac{a}{D}\,\frac{M_{\mathrm p}}{M_{\mathrm s}} \quad ,
+\end{eqnarray}
+% obviously fix to your notation!
+where $a$ is the semi-major axis, $D$ is the distance from the observer to the
+primary, and $M_{\mathrm{p}}/M_{\mathrm{s}}$ is the planet-to-star mass ratio.
+
+The single-visit precision of \gaia\ will vary with magnitude but is expected
+to be on the order of 40\,$\mu$as at these magnitudes \hoggtodo{cite
+something}.
+In detail the confidence with which an exoplanet can be detected or measured
+in the final \gaia\ data depends on this precision, the number of crossings of
+the star through the \gaia\ focal plane, and details of how the projected
+orbit is sampled by the time history of the focal-plane crossings.
+However, it is not expected that \gaia\ can detect or measure precisely
+exoplanet-induced astrometric wobbles that are much smaller in amplitude than
+the single-visit precision \citep{Perryman:2014}.
+
+The primary stars in the \kepler\  Field are typically at distances of $\sim
+500$\,pc, and typical mass ratios are in the $10^{-4}$ range.
+We therefore expect astrometric amplitudes in the 0.3 to 3\,$\mu$as range.
+These planets will not be detectable or measurable in the \gaia\ data under
+any circumstances.
+However, similar planets around closer stars \emph{will} be detectable with
+\gaia.
+This means that there will be a comparable exoplanet occurrence rate
+measurement from the \gaia\ data.
+It also means that many of the discoveries of the \tess\ Mission will be
+followed up and precisely measured by the \gaia\ Mission.
+
 \section{Discussion}\sectlabel{discussion}

### 2016-07-16 document/figures/model_comp.py

@@ -14,7 +14,8 @@ from peerless.search import search
 models = [
     ("variability", "gp", 7220674, 0),
     ("step", "step", 8631697, 0),
-    ("box", "box2", 5521451, 0),
+    ("box", "box1", 9411471, 0),
+    # ("box", "box2", 5521451, 0),
     ("transit", "transit", 8505215, 0),
 ]
 

### 2016-07-16 document/ms.tex
adding references for @timothydmorton's section

@@
 \begin{floattable}
-\begin{deluxetable}{ccccccccl}
+\begin{deluxetable}{cccccccccl}
 \tabletypesize{\footnotesize}
@@
 Various configurations of eclipsing binary stars can mimic the signal of a
-transiting planet \citep{}.  However, the occurrence rate calculation
+transiting planet.  However, the occurrence rate calculation
 presented in the preceding section assumes no astrophysical false positives
@@
 of the planet scenario, we define a custom \exosyspop\ population of planets
-according to the two-bin population model described by \ref{tab:occurrence} and 
+according to the two-bin population model described by Table~\ref{tab:occurrence} and
 generate a population of 1000 detected signals.
@@
 We list the probabilities for each of our candidates to belong to each
-hypothesis in \ref{tab:fpp}.  We find that the two deepest signals in our
+hypothesis in Table~\ref{tab:catalog}.  We find that the two deepest signals in our
 candidate catalog (9306307 and  10602068) are very likely to be EBs, though we
@@
 candidates  have false positive probabilities below 10\%.  We do note that as
-discussed in \sect{}, 4754460 (which we calculate to have a 5\% false positive
+discussed in \sect{catalog}, 4754460 (which we calculate to have a 5\% false positive
 probability) does show a partial deep eclipse right at the end of the \kepler\
@@
 \begin{floattable}
-\begin{deluxetable}{cccccccc}
+\begin{deluxetable}{ccccccccc}
 \tabletypesize{\footnotesize}
@@
 
-\hoggtodo{Comments about GAIA follow-up}
-
 In priniciple the \gaia\ Mission will be very sensitive to the astrometric
@@
 \begin{eqnarray}
-alpha &=& \frac{a}{D}\,\frac{M_{\mathrm p}}{M_{\mathrm s}} \quad ,
+\alpha &=& \frac{a}{D}\,\frac{M_{\mathrm p}}{M_{\mathrm s}} \quad ,
 \end{eqnarray}
@@
 measurement from the \gaia\ data.
-It also means that many of the discoveries of the \tess\ Mission will be
-followed up and precisely measured by the \gaia\ Mission.
+It also means that many of the discoveries of the \KT\ and \tess\ missions
+will be followed up and precisely measured by the \gaia\ Mission.
 

### 2016-07-16 document/ms.tex
hogg says assert
model comparison plot labels

@@
 posterior-median transit model over-plotted (orange).
+The y-axis shows the relative apparent flux of the light curve in parts per
+thousand (ppt).
 Candidates with two transits are folded on the posterior-median period.
@@
 The single-visit precision of \gaia\ will vary with magnitude but is expected
-to be on the order of 40\,$\mu$as at these magnitudes \hoggtodo{cite
-something}.
+to be on the order of 40\,$\mu$as at these magnitudes.
 In detail the confidence with which an exoplanet can be detected or measured

### 2016-07-16 document/figures/model_comp.py

@@ -12,14 +12,14 @@ import matplotlib.pyplot as pl
 from peerless.search import search
 
 models = [
-    ("variability", "gp", 7220674, 0),
     ("step", "step", 8631697, 0),
+    ("variability", "gp", 7220674, 0),
     ("box", "box1", 9411471, 0),
     # ("box", "box2", 5521451, 0),
     ("transit", "transit", 8505215, 0),
 ]
 
-fig, axes = pl.subplots(2, 2, figsize=(8, 8))
+fig, axes = pl.subplots(2, 2, figsize=(8.8, 8))
 
 os.makedirs("cache", exist_ok=True)
 for a, ax, (disp, name, kicid, peak_id) in zip("abcd", axes.flatten(), models):
@@ -46,16 +46,24 @@ for a, ax, (disp, name, kicid, peak_id) in zip("abcd", axes.flatten(), models):
     x, y = peak["data"][:2]
     m = (rng[0] < x) & (x < rng[1])
     x0 = np.linspace(rng[0], rng[1], 500)
-    ax.plot(24*(x[m] - t0), y[m], ".", color=COLORS["DATA"])
+    mean = np.median(y[m])
+    ax.plot(24*(x[m] - t0), (y[m] - mean)*1e3, ".", color=COLORS["DATA"])
 
     mu = gp.predict(y0, x0, return_cov=False)
-    ax.plot(24*(x0 - t0), mu, color=COLORS["MODEL_2"], lw=2.5, alpha=0.8)
+    ax.plot(24*(x0 - t0), (mu - mean) * 1e3, color=COLORS["MODEL_2"], lw=2.5,
+            alpha=0.8)
     ax.annotate("({0}) {1}".format(a, disp),
                 xy=(0, 0), xycoords="axes fraction",
                 xytext=(5, 12), textcoords="offset points")
 
+    mn, mx = (np.min(y[m]) - mean) * 1e3, (np.max(y[m]) - mean) * 1e3
+    delta, mid = 0.5 * 1.1 * (mx - mn), 0.5 * (mx + mn)
+    ax.set_ylim(mid - delta, mid + delta)
     ax.set_xlim(24*(rng - t0))
-    ax.set_yticklabels([])
+    ax.yaxis.set_major_locator(pl.MaxNLocator(5))
+    if a in "ac":
+        ax.set_ylabel("relative flux [ppt]")
+        ax.yaxis.set_label_coords(-0.25, 0.5)
[…]

### 2016-07-16 document/ms.tex
some words about the box model

@@
 \newcommand{\modelname}[1]{{\textsf{#1}}}
+\newcommand{\datareleaseurl}{url to be added at submission}
 
@@
 best fit impact parameter is less than $1 - R_\mathrm{P} / R_\star$.
+
+Since the search procedure described here was tuned to discover transit
+signals, we do not consider the distribution or potential astrophysical nature
+of any models besides the \modelname{transit} model.
+In the future, it would be interesting to relax this goal and investigate the
+other model classes because, for example, the \modelname{box} model is
+probably sensitive to other astrophysical phenomena like secondary eclipses.
+In a cursory investigation it is clear that the majority of signals labeled
+\modelname{box} in our analysis are noise but a subset are likely to be
+astrophysical in nature.
 

### 2016-07-16 peerless/occurrence.py
Adding table of candidates rejected for centroid shifts and v-shape

@@ -87,6 +87,10 @@ def compute_occurrence(inj, fits0, pgrid, rgrid,
             ("rate_density_uncert", int_rate/vol/np.sqrt(N)),
             ("rate_density_minus", int_rate_minus/vol),
             ("rate_density_minus_uncert", int_rate_minus/vol/np.sqrt(N)),
+            ("rate", int_rate),
+            ("rate_uncert", int_rate/np.sqrt(N)),
+            ("rate_minus", int_rate_minus),
+            ("rate_minus_uncert", int_rate_minus/np.sqrt(N)),
         ]))
 
     return pd.DataFrame(results)

### 2016-07-16 document/ms.tex
adding exosyspop footnote

@@
 
-\widowpenalty=100000
-\clubpenalty=100000
+\widowpenalty=10000
+\clubpenalty=10000
 
@@
 
-The candidate in the light curve of KIC~4754460 as an individual transit
+Five candidate transit events in the light curves of four targets were
+rejected because of a significant centroid shift or a large impact parameter.
+These events are probably astrophysical eclipses from binary star systems that
+were not found by previous studies of long-period eclipsing binary systems.
+We do not consider these events further in the rest of this \paper\ but
+Table~\ref{tab:rejects} lists these events and their properties for
+posterity.
+
+The candidate in the light curve of KIC~4754460 is an individual transit
 candidate but another deeper eclipse can be found at a KBJD of 1587.13; right
@@
 \end{figure*}
+
+\begin{floattable}
+\begin{deluxetable}{ccccl}
+\tabletypesize{\footnotesize}
+\caption{The signals rejected with a centroid shift or large impact parameter
+\label{tab:rejects}}
+\include{rejecttab}
+\end{deluxetable}
+\end{floattable}
 
@@
 may contain such false positives, we simulate populations of detected signals
-to predict how many we should expect.  To accomplish this, we use the python
-package \exosyspop\ \citep{Morton:2016b}, which we developed for this
-purpose.
+to predict how many we should expect.  To accomplish this, we use the Python
+package
+\exosyspop\footnote{\url{https://github.com/timothydmorton/exosyspop}}, which
+we developed for this purpose.
 

### 2016-07-16 document/ms.tex
words about integrated rate

@@
 \include{ortab}
-\tablenotetext{a}{$\Gamma_V = \dd^2 N/\dd\ln P\dd\ln R$; see \eq{rate-density}}
-\tablenotetext{b}{$\Gamma_V$ computed assuming that one candidate is a false
-positive; see \eq{rate-minus}}
+\tablenotetext{a}{The rate density is given by \eq{rate-density} and the
+value in parentheses is computed assuming one candidate is a false positive
+(\eqalt{rate-minus}).}
+\tablenotetext{b}{The integrated rate is computed by integrating the rate
+density over the bin. Note that the first two rows do not sum to the last row
+because each row is computed assuming that the rate density is uniform
+across the bin.}
 \tablecomments{These values are computed in the period range 2--25~years.}

### 2016-07-17 document/figures/completeness.py
print mean KOI completeness

@@ -4,7 +4,6 @@ from __future__ import division, print_function
 
 from peerless.plot_setup import SQUARE_FIGSIZE, COLORS
 
-# import numpy as np
 import pandas as pd
 from itertools import product
 import matplotlib.pyplot as pl
@@ -13,10 +12,21 @@ from scipy.optimize import minimize
 from autograd import grad
 import autograd.numpy as np
 
+from peerless.catalogs import KOICatalog
+
 
 inj = pd.read_hdf("../../results/injections-with-mass.h5", "injections")
 inj = inj[inj.ncadences > 0]
 rec = inj[inj.recovered]
+
+kois = set(KOICatalog().df.kepid)
+
+inj_koi = inj[inj.kicid.isin(kois)]
+rec_koi = rec[rec.kicid.isin(kois)]
+inj_no_koi = inj[~inj.kicid.isin(kois)]
+rec_no_koi = rec[~rec.kicid.isin(kois)]
+print("Completeness for KOIs: {0}".format(len(rec_koi) / len(inj_koi)))
+print("Completeness for non-KOIs: {0}".format(len(rec_no_koi)/len(inj_no_koi)))
 
 
 def analytic_model(params, ln_radius, ln_period):

### 2016-07-17 document/ms.tex
typo
comments about multis

@@
 
+Of the \numcands\ candidates, \numinner\ have known inner planets with three
+or more observable transits \citep{Coughlin:2016}.
+Given the fact that only \numkois\ of the \numtargets\ targets have known
+planets, this means that of the systems with known inner planets, \fracinner\
+have outer transiting planets with one or two transits detectable by our
+search.
+This fraction is nearly a factor of 20 larger than the same number for targets
+with no known inner transiting planets: $\fracnoinner$.
+This difference cannot be accounted for by differences in completeness between
+targets with known planets and without because the average detection
+efficiency for both populations is consistent within sampling uncertainty.
+This suggests that these long-period planets are preferentially aligned with
+the plane of any inner planets but a more detailed analysis would be needed to
+make a quantitative statement \citep[see, for example,][]{Tremaine:2012,
+Fang:2012, Ballard:2016, Moriarty:2015}.
+
 Five candidate transit events in the light curves of four targets were
@@
 Z(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max}) &\approx&
-    \frac{K}{J}\,\sum_{j=1}^{J} Q_k(w^{(j)})
+    \frac{K\,V}{J}\,\sum_{j=1}^{J} Q_{k_j}(w^{(j)})
 \end{eqnarray}

### 2016-07-17 document/ms.tex
words about integrated occurrence rates

--- 2016-07-16 document/ms.tex
@@
 
+Of the \numcands\ candidates, \numinner\ have known inner planets with three
+or more observable transits \citep{Coughlin:2016}.
+Given the fact that only \numkois\ of the \numtargets\ targets had previously
+known planets, this means that systems with short-period transiting planets
+are nearly a factor of 20 more likely to host long-period planets accessible
+by our method than systems with no known inner transiting planets.
+This difference cannot be accounted for by differences in completeness between
+targets with known planets and without because the average detection
+efficiency for both populations is consistent within sampling uncertainty.
+Qualitatively, this suggests that these long-period planets occur with a
+higher frequency in multi-planet systems or are preferentially aligned with
+the plane of any inner planets but a more detailed analysis would be needed to
+make a quantitative statement \citep[see, for example,][]{Tremaine:2012,
+Fang:2012, Ballard:2016, Moriarty:2015}.
+
 Five candidate transit events in the light curves of four targets were
@@
 Z(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max}) &\approx&
-    \frac{K}{J}\,\sum_{j=1}^{J} Q_k(w^{(j)})
+    \frac{K\,V}{J}\,\sum_{j=1}^{J} Q_{k_j}(w^{(j)})
 \end{eqnarray}
 where the sum is over all injections in the volume $V$.
-
-Using the injection results from \sect{completeness} and the catalog of
-discoveries from \sect{catalog}, we compute the occurrence rate in the period
-range 2 to 25 years and in two radius bins between 0.1 and
-$1.0\,R_\mathrm{J}$.
-The calculated occurrence rates are listed in Table~\ref{tab:occurrence}.
 
@@
 statistical uncertainties should not be taken too seriously.
+
+Using the injection results from \sect{completeness} and the catalog of
+discoveries from \sect{catalog}, we compute the occurrence rate in the period
+range 2 to 25 years and in two radius bins between 0.1 and
+$1.0\,R_\mathrm{J}$.
+The calculated occurrence rates are listed in Table~\ref{tab:occurrence}.
+Integrating the two bin model in this range, we find an expected occurrence
+rate of
+\begin{eqnarray}
+N_{0.1\,R_\mathrm{J}-1\,R_\mathrm{J},\,2\unit{yr}-25\unit{yr}} &=&
+    \intocc \unit{planets}
+\end{eqnarray}
+per G/K dwarf with radii in the range $0.1\,R_\mathrm{J}-1\,R_\mathrm{J}$ and
+periods in the range $2\unit{yr}-25\unit{yr}$.
+This result is qualitatively consistent with the Solar System where there is
+one planet~--~Jupiter~--~in this parameter range and Saturn is just outside
+the range with an orbital period of 29~years.
+In \sect{comparison}, we compare with similar occurrence rate estimates from
+the literature.
 

### 2016-07-17 document/ms.tex
comparisons

@@
 velocity, microlensing, and direct imaging surveys.
-These methods all measure the occurrence rate in units of mass and semi-major
-axis instead of radius and period.
-Using the transit method, we do not directly measure the mass of the planet.
-Instead, we must rely on a mass--radius (M--R) relationship constructed using
-exoplanets with both mass and radius measurements \citep[for
-example][]{Weiss:2014, Wolfgang:2016, Chen:2016} to predict the expected
-masses of the transiting planets.
+These methods all measure the occurrence rate as a function of planet mass
+instead of radius.
+Using the transit method, however, we do not directly measure the mass of the
+planet.
+Therefore, to compare our results with the literature, we must rely on a
+mass--radius (M--R) relationship constructed using exoplanets with both mass
+and radius measurements \citep[for example][]{Weiss:2014, Wolfgang:2016,
+Chen:2016} to predict the expected masses of the transiting planets.
 
@@
 \begin{eqnarray}\eqlabel{massocc}
-\frac{\dd^2 N}{\dd\ln M\,\dd\ln a} &=& \massocc
+\frac{\dd^2 N}{\dd\ln M\,\dd\ln a} &=& \masssemiocc
 \end{eqnarray}
 where $N$ is the expected number of planets per G/K dwarf.
-The uncertainty in \eq{massocc} does not take into account the uncertainties
-in the semi-major axis or mass estimates or any systematic noise in the
-mass--radius relationship.
-Therefore, the specific result should be taken with the appropriate grain of
-salt but a result in this parameter space eases qualitative comparison with
-occurrence rates measured using different methods.
-
-\dfmtodo{COMPARE!}
+This result and the equivalent result as a function of planet mass and orbital
+period are listed in Table~\ref{tab:occrates}.
+
+The uncertainty in \eq{massocc} and Table~\ref{tab:occrates} does not take
+into account the uncertainties in the mass estimates or any systematic noise
+in the mass--radius relationship.
+Therefore, these specific results should be taken with the appropriate grain
+of salt but predictions in these parameter spaces ease comparison with
+occurrence rates measured computed using different methods.
+
+\citet{Clanton:2014} studied the occurrence rate of long-period giant planets
+orbiting M-dwarfs by combining results from radial velocity and microlensing
+surveys.
+In the range $10^3\unit{days}<P<10^4\unit{days}$ and
+$10\,M_\oplus<M<10^4\,M_\oplus$, they find a mean occurrence rate density
+of
+\begin{eqnarray}
+\frac{\dd^2 N}{\dd\ln M/M_\mathrm{J}\,\dd\ln P/\unit{yr}}
+    &\lesssim& 0.026
+\end{eqnarray}
+per M-dwarf.
+This result is slightly lower than our estimated rate for a similar range of
+masses and periods but around G/K dwarfs.
+This difference is consistent with previous results that cooler stars host
+fewer long-period giant planets \citep[for example][]{Cumming:2008}.
+
+A recent review of the occurrence rate estimates based on direct imaging
+surveys \citep{Bowler:2016} reports the upper limit on the occurrence rate of
+giant planets orbiting F/G/K dwarfs as $<6.8\%$ in the range
+$5-13\,M_\mathrm{J}$ and $10-100\unit{au}$.
+Converted to a rate density, this gives
+\begin{eqnarray}
+\frac{\dd^2 N}{\dd\ln M\,\dd\ln a} &<& 0.03 \quad.
+\end{eqnarray}
+This value is lower than the value computed using our sample in
+Table~\ref{tab:occrates} but this is consistent with the fact that direct
+imaging is sensitive to larger planets at wider separations than the transit
+method.
 
@@
 \end{figure*}
+
+\begin{floattable}
+\begin{deluxetable}{ccc}
+\tabletypesize{\footnotesize}
+\caption{The occurrence rate computed in mass units
+\label{tab:occrates}}
+
+\tablehead{%
+    \colhead{volume} & \colhead{rate density\tablenotemark{a}} & \colhead{integrated rate}
+}
+
+\startdata
+$2\unit{yr}<P<25\unit{yr};\,0.01\,M_\mathrm{J} \le M < 20\,M_\mathrm{J}$ &
+\massocc & \massoccint \\
+$1.5\unit{au}<a<9\unit{au};\,0.01\,M_\mathrm{J} \le M < 20\,M_\mathrm{J}$ &
+\masssemiocc & \masssemioccint \\
+\enddata
+
+\tablenotetext{a}{The rate density is measured in natural logarithmic units.}
+\tablecomments{These values are computed assuming that the occurrence rate is
+flat in the logarithmic parameters.}
+\end{deluxetable}
+\end{floattable}
 

### 2016-07-17 document/ms.tex
some discussion

@@
 \caption{%
+Predicted eclipse shape distributions for the two false positive scenerios and
+exoplanet transits (grayscale heatmap).
+In this figure, the relative normalization of the maps are arbitrary but the
+actual normalizations are given in the text.
+The green points show the shapes parameters of the long-period exoplanet
+candidates from Table~\ref{tab:catalog}.
 \dfmfiglabel{shape-kdes}}
@@
 surveys.
-In the range $10^3\unit{days}<P<10^4\unit{days}$ and
-$10\,M_\oplus<M<10^4\,M_\oplus$, they find a mean occurrence rate density
-of
+In the period and mass range $10^3-10^4\unit{days}$ and $10-10^4\,M_\oplus$,
+they find a mean occurrence rate density of
 \begin{eqnarray}
@@
 fewer long-period giant planets \citep[for example][]{Cumming:2008}.
+
+Recently, \citep{Bryan:2016} studied the frequency of long-period giant
+planets in systems with inner hot-Jupiters based on long-baseline radial
+velocity monitoring of these systems \citep{Knutson:2014}.
+In this sample, the computed occurrence rate of long-period giant planets was
+found to be
+\begin{eqnarray}
+\frac{\dd^2 N}{\dd\ln M\,\dd\ln a} &=& 0.125 \pm 0.012
+\end{eqnarray}
+in the range $1-20\,M_\mathrm{J}$ and $5-20\unit{au}$.
+This result is about a factor of two larger than our estimate
+(\eqalt{massocc}) once again suggesting that cold-Jupiters preferentially
+occur in systems with inner planets.
 
@@
 
-We have developed a fully automated method to search for the transits and
-eclipses of long-period companions in photometric time series.
-Applying this method to a subset of the \kepler\ archival light curves, we
-discovered XX astrophysical transits.
+We have developed a fully automated method to search for the transits of
+long-period exoplanets in the \kepler\ archival light curves.
+This method uses probabilistic model comparison to veto non-transit signals.
+Applying this method to the brightest \numtargets\ G/K-dwarfs in the \kepler\
+target list, we discover \numcands\ systems with likely astrophysical
+transits and eclipses.
+Simulations of the false positive population~--~the secondary eclipses of
+binary systems and background eclipsing binaries~--~suggest that 13 of these
+candidates have high probability of being planetary in nature.
+
+We measure the empirical detection efficiency function of our search procedure
+by injecting simulated transit signals into the target light curves and
+measuring the recovery rate.
+By combining the measured detection efficiency and the catalog of exoplanet
+candidates, we estimate the integrated occurrence rate of exoplanets with
+orbital periods in the range $2-25\unit{years}$ and radii in the range
+$0.1-1\,R_\mathrm{J}$ to be \intocc\ planets per G/K-dwarf.
+
 Of these discoveries, at least about YY are likely to be planetary in nature.
@@
 So Hattori,
+Jeff Coughlin,
 Angie Wolfgang,

### 2016-07-17 document/ms.tex
words in discussion

@@
 Since the completeness function depends on the planet's radius and not its
-mass, a probabilistic mass--radius relation \citep{Chen:2016} was used to
+mass, a probabilistic mass--radius relationship \citep{Chen:2016} was used to
 convert radius to mass.
@@
 We have developed a fully automated method to search for the transits of
-long-period exoplanets in the \kepler\ archival light curves.
+long-period exoplanets with only one or two observable transits in the
+\kepler\ archival light curves.
 This method uses probabilistic model comparison to veto non-transit signals.
@@
 transits and eclipses.
+We fit the light curve for each candidate with a physical generative model and
+informative priors on eccentricity and stellar density to estimate the
+planet's orbital period.
 Simulations of the false positive population~--~the secondary eclipses of
@@
 $0.1-1\,R_\mathrm{J}$ to be \intocc\ planets per G/K-dwarf.
-
-Of these discoveries, at least about YY are likely to be planetary in nature.
-Combining this catalog of discoveries with a measurement of the completeness
-of our search method, we place a constraint on the occurrence rate of
-long-period exoplanets.
-
-Our method for transit detection finds convincing transit-shaped signals does
-a model comparison between a physical transit model.
-
+This result is qualitatively consistent with estimates from radial velocity,
+microlensing, and direct imaging surveys.
+
+These long-period exoplanet candidates are potentially interesting candidates
+for follow-up observations.
+Using a probabilistic mass--radius relationship, we predict the masses of our
+candidates and report predictions for the radial velocity amplitudes.
+Unfortunately, since the target stars are faint and the amplitudes are small,
+these targets are unlikely to be accessible with even the current
+state-of-the-art high-precision instruments.
+We also discuss the potential for astrometric follow-up using the forthcoming
+data from the \gaia\ Mission with similarly discouraging results.
+
+Our method of transit discovery is especially relevant for future photometric
+surveys like \KT, \tess, and \plato\ where the survey baseline is shorter than
+\kepler.
+The transits of planets with orbital periods longer than the observation
+baselines will be plentiful in these forthcoming data sets and this method
+can, in principle, be trivially generalized to discover these planets,
+prioritize follow-up, and study their population.
+
+\vspace{1.5em}
 All of the code used in this project is available from

### 2016-07-18 document/figures/completeness.py
completeness plots were wrong

@@ -17,7 +17,7 @@ from peerless.catalogs import KOICatalog
 
 inj = pd.read_hdf("../../results/injections-with-mass.h5", "injections")
 inj = inj[inj.ncadences > 0]
-rec = inj[inj.recovered]
+rec = inj[inj.accept]
 
 kois = set(KOICatalog().df.kepid)
 
@@ -50,7 +50,7 @@ def error(params, ln_radius, ln_period, flag):
 
 
 x, y = np.log(np.array(inj.radius)), np.log(np.array(inj.period))
-flag = np.array(inj.recovered, dtype=int)
+flag = np.array(inj.accept, dtype=int)
 params = np.array([0.0, 1.0, 0.0, 0.6, 0.0, 10.0, 0.0, -3.0])
 r = minimize(nll, params, jac=grad(nll), args=(x, y, flag))
 with open("../completenessfit.tex", "w") as f:

### 2016-07-18 document/ms.tex

@@
 
+The occurrence rates given here should be interpreted with a few caveats in
+mind.
+First, when we inferred the periods of the planets with only one transit, we
+assumed that the period was long enough that no other transit occurred during
+the \kepler\ lifetime.
+This neglects the small but non-negligible probability~--~less than one
+percent for the typical candidate~--~that a second transit might have
+occurred in a data gap.
+All of the candidates in our catalog are consistent with having periods this
+long but the geometric transit probability decreases quickly with orbital
+period.
+For the purposes of this \paper, we neglect this effect because its rigorous
+treatment is subtle.
+
 \begin{floattable}

### 2016-07-19 document/ms.tex
comments from hogg

@@
 
+\edef \mpia      {\arabic{affilcounter}}\stepcounter{affilcounter}
+\altaffiltext{\mpia}     {Max-Planck-Institut f\"ur Astronomie,
+                          K\"onigstuhl 17, D-69117 Heidelberg, Germany}
+
 \edef \cds       {\arabic{affilcounter}}\stepcounter{affilcounter}
@@
                           726 Broadway, 7th Floor, New York, NY, 10003, USA}
-
-\edef \mpia      {\arabic{affilcounter}}\stepcounter{affilcounter}
-\altaffiltext{\mpia}     {Max-Planck-Institut f\"ur Astronomie,
-                          K\"onigstuhl 17, D-69117 Heidelberg, Germany}
 
@@
     David~W.~Hogg\altaffilmark{\scda,\nyu,\mpia,\cds},
-    Eric~Agol\altaffilmark{\uw},
-    Bernhard~Sch\"olkopf\altaffilmark{\mpis},
-    and others
+    Eric~Agol\altaffilmark{\uw}, and
+    Bernhard~Sch\"olkopf\altaffilmark{\mpis}
 }
@@
 Transit surveys like \kepler\ are most sensitive to planets with shorter
-orbital periods than the gas giant planets that dominate the dynamics of our
+orbital periods than Jupiter and Saturn which dominate the dynamics of our
 Solar System.
@@
 or two transits in the archival \kepler\ light curves.
-When applied to the 40,000 brightest Sun-like target stars, this search
+When applied to the $\sim 40,000$ brightest Sun-like target stars, this search
 produces \numcands\ long-period exoplanet candidates.
+Of these candidates, 6 are novel discoveries and 5 are in systems with inner
+short-period transiting planets.
 Since our method involves no human intervention, we empirically characterize
@@
 
-Data from the \kepler\ Mission \citep{Borucki:2011} has been used to discover
+Data from the \kepler\ Mission \citep{Borucki:2011} have been used to discover
 thousands of transiting exoplanets.
@@
 the \kepler\ lifetime.
-This neglects the small but non-negligible probability~--~less than one
-percent for the typical candidate~--~that a second transit might have
+This neglects the small but non-negligible posterior probability~--~less than
+one percent for the typical candidate~--~that a second transit might have
 occurred in a data gap.
@@
 For the purposes of this \paper, we neglect this effect because its rigorous
-treatment is subtle.
+treatment is subtle but comment that this would only ever decrease the
+occurrence rate estimate.
+
+% This occurrence rate estimate~--~and all other results based on transit
+% surveys~--~is affected by Malmquist bias.
+% For a transit survey, this bias enters in two ways: \emph{(a)} contamination
+% of the sample by giants, and \emph{(b)} discrepancy
 
@@
 \citet{Clanton:2014} studied the occurrence rate of long-period giant planets
-orbiting M-dwarfs by combining results from radial velocity and microlensing
+orbiting M dwarfs by combining results from radial velocity and microlensing
 surveys.
@@
 \begin{eqnarray}
-\frac{\dd^2 N}{\dd\ln M/M_\mathrm{J}\,\dd\ln P/\unit{yr}}
+\frac{\dd^2 N}{\dd\ln M\,\dd\ln P}
     &\lesssim& 0.026
 \end{eqnarray}
-per M-dwarf.
+per M dwarf.
 This result is slightly lower than our estimated rate for a similar range of
@@
 
-\tablenotetext{a}{The rate density is measured in natural logarithmic units.}
+\tablenotetext{a}{The rate density is measured in natural logarithmic units;
+see \eq{massocc}.}
 \tablecomments{These values are computed assuming that the occurrence rate is
@@
 orbit is sampled by the time history of the focal-plane crossings.
-However, it is not expected that \gaia\ can detect or measure precisely
+However, it is not expected that \gaia\ can detect or precisely measure
 exoplanet-induced astrometric wobbles that are much smaller in amplitude than
@@
 It also means that many of the discoveries of the \KT\ and \tess\ missions
-will be followed up and precisely measured by the \gaia\ Mission.
-
-\section{Discussion}\sectlabel{discussion}
+could be followed up and precisely measured by the \gaia\ Mission.
+
+\section{Summary}\sectlabel{summary}
 
@@
 This method uses probabilistic model comparison to veto non-transit signals.
-Applying this method to the brightest \numtargets\ G/K-dwarfs in the \kepler\
+Applying this method to the brightest \numtargets\ G/K dwarfs in the \kepler\
 target list, we discover \numcands\ systems with likely astrophysical
@@
 orbital periods in the range $2-25\unit{years}$ and radii in the range
-$0.1-1\,R_\mathrm{J}$ to be \intocc\ planets per G/K-dwarf.
+$0.1-1\,R_\mathrm{J}$ to be \intocc\ planets per G/K dwarf.
 This result is qualitatively consistent with estimates from radial velocity,
 microlensing, and direct imaging surveys.
+
+\dfmtodo{More words here about comparison.}
 
@@
 It is a pleasure to thank
+Jeff Coughlin,
 So Hattori,
-Jeff Coughlin,
-Angie Wolfgang,
+Hans-Walter Rix,
+Dun Wang,
 and
-Hans-Walter Rix
+Angie Wolfgang
 for helpful contributions to the ideas and code presented here.

### 2016-07-19 document/ms.tex
editing

@@
 Since our method involves no human intervention, we empirically characterize
-the completeness and reliability of our search.
+the detection efficiency of our search.
 Based on these results, we measure the average occurrence rate of exoplanets
-smaller than Jupiter with orbital periods longer than two years.
+smaller than Jupiter with orbital periods longer than two years orbiting
+Sun-like stars.
 
@@
 For \kepler, with a baseline of about four years, this sets an absolute upper
-limit on the detectable periods of about two years.
+limit of about two years on the range of detectable periods.
 In the Solar System, Jupiter~--~with a period of 12 years~--~dominates the
@@
 Any single transit events discovered in the \kepler\ light curves are
-interesting in their own right but the development of a method for the
-discovery of planets with orbital periods longer than the survey baseline are
-crucial for the future of the study of exoplanets via the transit method.
+interesting in their own right but the development of a general and systematic
+method for the discovery of planets with orbital periods longer than the
+survey baseline are crucial for the future of of exoplanet research with the
+transit method.
 All future transit surveys have shorter observational baselines than the
 \kepler\ Mission (\KT, \citealt{Howell:2014}; \tess, \citealt{Ricker:2015};
-\plato, \citealt{Rauer:2014}).
-The methodology presented in the following pages can be modified to be applied
-to these forthcoming data sets as they are collecting in the upcoming years.
+\plato, \citealt{Rauer:2014}) and given suitable techniques, single transit
+events will be plentiful and easily discovered.
+The methodological framework presented in the following pages is a candidate
+for this task and it could be modified and applied to these forthcoming data
+sets as they are collecting in the upcoming years.
 
@@
 Furthermore, even at long orbital periods, the \kepler\ light curves should be
-sensitive to smaller planets than the current state-of-the-art radial velocity
-surveys.
+sensitive to planets at the detection limits of the current state-of-the-art
+radial velocity surveys.
 
@@
 Even when the most sophisticated methods for removing this variability are
-used, false signals far outnumber the true single transits in any traditional
+used, false signals far outnumber the true transit events in any traditional
 search.
@@
 Kipping:2016, Uehara:2016, Wang:2015}.
-Since all of these discoveries rely on human interaction, it is prohibitively
-expensive to reliably measure the completeness of these catalogs and they
-cannot be used to constrain the occurrence rate of long-period planets.
+These discoveries have already yielded some tantalizing insight into the
+population of long-period transiting planets but, since these previous results
+rely on human interaction, it is prohibitively expensive to reliably measure
+the completeness of these catalogs.
+As a result, the existing catalogs of long-period transiting planets cannot be
+used to rigorously constrain the occurrence rate of long-period planets.
 
@@
 We finish by discussing the potential effects of false positives, the
-prospects for radial velocity follow-up of these candidates, and compare to
-calculated occurrence rate to results based on discoveries using different
-planet discovery methods.
+prospects for follow-up, and compare to calculated occurrence rate to results
+based on discoveries using different planet discovery methods.
 
@@
 {\item light curve-level vetting (using automated model comparison) to remove
-signals that don't match a transit shape, and}
+signals that don't have a convincing transit shape, and}
 {\item pixel-level vetting to remove some astrophysical false positives.}
@@
 must estimate the marginalized likelihoods of several different models
-describing a transit and many other processes that ``look'' like transits but
-are actually caused by noise.
-This step is also conservative; unless a signal is a very convincing transit,
-it won't pass the test.
+describing a transit and other processes that ``look'' like transits but are
+actually caused by noise.
+This step is conservative: unless a signal is a very convincing transit, it
+won't pass the test.
 In practice, this means that all but the highest signal-to-noise events will
@@
 It is not computationally feasible to run a full model comparison at every
-conceivable transit time possible in the light curve so we must first find
-potentially interesting events.
+conceivable transit time in the light curve so we must first find potentially
+interesting events.
 For our purposes, ``interesting'' means high signal-to-noise and previously
@@
 half-width of 2~days to remove stellar variability.
-We then compute the signal-to-noise of the depth of a 0.6~day long
-transit on a grid of times spanning the full baseline of observations.
+We then compute the signal-to-noise of the depth of a 0.6~day long top hat on
+a grid of times spanning the full baseline of observations.
 
@@
 single transit duration because the following steps in this procedure are only
-sensitive to transits with very high signal-to-noise.
-In practice, the final results are insensitive to the specific choice of
-duration.
+sensitive to transits with very high signal-to-noise, and in practice, the
+final results are insensitive to the specific choice of duration.
 
@@
 computationally intractable to compute thousands of precise marginalized
-likelihoods for each model.
+likelihoods or expected utilities for each model.
 The BIC can be efficiently computed and it exhibits the desired
@@
 transit light curve,}
-{\item \modelname{variability} -- a pure Gaussian Process model to capture
+{\item \modelname{variability} -- a pure GP model to capture
 stellar variability,}
@@
 \end{itemize}
-The functional forms of these models are given in \app{model-details}.
+The functional forms of these models are given in \app{model-details} and the
+details of the technical methodology of GP fitting are described in
+\app{gp-regression}.
 
@@
 To further restrict to non-grazing transits, we also reject events where the
-best fit impact parameter is less than $1 - R_\mathrm{P} / R_\star$.
+maximum impact parameter is greater than $1 - R_\mathrm{P} / R_\star$.
 
@@
 models selected in this step.
-We find that these are sufficient for the targets discussed below but other
-target lists might require additional models to be included for robust
-selection.
+We find that these are sufficient for the targets discussed below but
+different target lists or data sets might require additional models to be
+included for robust selection.
 
@@
 The examples represent the following model categories:
-\emph{(a)} variability, \emph{(b)} step, \emph{(c)} box, and \emph{(d)}
+\emph{(a)} step \emph{(b)} variability, \emph{(c)} box, and \emph{(d)}
 transit.
@@
 For each candidate in our sample, we take the constraints on the stellar
-parameters from the \kepler\ stellar properties catalog\footnote{The
-\textsf{q1\_q17\_dr24\_stellar} table from the NASA Exoplanet Archive
-\citep{Huber:2014}} and assume an empirical beta function prior on the
-eccentricities based on the observed eccentricity distribution of long-period
-planets discovered using radial velocities \citep{Kipping:2013}.
+parameters from the \kepler\ DR24 stellar properties catalog and assume an
+empirical beta function prior on the eccentricities based on the observed
+eccentricity distribution of long-period planets discovered using radial
+velocities \citep{Kipping:2013}.
 Table~\ref{tab:parameters} lists all the fit parameters and their prior
@@
 
-As above, we model the light curve as GP with a physical transit model as the
-mean and a covariance matrix described by a Mat\'ern-3/2 kernel function.
+As above, we model the light curve as a Gaussian Process (GP) with a physical
+transit model as the mean and a covariance matrix described by a Mat\'ern-3/2
+kernel function.
 The full likelihood function and some details of GP regression are given in
@@
 The consistency between our results and the earlier catalogs is reassuring.
-Our automated search did not find any more candidates than visual inspection
-of the light curves of known KOIs \citep{Uehara:2016} and one candidate
-(KIC~3230491) reported by the human analysis was discarded as grazing by our
-search.
-The PH citizen science project reported five long-period candidates with one
-or two observed transits in our target list \citep{Wang:2015}.
+In the light curves of targets with previously known short-period planets, our
+automated search did not find any candidates that weren't previously detected
+by visual inspection \citep{Uehara:2016} and one candidate (KIC~3230491)
+reported by the human analysis was discarded as grazing by our search.
+The Planet Hunters citizen science project \citep{Fischer:2012} reported five
+long-period candidates with one or two observed transits in our target list
+\citep{Wang:2015}.
 Of these, we also find two (KIC~8410697 and KIC~10842718) although we find a
-second transit in the KIC~8410697 system that was not previously reported.
-The three other candidates reported by \citet{Wang:2015} that we miss
-(KIC~5536555, KIC~9662267, and KIC~12454613) are have low signal-to-noise
-transits that do not pass our initial signal-to-noise threshold.
+second transit in the KIC~8410697 system that was previously missed.
+We do not recover the three other candidates reported by \citet{Wang:2015}:
+KIC~5536555, KIC~9662267, and KIC~12454613.
+The transits of these candidates are all low signal-to-noise and they do not
+pass our initial signal-to-noise threshold.
 Six of the candidates in Table~\ref{tab:catalog} have not been previously
@@
 were not found by previous studies of long-period eclipsing binary systems.
-We do not consider these events further in the rest of this \paper\ but
-Table~\ref{tab:rejects} lists these events and their properties for
-posterity.
+We do not consider these events further in the following analysis but
+Table~\ref{tab:rejects} lists these events and their properties for posterity.
 
@@
 {\item The transit search method described in \sect{search}~--~including
-de-trending and all automated vetting~--~is applied to this light
+de-trending and \emph{all automated vetting}~--~is applied to this light
 curve with the injected transit signal.}
@@
 The fraction of recovered simulations as a function of the relevant parameters
-gives an estimate of the search completeness or the probability of detecting
-an exoplanet transit with a given set of parameters, \emph{conditioned on the
-fact that it transits}.
+gives an estimate of the probability of detecting an exoplanet transit with a
+given set of parameters, \emph{conditioned on the fact that it transits}.
 We will call this function $Q_{\mathrm{det},k}(\params)$ where \params\ is the
@@
 transit scales with the area ratio between the planet and the star.
+There is also a slight decrease in the completeness to larger planet radius.
+This trend is introduced in steps~2 and~3 of the search procedure where the
+tuning parameters were chosen to maximize the yield of convincing small
+transit discoveries.
 The decreasing completeness with orbital period is less intuitive because, on
@@
     \, \frac{1 + e\,\sin\omega}{1-e^2} \\
-&=& \left[\frac{4\,\pi^2}{G\,M_{\star,k}}\right]^{1/3}\,(R_{\star,k}+R)
-    \, \left[\frac{1 + e\,\sin \omega}{1-e^2}\right]
+&=& \left[\frac{4\,\pi^2}{G\,M_{\star,k}}\right]^{1/3}
+    \, \left[\frac{1 + e\,\sin \omega}{1-e^2}\right]\,(R_{\star,k}+R)
     \, P^{-2/3}
@@
 Note that we do not use this approximation in the following analysis but
-instead compute the relevant integrals using the injection catalog directly.
+instead compute the relevant integrals using the injection results directly.
 
@@
 This assumption is only justified because we are only making high-level
-measurements of the mean occurrence rate in large bins.
+measurements of the mean occurrence rate in bins larger than the uncertainties.
 
@@
 where the sum is over all injections in the volume $V$.
-
-For comparison, we repeated the analysis of \citet{Burke:2015} and fit a
-double power-law occurrence rate to the short-period \kepler\ planet
-candidates\footnote{The analysis was adapted from publicly available code that
-was demonstrated to reproduce the same results as \citet{Burke:2015} by
-\citet{Foreman-Mackey:2015a}.} and extrapolated to the center of the two
-bins where we computed the occurrence rate.
-At a period of 7~years and a radius of $0.2\,R_\mathrm{J}$, the extrapolated
-occurrence is $0.73\pm0.28$ and at a radius of $0.6\,R_\mathrm{J}$, the
-extrapolated rate is $0.15\pm0.05$.
-These extrapolated values are qualitatively consistent with the rates listed
-in Table~\ref{tab:occurrence} but we note that extrapolations and their
-statistical uncertainties should not be taken too seriously.
 
@@
 (depth, duration, and ingress-to-duration ratio, as defined in
-\citet{Morton:2012}).
+\citealt{Morton:2012}).
 
@@
 latitude $b=20$ to 0.05\,arcsec$^{-2}$ at $b=5$ (matching up well with the
-simulations of \citep{Morton:2011} at many different Galactic latitudes). Each
+simulations of \citet{Morton:2011} at many different Galactic latitudes). Each
 \kepler\ target star is then assigned a number of background stars drawn from
@@
 to quantify the probability that each of them may be a false positive.
+These distributions and the observed shape parameters are plotted in
+\dfmfig{shape-kdes}.
 
@@
 difference can be used to get a qualitative sense of the systematic
-uncertainty introduced by false positives.
+uncertainty introduced by the false positive population.
 
@@
 In this figure, the relative normalization of the maps are arbitrary but the
-actual normalizations are given in the text.
-The green points show the shapes parameters of the long-period exoplanet
+absolute normalization is discussed in \sect{false-positives}.
+The green points show the shape parameters of the long-period exoplanet
 candidates from Table~\ref{tab:catalog}.
@@
 statistical uncertainties in the M--R parameters.
-We compared the predictions with the predictions from \citet{Wolfgang:2016}
-and found similar values with smaller uncertainties and chose to use the
-\citet{Chen:2016} relationship because it was more conservative in the
-relevant range of parameter space.
+We compare the predictions with the predictions from \citet{Wolfgang:2016} and
+find similar values with smaller uncertainties and choose to use the
+\citet{Chen:2016} relationship because it is more conservative in the relevant
+range of parameter space.
 
@@
 their host star than any of the candidates discussed here.
-This effect would probably cause the masses of these cool planets to be
-systematically underestimated.
-
-Using the same M--R relationship, we can also compute the completeness of our
+This effect would cause the masses of these cool planets to be systematically
+underestimated.
+
+Using the same M--R relationship, we also compute the completeness of our
 transit search as a function of planet mass and orbital semi-major axis.
@@
 Z(a_\mathrm{min},\,a_\mathrm{max};\,M_\mathrm{min},\,M_\mathrm{max}) &\approx&
-    \frac{K}{J}\,\sum_{j=1}^{J}
+    \frac{K\,V}{J}\,\sum_{j=1}^{J}
     \frac{Q_k(w^{(j)})}{\tilde{p}(\ln a^{(j)},\,\ln M^{(j)})} \quad.
@@
 \begin{eqnarray}
-\frac{\dd^2 N}{\dd\ln M\,\dd\ln P}
-    &\lesssim& 0.026
+\frac{\dd^2 N}{\dd\ln M\,\dd\ln P} &\lesssim& 0.013
 \end{eqnarray}
@@
 
-Recently, \citep{Bryan:2016} studied the frequency of long-period giant
+Recently, \citet{Bryan:2016} studied the frequency of long-period giant
 planets in systems with inner hot-Jupiters based on long-baseline radial
@@
 This result is about a factor of two larger than our estimate
-(\eqalt{massocc}) once again suggesting that cold-Jupiters preferentially
-occur in systems with inner planets.
+(\eqalt{massocc}) once again suggesting that cold-Jupiters might
+preferentially occur in systems with inner planets.
 
@@
 \frac{\dd^2 N}{\dd\ln M\,\dd\ln a} &<& 0.03 \quad.
-\end{eqnarray}
-This value is lower than the value computed using our sample in
+\end{eqnarray} This value is lower than the value computed using our sample in
 Table~\ref{tab:occrates} but this is consistent with the fact that direct
-imaging is sensitive to larger planets at wider separations than the transit
-method.
+imaging is sensitive to the potentially less common large planets at wider
+separations than detections with the transit method.
+
+As a final comparison, we repeated the analysis of \citet{Burke:2015} and fit
+a double power-law occurrence rate to the short-period \kepler\ planet
+candidates\footnote{The analysis was adapted from publicly available code that
+was demonstrated to reproduce the same results as \citet{Burke:2015} by
+\citet{Foreman-Mackey:2015a}.} and extrapolated to the center of the two bins
+where we computed the occurrence rate.
+At a period of 7~years and a radius of $0.2\,R_\mathrm{J}$, the extrapolated
+occurrence is $0.73\pm0.28$ and at a radius of $0.6\,R_\mathrm{J}$, the
+extrapolated rate is $0.15\pm0.05$.
+These extrapolated values are qualitatively consistent with the rates listed
+in Table~\ref{tab:occurrence} but we note that extrapolations and their
+statistical uncertainties should not be taken too seriously.
 
@@
 
-% To evaluate \eq{gpmeangrad}, we must also evaluate the derivative of the mean
-% model with respect to its parameters.
-
 \bibliography{peerless}

### 2016-07-19 document/ms.tex
formatting
removing comment
intro minor TDM edits

@@
 
-\usepackage{endnotes}
-\let\footnote=\endnote
+% \usepackage{endnotes}
+% \let\footnote=\endnote
 
@@
 {\noindent\scriptsize Preprint typeset using \LaTeX\ style AASTeX6\\
-With modifications by David W. Hogg and Daniel Foreman-Mackey\\
-See the last page for endnotes
+With modifications by David W. Hogg and Daniel Foreman-Mackey
 }\par\vspace*{-\baselineskip}\vspace*{0.625in}
@@
 method for the discovery of planets with orbital periods longer than the
-survey baseline are crucial for the future of of exoplanet research with the
+survey baseline is crucial for the future of of exoplanet research with the
 transit method.
@@
 The methodological framework presented in the following pages is a candidate
-for this task and it could be modified and applied to these forthcoming data
-sets as they are collecting in the upcoming years.
+for this task.% and it could be modified and applied to these forthcoming data
+%sets as they are collecting in the upcoming years.
 
@@
 example][]{Gould:2010, Cassan:2012, Clanton:2014, Shvartzvald:2016}, and
-direct imaging \citep[for example][]{Bowler:2016}.
+direct imaging \citep[for example][]{Bowler:2016} \dfmtodo{incomplete sentence?}.
 Exoplanets with both mass and radius measurements can be used to study
@@
 We apply this method to a subset of the archival data from the \kepler\
-Mission, release a catalog of exoplanet candidates, and estimate the
+Mission, present a catalog of exoplanet candidates, and estimate the
 occurrence rate of long-period exoplanets.
-We finish by discussing the potential effects of false positives, the
-prospects for follow-up, and compare to calculated occurrence rate to results
-based on discoveries using different planet discovery methods.
+We finish by discussing the potential effects of false positives, evaluating the
+prospects for follow-up, and comparing our results to other studies
+based on different planet discovery methods.
 
@@
 
+\newpage
 \subsection{Target selection}\sectlabel{target-selection}
@@
 
-% This occurrence rate estimate~--~and all other results based on transit
-% surveys~--~is affected by Malmquist bias.
-% For a transit survey, this bias enters in two ways: \emph{(a)} contamination
-% of the sample by giants, and \emph{(b)} discrepancy
-
 \begin{floattable}
@@
 
-\dfmtodo{More words here about comparison.}
+\dfmtodo{More words here about comparison and interpretation.}
 
@@
 
-\theendnotes
+% \theendnotes
 

### 2016-07-19 document/ms.tex
tdm edit box paragraph

@@
 In the future, it would be interesting to relax this goal and investigate the
-other model classes because, for example, the \modelname{box} model is
-probably sensitive to other astrophysical phenomena like secondary eclipses.
-In a cursory investigation it is clear that the majority of signals labeled
-\modelname{box} in our analysis are noise but a subset are likely to be
+other model classes.  In particular, the \modelname{box} model is
+sensitive to astrophysical phenomena, notably occultations of white dwarfs,
+which produce a perfect box-shaped signal.  In a cursory investigation 
+it is clear that the majority of signals labeled
+\modelname{box} in our analysis are noise; however, a subset are likely to be
 astrophysical in nature.

### 2016-07-19 document/ms.tex
tdm semicolon

@@
 In the future, it would be interesting to relax this goal and investigate the
-other model classes.  In particular, the \modelname{box} model is
+other model classes; in particular, the \modelname{box} model is
 sensitive to astrophysical phenomena, notably occultations of white dwarfs,

### 2016-07-19 document/ms.tex
more tdm edits

@@
 smaller than Jupiter with orbital periods longer than two years orbiting
-Sun-like stars.
+Sun-like stars to be $1.80\pm 0.65$ planets per star.
 
@@
 To simplify the analysis, we will make the strong assumption that none of the
-candidates are astrophysical false positives (the eclipse of a stellar mass
-companion, a background eclipsing binary, or the secondary eclipse of a
-long-period binary system).
+candidates are astrophysical false positives (the eclipse or occultation 
+of a stellar mass companion, around either the target star or a 
+faint background star).
 We revisit this assumption and discuss its validity in the following section.
@@
 For the purposes of this \paper, we neglect this effect because its rigorous
-treatment is subtle but comment that this would only ever decrease the
+treatment is subtle, but comment that this would only ever decrease the
 occurrence rate estimate.
@@
 package
-\exosyspop\footnote{\url{https://github.com/timothydmorton/exosyspop}}, which
+\exosyspop\footnote{\url{https://github.com/timothydmorton/exosyspop}; in this
+work we use commit \textsf{e4f54288}}, which
 we developed for this purpose.
@@
 
-These results suggest that we might certainly expect to see some unblended
-eclipsing binary signals in our search.  However, this does not mean that  we
-should fear that $\sim$7 of the planet candidates might be EBs. Rather, we can
-instead inspect the synthetic observation simulations in more detail; in
+These prediction results suggest that we should indeed expect to see some 
+astrophysical false positives in our search.  However, this does not mean that  we
+should fear that $\sim$7 of the planet candidates might be EBs. In particular,
+we note that these simulations do not include the full vetting procedure 
+described in \sect{catalog}, and it is likely that the three impact-parameter-rejected
+candidates are EBs and that the centroid-rejected candidate is a BEB.  Thus,
+we might expect maybe two or three additional false positives among our planet
+candidates.
+
+In order to more precisely quantify which of the candidates might indeed be false
+positives, we can inspect the synthetic observation simulations in more detail. In
 particular, we can analyze the shape distribution of the different scenarios and
@@
 of the planet scenario, we define a custom \exosyspop\ population of planets
-according to the two-bin population model described by Table~\ref{tab:occurrence} and
+according to the two-bin population model described by the
+median posterior values in Table~\ref{tab:occurrence} and
 generate a population of 1000 detected signals.
@@
 candidates  have false positive probabilities below 10\%.  We do note that as
-discussed in \sect{catalog}, 4754460 (which we calculate to have a 5\% false positive
+discussed in \sect{catalog}, 4754460 (for which we calculate a 5\% false positive
 probability) does show a partial deep eclipse right at the end of the \kepler\
@@
 planet's orbital period.
-Simulations of the false positive population~--~the secondary eclipses of
-binary systems and background eclipsing binaries~--~suggest that 13 of these
+Simulations of the false positive population~--~lone primary or secondary eclipses of
+binary systems or background eclipsing binaries~--~suggest that 13 of these
 candidates have high probability of being planetary in nature.
@@
     \project{george} \citep{Ambikasaran:2016},
+    \project{isochrones} \citep{Morton:2015},
 	\project{matplotlib} \citep{Hunter:2007},

### 2016-07-19 document/ms.tex
added word

@@
 example][]{Gould:2010, Cassan:2012, Clanton:2014, Shvartzvald:2016}, and
-direct imaging \citep[for example][]{Bowler:2016} \dfmtodo{incomplete sentence?}.
+direct imaging \citep[for example][]{Bowler:2016} surveys.
 Exoplanets with both mass and radius measurements can be used to study

### 2016-07-19 document/ms.tex
added isochrones reference

@@
 work we use commit \textsf{e4f54288}}, which
-we developed for this purpose.
+we developed for this purpose and utilizes the \project{isochrones} 
+package \citep{Morton:2015} for simulations of stellar populations.
 

### 2016-07-19 document/ms.tex
tdm acknowledgments
Minor edits; added two paragraphs.

--- 2016-07-19 document/ms.tex
@@
 physical properties.
-Transit surveys like \kepler\ are most sensitive to planets with shorter
-orbital periods than Jupiter and Saturn which dominate the dynamics of our
-Solar System.
-We performed a fully automated search for long-period exoplanets with only one
+However, transit surveys like \kepler\ are most sensitive to planets with
+orbital periods shorter than a few years, which is shorter than the orbital periods of 
+Jupiter and Saturn, which dominate the dynamics of our Solar System.  To address this deficiency,
+we performed a fully automated search for long-period exoplanets with only one
 or two transits in the archival \kepler\ light curves.
 When applied to the $\sim 40,000$ brightest Sun-like target stars, this search
-produces \numcands\ long-period exoplanet candidates.
+produced \numcands\ long-period exoplanet candidates.
 Of these candidates, 6 are novel discoveries and 5 are in systems with inner
@@
 smaller than Jupiter with orbital periods longer than two years orbiting
-Sun-like stars to be $1.80\pm 0.65$ planets per star.
+Sun-like stars.  [Can this be summarized by a single value?]
 
@@
 So far, these results have been limited to relatively short orbital periods
-because existing transit search methods require the observation of at least
+because existing transit search methods impose the requirement of the detection of at least
 three transits within the baseline of the data.
@@
 mission would discover at least 10 exoplanets with only one or two observed
-transits \citep{Yee:2008} and subsequent searches for these signals have
+transits \citep{Yee:2008}, yet subsequent searches for these signals have
 already been more fruitful than expected \citep{Wang:2015, Uehara:2016}.
 However, the systematic study of the population of long-period exoplanets
-found in the \kepler\ data has, so far, been limited because of the
-substantial technical challenge and the subtleties of interpretation.
+found in the \kepler\ data to date has been hampered due to the
+substantial technical challenge of implementing a search, as well as the
+subtleties involved in intepreting the results. For example,
+false alarms in the form of uncorrected systematics in the data and background
+eclipsing binaries can make single-transit detections ambiguous.
+
 Any single transit events discovered in the \kepler\ light curves are
-interesting in their own right but the development of a general and systematic
+interesting in their own right, but the development of a general and systematic
 method for the discovery of planets with orbital periods longer than the
-survey baseline is crucial for the future of of exoplanet research with the
+survey baseline is also crucial for the future of of exoplanet research with the
 transit method.
@@
 The methodological framework presented in the following pages is a candidate
-for this task.% and it could be modified and applied to these forthcoming data
-%sets as they are collecting in the upcoming years.
+for this task as it could be modified and applied to these forthcoming data
+sets as they are collected in the upcoming years.
 
 A study of the population of long-period transiting planets complements
-parallel radial velocity \citep[for example][]{Cumming:2008,
+other planet detection techniques, such as radial velocity \citep[for example][]{Cumming:2008,
 Knutson:2014, Bryan:2016}, microlensing \citep[for
 example][]{Gould:2010, Cassan:2012, Clanton:2014, Shvartzvald:2016}, and
-direct imaging \citep[for example][]{Bowler:2016} surveys.
-Exoplanets with both mass and radius measurements can be used to study
+direct imaging \citep[for example][]{Bowler:2016}.  The marriage of
+the radial velocity and transit techniques is particularly powerful as
+exoplanets with both mass and radius measurements can be used to study
 planetary compositions and the formation of planetary systems \citep[for
 example][]{Weiss:2014, Rogers:2015, Wolfgang:2016}.
-The existing catalog of exoplanets with measured densities is sparsely
-populated at long orbital periods and discoveries with the transit method are
-compelling targets for follow-up observations.
+Unfortunately the existing catalog of exoplanets with measured densities is sparsely
+populated at long orbital periods;  this makes discoveries with the transit method 
+at long orbital period compelling targets for follow-up observations.
 Furthermore, even at long orbital periods, the \kepler\ light curves should be
@@
 
+Relaxing the requirement of three transits requires a higher signal-to-noise
+threshold per transit for validating candidate planets that display only one 
+to two transits.
+Higher signal-to-noise allows matching the candidate transit to the expected
+shape of a limb-darkened light curve, as well as ruling out various false
+alarms.  This is analagous to microlensing surveys, for which a planet can only be
+detected once, thus requiring high signal-to-noise for a reliable detection
+\citep{Gould:2004}.  %http://arxiv.org/abs/astro-ph/0405217
+
 Recent work has yielded discoveries of long-period transiting planets with
@@
 by visual inspection \citep{Wang:2013, Kipping:2014a, Osborn:2016,
-Kipping:2016, Uehara:2016, Wang:2015}.
+Kipping:2016, Uehara:2016, Wang:2015}.  Detection via visual inspection requires
+a high signal-to-noise for transit events to be seen by eye.
 These discoveries have already yielded some tantalizing insight into the
-population of long-period transiting planets but, since these previous results
+population of long-period transiting planets.  However, as these previous results
 rely on human interaction, it is prohibitively expensive to reliably measure
@@
 In this \paper, we develop a systematic method for reliably discovering the
-transits of large long-period companions in photometric time series
+transits of large, long-period companions in photometric time series
 \emph{without human intervention}.
@@
 We apply this method to a subset of the archival data from the \kepler\
-Mission, present a catalog of exoplanet candidates, and estimate the
+Mission, release a catalog of exoplanet candidates, and estimate the
 occurrence rate of long-period exoplanets.
-We finish by discussing the potential effects of false positives, evaluating the
-prospects for follow-up, and comparing our results to other studies
-based on different planet discovery methods.
+We finish by discussing the potential effects of false positives, the
+prospects for follow-up, and compare to calculated occurrence rate to results
+based on discoveries using different planet discovery methods.
 
@@
 half-width of 2~days to remove stellar variability.
-We then compute the signal-to-noise of the depth of a 0.6~day long top hat on
+We then compute the signal-to-noise of the depth of a 0.6~day-long top hat on
 a grid of times spanning the full baseline of observations.
@@
 This likelihood function provides a natural scalar objective: the
-signal-to-noise of the measured depth computed a function of time.
+signal-to-noise of the measured depth computed as a function of time.
 In principle this scalar is also a function of duration but we only use a
@@
 series using a robust running windowed variance estimate of the detection
-scalar and accepting peaks more than 25-times this noise as candidates.
+scalar.  We accept peaks that are more than 25-times this background noise 
+level as candidates.
 
 For the \kepler\ light curves, this procedure yields at least one candidate
-event in about 1~percent of targets and the three highest signal-to-noise
-events are investigated in the following step.
+event in about 1~percent of targets.  For these targets, we investigate 
+the three highest signal-to-noise events in the following step.
 
@@
 Criterion (BIC).
-The BIC is not the optimal choice for this model comparison but it is
-computationally intractable to compute thousands of precise marginalized
+The BIC is not the optimal choice for this model comparison, but it is
+more computationally computationally tractable than the alternatives, such
+as computing thousands of precise marginalized
 likelihoods or expected utilities for each model.
@@
 
-We consider the following mean models and this list provides a qualitative
-justification for each model:
+We consider the following mean models (this list provides a qualitative
+justification for each model):
 \begin{itemize}
-{\item \modelname{transit} -- a limb-darkened, exposure time integrated
+{\item \modelname{transit} -- a limb-darkened, exposure-time integrated
 transit light curve,}
@@
 In the future, it would be interesting to relax this goal and investigate the
-other model classes; in particular, the \modelname{box} model is
-sensitive to astrophysical phenomena, notably occultations of white dwarfs,
-which produce a perfect box-shaped signal.  In a cursory investigation 
-it is clear that the majority of signals labeled
-\modelname{box} in our analysis are noise; however, a subset are likely to be
+other model classes because, for example, the \modelname{box} model is
+probably sensitive to other astrophysical phenomena like secondary eclipses.
+In a cursory investigation it is clear that the majority of signals labeled
+\modelname{box} in our analysis are noise but a subset are likely to be
 astrophysical in nature.
@@
 For each transit candidate, we constrain the physical parameters of the system
-by fitting a section of light curve around each transit using an exposure time
+by fitting a section of light curve around each transit using an exposure-time
 integrated  Keplerian orbit with a quadratic limb darkening law for the
@@
 In the following paragraphs, we describe the components of the probabilistic
-model.
+model used to infer the planet candidates' properties.
 To perform parameter estimation under this model, we use the Markov Chain
@@
 As above, we model the light curve as a Gaussian Process (GP) with a physical
-transit model as the mean and a covariance matrix described by a Mat\'ern-3/2
+transit model as the mean, and a covariance matrix described by a Mat\'ern-3/2
 kernel function.
@@
 To simplify the analysis, we will make the strong assumption that none of the
-candidates are astrophysical false positives (the eclipse or occultation 
-of a stellar mass companion, around either the target star or a 
-faint background star).
+candidates are astrophysical false positives (the eclipse of a stellar mass
+companion, a background eclipsing binary, or the secondary eclipse of a
+long-period binary system).
 We revisit this assumption and discuss its validity in the following section.
@@
 For the purposes of this \paper, we neglect this effect because its rigorous
-treatment is subtle, but comment that this would only ever decrease the
+treatment is subtle but comment that this would only ever decrease the
 occurrence rate estimate.
@@
 package
-\exosyspop\footnote{\url{https://github.com/timothydmorton/exosyspop}; in this
-work we use commit \textsf{e4f54288}}, which
+\exosyspop\footnote{\url{https://github.com/timothydmorton/exosyspop}}, which
 we developed for this purpose.
@@
 
-These prediction results suggest that we should indeed expect to see some 
-astrophysical false positives in our search.  However, this does not mean that  we
-should fear that $\sim$7 of the planet candidates might be EBs. In particular,
-we note that these simulations do not include the full vetting procedure 
-described in \sect{catalog}, and it is likely that the three impact-parameter-rejected
-candidates are EBs and that the centroid-rejected candidate is a BEB.  Thus,
-we might expect maybe two or three additional false positives among our planet
-candidates.
-
-In order to more precisely quantify which of the candidates might indeed be false
-positives, we can inspect the synthetic observation simulations in more detail. In
+These results suggest that we might certainly expect to see some unblended
+eclipsing binary signals in our search.  However, this does not mean that  we
+should fear that $\sim$7 of the planet candidates might be EBs. Rather, we can
+instead inspect the synthetic observation simulations in more detail; in
 particular, we can analyze the shape distribution of the different scenarios and
@@
 Following the method of \citet{Morton:2012} used to compute false positive
-probabilities for the regular \kepler\ KOI catalogs \citet{Morton:2016}, we
+probabilities for the regular \kepler\ KOI catalogs \citep{Morton:2016}, we
 can calculate the posterior probability for each of our candidates to belong
@@
 of the planet scenario, we define a custom \exosyspop\ population of planets
-according to the two-bin population model described by the
-median posterior values in Table~\ref{tab:occurrence} and
+according to the two-bin population model described by Table~\ref{tab:occurrence} and
 generate a population of 1000 detected signals.
@@
 candidates  have false positive probabilities below 10\%.  We do note that as
-discussed in \sect{catalog}, 4754460 (for which we calculate a 5\% false positive
+discussed in \sect{catalog}, 4754460 (which we calculate to have a 5\% false positive
 probability) does show a partial deep eclipse right at the end of the \kepler\
@@
 planet's orbital period.
-Simulations of the false positive population~--~lone primary or secondary eclipses of
-binary systems or background eclipsing binaries~--~suggest that 13 of these
+Simulations of the false positive population~--~the secondary eclipses of
+binary systems and background eclipsing binaries~--~suggest that 13 of these
 candidates have high probability of being planetary in nature.
@@
 orbital periods in the range $2-25\unit{years}$ and radii in the range
-$0.1-1\,R_\mathrm{J}$ to be \intocc\ planets per G/K dwarf.
+$0.1-1\,R_\mathrm{J}$ to be \intocc\ planets per G/K dwarf. \dfmtodo{Should this
+go in the abstract?}
 This result is qualitatively consistent with estimates from radial velocity,
@@
 
+Follow-up observations would be fruitful in confirming the false-alarm
+rates that we have estimated by further demonstrating that these planet 
+candidates are non-stellar.  Better characterization of the host stars with,
+say, parallax measurements using \gaia would help further refine the
+properties of their transiting planets.
+
 \vspace{1.5em}
@@
 NNX12AI50G), and the Moore--Sloan Data Science Environment at NYU.  
+E.A. acknowledges support from NASA grants NNX13AF20G, NNX13AF62G, and NASA Astrobiology Institutes Virtual Planetary Laboratory, supported by NASA under cooperative agreement NNH05ZDA001C.
 
@@
     \project{george} \citep{Ambikasaran:2016},
-    \project{isochrones} \citep{Morton:2015},
 	\project{matplotlib} \citep{Hunter:2007},

### 2016-07-20 document/ms.tex
wording in abstract

--- 2016-07-19 document/ms.tex
@@
 Based on these results, we measure the average occurrence rate of exoplanets
-smaller than Jupiter with orbital periods longer than two years orbiting
-Sun-like stars to be $1.80\pm 0.65$ planets per star.
+smaller than Jupiter with orbital periods longer than two years to be $1.80\pm
+0.65$ planets per Sun-like star.
 
@@
 
+TDM was supported by the National Aeronautics and Space
+Administration, under the \kepler\ participating
+scientist program (grant NNX14AE11G), and is grateful for the
+hospitality of both the Institute for Advanced Study and Carnegie
+Observatories that helped support this work.
+
 DWH was partially supported by the National Science Foundation (grant

### 2016-07-20 document/ms.tex

--- 2016-07-19 document/ms.tex
@@
 Based on these results, we measure the average occurrence rate of exoplanets
-smaller than Jupiter with orbital periods longer than two years orbiting
-Sun-like stars.  [Can this be summarized by a single value?]
+smaller than Jupiter with orbital periods longer than two years to be $1.80\pm
+0.65$ planets per Sun-like star.
 
@@
 Any single transit events discovered in the \kepler\ light curves are
-interesting in their own right, but the development of a general and systematic
-method for the discovery of planets with orbital periods longer than the
-survey baseline is also crucial for the future of of exoplanet research with the
-transit method.
+interesting in their own right, but the development of a general and
+systematic method for the discovery of planets with orbital periods longer
+than the survey baseline is also crucial for the future of exoplanet research
+with the transit method.
 All future transit surveys have shorter observational baselines than the
@@
 The methodological framework presented in the following pages is a candidate
-for this task as it could be modified and applied to these forthcoming data
-sets as they are collected in the upcoming years.
-
-A study of the population of long-period transiting planets complements
-other planet detection techniques, such as radial velocity \citep[for example][]{Cumming:2008,
-Knutson:2014, Bryan:2016}, microlensing \citep[for
+for this task.
+
+A study of the population of long-period transiting planets complements other
+planet detection techniques, such as radial velocity \citep[for
+example][]{Cumming:2008, Knutson:2014, Bryan:2016}, microlensing \citep[for
 example][]{Gould:2010, Cassan:2012, Clanton:2014, Shvartzvald:2016}, and
-direct imaging \citep[for example][]{Bowler:2016}.  The marriage of
-the radial velocity and transit techniques is particularly powerful as
-exoplanets with both mass and radius measurements can be used to study
-planetary compositions and the formation of planetary systems \citep[for
+direct imaging \citep[for example][]{Bowler:2016} surveys.
+The marriage of the radial velocity and transit techniques is particularly
+powerful as exoplanets with both mass and radius measurements can be used to
+study planetary compositions and the formation of planetary systems \citep[for
 example][]{Weiss:2014, Rogers:2015, Wolfgang:2016}.
@@
 In the future, it would be interesting to relax this goal and investigate the
-other model classes because, for example, the \modelname{box} model is
-probably sensitive to other astrophysical phenomena like secondary eclipses.
-In a cursory investigation it is clear that the majority of signals labeled
-\modelname{box} in our analysis are noise but a subset are likely to be
+other model classes; in particular, the \modelname{box} model is
+sensitive to astrophysical phenomena, notably occultations of white dwarfs,
+which produce a perfect box-shaped signal.  In a cursory investigation
+it is clear that the majority of signals labeled
+\modelname{box} in our analysis are noise; however, a subset are likely to be
 astrophysical in nature.
@@
 To simplify the analysis, we will make the strong assumption that none of the
-candidates are astrophysical false positives (the eclipse of a stellar mass
-companion, a background eclipsing binary, or the secondary eclipse of a
-long-period binary system).
+candidates are astrophysical false positives (the eclipse or occultation
+of a stellar mass companion, around either the target star or a
+faint background star).
 We revisit this assumption and discuss its validity in the following section.
@@
 package
-\exosyspop\footnote{\url{https://github.com/timothydmorton/exosyspop}}, which
-we developed for this purpose.
+\exosyspop\footnote{\url{https://github.com/timothydmorton/exosyspop}; in this
+work we use commit \textsf{e4f54288}}, which
+we developed for this purpose and utilizes the \project{isochrones}
+package \citep{Morton:2015} for simulations of stellar populations.
 
@@
 
-These results suggest that we might certainly expect to see some unblended
-eclipsing binary signals in our search.  However, this does not mean that  we
-should fear that $\sim$7 of the planet candidates might be EBs. Rather, we can
-instead inspect the synthetic observation simulations in more detail; in
+These prediction results suggest that we should indeed expect to see some
+astrophysical false positives in our search.  However, this does not mean that  we
+should fear that $\sim$7 of the planet candidates might be EBs. In particular,
+we note that these simulations do not include the full vetting procedure
+described in \sect{catalog}, and it is likely that the three impact-parameter-rejected
+candidates are EBs and that the centroid-rejected candidate is a BEB.  Thus,
+we might expect maybe two or three additional false positives among our planet
+candidates.
+
+In order to more precisely quantify which of the candidates might indeed be false
+positives, we can inspect the synthetic observation simulations in more detail. In
 particular, we can analyze the shape distribution of the different scenarios and
@@
 NNX12AI50G), and the Moore--Sloan Data Science Environment at NYU.
-E.A. acknowledges support from NASA grants NNX13AF20G, NNX13AF62G, and NASA Astrobiology Institutes Virtual Planetary Laboratory, supported by NASA under cooperative agreement NNH05ZDA001C.
+E.A. acknowledges support from NASA grants NNX13AF20G, NNX13AF62G, and NASA
+Astrobiology Institutes Virtual Planetary Laboratory, supported by NASA under
+cooperative agreement NNH05ZDA001C.
 

### 2016-07-20 document/ms.tex
adding citation for confirmed planets

@@
 
-\newpage
 \subsection{Target selection}\sectlabel{target-selection}
@@
 error bars) compared to the \kepler\ candidates (blue points) and confirmed
-planets (black points), and the Solar System (orange squares).
+planets \citep[black points;][]{Morton:2016}, and the Solar System (orange
+squares).
 The vertical dashed line indicates the full lifetime of the \kepler\ Mission;
@@
 orbital periods in the range $2-25\unit{years}$ and radii in the range
-$0.1-1\,R_\mathrm{J}$ to be \intocc\ planets per G/K dwarf. \dfmtodo{Should this
-go in the abstract?}
+$0.1-1\,R_\mathrm{J}$ to be \intocc\ planets per G/K dwarf.
 This result is qualitatively consistent with estimates from radial velocity,

### 2016-07-20 document/ms.tex
comment from agol

@@
 At a period of 7~years and a radius of $0.2\,R_\mathrm{J}$, the extrapolated
-occurrence is $0.73\pm0.28$ and at a radius of $0.6\,R_\mathrm{J}$, the
-extrapolated rate is $0.15\pm0.05$.
+occurrence rate density is $0.73\pm0.28$ and at a radius of
+$0.6\,R_\mathrm{J}$, the extrapolated rate density is $0.15\pm0.05$.
 These extrapolated values are qualitatively consistent with the rates listed
@@
 where all of the parameters~--~including $t_0$~--~are included in the fit.
-To ensure that the widths $w_*$ remain positive, we fit for $\log w_*$.
+To ensure that the widths $w_1$ and $w_2$ remain positive, we fit for
+$\log w_1$ and $\log w_2$.
 }

### 2016-07-20 document/ms.tex
another typo caught by agol
adding corner plot into text

@@
 third of the chain as burn-in.
+The posterior constraints on a few physical parameters for the single transit
+candidate in the light curve of KIC~8505215 are shown in \dfmfig{corner}.
+
+\begin{figure}~\\
+\begin{center}
+\includegraphics[width=\textwidth]{figures/params/8505215.pdf}
+\end{center}
+\caption{%
+The posterior constraints on the physical parameters for the single transit
+candidate found in the light curve of KIC~8505215.
+The contour plots show estimates of the two-dimensional marginalized
+probability densities and the histograms show the marginalized density for
+each parameter.
+This figure was generated using \project{corner.py}
+\citep{Foreman-Mackey:2016}.
+\dfmfiglabel{corner}}~\\
+\end{figure}
 
@@
 \frac{\dd m(\bvec{t};\,\meanpars)}{\dd\meanpars}^\T \, K(\kernpars)^{-1} \,
-    m(\bvec{t};\,\meanpars)
+    \bvec{r}(\meanpars)
 \end{eqnarray}
@@
 
+\newpage
 \bibliography{peerless}

### 2016-07-20 document/ms.tex
paramtab format
table format
formatting of acknowledgements

@@
 \bibliographystyle{aasjournal}
-
-% \usepackage{endnotes}
-% \let\footnote=\endnote
 
@@
 \begin{floattable}
-\begin{deluxetable}{cccccccccl}
-\tabletypesize{\footnotesize}
+\begin{deluxetable}{cccccccccccl}
+\tabletypesize{\scriptsize}
 \caption{The inferred parameters for the long-period transiting exoplanet
@@
 albedo.}
-\tablenotetext{\dagger}{Candidate has two observed transits.}
+\tablenotetext{\dagger}{The KOI number and, if applicable, the \kepler\ number
+for the target.}
 \tablenotetext{a}{Included in the \citet{Wang:2015} catalog.}
 \tablenotetext{b}{Included in the \citet{Uehara:2016} catalog.}
+\tablenotetext{c}{Candidate has two observed transits.}
 \tablecomments{The values and uncertainties indicate the 16-th, 50-th, and
@@
 
-TDM was supported by the National Aeronautics and Space
+T.D.M.\ was supported by the National Aeronautics and Space
 Administration, under the \kepler\ participating
@@
 Observatories that helped support this work.
-
-DWH was partially supported by the National Science Foundation (grant
+D.W.H.\ was partially supported by the National Science Foundation (grant
 IIS-1124794), the National Aeronautics and Space Administration (grant
 NNX12AI50G), and the Moore--Sloan Data Science Environment at NYU.
-E.A. acknowledges support from NASA grants NNX13AF20G, NNX13AF62G, and NASA
+E.A.\ acknowledges support from NASA grants NNX13AF20G, NNX13AF62G, and NASA
 Astrobiology Institutes Virtual Planetary Laboratory, supported by NASA under
@@
 
-\newpage
 \bibliography{peerless}
 
-% \theendnotes
-
 \end{document}

### 2016-07-20 document/ms.tex
adding some refs

@@
 \title{%
+\vspace{\baselineskip}
 The population of long-period transiting exoplanets
-\vspace{-3\baselineskip}  % OMG AASTEX6 IS SO BROKEN
+\vspace{-2.5\baselineskip}  % OMG AASTEX6 IS SO BROKEN
 }
@@
     Bernhard~Sch\"olkopf\altaffilmark{\mpis}
+    \vspace{\baselineskip}
 }
@@
 
+\clearpage
 \section{Introduction}
@@
 detected once, thus requiring high signal-to-noise for a reliable detection
-\citep{Gould:2004}.  %http://arxiv.org/abs/astro-ph/0405217
+\citep{Gould:2004}.
 

### 2016-07-20 document/ms.tex
Adding data release url

@@
 \newcommand{\modelname}[1]{{\textsf{#1}}}
-\newcommand{\datareleaseurl}{url to be added at submission}
+\newcommand{\datareleaseurl}{\url{http://dx.doi.org/10.5281/zenodo.58273}}
 
@@
 The posterior constraints on a few physical parameters for the single transit
-candidate in the light curve of KIC~8505215 are shown in \dfmfig{corner}.
+candidate in the light curve of KIC~8505215 are shown in \dfmfig{corner} and
+all the chains are made available online\footnote{\datareleaseurl}.
 
@@
 with git commit \texttt{\githash} (\gitdate).
+The parameter estimation results are available for download as MCMC samplings
+on Zenodo at \datareleaseurl.
 

### 2016-07-20 document/ms.tex
Adding refs to Mullally

@@
 \emph{without human intervention}.
+The method is similar in character to the recently published fully automated
+method used to generate the official DR24 exoplanet candidate catalog from
+\kepler\ \citep{Mullally:2016, Coughlin:2016}.
 Since the search methodology is fully automated, we can robustly measure the
@@
 sufficiently ``transit-like'' in shape.
-To quantify this decision, we perform a model comparison between a physical
-transit model and a set of other parameterized models for systematics.
+This step is similar to the method independently developed and recently
+published by the \kepler\ team \citep{Mullally:2016}.
+To quantify the quality of a candidate, we perform a model comparison between
+a physical transit model and a set of other parameterized models for
+systematics.
 In order for a candidate to pass this vetting step, the transit model must be
@@
 Criterion (BIC).
-The BIC is not the optimal choice for this model comparison, but it is
-more computationally computationally tractable than the alternatives, such
-as computing thousands of precise marginalized
-likelihoods or expected utilities for each model.
+The BIC is not the optimal choice for this model comparison, but it is more
+computationally computationally tractable than the alternatives, such as
+computing thousands of precise marginalized likelihoods or expected utilities
+for each model.
 The BIC can be efficiently computed and it exhibits the desired
@@
 
-\dfmtodo{More words here about comparison and interpretation.}
+% \dfmtodo{More words here about comparison and interpretation.}
 
@@
 with git commit \texttt{\githash} (\gitdate).
-The parameter estimation results are available for download as MCMC samplings
-on Zenodo at \datareleaseurl.
+The parameter estimation results represented as MCMC samplings and the
+injection results are available for download from Zenodo at \datareleaseurl.
 

### 2016-07-20 document/ms.tex
some typos

@@
 orbital periods shorter than a few years, which is shorter than the orbital periods of
-Jupiter and Saturn, which dominate the dynamics of our Solar System.  To address this deficiency,
-we performed a fully automated search for long-period exoplanets with only one
-or two transits in the archival \kepler\ light curves.
+Jupiter and Saturn, which dominate the dynamics of our Solar System.
+To address this deficiency, we perform a fully automated search for
+long-period exoplanets with only one or two transits in the archival \kepler\
+light curves.
 When applied to the $\sim 40,000$ brightest Sun-like target stars, this search
-produced \numcands\ long-period exoplanet candidates.
+produces \numcands\ long-period exoplanet candidates.
 Of these candidates, 6 are novel discoveries and 5 are in systems with inner
@@
 \dfmfig{model-comp} shows representative events that fall into different
-classes and the corresponding maximum-likelihood model.
+classes and the corresponding maximum likelihood model.
 For each candidate event, the BIC of each of these models is computed and the
@@
 To further restrict to non-grazing transits, we also reject events where the
-maximum impact parameter is greater than $1 - R_\mathrm{P} / R_\star$.
+maximum likelihood impact parameter is greater than $1 - R_\mathrm{P} /
+R_\star$.
 

### 2016-07-20 document/ms.tex
Edited last paragraph in section 5 with further caveats

@@
 treatment is subtle, but comment that this would only ever decrease the
-occurrence rate estimate.
+occurrence rate estimate.   Second, we assume that each planet candidate transits
+the star that is characterized by \citet{Huber:2014}; i.e., that each planet
+does not transit a fainter companion star or a background star.  If the planet
+does transit a companion star, then the companion star must be fainter, and hence
+denser, causing the period estimate to be underestimated.  If the planet transits
+a background star, it is more likely to be a giant star due to Malmquist bias,
+hence the density of the star and period of the planet would be overestimated. 
+Either of these scenarios has a small
+probability, so we expect that our population estimates will stand, while
+the parameter estimates for individual candidates should be taken as provisional
+until more detailed follow-up is carried out, including high-contrast imaging,
+high-resolution spectroscopy, and parallax measurements.  Third, we assume
+that the \citet{Huber:2014} parameters are accurate for each star that is transited by
+a planet candidate, and that each transit is unaffected by blending.
+Malmquist bias, Eddington bias, and metallicity bias may affect the stellar parameters
+\citep{Gaidos:2012}, and so we again caution that the individual parameter
+estimates should be taken as provisional until more detailed follow-up is
+completed.
 

### 2016-07-20 document/ms.tex
I don't like 'i.e.'

@@
 occurrence rate estimate.   Second, we assume that each planet candidate transits
-the star that is characterized by \citet{Huber:2014}; i.e., that each planet
+the star that is characterized by \citet{Huber:2014}; we assert that each planet
 does not transit a fainter companion star or a background star.  If the planet

### 2016-07-22 document/figures/obs_dist.py
adding observed distribution comparison plot

@@ -1,0 +1,50 @@
+# -*- coding: utf-8 -*-
+
+from peerless.plot_setup import COLORS, SQUARE_FIGSIZE
+
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as pl
+
+from peerless.catalogs import TargetCatalog, KOICatalog
+
+targets = TargetCatalog().df
+kois = pd.merge(KOICatalog().df, targets, how="inner", on="kepid")
+kois = kois[(kois.koi_pdisposition == "CANDIDATE") &
+            np.isfinite(kois.koi_prad) &
+            (200 < kois.koi_period) &
+            (1 < kois.koi_prad) & (kois.koi_prad < 10)]
+
+fits = pd.read_csv("../../results/fits.csv")
+fits = fits[fits.period < 5000 / 365.25]
+
+s = np.array(SQUARE_FIGSIZE)
+s[0] *= 2
+fig, axes = pl.subplots(1, 2, figsize=s)
+
+def make_plot(ax, x1, x2, rng, nbins, ticks):
+    bins = np.exp(np.linspace(np.log(rng[0]), np.log(rng[1]), nbins))
+
+    ax.hist([x2, x1], bins, histtype="stepfilled", stacked=False,
+            color=[COLORS["MODEL_1"], COLORS["MODEL_2"]],
+            alpha=0.1, lw=0)
+    n, _, _ = ax.hist(x1, bins, histtype="step", color=COLORS["MODEL_2"], lw=2)
+    ax.hist(x2, bins, histtype="step", color=COLORS["MODEL_1"], lw=2,
+            hatch="/")
+    ax.set_ylim(0, np.max(n) + 0.5)
+
+    ax.set_xscale("log")
+    ax.set_xticks(ticks)
+    ax.get_xaxis().set_major_formatter(pl.ScalarFormatter())
+    ax.set_xlim(rng)
+
+make_plot(axes[0], np.array(kois.koi_period), np.array(fits.period) * 365.25,
+          (2e2, 5e3), 7, (200, 500, 1000, 2000, 5000))
+make_plot(axes[1], np.array(kois.koi_prad), np.array(fits.radius) / 0.092051,
+          (1, 10), 7, (1, 2, 5, 10))
+
+axes[0].set_ylabel("observed number")
+axes[0].set_xlabel("orbital period [days]")
+axes[1].set_xlabel("planet radius [$R_\oplus$]")
+
+fig.savefig("obs_dist.pdf", bbox_inches="tight")

### 2016-07-22 document/figures/radius_dist.py

@@ -1,33 +1,0 @@
-# -*- coding: utf-8 -*-
-
-from peerless.plot_setup import COLORS, SQUARE_FIGSIZE
-
-import numpy as np
-import pandas as pd
-import matplotlib.pyplot as pl
-
-from peerless.catalogs import TargetCatalog, KOICatalog
-
-targets = TargetCatalog().df
-kois = pd.merge(KOICatalog().df, targets, how="inner", on="kepid")
-print(kois)
-assert 0
-
-fits = pd.read_csv("../../results/fits.csv")
-
-fig, ax = pl.subplots(1, 1, figsize=SQUARE_FIGSIZE)
-
-x = np.array(fits.radius)
-bins = np.exp(np.linspace(np.log(0.1), np.log(2.0), 6))
-bins[-1] = 2.01
-n, _, _ = ax.hist(x, bins, histtype="step", color=COLORS["DATA"])
-bins[-1] = 2.0
-ax.set_xscale("log")
-ax.set_xticks([0.1, 0.2, 0.5, 1, 2])
-ax.get_xaxis().set_major_formatter(pl.ScalarFormatter())
-ax.set_xlim(0.1, 2)
-ax.set_ylim(0, 6.5)
-ax.set_ylabel("observed number")
-ax.set_xlabel("planet radius [$R_\mathrm{J}$]")
-
-fig.savefig("radius_dist.pdf", bbox_inches="tight")

### 2016-07-22 document/ms.tex
Adding paragraph about #18

@@
 
+In \dfmfig{obs-dist}, we compare the \emph{observed} period and radius
+distributions of our discoveries to the longest-period planet candidates
+discovered transiting stars in our target list by the official \kepler\
+transit search \citep{Coughlin:2016}.
+These histograms do not take uncertainties or detection efficiency into
+account so any conclusions based on these plots should be taken with caution.
+That being said, the apparent deficit of planets in the period range between
+600 and 1000~days cannot be explained by selection effects~--~in fact, the
+geometric transit probability exacerbates the signal~--~and should be
+investigated more thoroughly.
+We postulate three scenarios and expect that the observed effect is the result
+of some combination of the three:
+\begin{itemize}
+{\item the periods of some candidates are overestimated and the missing second
+transit occurs in a data gap,}
+{\item overestimated stellar densities leading to an overestimate of the
+orbital periods and an underestimate of the radii, or}
+{\item a physical rise in the frequency of giant planets at long orbital
+periods.}
+\end{itemize}
+The first two scenarios could be confirmed or ruled out by detailed analysis
+of each candidate system and follow-up data.
+Any result would be physically interesting but a rigorous analysis that is
+beyond the scope of this \paper\ would be required to make a conclusive claim.
+
 \begin{floattable}
@@
 \end{floattable}
+
+\begin{figure*}~\\
+\begin{center}
+\includegraphics[width=\textwidth]{figures/obs_dist.pdf}
+\end{center}
+\caption{%
+A comparison between the observed orbital period and planet radius
+distributions of the long-period planet candidates reported here (blue hatched
+histogram) and the previously known planet candidates \citep{Coughlin:2016}
+with periods longer than 200~days and radii in the range $1-10\,R_\oplus$
+(orange histogram).
+\dfmfiglabel{obs-dist}}~\\
+\end{figure*}
 

### 2016-07-22 document/figures/obs_dist.py

@@ -32,7 +32,6 @@ def make_plot(ax, x1, x2, rng, nbins, ticks):
     ax.hist(x2, bins, histtype="step", color=COLORS["MODEL_1"], lw=2,
             hatch="/")
     ax.set_ylim(0, np.max(n) + 0.5)
-
     ax.set_xscale("log")
     ax.set_xticks(ticks)
     ax.get_xaxis().set_major_formatter(pl.ScalarFormatter())

### 2016-07-22 document/publish.py
add script to prepare manuscript for arxiv

@@ -1,0 +1,52 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+from __future__ import division, print_function
+import os
+import re
+import glob
+import shutil
+from datetime import date
+from subprocess import check_call
+
+datestamp = date.today().strftime("%m%d")
+TMPDIR = "fore" + datestamp
+outfn = TMPDIR+".tar"
+tex = open("ms.tex", "r").read()
+
+try:
+    os.makedirs(TMPDIR)
+except os.error:
+    pass
+
+def rename(fn):
+    a, b = os.path.split(fn)
+    strt, end = os.path.split(a)
+    if len(strt):
+        b = end + "-" + b
+    return b, fn
+
+def find_figures(tex):
+    return re.findall("includegraphics(?:.*?){(.*)}", tex)
+
+def find_includes(tex):
+    return re.findall("\\include{(.*)}", tex)
+
+for fn in find_includes(tex):
+    txt = open(fn + ".tex").read()
+    tex = tex.replace("\\include{{{0}}}".format(fn), txt)
+
+for name, loc in map(rename, find_figures(tex)):
+    shutil.copyfile(loc, os.path.join(TMPDIR, name))
+    tex = tex.replace(loc, name)
+
+shutil.copyfile("aastex6.cls", os.path.join(TMPDIR, "aastex6.cls"))
+shutil.copyfile("aasjournal.bst", os.path.join(TMPDIR, "aasjournal.bst"))
+shutil.copyfile("ms.bbl", os.path.join(TMPDIR, "ms.bbl"))
+open(os.path.join(TMPDIR, "ms.tex"), "w").write(tex)
+check_call(" ".join(["cd", TMPDIR+";",
+                     "tar", "-cf", os.path.join("..", outfn), "*"]),
+           shell=True)
+shutil.rmtree(TMPDIR)
+
+print("Wrote file: '{0}'".format(outfn))

### 2016-07-22 document/ms.tex
making the catalog its own section
stoopid tex formatting
smaller font in table 7
moar stoopid tex formatting
Added further discussion of Figure 6

@@
 and quietest Sun-like stars for long-period transiting exoplanets.
-In this section, we describe the target selection process, the parameter
-estimation procedure, and present the catalog of discoveries.
+In this section, we describe the target selection process and the parameter
+estimation procedure.
 
@@
 
-\subsection{Catalog of transit candidates}\sectlabel{catalog}
+\section{Catalog of transit candidates}\sectlabel{catalog}
 
@@
 600 and 1000~days cannot be explained by selection effects~--~in fact, the
-geometric transit probability exacerbates the signal~--~and should be
-investigated more thoroughly.
+decreasing geometric transit probability and decreased orbital phase coverage at
+longer periods exacerbates the signal~--~and should be
+investigated more thoroughly.  The decline at longer periods can be attributed
+to the declining transit detection probability.
 We postulate three scenarios and expect that the observed effect is the result
@@
 beyond the scope of this \paper\ would be required to make a conclusive claim.
+
+The difference between the observed radius distributions apparent in Figure \ref{obs-dist}
+can be attributed to the drop off in sensitivity of our search at small planet
+radius depicted in Figure \ref{completeness}.  The \kepler\ survey, on the other 
+hand, has increasing sensitivity to smaller planets due to the addition of multiple 
+transits at shorter period.
 
@@
 
+\newpage
 \section{Empirical search completeness}\sectlabel{completeness}
@@
 \begin{deluxetable}{ccccccccc}
-\tabletypesize{\footnotesize}
+\tabletypesize{\scriptsize}
 \caption{The predicted masses and radial velocity signals for the candidates

### 2016-07-22 document/ms.tex
figure refs

@@
 
-The difference between the observed radius distributions apparent in Figure \ref{obs-dist}
-can be attributed to the drop off in sensitivity of our search at small planet
-radius depicted in Figure \ref{completeness}.  The \kepler\ survey, on the other 
-hand, has increasing sensitivity to smaller planets due to the addition of multiple 
-transits at shorter period.
+The difference between the observed radius distributions apparent in
+\dfmfig{obs-dist} can be attributed to the drop off in sensitivity of our
+search at small planet radius depicted in \dfmfig{completeness}.
+The \kepler\ survey, on the other hand, has increasing sensitivity to smaller
+planets due to the addition of multiple transits at shorter period.
 
@@
 
-\newpage
 \section{Empirical search completeness}\sectlabel{completeness}
@@
 
-\newpage
+% \newpage
 \bibliography{peerless}

### 2016-07-22 document/figures/completeness.py
changing units of analytic completeness model

@@ -48,8 +48,7 @@ def error(params, ln_radius, ln_period, flag):
     pred = m > 0.5
     return np.sum(pred != flag)
 
-
-x, y = np.log(np.array(inj.radius)), np.log(np.array(inj.period))
+x, y = np.log(np.array(inj.radius)/0.0995), np.log(np.array(inj.period)/365.25)
 flag = np.array(inj.accept, dtype=int)
 params = np.array([0.0, 1.0, 0.0, 0.6, 0.0, 10.0, 0.0, -3.0])
 r = minimize(nll, params, jac=grad(nll), args=(x, y, flag))

### 2016-07-22 document/figures/completeness.py
units of analytic completeness model

@@ -50,7 +50,7 @@ def error(params, ln_radius, ln_period, flag):
 
 x, y = np.log(np.array(inj.radius)/0.0995), np.log(np.array(inj.period)/365.25)
 flag = np.array(inj.accept, dtype=int)
-params = np.array([0.0, 1.0, 0.0, 0.6, 0.0, 10.0, 0.0, -3.0])
+params = np.array([0.0, 0.5, 0.0, 0.5, 0.0, 50.0, 0.0, -1.0])
 r = minimize(nll, params, jac=grad(nll), args=(x, y, flag))
 with open("../completenessfit.tex", "w") as f:
     f.write(r"""\newcommand{{\parama}}{{{0[0]:.2f}}}
@@ -71,7 +71,7 @@ fig, ax = pl.subplots(1, 1, figsize=s)
 ln_radius_bins = np.linspace(np.log(0.15), np.log(2.2), 100)
 ln_period_bins = np.linspace(np.log(2), np.log(25), 101)
 Y, X = np.meshgrid(ln_period_bins, ln_radius_bins, indexing="ij")
-Z = analytic_model(r.x, X + np.log(0.0995), Y + np.log(365.25))
+Z = analytic_model(r.x, X, Y)
 c = ax.pcolor(np.exp(ln_period_bins), np.exp(ln_radius_bins), Z.T,
               cmap="Blues", vmin=0, vmax=1)
 cbar = fig.colorbar(c)

### 2016-07-22 document/ms.tex
unambigous notation
edits to ms.tex

--- 2016-07-22 document/ms.tex
@@
 gives an estimate of the probability of detecting an exoplanet transit with a
-given set of parameters, \emph{conditioned on the fact that it transits}.
+given set of parameters, \emph{conditioned on the fact that it transits the
+star during a time when the star was being observed by \kepler\}.
 We will call this function $Q_{\mathrm{det},k}(\params)$ where \params\ is the

### 2016-07-22 document/completeness.jl

@@ -1,0 +1,15 @@
+using PyPlot
+using CGS
+nperiod = 100
+p = logspace(log10(2*365.25),log10(5000),nperiod)
+lnR = log(5*REARTH/RSUN)
+qdet = zeros(nperiod)
+for i=1:nperiod
+  qdet[i] = minimum([maximum([(-0.06*log(p[i])+0.78)*(-0.45*lnR+0.95),0]),1])/(1+exp(-(0.7*log(p[i])-1.1)*(lnR-(-0.07*log(p[i])-2.8))))
+end
+fduty = 0.97
+qwin = 1. - (1.-fduty).^(4./p)
+qgeom = 0.005./(p./365.25).^(2/3)
+loglog(p,qdet)
+loglog(p,qdet.*qwin)
+loglog(p,qdet.*qwin.*qgeom)

### 2016-07-22 document/ms.tex

@@
     \frac{\mathrm{min}[\mathrm{max}[a(P)\,b(R),\,0],\,1]}
-         {1+\exp\left[-k(P)\,(\ln R-x(P))\right]}
+         {1+\exp\left[-k(P)\,(\ln R / R_\mathrm{J}-x(P))\right]}
 \end{eqnarray}
@@
 \begin{eqnarray}
-a(P) = a_1\,\ln P + a_2 \,,\quad
-b(R) = b_1\,\ln R + b_2 \,,\quad \\
-k(P) = k_1\,\ln P + k_2 \,,\,\mathrm{and}\quad
-x(P) = x_1\,\ln P + x_2 \,.
+a(P) = a_1\,\ln P / \unit{yr} + a_2 \,,\quad
+b(R) = b_1\,\ln R / R_\mathrm{J} + b_2 \,,\quad \\
+k(P) = k_1\,\ln P / \unit{yr} + k_2 \,,\,\mathrm{and}\quad
+x(P) = x_1\,\ln P / \unit{yr} + x_2 \,.
 \end{eqnarray}

### 2016-07-22 document/ms.tex
overplotted completeness with period histogram

@@
 given set of parameters, \emph{conditioned on the fact that it transits the
-star during a time when the star was being observed by \kepler\}.
+star during a time when the star was being observed by Kepler}.
 We will call this function $Q_{\mathrm{det},k}(\params)$ where \params\ is the

### 2016-07-22 document/completeness.jl

@@ -1,15 +1,17 @@
 using PyPlot
 using CGS
 nperiod = 100
-p = logspace(log10(2*365.25),log10(5000),nperiod)
-lnR = log(5*REARTH/RSUN)
+p = logspace(log10(2),log10(5000/365.25),nperiod)
+lnR = log(4*REARTH/RJUPITER)
 qdet = zeros(nperiod)
 for i=1:nperiod
-  qdet[i] = minimum([maximum([(-0.06*log(p[i])+0.78)*(-0.45*lnR+0.95),0]),1])/(1+exp(-(0.7*log(p[i])-1.1)*(lnR-(-0.07*log(p[i])-2.8))))
+  qdet[i] = minimum([maximum([(-0.13*log(p[i])+0.95)*(-0.20*lnR+0.90),0]),1])/(1+exp(-(0.7*log(p[i])+3.06)*(lnR-(-0.07*log(p[i])-0.91))))
 end
 fduty = 0.97
 qwin = 1. - (1.-fduty).^(4./p)
-qgeom = 0.005./(p./365.25).^(2/3)
-loglog(p,qdet)
-loglog(p,qdet.*qwin)
-loglog(p,qdet.*qwin.*qgeom)
+qgeom = 0.005./p.^(2/3)
+#loglog(p,qdet)
+#loglog(p,qdet.*qwin)
+semilogx(p*365.25,qdet.*qwin.*qgeom.*1e4)
+plot([200,200,340,340,590,590],[0,15,15,12,12,0])
+plot([590,590,1000,1000,1700,1700,3000,3000,5000,5000],[0,1,1,6,6,5,5,3,3,0])

### 2016-07-24 document/ms.tex
comments from @bernhardschoelkopf

@@
 example][]{Gould:2010, Cassan:2012, Clanton:2014, Shvartzvald:2016}, and
-direct imaging \citep[for example][]{Bowler:2016} surveys.
+direct imaging \citep[for example][]{Bowler:2016}.
 The marriage of the radial velocity and transit techniques is particularly
@@
 The first is that the transit probability for long-period planets is very low;
-scaling as $\propto P^{-5/3}$ for orbital periods longer than the
+scaling as $\propto P^{-5/3}$ for orbital periods $P$ longer than the
 baseline of contiguous observations.
@@
 m(t) &=& \left\{\begin{array}{ll}
-    \mu, & \mbox{\,if $|t - t_0| < \tau/2$} \\
-    \mu - \delta, & \mbox{\,otherwise}
+    \mu - \delta, & \mbox{\,if $|t - t_0| < \tau/2$} \\
+    \mu, & \mbox{\,otherwise}
 \end{array}\right. \quad.
@@
 The BIC is not the optimal choice for this model comparison, but it is more
-computationally computationally tractable than the alternatives, such as
-computing thousands of precise marginalized likelihoods or expected utilities
-for each model.
+computationally tractable than the alternatives, such as computing thousands
+of precise marginalized likelihoods or expected utilities for each model.
 The BIC can be efficiently computed and it exhibits the desired
@@
 other model classes; in particular, the \modelname{box} model is
-sensitive to astrophysical phenomena, notably occultations of white dwarfs,
-which produce a perfect box-shaped signal.  In a cursory investigation
-it is clear that the majority of signals labeled
+sensitive to astrophysical phenomena, notably occultations of white dwarfs.
+In a cursory investigation it is clear that the majority of signals labeled
 \modelname{box} in our analysis are noise; however, a subset are likely to be
@@
 The candidate in the light curve of KIC~4754460 is an individual transit
-candidate but another deeper eclipse can be found at a KBJD of 1587.13; right
-at the beginning of Quarter 17.
+candidate but another deeper eclipse can be found at a \kepler\ Barycentric
+Julian Date (KBJD) of 1587.13; right at the beginning of Quarter 17.
 This eclipse was missed by the automated search because only the second half
@@
 The most likely explanation of this system is that the listed candidate is the
-secondary eclipse of a binary system but we will keep the candidate is the
+secondary eclipse of a binary system but we will keep the candidate in the
 list and treat this effect statistically in \sect{false-positives}.
@@
 the planet parameters (including orbital period).
-This assumption is only justified because we are only making high-level
-measurements of the mean occurrence rate in bins larger than the uncertainties.
+This assumption is justified because we are only making high-level
+measurements of the mean occurrence rate in bins larger than the
+uncertainties.
 
@@
 \tabletypesize{\scriptsize}
-\caption{The predicted masses and radial velocity signals for the candidates
-from Table~\ref{tab:catalog} \label{tab:masses}}
+\caption{The predicted masses and radial velocity semi-amplitudes for the
+candidates from Table~\ref{tab:catalog} \label{tab:masses}}
 \include{masstab}
@@
 astrometry would provide a measurement of the density of a planet that would
-be invaluable for the study of planetary compositions.
+be valuable for the study of planetary compositions.
 
@@
 
-In priniciple the \gaia\ Mission will be very sensitive to the astrometric
+In principle the \gaia\ Mission will be very sensitive to the astrometric
 wobble produced by a long-period exoplanet \citep{Perryman:2014}.
@@
 \end{eqnarray}
-% obviously fix to your notation!
 where $a$ is the semi-major axis, $D$ is the distance from the observer to the
@@
 in the final \gaia\ data depends on this precision, the number of crossings of
-the star through the \gaia\ focal plane, and details of how the projected
+the star through the \gaia\ field-of-view, and details of how the projected
 orbit is sampled by the time history of the focal-plane crossings.

### 2016-07-24 document/figures/full_sample.py
adding posterior samples to figure 5

@@ -2,16 +2,24 @@
 
 from peerless.plot_setup import COLORS
 
+import os
+import sys
+import h5py
 import matplotlib
 import numpy as np
 import pandas as pd
 import matplotlib.pyplot as pl
 
-from peerless.catalogs import KOICatalog
+from peerless.catalogs import KOICatalog, TargetCatalog
+
+np.random.seed(42)
+fits_path = sys.argv[1]
 
 fig, ax = pl.subplots(1, 1, figsize=(6, 4))
 
-kois = KOICatalog().df
+targets = TargetCatalog().df
+# kois = KOICatalog().df
+kois = pd.merge(KOICatalog().df, targets, how="inner", on="kepid")
 m = kois.koi_disposition == "CONFIRMED"
 x, y = kois[m].koi_period, kois[m].koi_prad
 
@@ -65,3 +73,18 @@ y = np.array(fits.radius) * rf
 ax.errorbar(x, y, xerr=xerr, yerr=yerr, fmt=".g", capsize=0)
 
 fig.savefig("full_sample_plus_cands.pdf", bbox_inches="tight")
+fig.savefig("full_sample_plus_cands.png", bbox_inches="tight")
+
+for kicid in np.array(fits.kicid):
+    fn = os.path.join(fits_path, "{0}.h5".format(kicid))
+    with h5py.File(fn, "r") as f:
+        nsamp, nwalk = f["chain"].shape
+        s_inds = np.random.randint(nsamp, size=500)
+        w_inds = np.random.randint(nwalk, size=500)
+        periods = f["params"]["period"][s_inds, w_inds]
+        radii = np.exp(f["chain"]["bodies[0]:ln_radius"][s_inds, w_inds])
+        radii /= 0.009171
+    ax.plot(periods, radii, ".g", alpha=0.1, ms=3, rasterized=True, mec="none")
+
+fig.savefig("full_sample_plus_cands_samps.pdf", bbox_inches="tight", dpi=300)
+fig.savefig("full_sample_plus_cands_samps.png", bbox_inches="tight", dpi=300)

### 2016-07-26 document/figures/full_sample.py
showing minimum period in sample plot

@@ -13,22 +13,28 @@ import matplotlib.pyplot as pl
 from peerless.catalogs import KOICatalog, TargetCatalog
 
 np.random.seed(42)
+all_kois = False
+if "--all-kois" in sys.argv:
+    sys.argv.pop(sys.argv.index("--all-kois"))
+    all_kois = True
 fits_path = sys.argv[1]
 
 fig, ax = pl.subplots(1, 1, figsize=(6, 4))
 
 targets = TargetCatalog().df
-# kois = KOICatalog().df
-kois = pd.merge(KOICatalog().df, targets, how="inner", on="kepid")
+if all_kois:
+    kois = KOICatalog().df
+else:
+    kois = pd.merge(KOICatalog().df, targets, how="inner", on="kepid")
 m = kois.koi_disposition == "CONFIRMED"
 x, y = kois[m].koi_period, kois[m].koi_prad
 
 x0 = np.exp(np.linspace(np.log(0.1), np.log(9e4), 500))
 for f in np.exp(np.linspace(np.log(0.001), np.log(100), 8)):
     y0 = np.sqrt(f * np.sqrt(x0))
-    ax.plot(x0, y0, "k", lw=0.5, alpha=0.5)
+    ax.plot(x0, y0, "k", lw=0.5, alpha=0.5, zorder=-100)
 
-ax.loglog(x, y, ".", color=COLORS["DATA"], ms=4)
+ax.loglog(x, y, ".", color=COLORS["DATA"], ms=3)
 ax.set_xlim(0.5, 450.)
 ax.set_ylim(0.3, 30)
 ax.set_xlabel("orbital period [days]")
@@ -41,8 +47,7 @@ ax.yaxis.set_major_formatter(fmt)
 # Plot KOIs.
 m = kois.koi_disposition == "CANDIDATE"
 x, y = kois[m].koi_period, kois[m].koi_prad
-ax.plot(x, y, ".",  # color=COLORS["MODEL_1"],
-        ms=3, alpha=0.3, zorder=-1)
+ax.plot(x, y, ".", ms=3, alpha=0.3, mec="none", zorder=-1)
 
 fig.set_tight_layout(True)
 fig.savefig("full_sample_no_ss_zoom.pdf", bbox_inches="tight")
@@ -52,10 +57,10 @@ rad = np.array("2439.7 6051.8 6371.00 3389.5 69911 58232 25362 24622"
                .split(), dtype=float)
[…]

### 2016-07-26 document/ms.tex

@@
 
-In \dfmfig{obs-dist}, we compare the \emph{observed} period and radius
-distributions of our discoveries to the longest-period planet candidates
-discovered transiting stars in our target list by the official \kepler\
-transit search \citep{Coughlin:2016}.
-These histograms do not take uncertainties or detection efficiency into
-account so any conclusions based on these plots should be taken with caution.
-That being said, the apparent deficit of planets in the period range between
-600 and 1000~days cannot be explained by selection effects~--~in fact, the
-decreasing geometric transit probability and decreased orbital phase coverage at
-longer periods exacerbates the signal~--~and should be
-investigated more thoroughly.  The decline at longer periods can be attributed
-to the declining transit detection probability.
-We postulate three scenarios and expect that the observed effect is the result
-of some combination of the three:
-\begin{itemize}
-{\item the periods of some candidates are overestimated and the missing second
-transit occurs in a data gap,}
-{\item overestimated stellar densities leading to an overestimate of the
-orbital periods and an underestimate of the radii, or}
-{\item a physical rise in the frequency of giant planets at long orbital
-periods.}
-\end{itemize}
-The first two scenarios could be confirmed or ruled out by detailed analysis
-of each candidate system and follow-up data.
-Any result would be physically interesting but a rigorous analysis that is
-beyond the scope of this \paper\ would be required to make a conclusive claim.
-
-The difference between the observed radius distributions apparent in
-\dfmfig{obs-dist} can be attributed to the drop off in sensitivity of our
-search at small planet radius depicted in \dfmfig{completeness}.
-The \kepler\ survey, on the other hand, has increasing sensitivity to smaller
-planets due to the addition of multiple transits at shorter period.
-
 \begin{floattable}
@@
 error bars) compared to the \kepler\ candidates (blue points) and confirmed
-planets \citep[black points;][]{Morton:2016}, and the Solar System (orange
-squares).
+planets \citep[black points;][]{Morton:2016} found in our target sample, and
+the Solar System (orange squares).
 The vertical dashed line indicates the full lifetime of the \kepler\ Mission;
@@
 \end{floattable}
-
-\begin{figure*}~\\
-\begin{center}
-\includegraphics[width=\textwidth]{figures/obs_dist.pdf}
-\end{center}
-\caption{%
-A comparison between the observed orbital period and planet radius
-distributions of the long-period planet candidates reported here (blue hatched
-histogram) and the previously known planet candidates \citep{Coughlin:2016}
-with periods longer than 200~days and radii in the range $1-10\,R_\oplus$
-(orange histogram).
-\dfmfiglabel{obs-dist}}~\\
-\end{figure*}
 

### 2016-07-26 document/figures/full_sample.py
error bar format

@@ -79,7 +79,7 @@ yerr = np.array(fits[["radius_uncert_minus", "radius_uncert_plus"]]).T * rf
 x = np.array(fits.period) * pf
 y = np.array(fits.radius) * rf
 ax.errorbar(x, y, xerr=xerr_2, fmt=",k", capsize=2, lw=0.5, zorder=-100)
-ax.errorbar(x, y, xerr=xerr, yerr=yerr, fmt=".g", capsize=0, lw=1.0)
+ax.errorbar(x, y, xerr=xerr, yerr=yerr, fmt=".g", capsize=1.5, lw=1.0)
 
 fig.savefig("full_sample_plus_cands.pdf", bbox_inches="tight")
 fig.savefig("full_sample_plus_cands.png", bbox_inches="tight", dpi=300)

### 2016-07-26 document/ms.tex
a few words about assumptions in summary

@@
 integrated  Keplerian orbit with a quadratic limb darkening law for the
-central body\footnote{Implemented at \url{https://github.com/dfm/transit};
-this \paper\ uses git commit \textsf{482d99b} of that repository.}.
+central body\footnote{\url{https://github.com/dfm/transit}; in this work, we
+use git commit \textsf{482d99b}.}.
 It has previously been established that the orbital period of a transiting
@@
 
-Five candidate transit events in the light curves of four targets were
-rejected because of a significant centroid shift or a large impact parameter.
-These events are probably astrophysical eclipses from binary star systems that
-were not found by previous studies of long-period eclipsing binary systems.
-We do not consider these events further in the following analysis but
-Table~\ref{tab:rejects} lists these events and their properties for posterity.
-
 The candidate in the light curve of KIC~4754460 is an individual transit
@@
 list and treat this effect statistically in \sect{false-positives}.
+
+Five candidate transit events in the light curves of four targets were
+rejected because of a significant centroid shift or a large impact parameter.
+These events are probably astrophysical eclipses from binary star systems that
+were not found by previous studies of long-period eclipsing binary systems.
+We do not consider these events further in the following analysis but
+Table~\ref{tab:rejects} lists these events and their properties for posterity.
 
@@
 the Solar System (orange squares).
-The vertical dashed line indicates the full lifetime of the \kepler\ Mission;
-planets with orbital periods longer than this will show at most one transit.
+The thin black error bars to the left of each candidate indicate the minimum
+period allowed for each candidate by the prior assumption that no other
+transit occurred during the baseline of \kepler\ observations of the target.
 The vertical solid line shows the absolute maximum period accessible to
-transit searches that require at least three transits.
+transit searches that require at least three transits in the \kepler\ data.
 \dfmfiglabel{full-sample}}~\\
@@
 \exosyspop\footnote{\url{https://github.com/timothydmorton/exosyspop}; in this
-work we use commit \textsf{e4f54288}}, which
+work, we use git commit \textsf{e4f54288}.}, which
 we developed for this purpose and utilizes the \project{isochrones}
@@
 planet's orbital period.
-Simulations of the false positive population~--~lone primary or secondary eclipses of
-binary systems or background eclipsing binaries~--~suggest that 13 of these
-candidates have high probability of being planetary in nature.
+The constraint on the period is also informed by the simplifying assumption
+that no other transit could occur during the baseline of \kepler\ observations
+of the target.
+Simulations of the false positive population~--~lone primary or secondary
+eclipses of binary systems or background eclipsing binaries~--~suggest that 13
+of these candidates have high probability of being planetary in nature.
 
@@
 
-% \dfmtodo{More words here about comparison and interpretation.}
-
-These long-period exoplanet candidates are potentially interesting candidates
-for follow-up observations.
 Using a probabilistic mass--radius relationship, we predict the masses of our
@@
 
+Any detailed analysis of individual systems detected with only a single
+transit requires follow-up observations to convincingly rule out false
+positive scenarios and to better characterize the stellar host parameters
+(with, for example, parallax measurements from \gaia).
+The conclusions of this work~--~and all other occurrence rate results based on
+\kepler\ data~--~are conditioned on the assumption that the stellar
+characterization of the target sample is systematic and un-biased.
+The main population-level results should be fairly insensitive systematic
+issues with the sample but a rigorous analysis of these effects will be
+required to come to more detailed conclusions about this population of
+long-period transiting planets.
+
 Our method of transit discovery is especially relevant for future photometric
@@
 prioritize follow-up, and study their population.
-
-Follow-up observations would be fruitful in confirming the false-alarm
-rates that we have estimated by further demonstrating that these planet
-candidates are non-stellar.  Better characterization of the host stars with,
-say, parallax measurements using \gaia would help further refine the
-properties of their transiting planets.
 
@@
 
-\acknowledgments
+% \acknowledgments
+\vspace{1.5em}
 It is a pleasure to thank
@@
 So Hattori,
+Heather Knutson,
 Hans-Walter Rix,
@@
 
+\newpage
 \appendix

### 2016-07-26 document/publish.py

@@ -4,7 +4,6 @@
 from __future__ import division, print_function
 import os
 import re
-import glob
 import shutil
 from datetime import date
 from subprocess import check_call

### 2016-07-27 document/ms.tex
adding window function figure

@@
 Angie Wolfgang
-for helpful contributions to the ideas and code presented here.
+for helpful discussions and contributions.
 

### 2016-07-27 document/figures/window_function.py

@@ -1,0 +1,24 @@
+# -*- coding: utf-8 -*-
+
+from __future__ import division, print_function
+
+import numpy as np
+import pandas as pd
+
+import matplotlib.pyplot as pl
+
+from peerless.plot_setup import SQUARE_FIGSIZE
+
+f_duty = 0.6
+T_k = 700.0
+
+P = np.linspace(100.0, 5000.0, 5000)
+
+fig, ax = pl.subplots(1, 1, figsize=SQUARE_FIGSIZE)
+ax.plot(P, 1.0 - (1.0 - f_duty) ** (T_k / P), "k")
+ax.plot(P, (T_k * f_duty) / P, "g")
+ax.xaxis.set_major_locator(pl.MaxNLocator(3))
+ax.set_ylim(0, 1.0)
+ax.set_xlabel("period")
+ax.set_ylabel("$Q_t$")
+fig.savefig("window_function.png")

### 2016-07-27 document/figures/window_function.py
window function

@@ -9,7 +9,7 @@ import matplotlib.pyplot as pl
 
 from peerless.plot_setup import SQUARE_FIGSIZE
 
-f_duty = 0.6
+f_duty = 0.7
 T_k = 700.0
 
 P = np.linspace(100.0, 5000.0, 5000)

### 2016-07-27 document/ms.tex
fixed window function

@@
 Based on these results, we measure the average occurrence rate of exoplanets
-smaller than Jupiter with orbital periods longer than two years to be $1.80\pm
-0.65$ planets per Sun-like star.
+smaller than Jupiter with orbital periods longer than two years to be
+$2.0\pm0.7$ planets per Sun-like star.
 
@@
 \begin{eqnarray}
-Q_{\mathrm{win},k} (\params) &=& 1 - (1 - f_{\mathrm{duty},k})^{T_k/P}
+Q_{\mathrm{win},k} (\params) &=& \left\{\begin{array}{ll}
+1 - (1 - f_{\mathrm{duty},k})^{T_k/P} & \quad\mbox{if $P \le T_k$} \\
+T_k\,f_{\mathrm{duty},k} / P & \quad\mbox{otherwise}
+\end{array}\right.
 \end{eqnarray}

### 2016-07-27 document/ms.tex
minor edit & GAIA may help with EB FAP

--- 2016-07-27 document/ms.tex
@@
 example][]{Gould:2010, Cassan:2012, Clanton:2014, Shvartzvald:2016}, and
-direct imaging \citep[for example][]{Bowler:2016}.
+direct imaging \citep[for example][]{Bowler:2016} surveys.
 The marriage of the radial velocity and transit techniques is particularly
@@
 The first is that the transit probability for long-period planets is very low;
-scaling as $\propto P^{-5/3}$ for orbital periods $P$ longer than the
+scaling as $\propto P^{-5/3}$ for orbital periods longer than the
 baseline of contiguous observations.
@@
 m(t) &=& \left\{\begin{array}{ll}
-    \mu - \delta, & \mbox{\,if $|t - t_0| < \tau/2$} \\
-    \mu, & \mbox{\,otherwise}
+    \mu, & \mbox{\,if $|t - t_0| < \tau/2$} \\
+    \mu - \delta, & \mbox{\,otherwise}
 \end{array}\right. \quad.
@@
 The BIC is not the optimal choice for this model comparison, but it is more
-computationally tractable than the alternatives, such as computing thousands
-of precise marginalized likelihoods or expected utilities for each model.
+computationally computationally tractable than the alternatives, such as
+computing thousands of precise marginalized likelihoods or expected utilities
+for each model.
 The BIC can be efficiently computed and it exhibits the desired
@@
 other model classes; in particular, the \modelname{box} model is
-sensitive to astrophysical phenomena, notably occultations of white dwarfs.
-In a cursory investigation it is clear that the majority of signals labeled
+sensitive to astrophysical phenomena, notably occultations of white dwarfs,
+which produce a perfect box-shaped signal.  In a cursory investigation
+it is clear that the majority of signals labeled
 \modelname{box} in our analysis are noise; however, a subset are likely to be
@@
 integrated  Keplerian orbit with a quadratic limb darkening law for the
-central body\footnote{\url{https://github.com/dfm/transit}; in this work, we
-use git commit \textsf{482d99b}.}.
+central body\footnote{Implemented at \url{https://github.com/dfm/transit};
+this \paper\ uses git commit \textsf{482d99b} of that repository.}.
 It has previously been established that the orbital period of a transiting
@@
 
-The candidate in the light curve of KIC~4754460 is an individual transit
-candidate but another deeper eclipse can be found at a \kepler\ Barycentric
-Julian Date (KBJD) of 1587.13; right at the beginning of Quarter 17.
-This eclipse was missed by the automated search because only the second half
-of the eclipse is observed.
-The most likely explanation of this system is that the listed candidate is the
-secondary eclipse of a binary system but we will keep the candidate in the
-list and treat this effect statistically in \sect{false-positives}.
-
 Five candidate transit events in the light curves of four targets were
@@
 Table~\ref{tab:rejects} lists these events and their properties for posterity.
+
+The candidate in the light curve of KIC~4754460 is an individual transit
+candidate but another deeper eclipse can be found at a KBJD of 1587.13; right
+at the beginning of Quarter 17.
+This eclipse was missed by the automated search because only the second half
+of the eclipse is observed.
+The most likely explanation of this system is that the listed candidate is the
+secondary eclipse of a binary system but we will keep the candidate is the
+list and treat this effect statistically in \sect{false-positives}.
+
+In \dfmfig{obs-dist}, we compare the \emph{observed} period and radius
+distributions of our discoveries to the longest-period planet candidates
+discovered transiting stars in our target list by the official \kepler\
+transit search \citep{Coughlin:2016}.
+These histograms do not take uncertainties or detection efficiency into
+account so any conclusions based on these plots should be taken with caution.
+That being said, the apparent deficit of planets in the period range between
+600 and 1000~days cannot be explained by selection effects~--~in fact, the
+decreasing geometric transit probability and decreased orbital phase coverage at
+longer periods exacerbates the signal~--~and should be
+investigated more thoroughly.  The decline at longer periods can be attributed
+to the declining transit detection probability.
+We postulate three scenarios and expect that the observed effect is the result
+of some combination of the three:
+\begin{itemize}
+{\item the periods of some candidates are overestimated and the missing second
+transit occurs in a data gap,}
+{\item overestimated stellar densities leading to an overestimate of the
+orbital periods and an underestimate of the radii, or}
+{\item a physical rise in the frequency of giant planets at long orbital
+periods.}
+\end{itemize}
+The first two scenarios could be confirmed or ruled out by detailed analysis
+of each candidate system and follow-up data.
+Any result would be physically interesting but a rigorous analysis that is
+beyond the scope of this \paper\ would be required to make a conclusive claim.
+
+The difference between the observed radius distributions apparent in
+\dfmfig{obs-dist} can be attributed to the drop off in sensitivity of our
+search at small planet radius depicted in \dfmfig{completeness}.
+The \kepler\ survey, on the other hand, has increasing sensitivity to smaller
+planets due to the addition of multiple transits at shorter period.
 
@@
 error bars) compared to the \kepler\ candidates (blue points) and confirmed
-planets \citep[black points;][]{Morton:2016} found in our target sample, and
-the Solar System (orange squares).
-The thin black error bars to the left of each candidate indicate the minimum
-period allowed for each candidate by the prior assumption that no other
-transit occurred during the baseline of \kepler\ observations of the target.
+planets \citep[black points;][]{Morton:2016}, and the Solar System (orange
+squares).
+The vertical dashed line indicates the full lifetime of the \kepler\ Mission;
+planets with orbital periods longer than this will show at most one transit.
 The vertical solid line shows the absolute maximum period accessible to
-transit searches that require at least three transits in the \kepler\ data.
+transit searches that require at least three transits.
 \dfmfiglabel{full-sample}}~\\
@@
 
+\begin{figure*}~\\
+\begin{center}
+\includegraphics[width=\textwidth]{figures/obs_dist.pdf}
+\end{center}
+\caption{%
+A comparison between the observed orbital period and planet radius
+distributions of the long-period planet candidates reported here (blue hatched
+histogram) and the previously known planet candidates \citep{Coughlin:2016}
+with periods longer than 200~days and radii in the range $1-10\,R_\oplus$
+(orange histogram).
+\dfmfiglabel{obs-dist}}~\\
+\end{figure*}
+
 \section{Empirical search completeness}\sectlabel{completeness}
 
-To measure the completeness of search procedure described in \sect{search}, we
+To measure the completeness of the search procedure described in \sect{search}, we
 exploit the fact that transit signals are sparse and rare.
@@
 the planet parameters (including orbital period).
-This assumption is justified because we are only making high-level
-measurements of the mean occurrence rate in bins larger than the
-uncertainties.
+This assumption is only justified because we are only making high-level
+measurements of the mean occurrence rate in bins larger than the uncertainties.
 
@@
 \exosyspop\footnote{\url{https://github.com/timothydmorton/exosyspop}; in this
-work, we use git commit \textsf{e4f54288}.}, which
+work we use commit \textsf{e4f54288}}, which
 we developed for this purpose and utilizes the \project{isochrones}
@@
 \tabletypesize{\scriptsize}
-\caption{The predicted masses and radial velocity semi-amplitudes for the
-candidates from Table~\ref{tab:catalog} \label{tab:masses}}
+\caption{The predicted masses and radial velocity signals for the candidates
+from Table~\ref{tab:catalog} \label{tab:masses}}
 \include{masstab}
@@
 astrometry would provide a measurement of the density of a planet that would
-be valuable for the study of planetary compositions.
+be invaluable for the study of planetary compositions.
 
@@
 
-In principle the \gaia\ Mission will be very sensitive to the astrometric
+In priniciple the \gaia\ Mission will be very sensitive to the astrometric
 wobble produced by a long-period exoplanet \citep{Perryman:2014}.
@@
 \end{eqnarray}
+% obviously fix to your notation!
 where $a$ is the semi-major axis, $D$ is the distance from the observer to the
@@
 in the final \gaia\ data depends on this precision, the number of crossings of
-the star through the \gaia\ field-of-view, and details of how the projected
+the star through the \gaia\ focal plane, and details of how the projected
 orbit is sampled by the time history of the focal-plane crossings.
@@
 These planets will not be detectable or measurable in the \gaia\ data under
-any circumstances.
+any circumstances, but it may be possible to identify which candidates are 
+false-alarms caused by eclipsing binaries.
 However, similar planets around closer stars \emph{will} be detectable with
@@
 planet's orbital period.
-The constraint on the period is also informed by the simplifying assumption
-that no other transit could occur during the baseline of \kepler\ observations
-of the target.
-Simulations of the false positive population~--~lone primary or secondary
-eclipses of binary systems or background eclipsing binaries~--~suggest that 13
-of these candidates have high probability of being planetary in nature.
+Simulations of the false positive population~--~lone primary or secondary eclipses of
+binary systems or background eclipsing binaries~--~suggest that 13 of these
+candidates have high probability of being planetary in nature.
 
@@
 
+% \dfmtodo{More words here about comparison and interpretation.}
+
+These long-period exoplanet candidates are potentially interesting candidates
+for follow-up observations.
 Using a probabilistic mass--radius relationship, we predict the masses of our
@@
 
-Any detailed analysis of individual systems detected with only a single
-transit requires follow-up observations to convincingly rule out false
-positive scenarios and to better characterize the stellar host parameters
-(with, for example, parallax measurements from \gaia).
-The conclusions of this work~--~and all other occurrence rate results based on
-\kepler\ data~--~are conditioned on the assumption that the stellar
-characterization of the target sample is systematic and un-biased.
-The main population-level results should be fairly insensitive systematic
-issues with the sample but a rigorous analysis of these effects will be
-required to come to more detailed conclusions about this population of
-long-period transiting planets.
-
 Our method of transit discovery is especially relevant for future photometric
@@
 prioritize follow-up, and study their population.
+
+Follow-up observations would be fruitful in confirming the false-alarm
+rates that we have estimated by further demonstrating that these planet
+candidates are non-stellar.  Better characterization of the host stars with,
+say, parallax measurements using \gaia would help further refine the
+properties of their transiting planets.
 
@@
 
-% \acknowledgments
-\vspace{1.5em}
+\acknowledgments
 It is a pleasure to thank
@@
 So Hattori,
-Heather Knutson,
 Hans-Walter Rix,
@@
 Angie Wolfgang
-for helpful discussions and contributions.
+for helpful contributions to the ideas and code presented here.
 

### 2016-07-27 document/ms.tex

--- 2016-07-27 document/ms.tex
@@
 
-To measure the completeness of search procedure described in \sect{search}, we
+To measure the completeness of the search procedure described in \sect{search}, we
 exploit the fact that transit signals are sparse and rare.

### 2016-07-27 document/ms.tex
whitespace
a few typos

@@
 However, transit surveys like \kepler\ are most sensitive to planets with
-orbital periods shorter than a few years, which is shorter than the orbital periods of
-Jupiter and Saturn, which dominate the dynamics of our Solar System.
+orbital periods much shorter than the orbital periods of Jupiter and Saturn,
+the most massive planets in our Solar System.
 To address this deficiency, we perform a fully automated search for
@@
 Based on these results, we measure the average occurrence rate of exoplanets
-smaller than Jupiter with orbital periods longer than two years to be
+smaller than Jupiter with orbital periods in the range 2--25~years to be
 $2.0\pm0.7$ planets per Sun-like star.
@@
 Recent work has yielded discoveries of long-period transiting planets with
-only one or two transits identified in archival \kepler\ and \KT\ light curves
-by visual inspection \citep{Wang:2013, Kipping:2014a, Osborn:2016,
-Kipping:2016, Uehara:2016, Wang:2015}.  Detection via visual inspection requires
-a high signal-to-noise for transit events to be seen by eye.
+only one or two high signal-to-noise transits identified in archival \kepler\
+and \KT\ light curves by visual inspection \citep{Wang:2013, Kipping:2014a,
+Wang:2015, Osborn:2016, Kipping:2016, Uehara:2016}.
 These discoveries have already yielded some tantalizing insight into the
-population of long-period transiting planets.  However, as these previous results
+population of long-period transiting planets but, since these previous results
 rely on human interaction, it is prohibitively expensive to reliably measure
@@
 Using a probabilistic mass--radius relationship, we predict the masses of our
-candidates and report predictions for the radial velocity amplitudes.
+candidates and report predictions for the radial velocity semi-amplitudes.
 Unfortunately, since the target stars are faint and the amplitudes are small,

### 2016-07-27 document/ms.tex
final tdm edits

@@
 does transit a companion star, then the companion star must be fainter, and hence
-denser, causing the period estimate to be underestimated.  If the planet transits
+denser, causing the period to be underestimated.  If the planet transits
 a background star, it is more likely to be a giant star due to Malmquist bias,
@@
 work, we use git commit \textsf{e4f54288}.}, which
-we developed for this purpose and utilizes the \project{isochrones}
-package \citep{Morton:2015} for simulations of stellar populations.
+we developed for this purpose and utilizes the \project{isochrones}, \project{vespa},
+and \project{batman} packages \citep{Morton:2015, Morton:2015b, Kreidberg:2015}
+ for simulations of stellar populations and their eclipses.
 
@@
 Recently, \citet{Bryan:2016} studied the frequency of long-period giant
-planets in systems with inner hot-Jupiters based on long-baseline radial
+planets in systems with inner hot Jupiters based on long-baseline radial
 velocity monitoring of these systems \citep{Knutson:2014}.
@@
 This result is about a factor of two larger than our estimate
-(\eqalt{massocc}) once again suggesting that cold-Jupiters might
-preferentially occur in systems with inner planets.
+(\eqalt{massocc}) once again suggesting that cold Jupiters might
+preferentially occur in systems with inner planets---or that the 
+presence of cold Jupiters encourages the formation of hot Jupiters.
 
@@
 \software{%
+    \project{batman} \citep{Kreidberg:2015},
     \project{ceres} \citep{Agarwal:2016},
@@
 	\project{numpy} \citep{Van-Der-Walt:2011},
-	\project{scipy} \citep{Jones:2001}}.
+	\project{scipy} \citep{Jones:2001},
+  \project{vespa} \citep{Morton:2015b}}.
 

### 2016-07-27 document/ms.tex
tiny typographical Bringhurst-isms

@@
 that of a planet if the eclipse is grazing, or if the EB only comprises a small
-fraction of the total light in the photometric aperture---a so-called blended
+fraction of the total light in the photometric aperture~--~a so-called blended
 eclipsing binary (BEB).  Additionally, if a binary star has an eccentric
@@
 (\eqalt{massocc}) once again suggesting that cold Jupiters might
-preferentially occur in systems with inner planets---or that the 
+preferentially occur in systems with inner planets~--~or that the
 presence of cold Jupiters encourages the formation of hot Jupiters.

### 2016-09-19 document/ms.tex
damn
adding referee report and starting to respond

@@
 
+% Response
+\newcommand{\response}[1]{{\color{blue}#1}}
+
 % Helpers for this paper:
@@
 The population of long-period transiting exoplanets
-\vspace{-2.5\baselineskip}  % OMG AASTEX6 IS SO BROKEN
+\vspace{-2\baselineskip}  % OMG AASTEX6 IS SO BROKEN
 }
@@
 \citep{Winn:2010}
-\begin{eqnarray}
+\begin{eqnarray}\eqlabel{geom-comp}
 Q_{\mathrm{geom},k} (\params) &=& \frac{R_{\star,k} + R}{a_k}
@@
 All of these parameters are included in \params.
+
+\response{%
+In \eq{geom-comp}, the term $(R_{\star,k}+R)$ takes grazing transits into
+account.
+This might seem counter intuitive because, as part of the search procedure, we
+rejected candidates where the maximum likelihood model had a grazing transit.
+However, since the measurement of $Q_{\mathrm{det},k}$ included a cut on the
+measured impact parameter, we argue that the $Q_{\mathrm{det},k}$ already
+takes this effect into account.
+In other words, $Q_{\mathrm{det},k}$ quantifies the probability that a transit
+of a given shape will be detected \emph{given that it transits at all} and
+$Q_{\mathrm{geom},k}$~--~the way it is written in \eq{geom-comp}~--~is the
+marginalized probability that the system will transit given its physical
+parameters.
+}
 
@@
 
-We list the probabilities for each of our candidates to belong to each
-hypothesis in Table~\ref{tab:catalog}.  We find that the two deepest signals in our
+\response{We list the probability that each candidate is a planet in
+Table~\ref{tab:catalog}.} We find that the two deepest signals in our
 candidate catalog (9306307 and  10602068) are very likely to be EBs, though we

### 2016-09-19 document/ms.tex
Adding reference to Clanton 2016

@@
 
-\citet{Clanton:2014} studied the occurrence rate of long-period giant planets
-orbiting M dwarfs by combining results from radial velocity and microlensing
-surveys.
+\response{%
+\citet{Clanton:2016} studied the occurrence rate of long-period giant planets
+orbiting M dwarfs by combining results from radial velocity, microlensing, and
+direct imaging surveys.
 In the period and mass range $10^3-10^4\unit{days}$ and $10-10^4\,M_\oplus$,
@@
 \begin{eqnarray}
-\frac{\dd^2 N}{\dd\ln M\,\dd\ln P} &\lesssim& 0.013
-\end{eqnarray}
-per M dwarf.
+\frac{\dd^2 N}{\dd\ln M\,\dd\ln P} &=& 0.023
+\end{eqnarray}
+% \begin{eqnarray}
+% \frac{\dd^2 N}{\dd\ln M\,\dd\ln P} &\lesssim& 0.013
+% \end{eqnarray}
+per M dwarf with large uncertainty.}
 This result is slightly lower than our estimated rate for a similar range of

### 2016-09-19 document/ms.tex
comment about Clanton comparison between stellar types

@@
 masses and periods but around G/K dwarfs.
+\response{%
 This difference is consistent with previous results that cooler stars host
-fewer long-period giant planets \citep[for example][]{Cumming:2008}.
+fewer long-period giant planets \citep[for example][]{Cumming:2008,
+Clanton:2016}.
+}
 

### 2016-09-19 document/ms.tex
clearing up wording in conclusion for comparisons with ulens

--- 2016-09-19 document/ms.tex
@@
 masses and periods but around G/K dwarfs.
-This difference is consistent with previous results that cooler stars host
-fewer long-period giant planets \citep[for example][]{Cumming:2008}.
+\response{%
+This difference is consistent with previous observational and theoretical
+results that cooler stars host fewer long-period giant planets \citep[for
+example][]{Laughlin:2004, Cumming:2008, Clanton:2016}.
+}
 
@@
 $0.1-1\,R_\mathrm{J}$ to be \intocc\ planets per G/K dwarf.
-This result is qualitatively consistent with estimates from radial velocity,
-microlensing, and direct imaging surveys.
+\response{%
+This result is qualitatively consistent with estimates of the occurrence rate
+of long-period giant planets based on data from radial velocity and direct
+imaging surveys.
+The occurrence rate measured here~--~for Sun-like hosts~--~is higher than
+microlensing results for lower mass stars \citep{Clanton:2014, Clanton:2016}
+but this discrepancy is consistent with predictions from the core-accretion
+model \citep{Laughlin:2004}.
+}
 

### 2016-09-19 document/ms.tex
addressed referee point (2)

@@
 
+We note that in the above procedure we have not corrected our predictions
+for the fact that our search has explicitly excluded KOIs
+that host known \kepler\ EBs---if any of these excluded systems show fewer than 
+three eclipses and do not present both primary and secondary eclipses, then they 
+should also should perhaps count towards the number of EBs we should have 
+expected to find in this survey.  However, as the \kepler\ EB catalog does not provide information
+on whether both primary and secondary eclipses are detected, we neglect this correction.
+We note that this is a conservative decision, in the sense that accounting for the
+effect of excluded EBs on our predictions would only further decrease the FPP of 
+the planetary signals, as they would be even less likely to be caused by EBs.
+
 \begin{figure*}[htbp]~\\

### 2016-09-29 document/ms.tex
Adding references for #23

--- 2016-09-19 document/ms.tex
@@
 substantial technical challenge of implementing a search, as well as the
-subtleties involved in intepreting the results. For example,
+subtleties involved in interpreting the results. For example,
 false alarms in the form of uncorrected systematics in the data and background
@@
 A study of the population of long-period transiting planets complements other
-planet detection techniques, such as radial velocity \citep[for
-example][]{Cumming:2008, Knutson:2014, Bryan:2016}, microlensing \citep[for
-example][]{Gould:2010, Cassan:2012, Clanton:2014, Shvartzvald:2016}, and
-direct imaging \citep[for example][]{Bowler:2016}.
+planet detection and characterization techniques, such as radial velocity
+\citep[for example][]{Cumming:2008, Knutson:2014, Bryan:2016}, microlensing
+\citep[for example][]{Gould:2010, Cassan:2012, Clanton:2014,
+Shvartzvald:2016}, direct imaging \citep[for example][]{Bowler:2016}, and
+transmission spectroscopy \citep[for example][]{Dalba:2015}.
 The marriage of the radial velocity and transit techniques is particularly
@@
 
+\response{%
+We note that in the above procedure we have not corrected our predictions
+for the fact that our search has explicitly excluded KOIs
+that host known \kepler\ EBs---if any of these excluded systems show fewer than
+three eclipses and do not present both primary and secondary eclipses, then they
+should also should perhaps count towards the number of EBs we should have
+expected to find in this survey.  However, as the \kepler\ EB catalog does not provide information
+on whether both primary and secondary eclipses are detected, we neglect this correction.
+We note that this is a conservative decision, in the sense that accounting for the
+effect of excluded EBs on our predictions would only further decrease the FPP of
+the planetary signals, as they would be even less likely to be caused by EBs.
+}
+
 \begin{figure*}[htbp]~\\
@@
 any prediction of a subsequent transit time will be too uncertain to schedule
-targeted photometric follow-up.
+targeted photometric follow-up \citep{Beichman:2016, Dalba:2016}.
 Instead, follow-up using radial velocity and astrometry are more promising.

### 2016-09-29 document/ms.tex
comments about geometry

@@
 However, since the measurement of $Q_{\mathrm{det},k}$ included a cut on the
-measured impact parameter, we argue that the $Q_{\mathrm{det},k}$ already
-takes this effect into account.
+measured impact parameter, the $Q_{\mathrm{det},k}$ term already takes this
+effect into account.
 In other words, $Q_{\mathrm{det},k}$ quantifies the probability that a transit
@@
 Heather Knutson,
+Phil Muirhead,
+Darin Ragozzine,
 Hans-Walter Rix,

### 2016-09-29 document/ms.tex
finishing response to referee

@@
 The occurrence rate measured here~--~for Sun-like hosts~--~is higher than
-microlensing results for lower mass stars \citep{Clanton:2014, Clanton:2016}
-but this discrepancy is consistent with predictions from the core-accretion
-model \citep{Laughlin:2004}.
+microlensing results for generally lower mass stars \citep{Gaudi:2012,
+Clanton:2014, Clanton:2016} but this discrepancy is consistent with
+predictions from the core-accretion model \citep{Laughlin:2004}.
 }
@@
 for helpful discussions and contributions.
+We thank the anonymous referee for comments that improved the presentation and
+clarity of this manuscript.
 

### 2017-03-24 document/period_estimate_e0.jl
added documents, period estimate for e=0

@@ -1,0 +1,80 @@
+using CGS
+# Period estimates for Dan's sample assuming e=0:
+ncand = 16
+KIC = ["3218908","3239945","4754460","6551440","8410697","8426957","8505215","8738735","8800954","9306307","10187159","10287723","10321319","10602068","10842718","11709124"]
+b = [0.,0.207,0.893,0.75,0.,0.889,0.,0.,0.,0.64,0.,0.8,0.7,0.6027,0.,0.55]
+rho = [2.716,2.963,0.8725,1.053,1.201,1.145,3.139,1.388,2.502,1.383,1.553,2.64,1.414,1.762,1.177,1.377]
+srho1 = [1.432,0.4687,0.476,0.6332,0.6885,0.7186,0.6771,0.5794,0.4743,0.9142,1.3,0.2721,0.8579,1.09,0.6849,0.5512]
+srho2 = [0.3974,0.2218,0.7728,0.5275,0.7425,0.4541,0.2093,0.1768,0.3012,1.01,0.6905,0.4805,0.7137,0.3954,0.5948,0.465]
+tdur = [21.45,16.202,15.92,10.85,19.77,39.4,20.06,27.44,15.76,8.499,11.81,9.49,16.84,12.804,35.92,17.75]
+rad = [0.514,0.876,0.67,0.282,0.698,1.04,0.277,0.355,0.386,1.22,0.43,0.266,0.163,2.0,0.74,0.83]*RJUPITER/REARTH
+srad = [0.092,0.039,0.16,0.093,0.107,0.30,0.017,0.045,0.025,0.49,0.21,0.027,0.046,0.66,0.16,0.12]
+#rho  = 3/pi^2*(period*24.*3600.)/GRAV/(tdur*3600.)^3*(1.-b^2)^1.5
+fac = pi^2/3/24./3600.*3600.^3*GRAV
+p = fac.*rho.*tdur.^3./(1-b.^2).^1.5
+p1 = p.*(1.-srho1./rho)
+p2 = p.*(1.+srho2./rho)
+p[2]=2.9328721*365.25
+p1[2]=(2.9328721-2.6e-6)*365.25
+p2[2]=(2.9328721+2.6e-6)*365.25
+p[5]=2.8688097*365.25
+p1[5]=(2.8688097-5.3e-6)*365.25
+p2[5]=(2.8688097+5.4e-6)*365.25
+p[9]=1.9279957*365.25
[…]

### 2017-03-24 document/ms.tex

@@
 % Response
-\newcommand{\response}[1]{{\color{blue}#1}}
+\newcommand{\response}[1]{{#1}}
+% \newcommand{\response}[1]{{\color{blue}#1}}
 
@@
 integrated  Keplerian orbit with a quadratic limb darkening law for the
-central body\footnote{\url{https://github.com/dfm/transit}; in this work, we
-use git commit \textsf{482d99b}.}.
+central body \cite{Foreman-Mackey:2016a}.
 It has previously been established that the orbital period of a transiting
@@
 to predict how many we should expect.  To accomplish this, we use the Python
-package
-\exosyspop\footnote{\url{https://github.com/timothydmorton/exosyspop}; in this
-work, we use git commit \textsf{e4f54288}.}, which
+package \exosyspop\ \citep{Morton:2016a}, which
 we developed for this purpose and utilizes the \project{isochrones}, \project{vespa},
@@
     \project{emcee} \citep{Foreman-Mackey:2013},
+    \project{exosyspop} \citep{Morton:2016a},
     \project{george} \citep{Ambikasaran:2016},
@@
 	\project{scipy} \citep{Jones:2001},
+    \project{transit} \citep{Foreman-Mackey:2016a},
   \project{vespa} \citep{Morton:2015b}}.
